### 2019-09-04 Notes/Notes.tex
inital commit

\documentclass[]{article}

%opening
\title{Notes}

\begin{document}

\maketitle

\section{Main Idea}

Integer linear programming is pretty useful apparently. The problem boils down to solving a system of linear equations and inequalities. Just Google linear integer programming, and Wikipedia has a good example for the general type of problem that is being solved. The underlying problem is classically NP-hard, so there is an possibility to exponentially speed-up this entire set of problems with quantum annealing. The main idea here is to encode inequalities into a quantum annealer.

Quick overview, a quantum annealers solves a QUBO problem (which is basically Ising Model). The problem can be boiled down to the form $x Q x$ where $x$ is a vector of qubits (so they can only take values of 0 or 1 or some super-position). We have to ``program'' $Q$ to solve our problem.

Following https://arxiv.org/abs/1812.06917 we know 1) how to encode fixed-precision numbers into a set of qubits. 2) We also know how to encode higher order problems (\textit{e.g.} $J x^4 + Q x^2$). 3)  We also learned that in general, since QA can only solve for the global minimum, we must optimize the squared-residual of a set of equations / inequalities. Anyways, read the paper if you haven't already.

To encode an inequality of the form $A < y < B$ we can introduce an auxiliary qubit $y_a$ such that the logical qubit is $Y = (y, y_a)$. The inequality is then encoded as minimizing the following $C_1 Y^4 - C_2 Y^2 + C_3$ such that we get a mexican-hat potential. Basically this was inspired from spontaneous symmetry breaking. I'm sure this can be connected to solving scalar phi-4 theory if we reallllly want to go there. But tuning the $C$s will tune the radius of the degeneracy and therefore change the range of $A$ and $B$.  Also $C_3$ shifts the minimum to zero, which is useful if we want to keep the energy positive, and interpret it as the squared-residual. Travis suggested that this might be connected to ``slack variables'' (see https://arxiv.org/abs/1811.11538 that I haven't read yet).

I'm worried that $y_a$ has nonlinear dependence with $y$ as we walk along the degeneracy though, which in practice may be an issue. Though increasing the number of qubits used to represent a fixed-precision decimal solves this problem exponentially quickly.

\end{document}

### 2019-09-04 Notes/Notes.tex
update notes

@@
 
-To encode an inequality of the form $A < y < B$ we can introduce an auxiliary qubit $y_a$ such that the logical qubit is $Y = (y, y_a)$.
+To encode an inequality of the form $A < y < B$ we can introduce an auxiliary qubit $y_a$ such that the logical qubit is $Y = (y, y_a)$ (where $y$ and $y_a$ are logical qubits representing fixed-precision numbers encoded by $n$ qubits).
 The inequality is then encoded as minimizing the following $C_1 Y^4 - C_2 Y^2 + C_3$ such that we get a mexican-hat potential.

### 2019-11-06 Notes/Notes.tex
Added preliminary notes on how the python module will work later on

@@
 \documentclass[]{article}
+
+\usepackage{amsmath}
+\usepackage{bbm}
+
+\newcommand{\argmax}[1]{\text{arg}\hspace{-2pt}\max\limits_{#1}}
+\newcommand{\bvec}[1]{\boldsymbol{#1}}
+
+\author{}
 
@@
 
+\section{Implementation}
+
+So I have been following up on @CCChen's notes and added a bit software to it.
+
+It's is basically the same thing minor two differences.
+
+\subsection{Integer problem optimization}
+What we eventually want to solve is an inequality of the form
+\begin{equation}\label{max-x}
+	\vec x_0 = \argmax{\vec x} \left( \vec c \cdot \vec x\right) \, ,
+\end{equation}
+for
+\begin{align}\label{condition-x}
+	A \vec x - \vec b &\leq \vec 0 \, , &
+	A &\in \text{Mat}(\mathbbm R, (N_x, N_e)) \, , &
+	\vec b &\in \mathbbm{R}^{N_e} \, &
+	\vec c &\in \mathbbm{R}^{N_x} \, , &
+	\vec x &\in \mathbbm{N}^{N_x}\, ,
+\end{align}
+where the additional dimension $N_e$ is the number of inequalities we have.
+Note that the inequality in the above equation is almost completely sufficient to characterize all problems because, for example a $\geq$ in a certain row can be obtained by multiplying the row with minus one and a $<$ can be obtained by an infinitesimal shift in $\vec b$.
+Equalities are different, but, when we introduce the slack variable, we can also take care this.
+For example, we know that for
+\begin{equation}\label{slack-optimization}
+	p >  \max\limits_{\vec x}\left(\vec c \cdot \vec x\right) \, , \qquad
+	\vec x_0 = \argmax{\vec x} \left( \vec c \cdot \vec x - p f(\vec x) \right)
+\end{equation}
+for constrained $\vec x$ and
+\begin{align}
+	f(\vec x) &= \min\limits_{\vec s}\left[
+		\left(\tilde A \vec x - \vec{\tilde{b}} + D \vec s\right) \cdot \left(\tilde A \vec x - \vec{\tilde{b}} + D \vec s\right)
+	\right]
+	\, , \\
+	\vec s &\in \mathbbm{N}^{N_e} \, , \qquad
+	D \in \text{Mat}(\{0, 1\}, (N_e, N_e)) \, .
+\end{align}
+More specifically $D$ is diagonal and it's entries are either one or zero (they are zero when we have an equality instead of an inequality).
+The entries 
+\begin{align}
+	\tilde A = (10^{m} A) & \in \text{Mat}(\mathbbm Z, (N_x, N_e)) \, , &
+	\vec{\tilde{b}} &= (10^m \vec{b}) \in \mathbbm{Z}^{N_e}
+\end{align}
+are rescaled with a factor such that they are integer valued.
+This assumes that $A$ and $\vec b$ are given for finite precision.
+Because they are integer valued, one can find a vector $\vec s$, such that $\forall \vec x \, \exists \vec s \, : \, \tilde A \vec x - \vec{\tilde{b}} + D \vec s = 0$.
+Thus $f(\vec x) \geq 0$ and furthermore
+\begin{equation}
+	f(\vec x_s) = 0 \iff A \vec x - \vec{b} \leq 0 \, .
+\end{equation}
+From left to right is true because each component $s_i \geq 0$ thus $\tilde A \vec x - \vec{\tilde{b}}$ must be $\leq \vec 0$ and this is invariant under scaling with a positive number.
+From right to left is true because if $A \vec x - \vec b$, this is true for their integer version as well.
+And since $- \vec m = \tilde A \vec x - \vec{\tilde{b}} \leq \vec 0$ for a vector $\vec m \in \mathbbm{N}^{N_e}$, we can pick $\vec m = \vec s$.
+
+Therefore, if $p$ is sufficiently large we know that the \eqref{slack-optimization} is maximal if $f(\vec x) = 0$ and the maximum of \eqref{slack-optimization} is thus equal to $\max\limits_{\vec x}(\vec c \cdot \vec x)$ under the specified constraints.
+
+\subsection{Map to bits}
+Next we want to code up $\vec x$ and $\vec s$ as bit vectors, e.g.,
+\begin{equation}
+	q = \sum_{n=0}^{N_b-1} 2^n \psi_n^{(q)} \, , \qquad \psi_n^{(q)} \in \{ 0, 1\}\, .
+\end{equation}
+Note that we in principle could have different $N_b$ for $x$ and $s$---I will discuss the reasoning behind that later.
+
+With this definition, we can introduce a new basis and map between integers and bits such that
+\begin{align}
+	q &= \vec Q \cdot \bvec{\psi}^{(q)} \, , &
+	\bvec{\psi}^{(q)} &\in \{ 0, 1\}^{N_b} \,, &
+	\vec Q^T &= \left(1, 2, 2^2, \cdots,  2^{N_b -1} \right) \, .
+\end{align}
+
+With these definition we have that
+\begin{align}
+	\vec \xi 
+	&= 
+	\begin{pmatrix}
+		\vec x \\
+		\vec s 
+	\end{pmatrix}
+	= Q \bvec \psi^{\left( \vec \xi \right)} \, , &
+	Q 
+	&=
+	\begin{pmatrix}
+		\vec Q^T & \vec 0^T & \vec 0^T & \cdots & \vec 0^T \\
+		\vec 0^T & \vec Q^T & \vec 0^T & \cdots & \vec 0^T \\
+		\vdots   & \ddots   & \ddots   & \ddots & \vdots \\
+		\vec 0^T & \vec 0^T & \vec 0^T & \cdots & \vec Q^T
+	\end{pmatrix}\, .
+	\, , & 
+	\psi^{\left( \vec \xi \right)} & \in \left(\{0, 1\}^{N_b}\right)^{N_e + N_x} \, ,
+\end{align}
+in other words $Q$ is a $(N_e + N_x) \times N_b(N_e + N_x)$ matrix.
+
+\subsection{Integer problem optimization using bits}
+Now we can map \eqref{slack-optimization} to the new basis
+\begin{align}
+	\vec x_0 
+	&= \argmax{\vec x}
+	\left( \bvec \gamma \cdot \bvec \psi^{\left( \vec \xi \right)} - p \phi\left(\bvec \psi^{\left( \vec \xi \right)}\right)\right) \, , &
+	\bvec \gamma &= \begin{pmatrix}
+		\vec c \\ \vec 0
+	\end{pmatrix} \cdot Q \in \mathbbm{R}^{(N_x + N_e )N_b} \, , 
+\end{align}
+which is in principle independent of the $\vec s$ pars and
+\begin{align}\label{bit-penalty}
+	\phi\left(\bvec \psi^{\left( \vec \xi \right)}\right)
+	&=
+	\min\limits_{\vec s}\left[
+	\left(\tilde \alpha Q \bvec \psi^{\left( \vec \xi \right)} - \vec{\tilde{\beta}}\right) 
+		\cdot \left(\tilde \alpha Q \bvec \psi^{\left( \vec \xi \right)} - \vec{\tilde{\beta}}\right)\right]
+	\, , &
+	 \vec{\tilde{\beta}} &= \begin{pmatrix}\vec{\tilde{b}}\\\vec 0 \end{pmatrix}
+	\,,&
+	\tilde \alpha &= \begin{pmatrix}
+		\tilde A & 0 \\ 0  & D
+	\end{pmatrix} \, , &
+\end{align}
+where the above quantities are split up in $\vec x$ and $\vec s$ space.
+
+In the following context we use that the components of the bit vector are either one or zero and thus $\psi^{\left( \vec \xi \right)}_i = \psi^{\left( \vec \xi \right)}_i \psi^{\left( \vec \xi \right)}_i$.
+The argument of equation \eqref{bit-penalty} simplifies to
+\begin{equation}
+	\psi^{\left( \vec \xi \right)}_\nu
+	\left[
+		(\tilde \alpha Q)_{i\nu} (\tilde \alpha Q)_{i\mu}
+		-  \delta_{\nu\mu}\tilde{\beta}_i (\tilde \alpha Q)_{i\mu}
+		- \delta_{\nu\mu} (\tilde \alpha Q)_{i\nu} \tilde{\beta}_i
+	\right]
+	\psi^{\left( \vec \xi \right)}_\mu
+	+ \tilde{\beta}_i \tilde{\beta}_i \, .
+\end{equation}
+Because the we compute the location of the optimal value, we can neglect the constant shift $\tilde{b}_i \tilde{b}_i$.
+Furthermore, we can combine the search for optimal $\vec x$ and $\vec s$ by a search for optimal $\vec \xi$ and hence optional $\bvec \psi^{\left( \vec \xi \right)}$.
+This results in
+\begin{align}
+	\bvec \psi^{\left( \vec \xi \right)}_{0} 
+	&=
+	\argmax{\psi^{\left( \vec \xi \right)}}\left( 
+		\bvec \psi^{\left( \vec \xi \right)} \cdot \Omega \bvec \psi^{\left( \vec \xi \right)}
+	\right)
+	\, , &
+	\Omega_{\nu\mu}
+	&=
+	\delta_{\nu\mu} \gamma_i Q_{i\nu}
+	- \tilde \alpha_{ij} Q_{j\nu} \tilde \alpha_{ik} Q_{k\mu}
+	+ 2 \delta_{\nu\mu}\tilde{\beta}_i \tilde \alpha_{ij} Q_{j\mu}
+\end{align}
+
 \end{document}

### 2019-11-06 Notes/Notes.tex
Typo fix
Improved notation

@@
 \usepackage{bbm}
+\usepackage{xcolor}
 
@@
 \newcommand{\bvec}[1]{\boldsymbol{#1}}
+\newcommand{\assumption}[1]{{\color{red}#1}}
 
@@
 
-So I have been following up on @CCChen's notes and added a bit software to it.
+So I have been following up on @CCChen's notes and extended the software a bit.
+The software is a Python module which converts a set of inequalities to the matrix we want to have on the quantum computer.
+I was wondering about the details of the derivation and if there are assumptions which may have consequences for the parameter space.
+Assumptions are defined by constraints which potentially make our approach not true given only \eqref{max-x} and \eqref{condition-x}.
+I have highlighted assumptions with the \assumption{green text}.
 
-It's is basically the same thing minor two differences.
+A little bit different to @CCChen's, I have introduced a matrix $Q$ which maps bit vectors to integer vectors.
+This helps the software a bit to stay general---and me to mimic the physics I am used to.
+
+Let me know if you have any questions.
 
 \subsection{Integer problem optimization}
-What we eventually want to solve is an inequality of the form
+What we eventually want to solve a maximization problem
 \begin{equation}\label{max-x}
@@
 \end{equation}
-for
+where $\vec x_0$ is the $\vec x$ which maximizes the above gradient under a set of inequalities
 \begin{align}\label{condition-x}
@@
 	\vec c &\in \mathbbm{R}^{N_x} \, , &
-	\vec x &\in \mathbbm{N}^{N_x}\, ,
+	\vec x &\in \mathbbm{N}^{N_x}\, .
 \end{align}
-where the additional dimension $N_e$ is the number of inequalities we have.
-Note that the inequality in the above equation is almost completely sufficient to characterize all problems because, for example a $\geq$ in a certain row can be obtained by multiplying the row with minus one and a $<$ can be obtained by an infinitesimal shift in $\vec b$.
-Equalities are different, but, when we introduce the slack variable, we can also take care this.
-For example, we know that for
-\begin{equation}\label{slack-optimization}
-	p >  \max\limits_{\vec x}\left(\vec c \cdot \vec x\right) \, , \qquad
-	\vec x_0 = \argmax{\vec x} \left( \vec c \cdot \vec x - p f(\vec x) \right)
-\end{equation}
-for constrained $\vec x$ and
-\begin{align}
+In this definition, the set of natural numbers $\mathbbm{N}$ includes zero (but no negative numbers).
+The additional dimension $N_e$ is the number of inequalities we have.
+
+In principle, one could also have inequalities of the form $A_{ij} x_j - b_j \geq 0$ or any other relations.
+But equation \eqref{condition-x} completely sufficient to characterize all problems with, because, for example a $\geq$ in a certain row can be obtained by multiplying the row with $-1$ and a $<$ can be obtained by an infinitesimal shift in $\vec b$.
+Equalities are a little bit different, in principle they can be brought to this form by combining $A_{ij} x_j - b_j \geq 0$ with $A_{ij} x_j - b_j \leq 0$, but this introduces two constraints.
+
+When introducing the slack variable, we can summarize the constraints in a single equation
+\begin{align}\label{slack-optimization}
+	\vec x_0 &= \argmax{\vec x} \left( \vec c \cdot \vec x - p f(\vec x) \right) \, , \\
 	f(\vec x) &= \min\limits_{\vec s}\left[
 		\left(\tilde A \vec x - \vec{\tilde{b}} + D \vec s\right) \cdot \left(\tilde A \vec x - \vec{\tilde{b}} + D \vec s\right)
-	\right]
-	\, , \\
+	\right] \, , &
+	p &\gg \max\limits_{\vec x}\left(\vec c \cdot \vec x\right) \, .
+\end{align}
+The quantities introduced in this equation are defined by
+\begin{align}
 	\vec s &\in \mathbbm{N}^{N_e} \, , \qquad
@@
 \end{align}
-are rescaled with a factor such that they are integer valued.
-This assumes that $A$ and $\vec b$ are given for finite precision.
-Because they are integer valued, one can find a vector $\vec s$, such that $\forall \vec x \, \exists \vec s \, : \, \tilde A \vec x - \vec{\tilde{b}} + D \vec s = 0$.
+are rescaled with a factor $10^m$ such that all entries of $\tilde A_{ij}$ and $\tilde b_{i}$ are integer valued.
+\assumption{This assumes that $A$ and $\vec b$ are given for finite precision.}
+
+Note that \assumption{for this particular condition we need that $x$ is constrained} and in principle \assumption{$p > \max\limits_{\vec x}\left(\vec c \cdot \vec x\right)$} would be suffice.
+However, this would require solving the problem.
+
+\subsubsection{Proof}
+Because $\tilde A$ and $\vec{\tilde{b}}$ are integer valued, one can find a vector $\vec s$, such that 
+\begin{equation}
+	\forall \vec x \quad \exists \vec s \in \mathbbm{N}^{N_e} \, : \, \tilde A \vec x - \vec{\tilde{b}} + D \vec s = 0 \, .
+\end{equation}
 Thus $f(\vec x) \geq 0$ and furthermore
 \begin{equation}
-	f(\vec x_s) = 0 \iff A \vec x - \vec{b} \leq 0 \, .
+	f(\vec x_s) = 0 \iff A \vec x - \vec{b} \leq \vec 0 \, .
 \end{equation}
-From left to right is true because each component $s_i \geq 0$ thus $\tilde A \vec x - \vec{\tilde{b}}$ must be $\leq \vec 0$ and this is invariant under scaling with a positive number.
-From right to left is true because if $A \vec x - \vec b$, this is true for their integer version as well.
+From $f(\vec x_s) = 0 \Rightarrow A \vec x - \vec{b} \leq \vec 0$ is true because each component of $\vec s$ is $\geq 0$ and thus $\tilde A \vec x - \vec{\tilde{b}} \leq \vec 0$.
+This is invariant under scaling with $10^{-m}$.
+
+Also, $A \vec x - \vec{b} \leq \vec 0 \Rightarrow f(\vec x_s) =  0  $ is true because if $A \vec x - \vec b \leq 0 \Rightarrow \tilde A \vec x - \vec{\tilde{b}} \leq \vec 0$.
 And since $- \vec m = \tilde A \vec x - \vec{\tilde{b}} \leq \vec 0$ for a vector $\vec m \in \mathbbm{N}^{N_e}$, we can pick $\vec m = \vec s$.
 
-Therefore, if $p$ is sufficiently large we know that the \eqref{slack-optimization} is maximal if $f(\vec x) = 0$ and the maximum of \eqref{slack-optimization} is thus equal to $\max\limits_{\vec x}(\vec c \cdot \vec x)$ under the specified constraints.
+Therefore, if $p$ is sufficiently large we know that the \eqref{slack-optimization} is maximal if $f(\vec x) = 0$ and the maximum of \eqref{slack-optimization} is thus equal to $\max\limits_{\vec x}(\vec c \cdot \vec x)$ under the specified constraints at the same location $\vec x_0$.
 
@@
 \end{equation}
-Note that we in principle could have different $N_b$ for $x$ and $s$---I will discuss the reasoning behind that later.
+Here, \assumption{the number of bits reduces the available number space to finite numbers}.
+This could potentially mean, if $N_b$ for $\vec x$ is not large enough, we do not probe $\vec x _0$.
+Also if the constrained space needs be extensively probed, e.g., if the optimal value $\vec x_0$ is far away from the boundary, we might need large $N_b$ to have large $\vec s$.
+One may even think about having different numbers of bits for $\vec x$ and $\vec s$.
 
@@
 
+To separate spaces, if introduced the notation that
+\begin{itemize}
+	\item greek vectors like $\vec \xi$ denote combined $\vec x$ and $\vec s$ space,
+	\item specifically the greek letter $\psi = 0, 1$ denotes bits,
+	\item the bold face vectors like $\bvec \psi^{\left( \vec \xi \right)}$ denote vectors in the bit basis (which do not necessarily have to be $0,1$).
+\end{itemize}
+
 \subsection{Integer problem optimization using bits}
@@
 	\vec x_0 
-	&= \argmax{\vec x}
-	\left( \bvec \gamma \cdot \bvec \psi^{\left( \vec \xi \right)} - p \phi\left(\bvec \psi^{\left( \vec \xi \right)}\right)\right) \, , &
+	&= \argmax{\vec x}\left(\min\limits_{\vec s}
+	\left( \bvec \gamma \cdot \bvec \psi^{\left( \vec \xi \right)} - p \phi\left(\bvec \psi^{\left( \vec \xi \right)}\right)\right)\right) \, , &
 	\bvec \gamma &= \begin{pmatrix}
@@
 \end{align}
-which is in principle independent of the $\vec s$ pars and
+where I have pulled out the $\min$ over $\vec s$ which is irrelevant for the $\bvec \gamma$ dot product since the $s$-component vanishes.
+The constrained $f \mapsto \phi$ is now given by
 \begin{align}\label{bit-penalty}
@@
 	&=
-	\min\limits_{\vec s}\left[
-	\left(\tilde \alpha Q \bvec \psi^{\left( \vec \xi \right)} - \vec{\tilde{\beta}}\right) 
-		\cdot \left(\tilde \alpha Q \bvec \psi^{\left( \vec \xi \right)} - \vec{\tilde{\beta}}\right)\right]
-	\, , &
-	 \vec{\tilde{\beta}} &= \begin{pmatrix}\vec{\tilde{b}}\\\vec 0 \end{pmatrix}
-	\,,&
-	\tilde \alpha &= \begin{pmatrix}
-		\tilde A & 0 \\ 0  & D
-	\end{pmatrix} \, , &
+	\left[
+	\left(
+		\tilde{\alpha} Q \bvec \psi^{\left( \vec \xi \right)} - \vec{\tilde{b}}\right) 
+		\cdot \left({\tilde{\alpha}} Q \bvec \psi^{\left( \vec \xi \right)} - \vec{\tilde{b}}\right)\right]
+	\, , \\
+	{\tilde{\alpha}} &= \left(\tilde{A},  D \right) \in \text{Mat}(\mathbbm{Z}, (N_x + N_e, N_e))\, ,
 \end{align}
@@
 
-In the following context we use that the components of the bit vector are either one or zero and thus $\psi^{\left( \vec \xi \right)}_i = \psi^{\left( \vec \xi \right)}_i \psi^{\left( \vec \xi \right)}_i$.
+In the following context we use that the components of the bit vector are either one or zero and thus $\psi^{\left( \vec \xi \right)}_\nu = \psi^{\left( \vec \xi \right)}_\nu \psi^{\left( \vec \xi \right)}_\nu$.
+Also, to simplify notation, indices to bit-space vectors are given by $\mu, \nu$, indices to $(\vec x, \vec s)$-space vectors are given by $i, j, k$ and it is summed over repeated entries.
 The argument of equation \eqref{bit-penalty} simplifies to
 \begin{equation}
+	\phi\left(\bvec \psi^{\left( \vec \xi \right)}\right)
+	=
 	\psi^{\left( \vec \xi \right)}_\nu
@@
 	\right)
-	\, , &
+	\, , \qquad
+	\vec x_0 =  (\mathbbm 1, 0) Q \bvec \psi^{\left( \vec \xi \right)}_{0} 
+	\\
 	\Omega_{\nu\mu}
@@
 	\delta_{\nu\mu} \gamma_i Q_{i\nu}
-	- \tilde \alpha_{ij} Q_{j\nu} \tilde \alpha_{ik} Q_{k\mu}
-	+ 2 \delta_{\nu\mu}\tilde{\beta}_i \tilde \alpha_{ij} Q_{j\mu}
+	- p \tilde \alpha_{ij} Q_{j\nu} \tilde \alpha_{ik} Q_{k\mu}
+	+ 2 p \delta_{\nu\mu}\tilde{\beta}_i \tilde \alpha_{ij} Q_{j\mu}
 \end{align}

### 2019-11-06 qlp/eqn_converter.py
Started modularizing the python module

@@ -1,0 +1,120 @@
+"""Converter for linear inequalities to matrices describing the quantum problem
+"""
+from typing import List, Tuple, Dict
+
+from decimal import Decimal
+
+from numpy import array, ndarray, arange, zeros
+
+from sympy import symbols, Matrix, Symbol
+from sympy.matrices import zeros as ZeroMatrix
+from sympy.core import relational
+
+
+def eqns_to_matrix(
+    eqns: List[relational.Relational], dependents: List[Symbol]
+) -> Tuple[Matrix, Matrix, Matrix]:
+    """Converts list of relations to slack variable matrix and vector formalism.
+
+    The result relates to the original eqn such that ``m.deps + v + s = 0``
+
+    For example ``[a1 * x <= b1, a2 * x >= b2]`` becomes
+
+    Code:
+        m = | a1 |  and v = | b1 | s = | - s1 |
+            | a2 |          | b2 |     | + s2 |
+
+    Arguments:
+        eqns:
+            List of relational equations. LHS must be linear in dependents, RHS constant.
+        dependents:
+            List of dependent variables.
+
+
+    Returns:
+        m and v, here m is the Matrix and v the vector containing the slack variable
+
+    """
+    dependents = set(dependents)
+
+    mat_coeffs = set()
+    vec_coeffs = set()
+    for eqn in eqns:
+        mat_coeffs = mat_coeffs.union(eqn.lhs.free_symbols.difference(set(dependents)))
+        vec_coeffs = vec_coeffs.union(eqn.rhs.free_symbols.difference(set(dependents)))
+
+    n_deps = len(dependents)
+    n_eqns = len(eqns)
+
+    s_vars = symbols(f"s(1:{n_eqns+1})")
+
+    v = Matrix([[-eqn.rhs] for eqn in eqns])
+    s = Matrix(
+        [
+            [s if isinstance(eqn, relational.LessThan) else -s]
+            for s, eqn in zip(s_vars, eqns)
+        ]
+    )
+    m = ZeroMatrix(rows=n_eqns, cols=n_deps)
+    for ne, eqn in enumerate(eqns):
+        for nd, dep in enumerate(dependents):
+            m[ne, nd] = eqn.lhs.coeff(dep)
+
+    return m, v, s
+
+
+def rescale_expressions(expr: Symbol, subs: Dict[str, str]) -> Symbol:
+    """Rescales and substitutes all values.
+
+    The values are multiplied by 10**power such that all values are integers.
+
+    Arguments:
[…]

### 2019-11-06 setup.py
Added module install options

@@ -1,0 +1,31 @@
+# -*- coding: utf-8 -*-
+"""Setup file for qlp
+"""
+__author__ = "None"
+__version__ = "0.1.0"
+
+from os import path
+
+from setuptools import setup, find_packages
+
+CWD = path.abspath(path.dirname(__file__))
+
+with open(path.join(CWD, "README.md"), encoding="utf-8") as inp:
+    LONG_DESCRIPTION = inp.read()
+
+with open(path.join(CWD, "requirements.txt"), encoding="utf-8") as inp:
+    REQUIREMENTS = [el.strip() for el in inp.read().split(",")]
+
+setup(
+    name="qlp",
+    version=__version__,
+    description=None,
+    long_description=LONG_DESCRIPTION,
+    long_description_content_type="text/markdown",
+    url=None,
+    author=__author__,
+    author_email=None,
+    keywords=[],
+    packages=find_packages(exclude=["docs", "tests"]),
+    install_requires=REQUIREMENTS,
+)

### 2019-11-06 qlp/eqn_converter.py
Adjusted to notes

@@ -6,8 +6,9 @@ from decimal import Decimal
 
 from numpy import array, ndarray, arange, zeros
 
-from sympy import symbols, Matrix, Symbol
+from sympy import Matrix, Symbol
 from sympy.matrices import zeros as ZeroMatrix
+from sympy.matrices import diag
 from sympy.core import relational
 
 
@@ -16,13 +17,13 @@ def eqns_to_matrix(
 ) -> Tuple[Matrix, Matrix, Matrix]:
     """Converts list of relations to slack variable matrix and vector formalism.
 
-    The result relates to the original eqn such that ``m.deps + v + s = 0``
+    The result relates to the original eqn such that ``m.deps + b + c.s = 0``
 
-    For example ``[a1 * x <= b1, a2 * x >= b2]`` becomes
+    For example ``[a1 * x <= b1, Eq(a2 * x, b2)]`` becomes
 
     Code:
-        m = | a1 |  and v = | b1 | s = | - s1 |
-            | a2 |          | b2 |     | + s2 |
+        a = | a1 |  and b = | b1 | c = | +1    0 |
+            | a2 |          | b2 |     |  0    0 |
 
     Arguments:
         eqns:
@@ -46,21 +47,14 @@ def eqns_to_matrix(
     n_deps = len(dependents)
     n_eqns = len(eqns)
 
-    s_vars = symbols(f"s(1:{n_eqns+1})")
-
-    v = Matrix([[-eqn.rhs] for eqn in eqns])
-    s = Matrix(
-        [
-            [s if isinstance(eqn, relational.LessThan) else -s]
-            for s, eqn in zip(s_vars, eqns)
-        ]
-    )
+    b = Matrix([[-eqn.rhs] for eqn in eqns])
+    c = diag(*[1 if isinstance(eqn, relational.LessThan) else 0 for eqn in eqns])
     m = ZeroMatrix(rows=n_eqns, cols=n_deps)
     for ne, eqn in enumerate(eqns):
         for nd, dep in enumerate(dependents):
             m[ne, nd] = eqn.lhs.coeff(dep)
 
-    return m, v, s
+    return m, b, c
 
 
 def rescale_expressions(expr: Symbol, subs: Dict[str, str]) -> Symbol:

### 2019-11-15 qlp/eqn_converter.py
Start to migrate notebook

@@ -196,7 +196,9 @@ def generate_table(
     dependents: List[relational.Relational],
     n_bits: int,
 ) -> DataFrame:
-    """Evaluates the matrix equation for all allowed bit vectors in the matrix basis
+    """Evaluates the matrix equation for all allowed bit vectors in the matrix basis.
+
+    Table is sorted by the value column in descending order.
 
     Arguments:
         matrix: The matrix.

### 2019-11-15 qlp/example/__init__.py

@@ -1,3 +1,4 @@
+# pylint: disable=C0103
 """Helper function for plotting
 """
 from typing import List
@@ -11,15 +12,15 @@ import qlp.eqn_converter as qe
 DEPENDENTS = [S("x_0"), S("x_1")]
 
 
-def f(x1: float, x2: float) -> float:
+def f(x0: float, x1: float) -> float:
     r"""Hyperbole function
 
     Implements
     $$
-        f(x_1, x_2) = 8 -(x_1 - 2)^2 - (x_2 - 2)^2
+        f(x_0, x_1) = 8 -(x_0 - 2)^2 - (x_1 - 2)^2
     $$
     """
-    return 8 - (x1 - 2) ** 2 - (x2 - 2) ** 2
+    return 8 - (x0 - 2) ** 2 - (x1 - 2) ** 2
 
 
 def get_omega_0(n_bits: int, as_numeric: bool = False) -> Matrix:
@@ -27,19 +28,27 @@ def get_omega_0(n_bits: int, as_numeric: bool = False) -> Matrix:
 
     E.g.,
     $$
-        f(x_1, x_2) = \psi_\alpha M_{\alpha \beta} \psi_\beta
+        f(x_0, x_1) = \psi_\alpha M_{\alpha \beta} \psi_\beta
         \, , \qquad
         M_{\alpha \beta}
         =
+        - Q_{0\alpha}Q_{0\beta}
         - Q_{1\alpha}Q_{1\beta}
-        - Q_{2\alpha}Q_{2\beta}
+        + 4Q_{0\alpha}\delta_{\alpha\beta}
         + 4Q_{1\alpha}\delta_{\alpha\beta}
-        + 4Q_{2\alpha}\delta_{\alpha\beta}
     $$
-    where $\psi$ is a bit vector.
+    where $\psi$ is a bit vector and $Q$ is given by
+    $$
+    \begin{pmatrix}
+        x_0 \\ x_1
+    \end{pmatrix}
+    =
+    Q
+    \vec \psi \, ,
+    $$
 
     Arguments:
-        n_bits: Number of bits
+        n_bits: Number of bits.
         as_numeric: Return numpy array if True. Else sympy expression.
     """
     q = qe.get_bit_map(len(DEPENDENTS), n_bits)

### 2019-11-15 qlp/example/plotting.py

@@ -1,0 +1,31 @@
+"""Plotting setup for example problem
+"""
+import numpy as np
+import plotly.graph_objects as go
+
+from qlp.example import f
+
+LAYOUT = go.Layout(
+    paper_bgcolor="white", plot_bgcolor="white", height=600, width=600, showlegend=False
+)
+
+
+def _get_f_data(zmin: float = 6.0) -> go.Heatmap:
+    """Plots heatmap for f
+    """
+    zmin = 6.0
+
+    xx, yy = np.meshgrid(*[np.linspace(0, 4, 100)] * 2)
+    zz = f(xx, yy)
+    zz = np.where(zz < zmin, np.nan, zz)
+    return go.Heatmap(
+        x=np.linspace(0, 4, 100),
+        y=np.linspace(0, 4, 100),
+        z=zz,
+        colorscale="Blues",
+        zmin=zmin,
+        zsmooth="best",
+    )
+
+
+F_DATA = _get_f_data()

### 2019-11-16 qlp/checks.py
Polishing presentation

@@ -2,14 +2,9 @@
 """
 from typing import List, Tuple, Dict, Any
 
-from itertools import product
-
-from sympy import Matrix, Symbol
 from sympy.core.relational import Relational
 
 from pandas import DataFrame, Series
-
-import qlp.eqn_converter as qec
 
 
 def check_inequalities(
@@ -40,20 +35,21 @@ def run_checks(  # pylint: disable=C0103
 ) -> bool:
     """Runs the following checks on a constraints table
 
-    1. Checks if all shifted constrained are larger or equal to zero.
-    2. If all inequalities are true for shifted constrained == 0 parameters.
-    3. If any inequality is false for shifted constrained > 0 parameters.
+    1. Checks if all `shifted_value` are larger or equal to zero.
+    2. If all inequalities are true for `shifted_value` == 0 parameters.
+    3. If any inequality is false for `shifted_value` > 0 parameters.
 
     Raise:
         AssertionError error if not all checks are fulfilled
     """
-    if not all(df.shifted_constrained.unique() >= 0):
+    df = df.reset_index()
+    if not all(df.shifted_value.unique() >= 0):
         raise AssertionError(
             "Not all values of shifted constrained are larger or equal to zero."
         )
 
     if not (
-        df.query("shifted_constrained == 0")
+        df.query("shifted_value == 0")
         .apply(lambda row: check_inequalities(row, inequalities), axis=1,)
         .astype(bool)
         .all()
@@ -64,7 +60,7 @@ def run_checks(  # pylint: disable=C0103
         )
 
     if (
-        df.query("shifted_constrained > 0")
+        df.query("shifted_value > 0")
         .apply(lambda row: check_inequalities(row, inequalities), axis=1,)
         .astype(bool)
         .all()

### 2019-11-16 qlp/eqn_converter.py

@@ -244,7 +244,7 @@ def generate_constrained_table(
     q = get_bit_map(len(xi), n_bits)
     constrained_mat = get_constrained_matrix(q, alpha, beta)
 
-    table = generate_table(constrained_mat, xi, n_bits)
+    table = generate_table(constrained_mat, dependents, n_bits)
     table["shifted_value"] = table["value"] + (beta.T @ beta)[0]
 
     return table.sort_values("shifted_value", ascending=True)

### 2019-11-16 qlp/example/plotting.py

@@ -1,31 +1,96 @@
 """Plotting setup for example problem
 """
+from typing import List
 import numpy as np
+
 import plotly.graph_objects as go
 
-from qlp.example import f
+from sympy import solve
+from sympy.core import relational
+from sympy.utilities.lambdify import lambdify
+
+
+from qlp.example import f, DEPENDENTS
 
 LAYOUT = go.Layout(
-    paper_bgcolor="white", plot_bgcolor="white", height=600, width=600, showlegend=False
+    paper_bgcolor="white",
+    plot_bgcolor="white",
+    height=600,
+    width=600,
+    showlegend=False,
+    xaxis=dict(
+        gridwidth=1,
+        gridcolor="LightGray",
+        range=[0.0, 4.1],
+        tickmode="linear",
+        tick0=-1.0,
+        dtick=1.0,
+        showline=True,
+        linecolor="LightGray",
+        title="$x_0$",
+    ),
+    yaxis=dict(
+        gridwidth=1,
+        gridcolor="LightGray",
+        range=[0.0, 4.1],
+        tickmode="linear",
+        tick0=-1.0,
+        dtick=1.0,
+        showline=True,
+        linecolor="LightGray",
+        title="$x_1$",
+    ),
 )
+
+_RANGE = np.linspace(0, 4, 100)
+_XX, _YY = np.meshgrid(*[_RANGE] * 2)
+_ZZ = f(_XX, _YY)
 
 
 def _get_f_data(zmin: float = 6.0) -> go.Heatmap:
     """Plots heatmap for f
     """
-    zmin = 6.0
-
-    xx, yy = np.meshgrid(*[np.linspace(0, 4, 100)] * 2)
-    zz = f(xx, yy)
-    zz = np.where(zz < zmin, np.nan, zz)
-    return go.Heatmap(
-        x=np.linspace(0, 4, 100),
-        y=np.linspace(0, 4, 100),
+    zz = np.where(_ZZ < zmin, np.nan, _ZZ)
+    hist = go.Heatmap(
+        x=_RANGE,
+        y=_RANGE,
         z=zz,
         colorscale="Blues",
         zmin=zmin,
         zsmooth="best",
+        opacity=0.9,
     )
+    return hist
 
 
 F_DATA = _get_f_data()
+
+
+def get_constrained_data(inequalities: List[relational.Relational]):
+    """
+    """
+    x0, x1 = DEPENDENTS
+
+    fill_kwargs = dict(
[…]

### 2019-11-16 qlp/example/__init__.py
Fixed typos and updated doc

@@ -59,7 +59,15 @@ def get_omega_0(n_bits: int, as_numeric: bool = False) -> Matrix:
 def get_omega(
     inequalities: List[Relational], n_bits: int, p: int = 10, as_numeric: bool = False
 ) -> Matrix:
-    """
+    """Computes `omega_0 - p * constraint**2` in the bit basis with slack variables.
+
+    Calls `qlp.eqn_converter.constraints_to_matrix` to compute the constrained matrix.
+
+    Arguments:
+        inequalities: The list of inequalities.
+        n_bits: The number of bits to represent integers.
+        p: The penalty term. Must be larger than the maximal value of the opt function.
+        as_numeric: Use numpy instead of sympy.
     """
     n_vars = len(DEPENDENTS) + len(inequalities)
     q = qe.get_bit_map(n_vars=n_vars, n_bits=n_bits)

### 2019-11-16 qlp/example/plotting.py

@@ -67,7 +67,7 @@ F_DATA = _get_f_data()
 
 
 def get_constrained_data(inequalities: List[relational.Relational]):
-    """
+    """Plots shaded area for excluded regions.
     """
     x0, x1 = DEPENDENTS
 

### 2019-11-16 Notes/Notes.tex
Updated notes and edited notebook
Added description of example problem in the pdf

@@
 \usepackage{xcolor}
+\usepackage{graphicx}
+\graphicspath{ {./figs/} }
 
@@
 \newcommand{\assumption}[1]{{\color{red}#1}} 
+\usepackage{listings}
+\newcommand{\codeword}[1]{\texttt{\textcolor{blue}{\lstinline{#1}}}
+}
 
@@
 \begin{equation}
+	\label{eq:constraint-matrix}
 	\phi\left(\bvec \psi^{\left( \vec \xi \right)}\right)
@@
 		(\tilde \alpha Q)_{i\nu} (\tilde \alpha Q)_{i\mu}
-		-  \delta_{\nu\mu}\tilde{\beta}_i (\tilde \alpha Q)_{i\mu}
-		- \delta_{\nu\mu} (\tilde \alpha Q)_{i\nu} \tilde{\beta}_i
+		-  \delta_{\nu\mu}\tilde{b}_i (\tilde \alpha Q)_{i\mu}
+		- \delta_{\nu\mu} (\tilde \alpha Q)_{i\nu} \tilde{b}_i
 	\right]
 	\psi^{\left( \vec \xi \right)}_\mu
-	+ \tilde{\beta}_i \tilde{\beta}_i \, .
+	+ \tilde{b}_i \tilde{b}_i \, .
 \end{equation}
@@
 	- p \tilde \alpha_{ij} Q_{j\nu} \tilde \alpha_{ik} Q_{k\mu}
-	+ 2 p \delta_{\nu\mu}\tilde{\beta}_i \tilde \alpha_{ij} Q_{j\mu}
+	+ 2 p \delta_{\nu\mu}\tilde{b}_i \tilde \alpha_{ij} Q_{j\mu}
 \end{align}
 
+\section{Example}
+In this section we present the optimization of
+\begin{equation}
+	\label{eq:g}
+	g(x_0, x_1) = 8 -(x_0 - 2)^2 - (x_1 - 2)^2 \, ,
+\end{equation}
+under different constraints.
+
+This repository contains the module \codeword{qlp} which provides functionality to implement the problem for bit operations.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{contour-opt}
+	\caption{
+		\label{fig:g}
+		Contour plot of $g$ defined in eq.~\eqref{eq:g}.
+		Darker colors denote larger values, lighter colors denote smaller values.
+		Values below $6$ are displayed as white.
+	}
+\end{figure}
+
+In the bit basis, $f$ is implemented as
+\begin{equation}
+	M_{\alpha \beta}
+        =
+        - Q_{0\alpha}Q_{0\beta}
+        - Q_{1\alpha}Q_{1\beta}
+        + 4Q_{0\alpha}\delta_{\alpha\beta}
+        + 4Q_{1\alpha}\delta_{\alpha\beta}
+   \, , \qquad
+   g(x_0, x_1) = \psi_\alpha M_{\alpha \beta} \psi_\beta + \vec b^2\, .
+\end{equation}
+This matrix is obtained by running \codeword{qlp.example.get_omega_0}.
+
+We implement the following three constraints (see also fig. \ref{fig:constraints})
+\begin{equation}
+	\label{eq:constrained}
+	0
+	\leq
+	f(\vec x)
+	=
+	\begin{cases}
+		4 - x_0 - x_1 & (A) \\ 
+		6 - x_0 - 3 x_1 & (B) \\
+		3 - x_0 - x_1 & (C)
+	\end{cases}
+	\, .
+\end{equation}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.32\textwidth]{contour-constraint-1}
+	\includegraphics[width=0.32\textwidth]{contour-constraint-2}
+	\includegraphics[width=0.32\textwidth]{contour-constraint-3}
+	\caption{
+		\label{fig:constraints}
+		Contour plot of $g$ defined in eq.~\eqref{eq:g} with additional constraints (A), (B) and (C) defined in eq.~\eqref{eq:constrained}.
+		The shaded red area displays the excluded space.
+		Furthermore, $x_0, x_1 \geq 0$.
+		The green dots display the location of the maximal value under the constrained are obtained by running the \codeword{qlp} toy problem.
+		Thus (A) does not change the location of the maximum, (B) shifts it and (C) shifts it but is degenerate.
+	}
+\end{figure}
+The function \codeword{qlp.eqn_converter.constraints_to_matrix} converts a general list of inequalities to the matrix defined in eq.~\eqref{eq:constraint-matrix}.
+This matrix does not contain the constant term $\vec b^2$.
+Thus the vector-matrix-vector product can be negative and thus result in negative constraint values (increasing the total optimal maximization value).
+However, for all bit vectors fulfilling the constraints, this negative value is the same and therefore does not influence the location of the optimal value.
+To check this, we have implemented the methods \codeword{qlp.eqn_converter.generate_constrained_table}  (generating a table of all vector-matrix-vector operation results for all allowed bit vectors) and \codeword{qlp.checks.run_checks} to check the consistency of the generated tables.
+
+The full matrix adding including the constraints is obtained by running \codeword{qlp.example.get_omega}.
+Similar to the checks we run \codeword{qlp.eqn_converter.generate_table} to probe the full bit space and pick the maximal value (displayed in fig.~\ref{fig:constraints}).
+
+The example is run in the notebook \codeword{notebooks/example-problem.ipynb}.
+To use this notebook, you have to run \codeword{pip install [--user] -e .} in the repo root directory first.
+
 \end{document}

### 2019-11-16 Notes/Notes.tex
Fixed typos

@@
 
-In the bit basis, $f$ is implemented as
+In the bit basis, $g$ is implemented as
 \begin{equation}
@@
 		Furthermore, $x_0, x_1 \geq 0$.
-		The green dots display the location of the maximal value under the constrained are obtained by running the \codeword{qlp} toy problem.
-		Thus (A) does not change the location of the maximum, (B) shifts it and (C) shifts it but is degenerate.
+		The green dots display the location of the maximal value under the constraints.
+		These values are obtained by running the \codeword{qlp} example problem.
+		The constraint (A) does not change the location of the maximum, (B) shifts the maximum to a new value and (C) shifts the maximum and is degenerate.
 	}
@@
 This matrix does not contain the constant term $\vec b^2$.
-Thus the vector-matrix-vector product can be negative and thus result in negative constraint values (increasing the total optimal maximization value).
+Thus the vector-matrix-vector product can be negative and thus results in negative constraint values (increasing the total optimal maximization value).
 However, for all bit vectors fulfilling the constraints, this negative value is the same and therefore does not influence the location of the optimal value.
@@
 
-The full matrix adding including the constraints is obtained by running \codeword{qlp.example.get_omega}.
+The full matrix including the constraints is obtained by running \codeword{qlp.example.get_omega}~.
 Similar to the checks we run \codeword{qlp.eqn_converter.generate_table} to probe the full bit space and pick the maximal value (displayed in fig.~\ref{fig:constraints}).
 
-The example is run in the notebook \codeword{notebooks/example-problem.ipynb}.
+The example is presented in the notebook \codeword{notebooks/example-problem.ipynb}.
 To use this notebook, you have to run \codeword{pip install [--user] -e .} in the repo root directory first.

### 2019-11-17 Notes/Notes.tex
Corrected min to max in bit representation of maximization condition

@@
 	\vec x_0 
-	&= \argmax{\vec x}\left(\min\limits_{\vec s}
+	&= \argmax{\vec x}\left(\max\limits_{\vec s}
 	\left( \bvec \gamma \cdot \bvec \psi^{\left( \vec \xi \right)} - p \phi\left(\bvec \psi^{\left( \vec \xi \right)}\right)\right)\right) \, , &
@@
 \end{align}
-where I have pulled out the $\min$ over $\vec s$ which is irrelevant for the $\bvec \gamma$ dot product since the $s$-component vanishes.
+where I have pulled out the $\min$ over $\vec s$ (which becomes a $\max$ because of the minus sign) which is irrelevant for the $\bvec \gamma$ dot product since the $s$-component vanishes.
 The constrained $f \mapsto \phi$ is now given by

### 2020-01-22 qlp/mds/solver.py
Updated energy computation

@@ -38,7 +38,7 @@ def classical_search(
             raise KeyboardInterrupt("Too many iterations abort.")
 
     # Brute force iterate space
-    for vv in tqdm(product(*[(0, 1)] * qubo.shape[1])):
+    for vv in tqdm(list(product(*[(0, 1)] * qubo.shape[1]))):
         ee = (vv @ qubo @ vv).flatten()[0]
         energies.append(ee)
         vecs.append(vv)
@@ -49,9 +49,6 @@ def classical_search(
     solutions = [tuple(vv) for vv, ee in zip(vecs, energies) if ee == e_min]
 
     if n_nodes is not None:
-        # Compute energy for one of the solution vectors by only considering n_nodes
-        v0 = np.array([vv if n < n_nodes else 0 for n, vv in enumerate(solutions[0])])
-        e_min = (v0 @ qubo @ v0).flatten()[0]
         # Reduce solutions to n_nodes entries
         solutions = [sol[:n_nodes] for sol in solutions]
 

### 2020-01-22 qlp/mds/qubo.py
Plotted additional rows

@@ -129,7 +129,7 @@ def main():  # pylint: disable=R0914
     from qlp.mds.solver import classical_search
 
     n_nodes = 5
-    n_edges = 5
+    n_edges = 6
     n_edge_max = 3
 
     test_graph = generate_graph(n_nodes, n_edges, n_edge_max=n_edge_max)
@@ -144,11 +144,14 @@ def main():  # pylint: disable=R0914
     # Plotting
     n_sols = len(solutions)
     col_wrap = 4
-    n_rows = max(n_sols // col_wrap, 1)
+    n_rows = n_sols // col_wrap + 1
     n_cols = col_wrap if col_wrap < n_sols else n_sols
 
     fig, axs = plt.subplots(ncols=n_cols, nrows=n_rows)
+    for ax in axs.flatten():
+        ax.set_visible(False)
     for sol, ax in zip(solutions, axs.flatten()):
+        ax.set_visible(True)
         get_plot_mpl(test_graph, color_nodes=sol, ax=ax)
 
     fig.suptitle(rf"$\gamma(G) \leq {e_min}$")

### 2020-01-22 qlp/mds/qubo.py
Added constraint check and command line interface

@@ -124,13 +124,26 @@ def get_mds_qubo(graph: Set[Tuple[int]]) -> dok_matrix:
 def main():  # pylint: disable=R0914
     """Generates a random graph
     """
+    from argparse import ArgumentParser
     import matplotlib.pylab as plt
     from qlp.mds.graph_tools import generate_graph, get_plot_mpl
     from qlp.mds.solver import classical_search
 
-    n_nodes = 5
-    n_edges = 6
-    n_edge_max = 3
+    parser = ArgumentParser(
+        "Generate random graph,"
+        " compute QUBO of minimal dominating set problem"
+        " and plot minimum solutions."
+    )
+    parser.add_argument("-n", "--n-nodes", type=int, help="Number of nodes.", default=5)
+    parser.add_argument("-e", "--n-edges", type=int, help="Number of edges.", default=5)
+    parser.add_argument(
+        "-m", "--n-edge-max", type=int, help="Max number of edges per node.", default=3
+    )
+    args = parser.parse_args()
+
+    n_nodes = args.n_nodes
+    n_edges = args.n_edges
+    n_edge_max = args.n_edge_max
 
     test_graph = generate_graph(n_nodes, n_edges, n_edge_max=n_edge_max)
     qubo = get_mds_qubo(test_graph)
@@ -141,13 +154,22 @@ def main():  # pylint: disable=R0914
     ### The number of constraints.
     e_min += (n_nodes + 1) * n_nodes
 
+    ## Check if constrained is violated, e.g., slacks contribute to energy
+    if any([len(sol) != e_min for sol in solutions]):
+        raise ValueError(
+            "Constraint not fulfilled for graph:"
+            f"\n{test_graph}"
+            "\nand solutions:"
+            f"\n{solutions}"
+        )
+
     # Plotting
     n_sols = len(solutions)
     col_wrap = 4
     n_rows = n_sols // col_wrap + 1
     n_cols = col_wrap if col_wrap < n_sols else n_sols
 
-    fig, axs = plt.subplots(ncols=n_cols, nrows=n_rows)
+    fig, axs = plt.subplots(ncols=n_cols, nrows=n_rows, squeeze=False)
     for ax in axs.flatten():
         ax.set_visible(False)
     for sol, ax in zip(solutions, axs.flatten()):

### 2020-01-22 Notes/Notes.tex
Started to work on notes

@@
 
-\usepackage{amsmath}
+\usepackage{amsmath,amssymb}
 \usepackage{bbm}
@@
 
+\clearpage
+
+\section{Minimum Dominating Set Problem}
+We want to find a minimum dominating set $D_\text{min}$ for a given graph $G(V,E)$.
+A \textit{dominating~set} $D$ is a set of vertices $V$ such that all vertices in the graph which are not in $D$ are adjacent to at least one point in this set.
+In other words each vertex in this graph is either in the dominating set or in the neighborhood $\mathcal N_i$ of a vertex $i \in D$.
+When $x_i = 0, 1$ is a variable representing if vertex $i$ is in the dominating set ($x_i = 1$), this constrained can be written as $|V|$ (number of all vertices) inequalities
+\begin{equation}\label{eq:ms-constraint}
+	x_i + \sum_{j \in \mathcal N_i} x_j \geq 1 \, , \qquad x_i = 0, 1 \, , \qquad \forall_{i \in V} \, .
+\end{equation}
+
+A \textit{minimal~dominating~set} is a dominating set which cannot be reduced by taking out vertices---if you are able to remove a vertex of your dominating set and still have a dominating set, it was not minimal.
+
+Finally, a \textit{minimum~dominating~set} (note that \textbf{minimum} $\neq$  \textbf{minimal}) is the smallest minimal dominating set you can find.
+Thus a minimum~dominating~set is a minimal~dominating~set but not necessarily the other way around.
+Note that there can be more then just one minimum~dominating~set for a given graph.
+Thus, the integer linear programming representation of the problem is given by eq.~\eqref{eq:ms-constraint} and
+\begin{equation}\label{mds:min-con-classical}
+	\min_{i \in V} \sum_i x_i \, .
+\end{equation}
+
+To allow the implementation of inequalities on D-Wave, we first map eq.~\eqref{eq:ms-constraint} to it's slack variable representation
+\begin{equation}\label{mds:con-slack-classical}
+	x_i  - s_{i} - 1 + \sum_{j \in \mathcal{N}_i} x_j = 0 \, , \quad 0 \leq s_{i} \leq |\mathcal{N}_i| \, .
+\end{equation}
+The solution to the Minimum Dominating Set Problem (MDSP) is found by finding the optimal vector $\vec \psi = (\vec x, \vec s)^T$ such that
+\begin{equation}\label{mds:objective-function}
+	f(\vec x, \vec s)
+	=
+	\sum_{i\in V} x_i
+	+ p \sum_{i \in V} \left(x_i  - s_{i} - 1  + \sum_{j \in\mathcal{N}_i} x_j\right)^2
+	\, ,
+	\qquad
+	p \geq |V| + 1 \, ,
+\end{equation}
+is minimal.
+To guarantee that the global minimum solution causes the constraint to be zero, $p$ needs to be larger than the minimization condition eq.~\eqref{mds:min-con-classical}.
+In principal, $p = |V| + 1$ is generally sufficient, it might be that one has to optimize this parameter in order to simplify convergence on the D-Wave.
+
+The values of the vertex variables $x_i$ are already in a bit representation and thus can be directly mapped onto QUBO components.
+The slack variables can be integers and thus have to be mapped onto bits.
+To ensure that eq.~\eqref{mds:con-slack-classical} is fulfilled, we introduce the following mapping procedure:
+For a given slack variable $s_i$, we find the smallest integer $b_i$ such that $2^{b_i}$ is larger or equal to the number of neighbors of vertex $i$
+\begin{equation}
+	|\mathcal{N}_i| \leq 2^{b_i-1} = \max(s_i)
+	\quad \Rightarrow \quad 
+	s_i = \sum_{k=0}^{b_i-1} 2^k q_{ik}
+	\, , \qquad 
+	q_{ik} = 0, 1
+	\, \qquad
+	\forall_{i \in V}
+	\, .
+\end{equation}
+For this choice, the basis of the QUBO $Q$ can be written by
+\begin{align}\label{mds:qubo}
+	Q &= 
+	\begin{pmatrix}\Omega & 0 \\ 0 & 0 \end{pmatrix}
+	+ p
+	\begin{pmatrix}\alpha & \beta \\ 0 & \gamma \end{pmatrix}
+	\, , & 
+	f(\vec x, \vec s)
+	&=
+	\vec \psi \cdot Q \cdot \vec \psi - p |V|
+	\, . 
+\end{align}
+for the bit vector $\vec q$ which relates to $\vec s$ using the bitmap $\vec B$
+\begin{equation}
+	\vec \psi \to \begin{pmatrix}
+		\vec x \\ \vec q
+	\end{pmatrix}
+	\, , \qquad
+	\vec q = (q_{00}, q_{01}, \cdots q_{0 b_0}, q_{10}, q_{11}, \cdots )^T
+	\, , \qquad
+	\vec s = B \vec q
+	\, .
+\end{equation}
+The first matrix in eq.~\eqref{mds:qubo} represents the minimization condition eq.~\eqref{mds:min-con-classical} while the second matrix describes the constraint eq.~\eqref{eq:ms-constraint}.
+The derivation of the QUBO utilizes that components of the bit vector squared are equal to the linear component, $\psi_\nu^2 = \psi_\nu$, and thus the QUBO represents the original objective function $f$ modulo a known constant.
+The block matrices can be found by multiplying out eq.~\eqref{mds:objective-function} and identifying the linear and quadratic components
+\begin{align}
+	\vec x \cdot \Omega \cdot \vec x 
+	&=
+	\sum_{i \in V} x_i
+	\, , \\
+    \vec x \cdot \alpha \cdot \vec x
+    &= 
+    \sum_{i \in V} \left[
+    	x_i^2 + 2 x_i \sum_j x_j  - 2 x_i - 2 \sum_j x_j + \left(\sum_j x_j\right)^2
+	\right]
+    \, , \\
+    \vec s \cdot \beta \cdot \vec x
+    &=
+    \sum_{i \in V} \left[ - 2 x_i s_i - 2 s_i \sum_j x_j\right]
+    \, , \\
+    \vec s \cdot \gamma \cdot \vec s 
+    &= 
+    \sum_{i \in V} \left[s_i^2 + 2 s_i\right] \, .
+\end{align}
+Given the adjacency matrix $A$ (symmetric matrix representing the graph with and zero diagonal and entries being either one or zero), one finds
+\begin{align}
+	\Omega &= \mathbbm{1} \, ,
+    &
+    \alpha &= - \mathbbm{1} + 2 A - 2 \text{diag}(|A|) + A^2
+    \, , \\
+    \beta &= -2 (\mathbbm{1} + A) B
+    \, , &
+     \gamma &= B^T B + 2 \text{diag}(|B|)
+    \, .
+\end{align}
+
+\subsection{Remarks on Scaling}
+The QUBO $Q$ is block upper-triangular, $\gamma$ is block diagonal and $\alpha, \beta$ are relatively dense because of the neighbors-to-neighbors entries ($A^2$) and neighbors-to-slack-bits entries ($A B$).
+Assuming there is maximal number of edges per vertex which does not scale with the number of vertices $|V|$, the total scaling is
+\begin{equation}
+	\text{rank}(Q) \sim |V| \, ,
+\end{equation}
+if the maximal number of edges is in some way proportional to $|V|$ one finds
+\begin{equation}
+	\text{rank}(Q) \lesssim |V| \log(|V|) \, .
+\end{equation}
+
+\subsection{Examples}
+I have implemented a Python module which takes a graph (defined by a set of edges) as input, computes the matrices $A$ and $B$, and eventually computes the QUBO $Q$.
+Next, the module classically searches the full bit-space for small example graphs to verify the solutions returned by the algorithm make sense.
+Below you can find a few example plots.
+
+If you run `\texttt{python qlp/mds/qubo.py}'\footnote{You have to install the scripts by running `\texttt{python~-m~pip~install~.}' before.} from the repo root, you will generate a random graph, compute the minimum QUBO, find the global minimum solutions and visualize them.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\textwidth]{mds-sol-n5-s.png}
+	\caption{
+		\label{fig:mds-sol-1}
+	}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.6\textwidth]{mds-sol-n5.png}
+	\caption{
+		\label{fig:mds-sol-2}
+	}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\textwidth]{mds-sol-n6.png}
+	\caption{
+		\label{fig:mds-sol-3}
+	}
+\end{figure}
+
 \end{document}

### 2020-01-22 qlp/mds/qubo.py
Typo fixes

@@ -1,4 +1,4 @@
-"""Tools to generate a Minimal Dominating Set QUBO from a graph
+"""Tools to generate a Minimum Dominating Set QUBO from a graph
 """
 from typing import Set, Tuple, List
 from scipy.sparse import dok_matrix, bmat
@@ -73,7 +73,7 @@ def get_bitmap(n_neigbors: List[int]) -> dok_matrix:
 
 
 def get_mds_qubo(graph: Set[Tuple[int]]) -> dok_matrix:
-    """This routine computes minimal dominating set QUBO for a given graph.
+    """This routine computes Minimum Dominating Set QUBO for a given graph.
 
     It assumes the graph is connected and nodes are labeled from 0...N-1.
     Self loops are forbidden.
@@ -121,8 +121,11 @@ def get_mds_qubo(graph: Set[Tuple[int]]) -> dok_matrix:
     return bmat([[alpha, beta], [None, gamma]]).todok()
 
 
-def main():  # pylint: disable=R0914
+def main(col_wrap: int = 4):  # pylint: disable=R0914
     """Generates a random graph
+
+    Arguments:
+        col_wrap: Plot at most graphs `col_wrap` in one row.
     """
     from argparse import ArgumentParser
     import matplotlib.pylab as plt
@@ -131,7 +134,7 @@ def main():  # pylint: disable=R0914
 
     parser = ArgumentParser(
         "Generate random graph,"
-        " compute QUBO of minimal dominating set problem"
+        " compute QUBO of Minimum Dominating Set problem"
         " and plot minimum solutions."
     )
     parser.add_argument("-n", "--n-nodes", type=int, help="Number of nodes.", default=5)
@@ -165,8 +168,7 @@ def main():  # pylint: disable=R0914
 
     # Plotting
     n_sols = len(solutions)
-    col_wrap = 4
-    n_rows = n_sols // col_wrap + 1
+    n_rows = n_sols // col_wrap + (1 if n_sols % col_wrap != 0 else 0)
     n_cols = col_wrap if col_wrap < n_sols else n_sols
 
     fig, axs = plt.subplots(ncols=n_cols, nrows=n_rows, squeeze=False)

### 2020-01-22 Notes/Notes.tex
Updated notes

--- 2019-11-17 Notes/Notes.tex
@@
 
-\author{}
+\author{C. C. Chang, C. C. Chen, C. K\"orber, T. Humble, J. Ostrowski}
 
@@
 
+\section{Minimum Dominating Set Problem}
+We want to find a Minimum~Dominating~Set (MDS) for a given graph $G(V,E)$ (defined by it's vertices $V$ and edges $E$).
+
+\begin{itemize}
+\item A \textit{dominating~set} $D$ is a set of vertices $V$ such that all vertices in the graph which are not in $D$ are adjacent to at least one point in this set.
+In other words: each vertex $i \in V$ is either in the dominating set $i \in D$ or in the neighborhood of a vertex in the dominating set $i \in \mathcal N_j$ for $j \in D$ (see also eq.~\eqref{eq:ms-constraint}).
+
+\item A \textit{minimal~dominating~set} is a dominating set which cannot be reduced by taking out vertices---if you are able to remove a vertex from your dominating set and still have a dominating set, it was not minimal.
+
+\item Finally, a \textit{minimum~dominating~set} $D_\text{min}$ (note that minimum $\neq$  minimal) is the smallest minimal dominating set you can find.
+Thus a Minimum~Dominating~Set is a minimal~dominating~set but not necessarily the other way around.
+Note that there can be more then just one minimum~dominating~set for a given graph.
+
+\item The \textit{Dominating~Set~Problem} (DSP) asks whether the number of vertices in the the smallest dominating set $\gamma(G) \equiv |D_\text{min}|$ is smaller or equal to a given integer number $\gamma(G) \leq K$.
+If one was able to find a global MDS, one would solve this problem for a given graph.
+\end{itemize}
+
+The integer linear programming representation of the MDS problem is given by the minimization condition
+\begin{equation}\label{mds:min-con-classical}
+	\min_{i \in V}\left( \sum_i x_i \right)\, ,
+\end{equation}
+and the $|V|$ (number of all vertices) constraint conditions
+\begin{equation}\label{eq:ms-constraint}
+	x_i + \sum_{j \in \mathcal N_i} x_j \geq 1 \, , \qquad x_i \in \{ 0, 1\} \, , \qquad \forall_{i \in V} \, ,
+\end{equation}
+where $x_i$ represents if vertex $i$ is in the dominating set ($i\in D_\text{min} \Rightarrow x_i = 1$) and $\mathcal N_i$ is the neighborhood of vertex $i$ (not including $i$ itself).
+
+To allow the implementation of inequalities on D-Wave, we first map eq.~\eqref{eq:ms-constraint} to it's slack variable representation
+\begin{equation}\label{mds:con-slack-classical}
+	x_i  - s_{i} - 1 + \sum_{j \in \mathcal{N}_i} x_j = 0 \, , \quad 0 \leq s_{i} \leq |\mathcal{N}_i| \, .
+\end{equation}
+The solution to the DSP is found by finding the optimal vector $\vec \psi = (\vec x, \vec s)^T$ such that the objective function $f$ is minimal
+\begin{equation}\label{mds:objective-function}
+	f(\vec x, \vec s)
+	=
+	\sum_{i\in V} x_i
+	+ p \sum_{i \in V} \left(x_i  - s_{i} - 1  + \sum_{j \in\mathcal{N}_i} x_j\right)^2
+	\, ,
+	\qquad
+	p \geq |V| + 1 \, .
+\end{equation}
+To guarantee that the global minimum solution fulfills the constraints, $p$ needs to be larger than the minimization condition eq.~\eqref{mds:min-con-classical}.
+In principal, for any graph $p = |V| + 1$ is sufficient---nevertheless it might be that one has to optimize this parameter in order to simplify convergence on the D-Wave.
+
+The values of the vertex variables $x_i$ are already in a bit representation and thus can be directly mapped onto QUBO components.
+The slack variables can be integers and thus have to be mapped onto bits.
+To ensure that eq.~\eqref{mds:con-slack-classical} is fulfilled, we introduce the following mapping procedure:
+For a given slack variable $s_i$, we find the smallest integer $b_i$ such that $2^{b_i}$ is larger than the number of neighbors of vertex $i$
+\begin{equation}
+	|\mathcal{N}_i| \leq 2^{b_i} - 1 = \max(s_i)
+	\quad \Rightarrow \quad 
+	s_i = \sum_{k=0}^{b_i-1} 2^k q_{ik}
+	\, , \qquad 
+	q_{ik} = 0, 1
+	\, \qquad
+	\forall_{i \in V}
+	\, .
+\end{equation}
+For this choice, the objective function can be written in terms of a vector-matrix-vector product of QUBO $Q$ 
+\begin{align}\label{mds:qubo}
+	Q &= 
+	\begin{pmatrix}\Omega & 0 \\ 0 & 0 \end{pmatrix}
+	+ p
+	\begin{pmatrix}\alpha & \beta \\ 0 & \gamma \end{pmatrix}
+	\, , & 
+	f(\vec x, \vec s)
+	&=
+	\vec \psi \cdot Q \cdot \vec \psi + p |V|
+	\, . 
+\end{align}
+The bit vector $\vec q$ is related to the slack variable $\vec s$ by the bitmap $\vec B$
+\begin{equation}
+	\vec \psi \to \begin{pmatrix}
+		\vec x \\ \vec q
+	\end{pmatrix}
+	\, , \qquad
+	\vec q = (q_{00}, q_{01}, \cdots q_{0 b_0}, q_{10}, q_{11}, \cdots )^T
+	\, , \qquad
+	\vec s = B \vec q
+	\, .
+\end{equation}
+The first matrix in eq.~\eqref{mds:qubo} represents the minimization condition eq.~\eqref{mds:min-con-classical} while the second matrix describes the constraint eq.~\eqref{eq:ms-constraint}.
+The derivation of the QUBO utilizes that components of the bit vector squared are equal to the component, $\psi_\nu^2 = \psi_\nu$, and thus the quadratic QUBO element is able to represent the original objective function $f$ modulo a known constant.
+
+The block matrices are determined by the linear and quadratic components of eq.~\eqref{mds:objective-function}
+\begin{align}
+	\vec x \cdot \Omega \cdot \vec x 
+	&=
+	\sum_{i \in V} x_i
+	\, , \\
+    \vec x \cdot \alpha \cdot \vec x
+    &= 
+    \sum_{i \in V} \left[
+    	x_i^2 + 2 x_i \sum_j x_j  - 2 x_i - 2 \sum_j x_j + \left(\sum_j x_j\right)^2
+	\right]
+    \, , \\
+    \vec s \cdot \beta \cdot \vec x
+    &=
+    \sum_{i \in V} \left[ - 2 x_i s_i - 2 s_i \sum_j x_j\right]
+    \, , \\
+    \vec s \cdot \gamma \cdot \vec s 
+    &= 
+    \sum_{i \in V} \left[s_i^2 + 2 s_i\right] \, .
+\end{align}
+Given the adjacency matrix $A$\footnote{The adjacency matrix used in this context is defined as the symmetric matrix representing the graph with and zero diagonal entries.
+Other entries are either equal to one or zero.} and the slack-bitmap $B$, one finds
+\begin{align}
+	\Omega &= \mathbbm{1} \, ,
+    &
+    \alpha &= - \mathbbm{1} + 2 A - 2 \text{diag}(|A|) + A^2
+    \, , \\
+    \beta &= -2 (\mathbbm{1} + A) B
+    \, , &
+     \gamma &= B^T B + 2 \text{diag}(|B|)
+    \, .
+\end{align}
+The result of the matrix operation $|M|$ defines a vector given by the sum over the matrix columns $|M| = \sum_{ij} M_{ij} \vec e_j$.
+
+\subsection{Remarks on Scaling}
+The QUBO $Q$ is upper block triangular (does this word exist?), $\gamma$ is block diagonal and $\alpha, \beta$ are relatively dense because of the neighbors-to-neighbors entries ($A^2$) and neighbors-to-slack-bits entries ($A B$).
+Assuming there is maximal number of edges per vertex which does not scale with the number of vertices $|V|$, the total scaling is
+\begin{equation}
+	\text{rank}(Q) \sim |V| \, ,
+\end{equation}
+if the maximal number of edges is in some way proportional to $|V|$ one finds
+\begin{equation}
+	\text{rank}(Q) \lesssim |V| \log(|V|) \, .
+\end{equation}
+
+\subsection{Examples}
+I have implemented a Python module which takes a graph (defined by a set of edges) as input, computes the matrices $A$ and $B$, and eventually computes the QUBO $Q$.
+Next, the module classically searches the full bit-space for small example graphs to verify that the solutions returned by the algorithm make sense.
+You can find a few example plots in fig.~\ref{fig:mds-sol-1}.
+
+If you run `\texttt{python qlp/mds/qubo.py}'\footnote{You have to install the scripts by running `\texttt{python~-m~pip~install~.}' before you are able to run the code.} from the repo root, you will generate a random graph, compute the minimum QUBO, find the global minimum solutions and visualize them.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.64\textwidth]{mds-sol-n5-s.png}
+	\includegraphics[width=0.32\textwidth]{mds-sol-n5.png}
+	\includegraphics[width=0.49\textwidth]{mds-sol-n6.png}
+	\includegraphics[width=0.49\textwidth]{mds-sol-n7.png}
+	\caption{
+		\label{fig:mds-sol-1} Vertex representation for global minimum solution of $\vec \psi \cdot Q \cdot \vec \psi$ for random 5-, 6- and 7-vertex graphs.
+		Green vertices are included in the MDS.
+	}
+\end{figure}
+
 \end{document}

### 2020-02-06 paper/main.tex

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{color}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=blue,          % color of internal links
    citecolor=blue,        % color of links to bibliography
    filecolor=blue,      % color of file links
    urlcolor=blue           % color of external links
}

\title{Solutions to Integer Linear Programming from Quantum Annealing}

\author[1,*]{Chia~Cheng~Chang}
\author[2]{Chih-Chieh~Chen}
\author[3]{Christopher K\"orber}
\author[4]{Travis~Humble}
\author[5]{Jim~Ostrowski}

\affil[1]{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
\affil[1]{Department of Physics, University of California, Berkeley, California 94720, USA}
\affil[1]{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
\affil[2]{?}
\affil[3]{Department of Physics, University of California, Berkeley, California 94720, USA}
\affil[4]{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
\affil[4]{University of Tennessee}
\affil[*]{chiacheng.chang@riken.jp}

\begin{abstract}
\cite{Chang:2018uxx}
\end{abstract}

\begin{document}

\flushbottom
\maketitle

\noindent\textbf{INTRODUCTION.}

Motivate ILP and quantum annealing.

\noindent{\textit{\textbf{Integer Linear Programming.}}}

Problem definition and classical solutions.

\noindent{\textbf{RESULTS}}

\noindent\textit{\textbf{ILP Mapping to QUBO}}

Write down how the mapping is done.

\noindent\textit{\textbf{Application to Minimum Dominating Set}}

Write down mapping to QUBO

\noindent{\textbf{DISCUSSION}}

\noindent\textit{\textbf{ILP examples}}

Simple problems and scaling with problem size for single global solution.

- number of constraint equations (slack variables)
- range of integer values
- number of variables
- precision of problem (decimal places needed)

Problems with degenerate minima

- does D-Wave find them with expected distribution for very small systems?
- at what problem size does this break?

\noindent\textit{\textbf{Dominating Set}}

Demonstrate simple dominating set problem.

Study scaling with random graphs (but fixed number of vertices?)

\noindent\textbf{METHODS}

Might not be necessary to have this section.

\noindent{\textbf{DATA AVAILABILITY}

Link to GitHub.

\noindent{\textbf{ACKNOWLEDGMENTS}

We thank x, y, z...

\noindent{\textbf{AUTHOR CONTRIBUTIONS}}

...

\noindent{\textbf{ADDITIONAL INFORMATION}}

\textbf{Competing Interests:} The authors declare no competing interests.

\bibliography{qilp}

\end{document}

### 2020-02-07 paper/main.tex
kinda first draft

@@
 \usepackage{color}
+\usepackage{dsfont}
 
@@
 
-\title{Solutions to Integer Linear Programming from Quantum Annealing}
+\title{Solutions to Integer Programming from Quantum Annealing}
 
-\author[1,*]{Chia~Cheng~Chang}
-\author[2]{Chih-Chieh~Chen}
-\author[3]{Christopher K\"orber}
+\author[1,*]{Christopher K\"orber}
+\author[2]{Chia~Cheng~Chang}
+\author[3]{Chih-Chieh~Chen}
 \author[4]{Travis~Humble}
@@
 \affil[4]{University of Tennessee}
-\affil[*]{chiacheng.chang@riken.jp}
+\affil[*]{ckoerber@berkeley.edu}
 
@@
 
-\noindent\textbf{INTRODUCTION.}
+\section{INTRODUCTION}
+\label{sec:introduction}
 
-Motivate ILP and quantum annealing.
+Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints and is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and z~\cite{}.
+In general however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
+The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem can be obtained in polynomial time, the optimal integer solution in general must be found in the $2^n$ integer solutions which surround the real number solution.
+Due to the importance and difficulty, in this work we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.
 
-\noindent{\textit{\textbf{Integer Linear Programming.}}}
+Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{}.
+Through the adiabatic theorem of quantum mechanics, the annealer is prepared initially in a trivial ground state while the solution to ILP is encoded in the target Hamiltonian.
+Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems.
 
-Problem definition and classical solutions.
+Formally, ILP is defined as the optimization of a linear function
+\begin{align}
+f(x) = &\min(c_i x_i),\\
+\textrm{subject to} \quad & A_{ij}x_j +b_i \leq 0_i,\\
+& x_i \geq 0_i,\\
+& x_i \in \mathbb{Z},
+\end{align}
+where the inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
+\begin{align}
+f(x) = &\min(c_i x_i),\\
+\textrm{subject to} \quad & A_{ij}x_j + s_i + b_i = 0_i,\\
+& s_i \geq 0_i,\\
+& x_i \geq 0_i,\\
+& x_i \in \mathbb{Z}.
+\end{align}
 
-\noindent{\textbf{RESULTS}}
+Since quantum annealing solves the QUBO problem, we extend the proposed algorithm to solve integer quadratic optimization problems such that
+\begin{align}
+f(x) = \min(x_i d_{ij} x_j + c_i x_i)
+\end{align}
+without the introduction of auxiliary qubits.
 
-\noindent\textit{\textbf{ILP Mapping to QUBO}}
+{\color{red} Paragraph on how this is solved classically. Include strengths and drawbacks of classical solution.}
 
-Write down how the mapping is done.
+\section{RESULTS}
+\label{sec:results}
+We map integer variables $z_i$ to qubits under the following transformation~\cite{Chang:2018uoc}
+\begin{align}
+z_i = & \sum_{r=0}^{R_i-1} 2^r \psi_{ri}
+\label{eq:int_to_bin}
+\end{align}
+where $\psi \in \{0, 1\}$ while the number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
+The transformation can in general be express as a rectangular matrix.
+For example, a vector of two integer variables $z_0$ and $z_1$ represented by one and two qubits respectively is given as
+\begin{align}
+\begin{pmatrix}
+z_0\\
+z_1
+\end{pmatrix}
+= &
+\begin{pmatrix}
+2^0 & 0 & 0\\
+0 & 2^0 & 2^1
+\end{pmatrix}
+\begin{pmatrix}
+\psi_{00}\\
+\psi_{01}\\
+\psi_{11}
+\end{pmatrix}
+\equiv T^z \begin{pmatrix}
+\psi_{00}\\
+\psi_{01}\\
+\psi_{11}
+\end{pmatrix}
+\end{align}
+The transformation can be reduced to a tensor product if $R_i$ is a constant for all $i$ such that
+\begin{align}
+\mathcal{R} = & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},\\
+\mathcal{Z} = & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},\\
+|\mathds{1}| = & |\mathcal{Z}|,\\
+T^z = & \mathds{1}\otimes \mathcal{R}.
+\end{align}
 
-\noindent\textit{\textbf{Application to Minimum Dominating Set}}
+While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbb{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).
 
-Write down mapping to QUBO
+\subsection{Integer Programming Mapping to QUBO}
+\label{sec:results:ilp}
+The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
+\begin{align}
+\chi^2 = & \left[\Psi^x_{j^\prime} T^x_{j^\prime i}d_{ij} T^x_{jk}\Psi^x_k + c_i T^x_{ij} \Psi^x_j + p (A_{ij} T^x_{jk} \Psi^x_{k} + T^s_{ij} \Psi^s_j + b_i)^2 \right],\\
+\Psi = & \begin{pmatrix}
+\Psi^x\\
+\Psi^s
+\end{pmatrix},
+\end{align}
+where $p$ is the strength of the penalty factor which must be set large enough such that the constraints are satisfied under minimization.
+The objective function can be represented as a QUBO Hamiltonian
+\begin{align}
+E = &
+\begin{pmatrix}
+\Psi^x & \Psi^s
+\end{pmatrix}
+\begin{pmatrix}
+{T^{x}}^T Q_{00} T^x & {T^{x}}^T Q_{01} T^s\\
+{T^{s}}^T Q_{10} T^{x} & {T^{s}}^T Q_{11} T^s
+\end{pmatrix}
+\begin{pmatrix}
+\Psi^x\\ \Psi^s
+\end{pmatrix} + b^2,\\
+\equiv & \Psi^T Q \Psi + C,
+\end{align}
+where
+\begin{align}
+Q_{00} = & d + A^T A + \mathrm{Diag} \left(c + A^T b + b^T A\right),\\
+Q_{01} = & Q_{10}^T = A^T,\\
+Q_{11} = & \mathrm{Diag}\left(1 + b^T + b\right).
+\end{align}
+The function $\mathrm{Diag}(x) = \mathds{1}\circ(x\otimes\mathbf{1})$ embeds a vector $x$ into a diagonal matrix, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.
 
-\noindent{\textbf{DISCUSSION}}
+\subsection{Application to Minimum Dominating Set}
+\label{sec:results:mds}
 
-\noindent\textit{\textbf{ILP examples}}
+Given a graph $G(E,V)$ defined by the set of $V$ vertices and $E$ edges and a subset $D \subseteq V(G)$, if the nearest-neighbor vertices of $\mathit{N}(D) = V(G)$, then $D$ is a dominating set, where an example is given by Fig.~\ref{fig:dominating_sets}a.
+The set $D$ is a minimal dominating set if there is no proper subset of $D$ that is a dominating set, {\it{i.e.}}, the removal of any vertex in $D$ results in $N(D) \neq V(G)$.
+An example is given by Fig.~\ref{fig:dominating_sets}b.
+The domination number of $D$ is given by the cardinality of $|D| \equiv \overline{\overline{D}}$.
+The minimum dominating set is defined by $D$ with the smallest domination number.
+Fig.~\ref{fig:dominating_sets}c shows an example of the minimum dominating set of $G(V, E)$ and is different from the minimal dominating set.
+We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set in general can have a smaller domination number.
+As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a problem that is well studied for quantum annealers~\cite{}.
+
+\begin{figure*}
+	\centering
+	\begin{tabular}{p{0.3\textwidth}p{0.3\textwidth}p{0.3\textwidth}}
+	\includegraphics[width=0.20\textwidth]{./figures/subaru_ds.pdf}
+&
+	\includegraphics[width=0.20\textwidth]{./figures/subaru_mds4.pdf}
+&
+	\includegraphics[width=0.20\textwidth]{./figures/subaru_mds2.pdf}\\
+	\centering\bf{a} & \centering\bf{b} & \centering\bf{c}
+	\end{tabular}
+	\caption{Example of different dominating sets for the Pleiades constellation $G(V, E)$.
+Vertices in the dominating set $D$ are highlighted in blue.
+{\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 5$.
+{\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 4$.
+We note that $D$ is also the maximum independent set of $G$.
+{\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.}
+	\label{fig:dominating_sets}
+\end{figure*}
+
+The solution to the minimum independent set can be expressed as an integer optimization problem given by,
+\begin{align}
+f(x) = &\min(\sum_{v_i\in V} \psi_{v_i}),\\
+\textrm{subject to} \quad & \psi_{v_i} + \sum_{v_j \in \mathit{N}(v_i)} \psi_{v_j} \geq 1,\\
+& \psi_{v_i} \in \{0, 1\}.
+\end{align}
+The problem minimizes the number of vertices in $D$ with a binary variable $\psi$ encoded by a single qubit, subject to the constraint that at least one vertex in $\mathit{N}(v_i)$ is in $D$.
+We introduce slack variables to encode the inequality constraint such that
+\begin{align}
+f(x) = &\min(\sum_{v_i\in V} \psi_{v_i}),\\
+\textrm{subject to} \quad & \psi_{v_i} + s_{v_i} + J_{v_i v_j} \psi_{v_j} = 1,\\
+& \psi_{v_i} \in \{0, 1\},\\
+& 0 \leq s_{v_i} \leq |\mathrm{N}(v_i)|\\
+& s_{v_i} \in \mathbb{Z},
+\end{align}
+where the nearest-neighbor sum is expressed by $J$, the adjacency matrix for $G$.
+The algorithm uses $\overline{\overline{V}}$ qubits to encode $\overline{\overline{V}}$ vertices and $\sum_{v_i \in V} \log_2 \mathit(N(v_i))$ qubits to embed the slack variables.
+Therefore, the embedding at worse scales with $\overline{\overline{V}} \log_2 |\overline{\overline{V}}|$ qubits for fully connected graphs.
+
+\section{DISCUSSION}
+
+\subsection{ILP Examples}
 
@@
 
-\noindent\textit{\textbf{Dominating Set}}
+\subsection{Dominating Set}
 
@@
 
-\noindent\textbf{METHODS}
+\subsection{Total Domination with Quantum Annealing}
+
+Solve the total dominating set problem.
+
+This probably just involves making the inequality constraint > 1 instead of > 0.
+
+\section{METHODS}
 
@@
 
-\noindent{\textbf{DATA AVAILABILITY}
+\section{DATA AVAILABILITY}
 
@@
 
-\noindent{\textbf{ACKNOWLEDGMENTS}
+\section{ACKNOWLEDGEMENTS}
 
@@
 
-\noindent{\textbf{AUTHOR CONTRIBUTIONS}}
+\section{AUTHOR CONTRIBUTIONS}
 
@@
 
-\noindent{\textbf{ADDITIONAL INFORMATION}}
+\section{ADDITIONAL INFORMATION}
 

### 2020-02-07 qlp/checks.py

@@ -1,73 +1,0 @@
-"""Cross checks for integer map problems
-"""
-from typing import List, Tuple, Dict, Any
-
-from sympy.core.relational import Relational
-
-from pandas import DataFrame, Series
-
-
-def check_inequalities(
-    data: Tuple[Dict[Any, Any], Series], inequalities: List[Relational]
-) -> bool:
-    """Checks wether all inequalities are fulfilled by dependents.
-
-    Arguments:
-        data:
-            Dict or series containing key value pair for all dependents in all
-            inequalities. Must contain only those keys or keys which contain
-            `constrained`.
-        inequalities:
-            List of all inequalities.
-    """
-    if isinstance(data, Series):
-        data = data.to_dict()
-    dependents = [var for var in data if "constrained" not in str(var)]
-    return bool(
-        all(
-            [ineq.subs({dep: data[dep] for dep in dependents}) for ineq in inequalities]
-        )
-    )
-
-
-def run_checks(  # pylint: disable=C0103
-    df: DataFrame, inequalities: List[Relational]
-) -> bool:
-    """Runs the following checks on a constraints table
-
-    1. Checks if all `shifted_value` are larger or equal to zero.
-    2. If all inequalities are true for `shifted_value` == 0 parameters.
-    3. If any inequality is false for `shifted_value` > 0 parameters.
-
-    Raise:
-        AssertionError error if not all checks are fulfilled
-    """
-    df = df.reset_index()
-    if not all(df.shifted_value.unique() >= 0):
-        raise AssertionError(
-            "Not all values of shifted constrained are larger or equal to zero."
-        )
-
-    if not (
-        df.query("shifted_value == 0")
-        .apply(lambda row: check_inequalities(row, inequalities), axis=1,)
-        .astype(bool)
-        .all()
-    ):
-        raise AssertionError(
-            "Not all values where the shifted constraints are zero"
-            " fulfill all inequalities."
-        )
-
-    if (
-        df.query("shifted_value > 0")
-        .apply(lambda row: check_inequalities(row, inequalities), axis=1,)
-        .astype(bool)
-        .all()
-    ):
-        raise AssertionError(
-            "Not all values where the shifted constraints are larger than zero"
-            " do not fulfill all inequalities."
-        )
-
-    return True

### 2020-02-07 qlp/eqn_converter.py

@@ -1,250 +1,0 @@
-"""Converter for linear inequalities to matrices describing the quantum problem
-"""
-from typing import List, Tuple, Dict, Optional, Union
-
-from decimal import Decimal
-from itertools import product
-
-import numpy as np
-from pandas import DataFrame
-
-from sympy import Matrix, Symbol, S
-from sympy.matrices import zeros as ZeroMatrix
-from sympy.matrices import diag
-from sympy.core import relational
-
-
-def get_basis(
-    dependents: List[Symbol], n_constraints: int
-) -> Tuple[Matrix, np.ndarray]:
-    """Converts dependent variables and number of constraints to a joined problem vector.
-
-    Arguments:
-        dependents: List of dependent variables. Will conserve the order.
-        n_constraints: Number of inequalities constraining the problem.
-
-    Returns:
-        xi:
-            The joined vector of dependent and slack variables
-        xi_to_x:
-            A matrix which converts xi to an x vector.
-            The vector has the same size as xi but the slack variable components are
-            zero.
-
-    Example:
-        ```
-        xi, xi_to_x = get_integer_basis(dependents=[x0, x1], n_constraints=1)
-
-        xi == [x0, x1, s0]
-        xi_to_x@xi == [x0, x1, 0]
-        ```
-    """
-    xi = Matrix(
-        [dep for dep in dependents] + [S(f"s_{i}") for i in range(n_constraints)]
-    )
-    xi_to_x = np.diag(
-        ([1 for i in range(len(dependents))] + [0 for i in range(n_constraints)])
-    )
-
-    return xi, xi_to_x
-
-
-def constraints_to_matrix(
-    inequalities: List[relational.GreaterThan],
-    dependents: List[Symbol],
-    as_numeric: bool = False,
-) -> Tuple[Matrix, Matrix]:
-    """Converts list of linear inequalities to slack variable matrix-vector equations.
-
-    The result relates to the original eqn such that ``m@(deps, s) + b = 0``
-
-    Arguments:
-        inequalities:
-            List of relational equations. LHS must be linear in dependents, RHS constant.
-        dependents:
-            List of dependent variables.
-        as_numeric:
-            Convert sympy matrix to float if possible.
-
-    Returns:
-        m and v, here m is the Matrix and v the vector containing the slack variable
-
[…]

### 2020-02-07 qlp/example/__init__.py

@@ -1,80 +1,0 @@
-# pylint: disable=C0103
-"""Helper function for plotting
-"""
-from typing import List
-
-import numpy as np
-from sympy import Matrix, S
-from sympy.core.relational import Relational
-
-import qlp.eqn_converter as qe
-
-DEPENDENTS = [S("x_0"), S("x_1")]
-
-
-def f(x0: float, x1: float) -> float:
-    r"""Hyperbole function
-
-    Implements
-    $$
-        f(x_0, x_1) = 8 -(x_0 - 2)^2 - (x_1 - 2)^2
-    $$
-    """
-    return 8 - (x0 - 2) ** 2 - (x1 - 2) ** 2
-
-
-def get_omega_0(n_bits: int, as_numeric: bool = False) -> Matrix:
-    r"""Computes the matrix which represents $f$ as a bit matrix-vector operation
-
-    E.g.,
-    $$
-        f(x_0, x_1) = \psi_\alpha M_{\alpha \beta} \psi_\beta
-        \, , \qquad
-        M_{\alpha \beta}
-        =
-        - Q_{0\alpha}Q_{0\beta}
-        - Q_{1\alpha}Q_{1\beta}
-        + 4Q_{0\alpha}\delta_{\alpha\beta}
-        + 4Q_{1\alpha}\delta_{\alpha\beta}
-    $$
-    where $\psi$ is a bit vector and $Q$ is given by
-    $$
-    \begin{pmatrix}
-        x_0 \\ x_1
-    \end{pmatrix}
-    =
-    Q
-    \vec \psi \, ,
-    $$
-
-    Arguments:
-        n_bits: Number of bits.
-        as_numeric: Return numpy array if True. Else sympy expression.
-    """
-    q = qe.get_bit_map(len(DEPENDENTS), n_bits)
-    mat = -q.T @ q + 4 * np.diag(np.sum(q, axis=0))
-    return np.array(mat) if as_numeric else mat
-
-
-def get_omega(
-    inequalities: List[Relational], n_bits: int, p: int = 10, as_numeric: bool = False
-) -> Matrix:
-    """Computes `omega_0 - p * constraint**2` in the bit basis with slack variables.
-
-    Calls `qlp.eqn_converter.constraints_to_matrix` to compute the constrained matrix.
-
-    Arguments:
-        inequalities: The list of inequalities.
-        n_bits: The number of bits to represent integers.
[…]

### 2020-02-07 qlp/example/plotting.py

@@ -1,96 +1,0 @@
-"""Plotting setup for example problem
-"""
-from typing import List
-import numpy as np
-
-import plotly.graph_objects as go
-
-from sympy import solve
-from sympy.core import relational
-from sympy.utilities.lambdify import lambdify
-
-
-from qlp.example import f, DEPENDENTS
-
-LAYOUT = go.Layout(
-    paper_bgcolor="white",
-    plot_bgcolor="white",
-    height=600,
-    width=600,
-    showlegend=False,
-    xaxis=dict(
-        gridwidth=1,
-        gridcolor="LightGray",
-        range=[0.0, 4.1],
-        tickmode="linear",
-        tick0=-1.0,
-        dtick=1.0,
-        showline=True,
-        linecolor="LightGray",
-        title="$x_0$",
-    ),
-    yaxis=dict(
-        gridwidth=1,
-        gridcolor="LightGray",
-        range=[0.0, 4.1],
-        tickmode="linear",
-        tick0=-1.0,
-        dtick=1.0,
-        showline=True,
-        linecolor="LightGray",
-        title="$x_1$",
-    ),
-)
-
-_RANGE = np.linspace(0, 4, 100)
-_XX, _YY = np.meshgrid(*[_RANGE] * 2)
-_ZZ = f(_XX, _YY)
-
-
-def _get_f_data(zmin: float = 6.0) -> go.Heatmap:
-    """Plots heatmap for f
-    """
-    zz = np.where(_ZZ < zmin, np.nan, _ZZ)
-    hist = go.Heatmap(
-        x=_RANGE,
-        y=_RANGE,
-        z=zz,
-        colorscale="Blues",
-        zmin=zmin,
-        zsmooth="best",
-        opacity=0.9,
-    )
-    return hist
-
-
-F_DATA = _get_f_data()
-
-
-def get_constrained_data(inequalities: List[relational.Relational]):
-    """Plots shaded area for excluded regions.
-    """
-    x0, x1 = DEPENDENTS
-
-    fill_kwargs = dict(
-        mode="lines", fillcolor="rgba(255, 0, 0, 0.2)", line={"width": 0},
-    )
-
-    data = []
-    for ineq in inequalities:
-        y = solve(ineq.lhs, x1)[0]
-        func = lambdify(x0, y, "numpy")
-        if isinstance(ineq, relational.GreaterThan):
-            data.append(go.Scatter(x=_RANGE, y=func(_RANGE), **fill_kwargs))
-            data.append(
-                go.Scatter(
[…]

### 2020-02-07 qlp/mds/graph_tools.py

@@ -1,190 +1,0 @@
-"""Routines which are useful to create and plot graphs
-"""
-from typing import Set, Tuple, Optional, List
-
-from numpy import random as rand
-import matplotlib.pyplot as plt
-
-import networkx as nx
-
-
-def generate_graph(
-    n_nodes: int, n_edges: int, n_edge_max: int = 5, seed: Optional[int] = None
-) -> Set[Tuple[int]]:
-    """Creates random edges for graph.
-
-    Node labels are from 0 to n_nodes - 1
-
-    Arguments:
-        n_nodes: Number of nodes.
-        n_edges: Number of edges.
-        n_edge_max: Maximal number of edges for graph.
-        seed: Random seed to set before graph is generated.
-
-    Todo:
-        What about connected / unconnected graphs?
-        Am I creating the right graph?
-        Think about ill input conditions.
-    """
-    assert n_edge_max > 0
-    assert n_nodes * n_edge_max // 2 > n_edges
-
-    if seed:
-        rand.seed(42)
-
-    nodes = {n: 0 for n in range(n_nodes)}
-    edges = set()
-
-    while len(edges) < n_edges:
-        choices = [n for n, count in nodes.items() if count <= n_edge_max]
-        e1, e2 = (int(e) for e in rand.choice(choices, size=2, replace=False))
-        edge = (e2, e1) if e2 < e1 else (e1, e2)
-        if edge not in edges:
-            edges.add(edge)
-            nodes[e1] += 1
-            nodes[e2] += 2
-
-    return edges
-
-
-def get_plot(
-    graph: Set[Tuple[int]],
-    color_nodes: Optional[List[int]] = None,
-    show_plot: bool = False,
-    backend="mpl",
-    seed: int = 42,
-):
-    """Creates graph plot from edge set.
-
-    Arguments:
-        graph: The graph to plot.
-        color_nodes: Colors given nodes green, default is white.
-        show_plot: Wether or not the plot should be rendered.
-        backend: The plotting backend. Either "mpl" or "bokeh".
-    """
-    if backend == "mpl":
-        fig = get_plot_mpl(
-            graph, color_nodes=color_nodes, show_plot=show_plot, seed=seed
-        )
-    elif backend == "bokeh":
-        fig = get_plot_bokeh(graph, color_nodes=color_nodes, show_plot=show_plot)
-    else:
[…]

### 2020-02-07 qlp/mds/qubo.py

@@ -1,186 +1,0 @@
-"""Tools to generate a Minimum Dominating Set QUBO from a graph
-"""
-from typing import Set, Tuple, List
-from scipy.sparse import dok_matrix, bmat
-import numpy as np
-
-
-def get_adjacency(graph: Set[Tuple[int]]) -> dok_matrix:
-    """This routine computes the adjecency matrix for a given graph.
-
-    It assumes the graph is connected and nodes are labeled from 0...N-1.
-    Self loops are forbidden.
-    """
-    if not isinstance(graph, set):
-        raise TypeError("Graph must be a set of tuples")
-
-    nodes = set()
-    adj = dict()
-
-    for v1, v2 in graph:
-        if v1 == v2:
-            raise KeyError(f"Self loops are not allowed (v={v1}).")
-
-        nodes.add(v1)
-        nodes.add(v2)
-        adj[(v1, v2)] = 1
-
-    nodes = sorted(nodes)
-    n_nodes = len(nodes)
-
-    if nodes != list(range(n_nodes)):
-        raise KeyError("Nodes must be from 0 ... n_nodes")
-
-    adjacency = dok_matrix((n_nodes, n_nodes), dtype=int)
-    for (v1, v2), val in adj.items():
-        adjacency[(v1, v2)] = val
-        adjacency[(v2, v1)] = val
-
-    if not all([val == 1 for val in adjacency.values()]):
-        raise KeyError("Double entries in graph")
-
-    return adjacency
-
-
-def get_bitmap(n_neigbors: List[int]) -> dok_matrix:
-    r"""Computes the map of slack-bits to slack integers.
-
-    This matrix B maps the bit vector b to slack variables s.
-    Each s_i has max(s_i) >= N_i where N_i is the number of
-    neigbors of vertex i.
-    The bit vector b = (b_00, b_01, b_02, ... , b_11, b_12, ...)
-    with b_ij will be mapped onto s_iaccording to
-    s_i = sum_j 2**j b_ij.
-    Thus the size of the returned matrix scales as
-    ~ sum_i log2(N_i)
-
-    Arguments:
-        n_neigbors: The number of neighbors for each vertex.
-    """
-    n_nodes = len(n_neigbors)
-
-    # Figure out how many bits we need for each neighborhood
-    n_bits = np.floor(np.log2(n_neigbors) + 1).astype(int)
[…]

### 2020-02-07 qlp/mds/solver.py

@@ -1,60 +1,0 @@
-"""QUBO solver routines to obtain global optimal solution.
-"""
-from typing import List, Tuple, Union, Optional
-from itertools import product
-
-import numpy as np
-
-from tqdm import tqdm
-
-
-def classical_search(
-    qubo: "SparseMatrix", n_nodes: Optional[int] = None
-) -> Union[int, List[Tuple[int]]]:
-    """Classicaly searches minimal energy for all integer solutions.
-
-    Assumes that the first n_nodes entries correspond to sorted vertex numbers.
-
-    Arguments:
-        qubo: The QUBO to optimize.
-        n_nodes: If present, optimizes the spaces for the full qubo but only returns
-            solutions accounting for entries from zero to n_nodes (exclusive).
-            This means that the energy and slack contributions are excluced from the
-            presentation of the solution.
-
-    Returns:
-        e_min: The minimal energy.
-        solutions: A list of vertices (qubo entries) which are non-zero.
-    """
-    energies = []
-    vecs = []
-
-    n_iterations = 2 ** qubo.shape[1]
-    if n_iterations > 10 ** 5:
-        go_on = input(
-            f"This search will execute {n_iterations} iterations. Continue (y/n)?"
-        )
-        if go_on.lower() != "y":
-            raise KeyboardInterrupt("Too many iterations abort.")
-
-    # Brute force iterate space
-    for vv in tqdm(list(product(*[(0, 1)] * qubo.shape[1]))):
-        ee = (vv @ qubo @ vv).flatten()[0]
-        energies.append(ee)
-        vecs.append(vv)
-
-    # Find minimal energy
-    e_min = np.min(energies)
-    # And corresponding vectors
-    solutions = [tuple(vv) for vv, ee in zip(vecs, energies) if ee == e_min]
-
-    if n_nodes is not None:
-        # Reduce solutions to n_nodes entries
-        solutions = [sol[:n_nodes] for sol in solutions]
-
-    # Convert bit list to vertex numbers
-    solutions = [
-        tuple([n for n, vv in enumerate(sol[:n_nodes]) if vv == 1]) for sol in solutions
-    ]
-
-    return e_min, solutions

### 2020-02-08 paper/main.tex
first draft ish

@@
 \Psi^x\\ \Psi^s
-\end{pmatrix} + b^2,\\
+\end{pmatrix} + pb^2,\\
 \equiv & \Psi^T Q \Psi + C,
+\label{eq:matrix_form}
 \end{align}
@@
 \begin{align}
-Q_{00} = & d + A^T A + \mathrm{Diag} \left(c + A^T b + b^T A\right),\\
-Q_{01} = & Q_{10}^T = A^T,\\
-Q_{11} = & \mathrm{Diag}\left(1 + b^T + b\right).
+Q_{00} = & d + \mathrm{Diag}(c) + p \left[ A^T A + \mathrm{Diag} \left(A^T b + b^T A\right)\right],\\
+Q_{01} = & Q_{10}^T = pA^T,\\
+Q_{11} = & p\mathrm{Diag}\left(1 + b^T + b\right).
 \end{align}
@@
 
-\subsection{Application to Minimum Dominating Set}
+\subsection{Application to the Dominating Set Problem}
 \label{sec:results:mds}
@@
 
+\subsubsection{Minimum Dominating Set}
 The solution to the minimum independent set can be expressed as an integer optimization problem given by,
@@
 The problem minimizes the number of vertices in $D$ with a binary variable $\psi$ encoded by a single qubit, subject to the constraint that at least one vertex in $\mathit{N}(v_i)$ is in $D$.
-We introduce slack variables to encode the inequality constraint such that
+We introduce slack variables $s_{v_i} = T^s_{v_i v_j} \psi^s_{v_j}$ to encode the inequality constraint such that
 \begin{align}
 f(x) = &\min(\sum_{v_i\in V} \psi_{v_i}),\\
-\textrm{subject to} \quad & \psi_{v_i} + s_{v_i} + J_{v_i v_j} \psi_{v_j} = 1,\\
+\textrm{subject to} \quad & \psi_{v_i} + T^s_{v_i v_j} \psi^s_{v_j} + J_{v_i v_j} \psi_{v_j} = 1,\\
 & \psi_{v_i} \in \{0, 1\},\\
@@
 Therefore, the embedding at worse scales with $\overline{\overline{V}} \log_2 |\overline{\overline{V}}|$ qubits for fully connected graphs.
+
+The target Hamiltonian can be written in the convenient matrix form
+\begin{align}
+E = &
+\begin{pmatrix}
+\Psi^x & \Psi^s
+\end{pmatrix}
+\begin{pmatrix}
+1 + p\left[1+J^T J + 2(J+J^T)\right] &p(1+J^T)T^s\\
+p{T^s}^T(1+J)& p\left[{T^s}^T T^s + {T^s}^T + T^s\right]
+\end{pmatrix}
+\begin{pmatrix}
+\Psi^x\\ \Psi^s
+\end{pmatrix} + p.
+\label{eq:matrix_form}
+\end{align}
+
+\subsubsection{Total Dominating Set}
 

### 2020-02-08 qlp/checks.py

@@ -1,0 +1,73 @@
+"""Cross checks for integer map problems
+"""
+from typing import List, Tuple, Dict, Any
+
+from sympy.core.relational import Relational
+
+from pandas import DataFrame, Series
+
+
+def check_inequalities(
+    data: Tuple[Dict[Any, Any], Series], inequalities: List[Relational]
+) -> bool:
+    """Checks wether all inequalities are fulfilled by dependents.
+
+    Arguments:
+        data:
+            Dict or series containing key value pair for all dependents in all
+            inequalities. Must contain only those keys or keys which contain
+            `constrained`.
+        inequalities:
+            List of all inequalities.
+    """
+    if isinstance(data, Series):
+        data = data.to_dict()
+    dependents = [var for var in data if "constrained" not in str(var)]
+    return bool(
+        all(
+            [ineq.subs({dep: data[dep] for dep in dependents}) for ineq in inequalities]
+        )
+    )
+
+
+def run_checks(  # pylint: disable=C0103
+    df: DataFrame, inequalities: List[Relational]
+) -> bool:
+    """Runs the following checks on a constraints table
+
+    1. Checks if all `shifted_value` are larger or equal to zero.
+    2. If all inequalities are true for `shifted_value` == 0 parameters.
+    3. If any inequality is false for `shifted_value` > 0 parameters.
+
+    Raise:
+        AssertionError error if not all checks are fulfilled
+    """
+    df = df.reset_index()
+    if not all(df.shifted_value.unique() >= 0):
+        raise AssertionError(
+            "Not all values of shifted constrained are larger or equal to zero."
+        )
+
+    if not (
+        df.query("shifted_value == 0")
+        .apply(lambda row: check_inequalities(row, inequalities), axis=1,)
+        .astype(bool)
+        .all()
+    ):
+        raise AssertionError(
+            "Not all values where the shifted constraints are zero"
+            " fulfill all inequalities."
+        )
+
+    if (
+        df.query("shifted_value > 0")
+        .apply(lambda row: check_inequalities(row, inequalities), axis=1,)
+        .astype(bool)
+        .all()
+    ):
+        raise AssertionError(
+            "Not all values where the shifted constraints are larger than zero"
+            " do not fulfill all inequalities."
+        )
+
+    return True

### 2020-02-08 qlp/eqn_converter.py

@@ -1,0 +1,250 @@
+"""Converter for linear inequalities to matrices describing the quantum problem
+"""
+from typing import List, Tuple, Dict, Optional, Union
+
+from decimal import Decimal
+from itertools import product
+
+import numpy as np
+from pandas import DataFrame
+
+from sympy import Matrix, Symbol, S
+from sympy.matrices import zeros as ZeroMatrix
+from sympy.matrices import diag
+from sympy.core import relational
+
+
+def get_basis(
+    dependents: List[Symbol], n_constraints: int
+) -> Tuple[Matrix, np.ndarray]:
+    """Converts dependent variables and number of constraints to a joined problem vector.
+
+    Arguments:
+        dependents: List of dependent variables. Will conserve the order.
+        n_constraints: Number of inequalities constraining the problem.
+
+    Returns:
+        xi:
+            The joined vector of dependent and slack variables
+        xi_to_x:
+            A matrix which converts xi to an x vector.
+            The vector has the same size as xi but the slack variable components are
+            zero.
+
+    Example:
+        ```
+        xi, xi_to_x = get_integer_basis(dependents=[x0, x1], n_constraints=1)
+
+        xi == [x0, x1, s0]
+        xi_to_x@xi == [x0, x1, 0]
+        ```
+    """
+    xi = Matrix(
+        [dep for dep in dependents] + [S(f"s_{i}") for i in range(n_constraints)]
+    )
+    xi_to_x = np.diag(
+        ([1 for i in range(len(dependents))] + [0 for i in range(n_constraints)])
+    )
+
+    return xi, xi_to_x
+
+
+def constraints_to_matrix(
+    inequalities: List[relational.GreaterThan],
+    dependents: List[Symbol],
+    as_numeric: bool = False,
+) -> Tuple[Matrix, Matrix]:
+    """Converts list of linear inequalities to slack variable matrix-vector equations.
+
+    The result relates to the original eqn such that ``m@(deps, s) + b = 0``
+
+    Arguments:
+        inequalities:
+            List of relational equations. LHS must be linear in dependents, RHS constant.
+        dependents:
+            List of dependent variables.
+        as_numeric:
+            Convert sympy matrix to float if possible.
+
+    Returns:
+        m and v, here m is the Matrix and v the vector containing the slack variable
+
[…]

### 2020-02-08 qlp/example/__init__.py

@@ -1,0 +1,80 @@
+# pylint: disable=C0103
+"""Helper function for plotting
+"""
+from typing import List
+
+import numpy as np
+from sympy import Matrix, S
+from sympy.core.relational import Relational
+
+import qlp.eqn_converter as qe
+
+DEPENDENTS = [S("x_0"), S("x_1")]
+
+
+def f(x0: float, x1: float) -> float:
+    r"""Hyperbole function
+
+    Implements
+    $$
+        f(x_0, x_1) = 8 -(x_0 - 2)^2 - (x_1 - 2)^2
+    $$
+    """
+    return 8 - (x0 - 2) ** 2 - (x1 - 2) ** 2
+
+
+def get_omega_0(n_bits: int, as_numeric: bool = False) -> Matrix:
+    r"""Computes the matrix which represents $f$ as a bit matrix-vector operation
+
+    E.g.,
+    $$
+        f(x_0, x_1) = \psi_\alpha M_{\alpha \beta} \psi_\beta
+        \, , \qquad
+        M_{\alpha \beta}
+        =
+        - Q_{0\alpha}Q_{0\beta}
+        - Q_{1\alpha}Q_{1\beta}
+        + 4Q_{0\alpha}\delta_{\alpha\beta}
+        + 4Q_{1\alpha}\delta_{\alpha\beta}
+    $$
+    where $\psi$ is a bit vector and $Q$ is given by
+    $$
+    \begin{pmatrix}
+        x_0 \\ x_1
+    \end{pmatrix}
+    =
+    Q
+    \vec \psi \, ,
+    $$
+
+    Arguments:
+        n_bits: Number of bits.
+        as_numeric: Return numpy array if True. Else sympy expression.
+    """
+    q = qe.get_bit_map(len(DEPENDENTS), n_bits)
+    mat = -q.T @ q + 4 * np.diag(np.sum(q, axis=0))
+    return np.array(mat) if as_numeric else mat
+
+
+def get_omega(
+    inequalities: List[Relational], n_bits: int, p: int = 10, as_numeric: bool = False
+) -> Matrix:
+    """Computes `omega_0 - p * constraint**2` in the bit basis with slack variables.
+
+    Calls `qlp.eqn_converter.constraints_to_matrix` to compute the constrained matrix.
+
+    Arguments:
+        inequalities: The list of inequalities.
+        n_bits: The number of bits to represent integers.
[…]

### 2020-02-08 qlp/example/plotting.py

@@ -1,0 +1,96 @@
+"""Plotting setup for example problem
+"""
+from typing import List
+import numpy as np
+
+import plotly.graph_objects as go
+
+from sympy import solve
+from sympy.core import relational
+from sympy.utilities.lambdify import lambdify
+
+
+from qlp.example import f, DEPENDENTS
+
+LAYOUT = go.Layout(
+    paper_bgcolor="white",
+    plot_bgcolor="white",
+    height=600,
+    width=600,
+    showlegend=False,
+    xaxis=dict(
+        gridwidth=1,
+        gridcolor="LightGray",
+        range=[0.0, 4.1],
+        tickmode="linear",
+        tick0=-1.0,
+        dtick=1.0,
+        showline=True,
+        linecolor="LightGray",
+        title="$x_0$",
+    ),
+    yaxis=dict(
+        gridwidth=1,
+        gridcolor="LightGray",
+        range=[0.0, 4.1],
+        tickmode="linear",
+        tick0=-1.0,
+        dtick=1.0,
+        showline=True,
+        linecolor="LightGray",
+        title="$x_1$",
+    ),
+)
+
+_RANGE = np.linspace(0, 4, 100)
+_XX, _YY = np.meshgrid(*[_RANGE] * 2)
+_ZZ = f(_XX, _YY)
+
+
+def _get_f_data(zmin: float = 6.0) -> go.Heatmap:
+    """Plots heatmap for f
+    """
+    zz = np.where(_ZZ < zmin, np.nan, _ZZ)
+    hist = go.Heatmap(
+        x=_RANGE,
+        y=_RANGE,
+        z=zz,
+        colorscale="Blues",
+        zmin=zmin,
+        zsmooth="best",
+        opacity=0.9,
+    )
+    return hist
+
+
+F_DATA = _get_f_data()
+
+
+def get_constrained_data(inequalities: List[relational.Relational]):
+    """Plots shaded area for excluded regions.
+    """
+    x0, x1 = DEPENDENTS
+
+    fill_kwargs = dict(
+        mode="lines", fillcolor="rgba(255, 0, 0, 0.2)", line={"width": 0},
+    )
+
+    data = []
+    for ineq in inequalities:
+        y = solve(ineq.lhs, x1)[0]
+        func = lambdify(x0, y, "numpy")
+        if isinstance(ineq, relational.GreaterThan):
+            data.append(go.Scatter(x=_RANGE, y=func(_RANGE), **fill_kwargs))
+            data.append(
+                go.Scatter(
[…]

### 2020-02-08 qlp/mds/graph_tools.py

@@ -1,0 +1,190 @@
+"""Routines which are useful to create and plot graphs
+"""
+from typing import Set, Tuple, Optional, List
+
+from numpy import random as rand
+import matplotlib.pyplot as plt
+
+import networkx as nx
+
+
+def generate_graph(
+    n_nodes: int, n_edges: int, n_edge_max: int = 5, seed: Optional[int] = None
+) -> Set[Tuple[int]]:
+    """Creates random edges for graph.
+
+    Node labels are from 0 to n_nodes - 1
+
+    Arguments:
+        n_nodes: Number of nodes.
+        n_edges: Number of edges.
+        n_edge_max: Maximal number of edges for graph.
+        seed: Random seed to set before graph is generated.
+
+    Todo:
+        What about connected / unconnected graphs?
+        Am I creating the right graph?
+        Think about ill input conditions.
+    """
+    assert n_edge_max > 0
+    assert n_nodes * n_edge_max // 2 > n_edges
+
+    if seed:
+        rand.seed(42)
+
+    nodes = {n: 0 for n in range(n_nodes)}
+    edges = set()
+
+    while len(edges) < n_edges:
+        choices = [n for n, count in nodes.items() if count <= n_edge_max]
+        e1, e2 = (int(e) for e in rand.choice(choices, size=2, replace=False))
+        edge = (e2, e1) if e2 < e1 else (e1, e2)
+        if edge not in edges:
+            edges.add(edge)
+            nodes[e1] += 1
+            nodes[e2] += 2
+
+    return edges
+
+
+def get_plot(
+    graph: Set[Tuple[int]],
+    color_nodes: Optional[List[int]] = None,
+    show_plot: bool = False,
+    backend="mpl",
+    seed: int = 42,
+):
+    """Creates graph plot from edge set.
+
+    Arguments:
+        graph: The graph to plot.
+        color_nodes: Colors given nodes green, default is white.
+        show_plot: Wether or not the plot should be rendered.
+        backend: The plotting backend. Either "mpl" or "bokeh".
+    """
+    if backend == "mpl":
+        fig = get_plot_mpl(
+            graph, color_nodes=color_nodes, show_plot=show_plot, seed=seed
+        )
+    elif backend == "bokeh":
+        fig = get_plot_bokeh(graph, color_nodes=color_nodes, show_plot=show_plot)
+    else:
[…]

### 2020-02-08 qlp/mds/qubo.py

@@ -1,0 +1,186 @@
+"""Tools to generate a Minimum Dominating Set QUBO from a graph
+"""
+from typing import Set, Tuple, List
+from scipy.sparse import dok_matrix, bmat
+import numpy as np
+
+
+def get_adjacency(graph: Set[Tuple[int]]) -> dok_matrix:
+    """This routine computes the adjecency matrix for a given graph.
+
+    It assumes the graph is connected and nodes are labeled from 0...N-1.
+    Self loops are forbidden.
+    """
+    if not isinstance(graph, set):
+        raise TypeError("Graph must be a set of tuples")
+
+    nodes = set()
+    adj = dict()
+
+    for v1, v2 in graph:
+        if v1 == v2:
+            raise KeyError(f"Self loops are not allowed (v={v1}).")
+
+        nodes.add(v1)
+        nodes.add(v2)
+        adj[(v1, v2)] = 1
+
+    nodes = sorted(nodes)
+    n_nodes = len(nodes)
+
+    if nodes != list(range(n_nodes)):
+        raise KeyError("Nodes must be from 0 ... n_nodes")
+
+    adjacency = dok_matrix((n_nodes, n_nodes), dtype=int)
+    for (v1, v2), val in adj.items():
+        adjacency[(v1, v2)] = val
+        adjacency[(v2, v1)] = val
+
+    if not all([val == 1 for val in adjacency.values()]):
+        raise KeyError("Double entries in graph")
+
+    return adjacency
+
+
+def get_bitmap(n_neigbors: List[int]) -> dok_matrix:
+    r"""Computes the map of slack-bits to slack integers.
+
+    This matrix B maps the bit vector b to slack variables s.
+    Each s_i has max(s_i) >= N_i where N_i is the number of
+    neigbors of vertex i.
+    The bit vector b = (b_00, b_01, b_02, ... , b_11, b_12, ...)
+    with b_ij will be mapped onto s_iaccording to
+    s_i = sum_j 2**j b_ij.
+    Thus the size of the returned matrix scales as
+    ~ sum_i log2(N_i)
+
+    Arguments:
+        n_neigbors: The number of neighbors for each vertex.
+    """
+    n_nodes = len(n_neigbors)
+
+    # Figure out how many bits we need for each neighborhood
+    n_bits = np.floor(np.log2(n_neigbors) + 1).astype(int)
[…]

### 2020-02-08 qlp/mds/solver.py

@@ -1,0 +1,60 @@
+"""QUBO solver routines to obtain global optimal solution.
+"""
+from typing import List, Tuple, Union, Optional
+from itertools import product
+
+import numpy as np
+
+from tqdm import tqdm
+
+
+def classical_search(
+    qubo: "SparseMatrix", n_nodes: Optional[int] = None
+) -> Union[int, List[Tuple[int]]]:
+    """Classicaly searches minimal energy for all integer solutions.
+
+    Assumes that the first n_nodes entries correspond to sorted vertex numbers.
+
+    Arguments:
+        qubo: The QUBO to optimize.
+        n_nodes: If present, optimizes the spaces for the full qubo but only returns
+            solutions accounting for entries from zero to n_nodes (exclusive).
+            This means that the energy and slack contributions are excluced from the
+            presentation of the solution.
+
+    Returns:
+        e_min: The minimal energy.
+        solutions: A list of vertices (qubo entries) which are non-zero.
+    """
+    energies = []
+    vecs = []
+
+    n_iterations = 2 ** qubo.shape[1]
+    if n_iterations > 10 ** 5:
+        go_on = input(
+            f"This search will execute {n_iterations} iterations. Continue (y/n)?"
+        )
+        if go_on.lower() != "y":
+            raise KeyboardInterrupt("Too many iterations abort.")
+
+    # Brute force iterate space
+    for vv in tqdm(list(product(*[(0, 1)] * qubo.shape[1]))):
+        ee = (vv @ qubo @ vv).flatten()[0]
+        energies.append(ee)
+        vecs.append(vv)
+
+    # Find minimal energy
+    e_min = np.min(energies)
+    # And corresponding vectors
+    solutions = [tuple(vv) for vv, ee in zip(vecs, energies) if ee == e_min]
+
+    if n_nodes is not None:
+        # Reduce solutions to n_nodes entries
+        solutions = [sol[:n_nodes] for sol in solutions]
+
+    # Convert bit list to vertex numbers
+    solutions = [
+        tuple([n for n, vv in enumerate(sol[:n_nodes]) if vv == 1]) for sol in solutions
+    ]
+
+    return e_min, solutions

### 2020-02-08 paper/main.tex
Updated paper and checked QUBO

@@
 \usepackage{amsmath,amssymb}
-\usepackage{bm}
+\usepackage{bm,bbm}
 \usepackage{graphicx}
@@
 \begin{align}
-f(x) = &\min(c_i x_i),\\
-\textrm{subject to} \quad & A_{ij}x_j +b_i \leq 0_i,\\
-& x_i \geq 0_i,\\
-& x_i \in \mathbb{Z},
+f(x) = &\min\limits_{x}(c_i x_i),\\
+\textrm{subject to} \quad & A_{aj}x_i +b_a \leq 0 \\
+& x_i \geq 0,\\
+& x_i \in \mathbb{Z}
 \end{align}
-where the inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
+where $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
+The inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
 \begin{align}
 f(x) = &\min(c_i x_i),\\
-\textrm{subject to} \quad & A_{ij}x_j + s_i + b_i = 0_i,\\
-& s_i \geq 0_i,\\
-& x_i \geq 0_i,\\
+\textrm{subject to} \quad & A_{a i}x_i + s_a + b_a = 0,\\
+& s_a \geq 0,\\
+& s_a \in \mathbb{Z},\\
+& x_i \geq 0,\\
 & x_i \in \mathbb{Z}.
@@
 \begin{align}
-f(x) = \min(x_i d_{ij} x_j + c_i x_i)
+f(x) = \min\limits_{x}(x_i d_{ij} x_j + c_i x_i)
 \end{align}
@@
 \end{align}
-where $\psi \in \{0, 1\}$ while the number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
+where $\psi_{ri} \in \{0, 1\}$ while the number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
 The transformation can in general be express as a rectangular matrix.
@@
 \begin{align}
-\chi^2 = & \left[\Psi^x_{j^\prime} T^x_{j^\prime i}d_{ij} T^x_{jk}\Psi^x_k + c_i T^x_{ij} \Psi^x_j + p (A_{ij} T^x_{jk} \Psi^x_{k} + T^s_{ij} \Psi^s_j + b_i)^2 \right],\\
+\chi^2 = & \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu + p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
 \Psi = & \begin{pmatrix}
@@
 \begin{pmatrix}
-{T^{x}}^T Q_{00} T^x & {T^{x}}^T Q_{01} T^s\\
-{T^{s}}^T Q_{10} T^{x} & {T^{s}}^T Q_{11} T^s
+ Q_{00} & Q_{01}\\
+Q_{10} & {T^{s}}^T Q_{11} T^s
 \end{pmatrix}
@@
 \begin{align}
-Q_{00} = & d + \mathrm{Diag}(c) + p \left[ A^T A + \mathrm{Diag} \left(A^T b + b^T A\right)\right],\\
-Q_{01} = & Q_{10}^T = pA^T,\\
-Q_{11} = & p\mathrm{Diag}\left(1 + b^T + b\right).
+Q_{00} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x + \mathrm{Diag}_{\psi^x}(c) T^x,\\
+Q_{01} = & Q_{10}^T = p {T^{x}}^T A^T T^s,\\
+Q_{11} = & p\mathrm{Diag}_{\psi^s}\left(1 + b^T + b\right).
 \end{align}
-The function $\mathrm{Diag}(x) = \mathds{1}\circ(x\otimes\mathbf{1})$ embeds a vector $x$ into a diagonal matrix, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.
+The function $\mathrm{Diag}_{z}(v)$ embeds a vector $v$ into a diagonal matrix in subspace $z$, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.
 
@@
 
-Given a graph $G(E,V)$ defined by the set of $V$ vertices and $E$ edges and a subset $D \subseteq V(G)$, if the nearest-neighbor vertices of $\mathit{N}(D) = V(G)$, then $D$ is a dominating set, where an example is given by Fig.~\ref{fig:dominating_sets}a.
-The set $D$ is a minimal dominating set if there is no proper subset of $D$ that is a dominating set, {\it{i.e.}}, the removal of any vertex in $D$ results in $N(D) \neq V(G)$.
+Given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, and a subset of vertices $D \subseteq V$.
+If the set of all vertices not in $D$ is adjacent to at least one vertex in $D$, then $D$ is a dominating set.
+This is equivalent to requiring the set of nearest-neighbor vertices of $D$ (exclusive) and $D$ cover all vertices $N(D) \cup D = V$ (an example is given by Fig.~\ref{fig:dominating_sets}a).
+The set $D$ is a minimal dominating set if there is no proper subset of $D$ that is a dominating set, {\it{i.e.}}, the removal of any vertex in $D$ results in $N(D) \cup D  \neq V$.
 An example is given by Fig.~\ref{fig:dominating_sets}b.
@@
 \begin{align}
-f(x) = &\min(\sum_{v_i\in V} \psi_{v_i}),\\
-\textrm{subject to} \quad & \psi_{v_i} + \sum_{v_j \in \mathit{N}(v_i)} \psi_{v_j} \geq 1,\\
-& \psi_{v_i} \in \{0, 1\}.
+f(x) = &\min(\sum_{\nu \in V} \psi^x_{\nu}),\\
+\textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1,\\
+& \psi^x_{\nu} \in \{0, 1\}
 \end{align}
-The problem minimizes the number of vertices in $D$ with a binary variable $\psi$ encoded by a single qubit, subject to the constraint that at least one vertex in $\mathit{N}(v_i)$ is in $D$.
-We introduce slack variables $s_{v_i} = T^s_{v_i v_j} \psi^s_{v_j}$ to encode the inequality constraint such that
+where the dimension of the dependent variable $x$ is the number of vertices $\overline{\overline{V}}$.
+The problem minimizes the number of vertices in $D$ with a binary variable $\psi^x$ encoded by a single qubit, subject to the constraint that at least one vertex in $\mathit{N}(\nu)$ is in $D$.
+For each vertex in $V$ we introduce slack variables $s_{\nu} = T^s_{\nu \alpha} \psi^s_{\alpha}$ to encode the inequality constraint such that
 \begin{align}
-f(x) = &\min(\sum_{v_i\in V} \psi_{v_i}),\\
-\textrm{subject to} \quad & \psi_{v_i} + T^s_{v_i v_j} \psi^s_{v_j} + J_{v_i v_j} \psi_{v_j} = 1,\\
-& \psi_{v_i} \in \{0, 1\},\\
-& 0 \leq s_{v_i} \leq |\mathrm{N}(v_i)|\\
-& s_{v_i} \in \mathbb{Z},
+f(x) = &\min(\sum_{\nu\in V} \psi^x_{\nu}),\\
+\textrm{subject to} \quad & \psi^x_{\nu} + J_{\nu \mu} \psi^x_{\mu}- T^s_{\nu \alpha} \psi^s_{\alpha}  - 1 = 0,\\
+& \psi_{\nu} \in \{0, 1\},\\
+& 0 \leq s_{\nu} \leq |\mathrm{N}(\nu)|\\
+& s_{\nu} \in \mathbb{Z},
 \end{align}
-where the nearest-neighbor sum is expressed by $J$, the adjacency matrix for $G$.
-The algorithm uses $\overline{\overline{V}}$ qubits to encode $\overline{\overline{V}}$ vertices and $\sum_{v_i \in V} \log_2 \mathit(N(v_i))$ qubits to embed the slack variables.
+where the nearest-neighbor sum is expressed by $J$ (symmetric and zero diagonal), the adjacency matrix for $G$.
+The algorithm uses $N_q = \overline{\overline{V}} + \sum_{\nu \in V} \log_2 \mathit(N(\nu))$ qubits---$\overline{\overline{V}}$ qubits to encode the vertices and another $\sum_{\nu \in V} \log_2 \mathit(N(\nu))$ qubits to embed the slack variables.
 Therefore, the embedding at worse scales with $\overline{\overline{V}} \log_2 |\overline{\overline{V}}|$ qubits for fully connected graphs.
 
-The target Hamiltonian can be written in the convenient matrix form
+The target Hamiltonian can be written in the matrix form
 \begin{align}
@@
 \begin{pmatrix}
-1 + p\left[1+J^T J + 2(J+J^T)\right] &p(1+J^T)T^s\\
-p{T^s}^T(1+J)& p\left[{T^s}^T T^s + {T^s}^T + T^s\right]
+\mathbbm{1} + p\left[J^2 + 2 J - \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] & - p(\mathbbm{1}+J)T^s\\
+- p{T^s}^T(\mathbbm{1}+J)& p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]
 \end{pmatrix}
@@
 \Psi^x\\ \Psi^s
-\end{pmatrix} + p.
+\end{pmatrix} + p
 \label{eq:matrix_form}
 \end{align}
+where $ |M| \equiv \sum_{\nu} M_{\nu \mu}$.
 

### 2020-02-10 qlp/mds/graph_tools.py
Allowed plotting of directed graphs

@@ -9,7 +9,7 @@ import networkx as nx
 
 
 def generate_graph(
-    n_nodes: int, n_edges: int, n_edge_max: int = 5, seed: Optional[int] = None
+    n_nodes: int, n_edges: int, n_edge_max: int = 5, seed: Optional[int] = None,
 ) -> Set[Tuple[int]]:
     """Creates random edges for graph.
 
@@ -53,6 +53,7 @@ def get_plot(
     show_plot: bool = False,
     backend="mpl",
     seed: int = 42,
+    directed: bool = False,
 ):
     """Creates graph plot from edge set.
 
@@ -61,12 +62,19 @@ def get_plot(
         color_nodes: Colors given nodes green, default is white.
         show_plot: Wether or not the plot should be rendered.
         backend: The plotting backend. Either "mpl" or "bokeh".
+        directed: Plot graph as a directed graph
     """
     if backend == "mpl":
         fig = get_plot_mpl(
-            graph, color_nodes=color_nodes, show_plot=show_plot, seed=seed
+            graph,
+            color_nodes=color_nodes,
+            show_plot=show_plot,
+            seed=seed,
+            directed=directed,
         )
     elif backend == "bokeh":
+        if directed:
+            print("Directed graph not supported for bokeh")
         fig = get_plot_bokeh(graph, color_nodes=color_nodes, show_plot=show_plot)
     else:
         raise KeyError("Only implemented matplotlib ('mpl') or ")
@@ -80,6 +88,7 @@ def get_plot_mpl(
     show_plot: bool = False,
     ax: Optional["Axes"] = None,
     seed: int = 42,
+    directed: bool = False,
 ) -> Optional["Figure"]:
     """Creates matplotlib graph plot from edge set.
 
@@ -88,13 +97,14 @@ def get_plot_mpl(
         color_nodes: Colors given nodes green, default is white.
         show_plot: Wether or not the plot should be rendered.
         ax: The axes to plot in
+        directed: Plot graph as a directed graph
     """
     if not ax:
         fig, ax = plt.subplots()
     else:
         fig = None
 
-    G = nx.Graph(list(graph))
+    G = nx.DiGraph(list(graph)) if directed else nx.Graph(list(graph))
     node_color = (
         ["lightgreen" if node in color_nodes else "white" for node in G.nodes]
         if color_nodes

### 2020-02-10 qlp/mds/qubo.py
Added example for directed mds.
@cchang5: Please check my code if it makes sense to you

@@ -5,11 +5,17 @@ from scipy.sparse import dok_matrix, bmat
 import numpy as np
 
 
-def get_adjacency(graph: Set[Tuple[int]]) -> dok_matrix:
+def get_adjacency(graph: Set[Tuple[int]], directed: bool = False) -> dok_matrix:
     """This routine computes the adjecency matrix for a given graph.
 
     It assumes the graph is connected and nodes are labeled from 0...N-1.
     Self loops are forbidden.
+
+    Arguments:
+        graph: The graph. If the graph is directed, first entry points to second.
+        directed: Whether or not this is a directed graph. If not directed, the graph
+            is symmeterized.
+
     """
     if not isinstance(graph, set):
         raise TypeError("Graph must be a set of tuples")
@@ -25,7 +31,7 @@ def get_adjacency(graph: Set[Tuple[int]]) -> dok_matrix:
         nodes.add(v2)
         adj[(v1, v2)] = 1
 
-    nodes = sorted(nodes)
+    nodes = sorted(list(nodes))
     n_nodes = len(nodes)
 
     if nodes != list(range(n_nodes)):
@@ -34,7 +40,8 @@ def get_adjacency(graph: Set[Tuple[int]]) -> dok_matrix:
     adjacency = dok_matrix((n_nodes, n_nodes), dtype=int)
     for (v1, v2), val in adj.items():
         adjacency[(v1, v2)] = val
-        adjacency[(v2, v1)] = val
+        if not directed:
+            adjacency[(v2, v1)] = val
 
     if not all([val == 1 for val in adjacency.values()]):
         raise KeyError("Double entries in graph")
@@ -60,7 +67,9 @@ def get_bitmap(n_neigbors: List[int]) -> dok_matrix:
     n_nodes = len(n_neigbors)
 
     # Figure out how many bits we need for each neighborhood
-    n_bits = np.floor(np.log2(n_neigbors) + 1).astype(int)
+    n_bits = np.array(
+        [np.floor(np.log2(nn) + 1).astype(int) if nn > 0 else 0 for nn in n_neigbors]
+    )
     bitmap = dok_matrix((n_nodes, n_bits.sum()), dtype=int)
 
     acc = 0
@@ -72,53 +81,58 @@ def get_bitmap(n_neigbors: List[int]) -> dok_matrix:
     return bitmap
 
 
-def get_mds_qubo(graph: Set[Tuple[int]]) -> dok_matrix:
[…]

### 2020-02-10 qlp/mds/qubo.py
Added triangularization flag

@@ -1,7 +1,7 @@
 """Tools to generate a Minimum Dominating Set QUBO from a graph
 """
 from typing import Set, Tuple, List
-from scipy.sparse import dok_matrix, bmat
+from scipy.sparse import dok_matrix, bmat, triu, tril
 import numpy as np
 
 
@@ -81,7 +81,9 @@ def get_bitmap(n_neigbors: List[int]) -> dok_matrix:
     return bitmap
 
 
-def get_mds_qubo(graph: Set[Tuple[int]], directed: bool = False) -> dok_matrix:
+def get_mds_qubo(
+    graph: Set[Tuple[int]], directed: bool = False, triangularize: bool = False
+) -> dok_matrix:
     """This routine computes Minimum Dominating Set QUBO for a given graph.
 
     It assumes the graph is connected and nodes are labeled from 0...N-1.
@@ -90,6 +92,7 @@ def get_mds_qubo(graph: Set[Tuple[int]], directed: bool = False) -> dok_matrix:
     Arguments:
         graph: The graph. If the graph is directed, first entry points to second.
         directed: Whether or not this is a directed graph.
+        triangularize: Put lower triangular entries in the upper diagonal.
     """
     ## This is J
     adjacency = get_adjacency(graph, directed=directed)
@@ -132,7 +135,11 @@ def get_mds_qubo(graph: Set[Tuple[int]], directed: bool = False) -> dok_matrix:
     q_xx += one
 
     ## Construt QUBO
-    return bmat([[q_xx, q_xs], [None, q_ss]]).todok()
+    q = bmat([[q_xx, q_xs], [None, q_ss]]).todok()
+
+    if triangularize:
+        q = triu(q) + tril(q, -1).T
+    return q
 
 
 def main(col_wrap: int = 4):  # pylint: disable=R0914

### 2020-02-11 Notes/Notes.tex
Added idea on how to incorporate annealing time in H

@@
 
+\section{Ideas}
+\subsection{Penalty as a function of annealing time}
+The annealer encodes
+\begin{equation}
+	H(s) = (1-s)H_{init} + s H_{final} \, ,
+\end{equation}
+where $s$ is the annealing time.
+
+If our final Hamiltonian is linear in a computation parameter time, then we can ramp up this parameter as a function of annealing time.
+
+For example, in the MDS, we have
+\begin{equation}
+	H_{final} = H_{opt} + p H_{constraint} \, ,
+\end{equation}
+where $H_{opt} \leftrightarrow \sum_i x_i$ and $H_{constraint}$ encodes the Dominating set constraint.
+To have $H_{final} = p \tilde{H}_{constraint}$, we have to place the optimization condition in $H_{constraint}$.
+
+The idea here is: given a possible guess $\gamma$ for an MDS (which you can find using greedy search), is it possible to find a smaller solution.
+In other words, you map $H_{opt}$ to a new constraint
+\begin{equation}
+	 H_{constraint} \mapsto  p  H_{constraint} + p  \tilde H_{opt} = p \tilde H_{final} 
+	\, , \quad
+	\tilde H_{opt} \leftrightarrow \sum_i x_i < \gamma \, .
+\end{equation}
+Note that in principle you can have different $p$s here.
+You can now say that $p = \alpha s$ and ramp up the penalty as a function of annealing time.
+Because you also get the wave function and now the energy (zero - const if constraints are fulfilled), you do also get a better solution if possible.
+Also, since you ask for smaller, you might actually be lucky and get the optimal solution even if your guess was not really close.
+
 \end{document}

### 2020-02-24 Notes/Notes.tex
some qubo re-scale discussion in Notes
added a few words

@@
 
+\section{re-scale QUBO using ancillary qubits?}
+
+Original qubo is
+\begin{equation}
+f= \psi^T Q \psi .
+\end{equation}
+We can re-scale Q by a factor of 2 like:
+ \begin{align}
+\psi_2 &= (\psi , \psi)^T \\
+Q_2 &= 
+\begin{pmatrix}
+\frac{Q}{2} & 0 \\
+0 & \frac{Q}{2} \\
+\end{pmatrix} .
+\end{align}
+Then we have the re-scaled qubo:
+\begin{align}
+f &= \psi_2^T Q_2 \psi_2 \\
+&=  \psi^T  \frac{Q}{2} \psi +  \psi^T  \frac{Q}{2} \psi \\
+&=  \psi^T Q \psi .
+\end{align}
+The re-scaled qubo in general is
+ \begin{align}
+\psi_2 &= (\psi_a , \psi_b)^T \\
+Q_2 &= 
+\begin{pmatrix}
+\frac{Q}{2} & 0 \\
+0 & \frac{Q}{2} \\
+\end{pmatrix} .
+\end{align}
+\begin{align}
+f &= \psi_2^T Q_2 \psi_2 \\
+&=  \psi_a^T  \frac{Q}{2} \psi_a +  \psi_b^T  \frac{Q}{2} \psi_b .
+\end{align}
+This function reaches the maximum if and only if both $\psi_a$ and $\psi_b$ are in the solution space.
+
 \end{document}

### 2020-02-28 Notes/Notes.tex
Added notes on how to ask MDS question

@@
 
+\section{Asking MDS Question}
+Instead of minimizing the size of the minimum dominating set under constraints, we can also ask if the number of nodes is smaller than an input dominating number
+\begin{equation}
+	\sum_{i \in V} x_i \leq \gamma_D \quad \Rightarrow \quad \sum_{i \in V} x_i - \gamma_D + s_D = 0 \, .
+\end{equation}
+Note that we still obtain solution vectors.
+In principle this means one has to iterate approaches to get the best energy solution but it is also possible to find $E_0 = \gamma + n$ with $n\geq1$.
+The QUBO now becomes
+\begin{align}\label{mds2:qubo}
+	Q &= 
+	\begin{pmatrix}\alpha & \beta & 0 \\ 0 & \gamma & 0 \\ 0 & 0 & 0 \end{pmatrix}
+	+
+	A \begin{pmatrix}\alpha' & 0 & \beta' \\ 0 & 0 & 0 \\ 0 & 0 & \gamma' \end{pmatrix}
+	\, , & 
+	f(\vec x, \vec s, s_D)
+	&=
+	\vec \psi \cdot Q \cdot \vec \psi + |V| + A \gamma_D^2
+	\, ,
+\end{align}
+where $\alpha, \beta, \gamma$ are the same as before and $\alpha', \beta', \gamma'$ implement the new constraint.
+In particular 
+\begin{align}
+	\vec x \cdot \alpha' \vec x &= \left(\sum_i x_i\right)^2 - 2 \left(\sum_i x_i\right) \gamma_D 
+	&& \Rightarrow &
+	\alpha' &= \vec 1_x \vec 1_x^T - 2 \gamma_D \mathbbm{1}_x
+	\\
+	\vec x \cdot \beta' \vec s &= 2 \left(\sum_i x_i\right) s_D \gamma_D 
+	&& \Rightarrow &
+	\beta' &= 2 \gamma_D \vec 1_x B'
+	\\
+	\vec s \cdot \gamma' \vec s &= s_D^2 - 2 s_D \gamma_D 
+	&& \Rightarrow &
+	\alpha' &= B'^T B' - 2 \gamma_D B'
+	\\
+\end{align}
+
 \end{document}

### 2020-02-28 qlp/mds/graph_tools.py
Added fontzise kwarg

@@ -277,7 +277,7 @@ def get_plot_bokeh(  # pylint: disable=R0914
 
 
 def plot_qubo(
-    qubo, ax: Optional["Axes"] = None, axes: bool = False, **kwargs
+    qubo, ax: Optional["Axes"] = None, axes: bool = False, fontsize: int = 4, **kwargs
 ) -> "Axes":
     """Plots qubo as heat map
 
@@ -291,7 +291,7 @@ def plot_qubo(
 
     data = dict(
         annot=True,
-        annot_kws={"fontsize": 4},
+        annot_kws={"fontsize": fontsize},
         cmap="RdBu_r",
         vmin=-vmax,
         vmax=vmax,

### 2020-02-28 Notes/Notes.tex
Typos

@@
 \end{equation}
+This approach is interesting as it is constraints only.
 Note that we still obtain solution vectors.
-In principle this means one has to iterate approaches to get the best energy solution but it is also possible to find $E_0 = \gamma + n$ with $n\geq1$.
+In principle this means one has to iterate approaches to get the best energy solution but it is also possible to find $E_0 = \gamma - n$ with $n\geq1$.
 The QUBO now becomes

### 2020-03-11 paper/main.tex
Updated initial QUBO to factored out T
Synced presentation with paper
Re-included transpose adjacency for mds
Added classical section

@@
 \begin{pmatrix}
- Q_{00} & Q_{01}\\
-Q_{10} & {T^{s}}^T Q_{11} T^s
+Q_{xx} & Q_{xs}\\
+Q_{sx} & Q_{ss} 
 \end{pmatrix}
@@
 \begin{align}
-Q_{00} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x + \mathrm{Diag}_{\psi^x}(c) T^x,\\
-Q_{01} = & Q_{10}^T = p {T^{x}}^T A^T T^s,\\
-Q_{11} = & p\mathrm{Diag}_{\psi^s}\left(1 + b^T + b\right).
+Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x + \mathrm{Diag}_{\psi^x}(c) T^x,\\
+Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,\\
+Q_{ss} = & p\left[ {T^{s}}^T T^s + \mathrm{Diag}_{\psi^s}\left( {T^{s}}^T b + b^T T^s\right) \right].
 \end{align}
@@
 The domination number of $D$ is given by the cardinality of $|D| \equiv \overline{\overline{D}}$.
-The minimum dominating set is defined by $D$ with the smallest domination number.
+The minimum dominating set (MDS) is defined by $D$ with the smallest domination number.
 Fig.~\ref{fig:dominating_sets}c shows an example of the minimum dominating set of $G(V, E)$ and is different from the minimal dominating set.
@@
 	\label{fig:dominating_sets}
+\end{figure*}
+
+For general graphs, existing "classical" algorithms either find minimal solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or approximate solutions in polynomial time.
+For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
+Thus one is guaranteed to find a dominating set but not necessarily a MDS.
+We demonstrate an example greedy algorithm in figure Fig.~\ref{fig:mds-greedy}.
+\begin{figure*}
+	\centering
+	\begin{tabular}{p{0.22\textwidth}p{0.22\textwidth}p{0.22\textwidth}p{0.22\textwidth}}
+	\includegraphics[width=0.20\textwidth]{./figures/greedy-1.pdf}
+&
+	\includegraphics[width=0.20\textwidth]{./figures/greedy-2.pdf}
+&
+	\includegraphics[width=0.20\textwidth]{./figures/greedy-3.pdf}
+&
+	\includegraphics[width=0.20\textwidth]{./figures/greedy-4.pdf}\\
+	\centering\bf{a} & \centering\bf{b} & \centering\bf{c} & \centering\bf{d}
+	\end{tabular}
+	\caption{
+		Example of greedy MDS algorithm:
+		The algorithm iteratively adds vertices to the dominating set (black nodes) such that newly added nodes are maximally unconnected (white nodes).
+		Connected nodes are neighbors of the DS (turquoise) or already in the DS.
+		In (a), one finds three unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
+		In the first step $a\to b$, randomly the node (4) is picked.
+		In (b), one has two unconnected choices [(1), (2)] with each adjacent to another unconnected node.
+		After randomly selecting (2) when going from $b \to c$, only one unconnected node is remaining (6).
+		The found solution is a (minimal) dominating set but not a MDS.
+		To find the MDS using this greedy algorithm, the first node choice must be either (2) or (5).
+	}
+	\label{fig:mds-greedy}
 \end{figure*}
@@
 \begin{pmatrix}
-\mathbbm{1} + p\left[J^2 + 2 J - \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] & - p(\mathbbm{1}+J)T^s\\
+\mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] & - p(\mathbbm{1}+J^T)T^s\\
 - p{T^s}^T(\mathbbm{1}+J)& p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]
@@
 \Psi^x\\ \Psi^s
-\end{pmatrix} + p
+\end{pmatrix} + p \overline{\overline{V}}
 \label{eq:matrix_form}

### 2020-03-12 paper/main.tex
add qubo reference

@@
 
-\affil[1]{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
 \affil[1]{Department of Physics, University of California, Berkeley, California 94720, USA}
 \affil[1]{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
-\affil[2]{?}
-\affil[3]{Department of Physics, University of California, Berkeley, California 94720, USA}
+\affil[2]{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
+\affil[2]{Department of Physics, University of California, Berkeley, California 94720, USA}
+\affil[3]{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
 \affil[4]{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
@@
 Through the adiabatic theorem of quantum mechanics, the annealer is prepared initially in a trivial ground state while the solution to ILP is encoded in the target Hamiltonian.
-Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems.
+Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems~\cite{2018Glover}.
 

### 2020-03-21 Notes/Notes.tex
notes for time-dependent simulation of annealing

@@
 
+\section{Time-dependent simulation of quantum annealing}
+
+I tried to follow DWave's convention as much as I can.
+This notebook is to solve time-dependent Schrodinger equation for quantum annealing Hamiltonian.
+Then use final wavefunction to check the overlap with the Ising ground state from exact diagonalization.
+The absolute square of the overlap is the probability that the measurement result gives the solution.
+This is like what Nishimori did in his original paper.
+
+Time dependent Hamiltoniain is
+\begin{align}
+H_{anneal}(t) =  \frac{-A(t)}{2} (\sum_i \sigma^x_i) + \frac{B(t)}{2} (\sum_{i>j} J_{ij} \sigma^z_i \sigma^z_j +\sum_i h_i \sigma^z_i ) 
+\end{align}
+
+The goal is to solve 
+\begin{align}
+i \partial_t \psi(t) = H(t) \psi(t)
+\end{align}
+with initial condition
+\begin{align}
+\psi(t=0)= \otimes_i  |\rightarrow \rangle_i
+\end{align}
+
+The time period is set to $[0,1]$.
+
+The probability to get the ground state at measurement is
+\begin{align}
+P = | \langle \psi (t)  | gnd \rangle |^2
+\end{align}
+
+For now the offset is included in the following way: 
+\begin{align}
+H_{offset}(t) =  \frac{-A(t)}{2} ( \sum_i c_i(t) \sigma^x_i) + \frac{B(t)}{2} (\sum_{i>j} \frac{c_i(t)+c_j(t)}{2} \sigma^z_i \sigma^z_j +\sum_i  c_i(t) \sigma^z_i ) 
+\end{align}
+
+So the total Hamiltonian is $H=H_{anneal}+H_{offset}$.
+
+Users can define functions $c_i(t)$, $A(t)$, $B(t)$ in the code.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.5\textwidth]{annealingschedule.png}
+	\includegraphics[width=0.5\textwidth]{probt.png}
+	\caption{
+		\label{tdse} time-dependent Schrodinger equation simulation of quantum annealing.
+	}
+\end{figure}
+
 \end{document}

### 2020-03-24 qlp/tdse.py
fixed some more bugs for tdse

@@ -8,27 +8,33 @@ from qlp.mds.mds_qlpdb import QUBO_to_Ising, find_offset, AnnealOffset
 
 # Get DWave anneal schedule
 class s_to_offset:
-    def __init__(self):
-        params = {
+    def __init__(self, fill_value):
+        if fill_value == "extrapolate":
+            fill_valueC = fill_value
+            fill_valueA = fill_value
+            fill_valueB = fill_value
+        elif fill_value == "truncate":
+            fill_valueC = (0, 1)
+            fill_valueA = (10.3214800, 0.0000026)
+            fill_valueB = (0.4927432, 11.8604700)
+        paramsC = {
             "kind": "linear",
-            "fill_value": "extrapolate",
+            "fill_value": fill_valueC,
+        }  # linear makes for more sensible extrapolation.
+        paramsA = {
+            "kind": "linear",
+            "fill_value": fill_valueA,
+        }  # linear makes for more sensible extrapolation.
+        paramsB = {
+            "kind": "linear",
+            "fill_value": fill_valueB,
         }  # linear makes for more sensible extrapolation.
         self.anneal_schedule = read_excel(
             io="./09-1212A-B_DW_2000Q_5_anneal_schedule.xlsx", sheet_name=1
         )
-        self.interpC = interp1d(
-            self.anneal_schedule["s"], self.anneal_schedule["C (normalized)"], **params
-        )
-        normA = (
-            self.anneal_schedule["A(s) (GHz)"]
-            / self.anneal_schedule["A(s) (GHz)"].max()
-        )
-        self.interpA = interp1d(self.anneal_schedule["C (normalized)"], normA, **params)
-        normB = (
-            self.anneal_schedule["B(s) (GHz)"]
-            / self.anneal_schedule["B(s) (GHz)"].max()
-        )
-        self.interpB = interp1d(self.anneal_schedule["C (normalized)"], normB, **params)
+        self.interpC = interp1d(self.anneal_schedule["s"], self.anneal_schedule["C (normalized)"], **paramsC)
+        self.interpA = interp1d(self.anneal_schedule["C (normalized)"], self.anneal_schedule["A(s) (GHz)"], **paramsA)
[…]

### 2020-03-24 Notes/Notes.tex

@@
 \begin{align}
-H_{anneal}(t) =  \frac{-A(t)}{2} (\sum_i \sigma^x_i) + \frac{B(t)}{2} (\sum_{i>j} J_{ij} \sigma^z_i \sigma^z_j +\sum_i h_i \sigma^z_i ) 
+H_{anneal}(t) =  \frac{-1}{2} (\sum_i  A_i(t)\sigma^x_i) + \frac{1}{2} (\sum_{i>j} \frac{B_{i}(t)+B_{j}(t)}{2} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i ) ,
 \end{align}
+where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions. The site-dependence taking into account of possible annealing offsets.
 
@@
 \begin{align}
-i \partial_t \psi(t) = H(t) \psi(t)
+i \partial_t \psi(t) = H(t) \psi(t) .
 \end{align}
-with initial condition
-\begin{align}
-\psi(t=0)= \otimes_i  |\rightarrow \rangle_i
-\end{align}
+
+The initial condition is the ground state of $H(s=0)$.
+This state is slightly different from the pure transverse  field eigenstate $\psi(t=0)= \otimes_i  |\rightarrow \rangle_i$, because the annealing schedule $B_i(s=0)> 0$.
 
@@
 
-For now the offset is included in the following way: 
-\begin{align}
-H_{offset}(t) =  \frac{-A(t)}{2} ( \sum_i c_i(t) \sigma^x_i) + \frac{B(t)}{2} (\sum_{i>j} \frac{c_i(t)+c_j(t)}{2} \sigma^z_i \sigma^z_j +\sum_i  c_i(t) \sigma^z_i ) 
-\end{align}
-
-So the total Hamiltonian is $H=H_{anneal}+H_{offset}$.
-
-Users can define functions $c_i(t)$, $A(t)$, $B(t)$ in the code.
-
 \begin{figure}[htb]
 	\centering
-	\includegraphics[width=0.5\textwidth]{annealingschedule.png}
+	%\includegraphics[width=0.5\textwidth]{annealingschedule.png}
 	\includegraphics[width=0.5\textwidth]{probt.png}
 	\caption{
-		\label{tdse} time-dependent Schrodinger equation simulation of quantum annealing.
+		\label{tdse} time-dependent Schrodinger equation simulation of quantum annealing. Annealing time=100 $\mu s$.
 	}

### 2020-03-24 qlp/tdse.py
blehhhh

@@ -11,30 +11,22 @@ class s_to_offset:
     def __init__(self, fill_value):
         if fill_value == "extrapolate":
             fill_valueC = fill_value
-            fill_valueA = fill_value
-            fill_valueB = fill_value
         elif fill_value == "truncate":
             fill_valueC = (0, 1)
-            fill_valueA = (10.3214800, 0.0000026)
-            fill_valueB = (0.4927432, 11.8604700)
         paramsC = {
             "kind": "linear",
             "fill_value": fill_valueC,
         }  # linear makes for more sensible extrapolation.
-        paramsA = {
+        params = {
             "kind": "linear",
-            "fill_value": fill_valueA,
-        }  # linear makes for more sensible extrapolation.
-        paramsB = {
-            "kind": "linear",
-            "fill_value": fill_valueB,
+            "fill_value": "extrapolate",
         }  # linear makes for more sensible extrapolation.
         self.anneal_schedule = read_excel(
             io="./09-1212A-B_DW_2000Q_5_anneal_schedule.xlsx", sheet_name=1
         )
         self.interpC = interp1d(self.anneal_schedule["s"], self.anneal_schedule["C (normalized)"], **paramsC)
-        self.interpA = interp1d(self.anneal_schedule["C (normalized)"], self.anneal_schedule["A(s) (GHz)"], **paramsA)
-        self.interpB = interp1d(self.anneal_schedule["C (normalized)"], self.anneal_schedule["B(s) (GHz)"], **paramsB)
+        self.interpA = interp1d(self.anneal_schedule["C (normalized)"], self.anneal_schedule["A(s) (GHz)"], **params)
+        self.interpB = interp1d(self.anneal_schedule["C (normalized)"], self.anneal_schedule["B(s) (GHz)"], **params)
 
     def sanity_check(self):
         # Sanity check: The data and interpolation should match

### 2020-03-27 qlp/tdse.py
cleaned up code, fix mixed state degeneracy

@@ -1,11 +1,12 @@
 # Library to solve the time dependent schrodinger equation in the many-body Fock space.
 from pandas import read_excel
 import numpy as np
-import scipy as sp
+from numpy.linalg import eigh
 from scipy.integrate import solve_ivp
 from scipy.interpolate import interp1d
-from qlp.mds.mds_qlpdb import QUBO_to_Ising, find_offset, AnnealOffset
 import matplotlib.pyplot as plt
+
+from qlp.mds.mds_qlpdb import AnnealOffset
 
 # Get DWave anneal schedule
 class s_to_offset:
@@ -65,12 +66,12 @@ class s_to_offset:
         self.interpA = interp1d(
             self.anneal_schedule["C (normalized)"],
             self.anneal_schedule["A(s) (GHz)"],
-            **paramsA
+            **paramsA,
         )
         self.interpB = interp1d(
             self.anneal_schedule["C (normalized)"],
             self.anneal_schedule["B(s) (GHz)"],
-            **paramsB
+            **paramsB,
         )
 
     def sanity_check(self):
@@ -114,6 +115,7 @@ class AnnealSchedule:
         offset_range,
         fill_value="extrapolate",
         anneal_curve="linear",
+        **kwargs,
     ):
         AO = AnnealOffset(offset)
         self.offset_list, self.offset_tag = AO.fcn(
@@ -136,9 +138,11 @@ class AnnealSchedule:
 
 
 class TDSE:
-    def __init__(self, n, ising_params, offset_params):
+    def __init__(self, n, ising_params, offset_params, solver_params):
         self.n = n
         self.ising = ising_params
+        self.offset_params = offset_params
+        self.solver_params = solver_params
         self.id2, self.sigx, self.sigz = self.pauli()
         self.FockX, self.FockZ, self.FockZZ = self.init_Fock()
         self.AS = AnnealSchedule(**offset_params)
@@ -146,7 +150,7 @@ class TDSE:
             self.Bij(self.AS.B(1)) * self.ising["Jij"], self.AS.B(1) * self.ising["hi"]
         )
 
-    def __call__(self, t, y):
+    def tdse(self, t, y):
         """Define time-dependent Schrodinger equation"""
         f = -1j * np.dot(self.annealingH(t), y)
         return f
@@ -161,6 +165,40 @@ class TDSE:
         sigz[0, 0] = 1.0
         sigz[1, 1] = -1.0
         return id2, sigx, sigz
+
[…]

### 2020-03-27 qlp/tdse.py
clean up code

@@ -182,7 +182,7 @@ class TDSE:
         )
         return overlap
 
-    def init_wavefunction(self, type="transverse"):
+    def init_eigen(self, type):
         if type == "true":
             # true ground state
             eigvalue, eigvector = eigh(
@@ -197,8 +197,37 @@ class TDSE:
             )
         else:
             raise TypeError("Undefined initial wavefunction.")
+        return eigvalue, eigvector
+
+    def init_wavefunction(self, type="transverse"):
+        eigvalue, eigvector = self.init_eigen(type)
         y1 = (1.0 + 0.0j) * eigvector[:, 0]
         return y1
+
+    def init_densitymatrix(self, temp=13e-3, type="transverse", debug=False):
+        """Initial density matrix
+        temperature in kelvins
+        """
+        kb = 8.617333262145e-5  # Boltzmann constant [eV / K]
+        h = 4.135667696e-15  # Plank constant [eV s] (no 2 pi)
+        one = 1e-9  # GHz s
+        beta = 1 / (temp * kb / h * one)  # inverse temperature [h/GHz]
+
+        # construct initial density matrix
+        eigvalue, eigvector = self.init_eigen(type)
+
+        dE = eigvalue[:] - eigvalue[0]
+        pr = np.exp(-beta * dE)
+        pr = pr / sum(pr)
+        if debug:
+            print("dE", dE)
+            print("pr", pr, "total", sum(pr))
+
+        rho = np.zeros((eigvalue.size * eigvalue.size))
+        for i in range(eigvalue.size):
+            rho = rho + (pr[i]) * np.kron(eigvector[:, i], np.conj(eigvector[:, i]))
+        rho = (1.0 + 0.0j) * rho
+        return rho
 
     def init_Fock(self):
         """Finish all the operators here and store them"""
@@ -256,7 +285,7 @@ class TDSE:
         end = self.offset_params["normalized_time"][1]
         interval = np.linspace(start, end, ngrid)
 
-        sol = sol_interface(y1)
+        sol = pure_sol_interface(y1)
 
         for jj in range(ngrid - 1):
             y1 = y1 / (np.sqrt(np.absolute(np.dot(np.conj(y1), y1))))
@@ -274,7 +303,22 @@ class TDSE:
             )
         return sol
 
-class sol_interface():
+    def annealingH_densitymatrix(self, s):
+        Fockid = np.identity(self.Focksize)
[…]

### 2020-03-27 Notes/Notes.tex
update notes for simulator

@@
 I tried to follow DWave's convention as much as I can.
-This notebook is to solve time-dependent Schrodinger equation for quantum annealing Hamiltonian.
+This notebook is to solve for time evolution dynamics of quantum annealing Hamiltonian.
 Then use final wavefunction to check the overlap with the Ising ground state from exact diagonalization.
@@
 \begin{align}
-H_{anneal}(t) =  \frac{-1}{2} (\sum_i  A_i(t)\sigma^x_i) + \frac{1}{2} (\sum_{i>j} \frac{B_{i}(t)+B_{j}(t)}{2} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i ) ,
+H_{anneal}(t) =  - \sum_i  A_i(t)\sigma^x_i +  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,
 \end{align}
@@
 
-The goal is to solve 
+The goal is to solve the time-dependent Schrodinger equation 
 \begin{align}
@@
 \begin{align}
-P = | \langle \psi (t)  | gnd \rangle |^2
+P =\sum_i | \langle \psi (t)  | \mbox{gnd}_i \rangle |^2 ,
 \end{align}
+where the summation runs over degenerated ground states.
 
@@
 
+For mixed state simulation the initial density matrix is the Gibbs canonical ensemble
+\begin{equation}
+\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} .
+\end{equation}
+The time evolution of density matrix is governed by von Neumann equation
+\begin{align}
+i \partial_t \rho (t) = [H(t) , \rho(t)] ,
+\end{align}
+where $[,]$ denotes the Lie bracket.
+
+The probability to get the ground state at measurement is
+\begin{align}
+P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
+\end{align}
+where the projection operator onto the ground state subspace is $\pi_{\mbox{gnd}}=\sum_i |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
+
 \end{document}

### 2020-03-29 Notes/Notes.tex
add unit conversion discussion in notes

@@
 
+\subsection{unit conversion}
+
+So this part is typed up just to fix units and $2\pi$ not for correct math, please check if this makes sense...
+
+We have time $t \in [0,T]$ where $T=N_T \times 10^{-6} sec$ is annealing time with unit of micro sec.
+$N_T$ is just dimensionless number.
+The time is mapped to the dimensionless schedule $s\in [0,1]$ through $s=t/T$.
+
+Now the equation we are solving is
+\begin{equation}
+ i \hbar \frac{d}{dt}\psi = H \psi .
+\end{equation}
+
+The Hamiltonian is $H=N_H \times GHz \times h =N_H \times 10^9  \times h/( sec)$ where $N_H$ is the dimensionless numerical value. Use
+\begin{equation}
+\frac{d}{dt}\psi = \frac{d}{Tds}\psi .
+\end{equation}
+So the equation is
+\begin{align}
+  \frac{d}{ds}\psi  &=  -i \frac{H\times T}{\hbar} \psi  &\\
+   &=  -i \frac{N_H \times 10^9 \times h \times N_T \times 10^{-6} sec \times 2\pi }{h\times sec  } \psi &  \\
+  &= -i N_H \times N_T \times 10^{3} \times (2\pi) \psi  &.
+\end{align}
+and this is why the factor $10^{3} \times (2\pi)$.
+
 \end{document}

### 2020-03-30 Notes/Notes.tex
change name to tdse_notebook.ipynb

@@
 \graphicspath{ {./figs/} }
+\usepackage{hyperref}
 
@@
 \begin{align}
+\label{eq:annealH}
 H_{anneal}(t) =  - \sum_i  A_i(t)\sigma^x_i +  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,
@@
 
-The Hamiltonian is $H=N_H \times GHz \times h =N_H \times 10^9  \times h/( sec)$ where $N_H$ is the dimensionless numerical value. Use
+The dimension of the Hamiltonian is $[H]=N_H \times GHz \times h =N_H \times 10^9  \times h/( sec)$ where $N_H$ is the dimensionless numerical value. See 
+\href{https://docs.dwavesys.com/docs/latest/c_qpu_0.html#quantum-annealing-with-ising-spins-in-a-transverse-field}{DWave documentation} Fig.
+72.
+The Hamiltonian of Eq.~(\ref{eq:annealH}) only has units in $A(s)$ and $B(s)$ and are given by DWave as GHz, or $\mathrm{energy}/h$ and not $\hbar$.
+Use
 \begin{equation}
@@
   \frac{d}{ds}\psi  &=  -i \frac{H\times T}{\hbar} \psi  &\\
-   &=  -i \frac{N_H \times 10^9 \times h \times N_T \times 10^{-6} sec \times 2\pi }{h\times sec  } \psi &  \\
+   &=  -i \frac{N_H \times 10^9 \times h \times N_T \times 10^{-6} sec}{ sec  }\frac{2\pi}{h} \psi &  \\
   &= -i N_H \times N_T \times 10^{3} \times (2\pi) \psi  &.
@@
 
+\subsection{Simulating DWave}
+We allow the ability to define arbitrary annealing schedules as shown in Fig.~\ref{fig:anneal_schedules}.
+We also allow for per qubit offsets as suggested by Eq.~(\ref{eq:annealH}), with an example annealing schedule shown in Fig.~\ref{fig:anneal_offset} as well.
+For DWave's implementation, anneal offset yields systematic errors because the qubits no longer all start and end with the same coefficients.
+For our simulation, we allow for extended anneal schedules, which allow all qubits to undergo the full annealing process, yielding a true temporal offset for inhomogeneous driving fields.
+
+At the level of the scripts the problem that we solve are MDS for graph problems. In there, there is an option
+\begin{itemize}
+	\item \texttt{embed}: This embeds the QUBO into a chimera graph. Currently there is only an explicit result from G(2). I will in the future actually embed with DWave minorminer.
+\end{itemize}
+
+The options for controlling the annealing time and annealing schedule are:
+\begin{itemize}
+	\item \texttt{annealing\_time}: annealing time as defined from $s=[0, 1]$ in microseconds
+	\item \texttt{normalized\_time}: this is $s$. Set it to $<0$ or $>1$ if offset is used to allow for a complete annealing schedule. The total time in microseconds will increase accordingly.
+	\item \texttt{offset}: This is a string argument to the \texttt{fcn} method of the class \texttt{AnnealOffset} in \texttt{qlp.mds.mds\_qlpdb}.
+Define your own anneal offset routine here or call an existing one.
+E-mail me if you need more explanation.
+	\item \texttt{fill\_value}: If \texttt{normalized\_time} is extended beyond (0, 1), this option decides whether to extrapolate the anneal schedule, or truncate it at the nearest value.
+	\item \texttt{offset\_min}: Argument to \texttt{AnnealOffset} class.
+	\item \texttt{offset\_range}: Argument to \texttt{AnnealOffset} class.
+\end{itemize}
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.49\textwidth]{coefficient_dwave.pdf}
+	\includegraphics[width=0.49\textwidth]{coefficient_linear.pdf}
+	\caption{\label{fig:anneal_schedules} Examples of anneal schedules.
+In figure are value of $A(s)$ and $B(s)$ as a function of normalized time $s$.
+The DWave schedule (left), and a idealized linear annealing schedule (right).
+	}
+\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.49\textwidth]{coefficient_dwave_offset.pdf}
+	\includegraphics[width=0.49\textwidth]{coefficient_dwave_offset_full.pdf}
+	\caption{\label{fig:anneal_offset} (left) Dwave schedule with offset.
+Note that the values of $A(s)$ and $B(s)$ are no longer the same for all qubits at the start and end of the anneal.
+(right) An extended anneal schedule that allows all qubits to start and end with the same coefficients.
+	}
+\end{figure}
+
+The ODE solver we currently call is from \texttt{scipy.integrate.solve\_ivp}.
+In the future, we should consider migrating this to use \texttt{qutip.ssesolve} or some equivalent.
+See \href{http://qutip.org/docs/latest/guide/dynamics/dynamics-time.html}{QuTiP time-dependent solvers Documentation}.
+For now, the solver parameters are
+\begin{itemize}
+	\item \texttt{method}: The default is RK45, which is a 5th order Runge-Kutta algorithm.
+	\item \texttt{rtol}: The relative tolerance for the solver.
+	\item \texttt{atol}: The absolute tolerance.
+\end{itemize}
+
+We have also implemented both a pure-state simulation, as well as a mixed-state simulation.
+These can be chosen with the following parameters:
+
+\begin{itemize}
+	\item \texttt{pure\_tdse}: This is a boolean (True / False) flag and runs the pure state solver.
+	\item \texttt{mixed\_tdse}: This boolean flag runs the mixed state solver.
+	\item \texttt{temp}: This sets the temperature for the mixed state solver in kelvins.
+	\item \texttt{initial\_wavefunction}: For the pure state solver, the initial wavefunction can be chosen to be the ground state of $\sum_i \sigma_i^x$ (\texttt{transverse}) or $H(0)$ (\texttt{real}).
+For the DWave anneal schedule, or when annealing offsets are used without extended annealing times, these two options are not the same.
+	\item \texttt{degeneracy\_tol}: This sets the numerical tolerance as to when an excited-state is labeled as degenerate to the ground state. This is important for graphs with degenerate ground states.
+\end{itemize}
+
+A quick study below.
+We run a simulation with anneal offsets similar to what we ran on DWave (Fig.~\ref{dwave_result}).
+We see that if we apply a delay on qubits with small values and advance qubits with of $h_i$ (binary), then the performance improves.
+And vice versa.
+This is completely unexpected from the point of view of many-body localization.
+Because this result was so surprising, we wrote this simulator.
+Under DWave conditions (embedded problem, non-linear anneal schedule, truncating offset), we are able to reproduce this behavior (fig~\ref{fig:proba_dwave}).
+Here I note that if we run the idealized scenario (more importantly, without embedding), the behavior is reverse, and is consistent with what is expected due to many-body localization.
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.8\textwidth]{scaling_full_0p10.pdf}
+	\caption{\label{fig:dwave_result} DWave results.
+	}
+\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\includegraphics[width=0.49\textwidth]{proba_binary.pdf}
+	\includegraphics[width=0.49\textwidth]{proba_negbinary.pdf}
+	\caption{\label{fig:proba_dwave} (left) Binary offset and (right) NegBinary offset.
+	}
+\end{figure}
+
 \end{document}

### 2020-03-30 qlp/mds/mds_qlpdb.py

@@ -13,6 +13,8 @@ import yaml
 
 
 class AnnealOffset:
+    """https://docs.dwavesys.com/docs/latest/c_qpu_0.html#anneal-offsets
+    """
     def __init__(self, tag):
         self.tag = tag
 

### 2020-03-30 qlp/tdse.py

@@ -343,6 +343,9 @@ def plot_anneal_schedule(tdse, normalized_time):
     for qubit in range(len(yA[0])):
         ax.errorbar(x=X, y=yA[:, qubit])
         ax.errorbar(x=X, y=yB[:, qubit], ls="--")
+    ax.set_xlabel("normalized time")
+    ax.set_ylabel("energy/h [GHz]")
+    plt.savefig("./coefficient.pdf")
     plt.draw()
     plt.show()
 

### 2020-03-30 qlp/tdse.py
Blacking file

@@ -314,18 +314,20 @@ class TDSE:
 
     def f_densitymatrix2(self, t, y):
         """Define time-dependent Schrodinger equation for density matrix"""
-        #f = -1j * np.dot(self.annealingH_densitymatrix(t), y)
-        #print('waht', type(self.Focksize))
-        #print(self.Focksize)
-        ymat=y.reshape((self.Focksize,self.Focksize))
-        H=self.annealingH(t)
-        ymat= -1j *( np.dot(H, ymat)-np.dot(ymat, H))
-        f=ymat.reshape(self.Focksize**2)
+        # f = -1j * np.dot(self.annealingH_densitymatrix(t), y)
+        # print('waht', type(self.Focksize))
+        # print(self.Focksize)
+        ymat = y.reshape((self.Focksize, self.Focksize))
+        H = self.annealingH(t)
+        ymat = -1j * (np.dot(H, ymat) - np.dot(ymat, H))
+        f = ymat.reshape(self.Focksize ** 2)
         return f
 
     def solve_mixed(self, rho):
         self.Focksize = int(np.sqrt(len(rho)))
-        sol = solve_ivp(self.f_densitymatrix2, self.offset_params["normalized_time"], rho)
+        sol = solve_ivp(
+            self.f_densitymatrix2, self.offset_params["normalized_time"], rho
+        )
         return sol
 
 
@@ -333,6 +335,7 @@ class pure_sol_interface:
     def __init__(self, y1):
         self.t = np.zeros((0))
         self.y = np.zeros((y1.size, 0))
+
 
 def plot_anneal_schedule(tdse, normalized_time):
     plt.figure()

### 2020-03-30 qlp/tdse.py
Linting

@@ -1,9 +1,13 @@
-# Library to solve the time dependent schrodinger equation in the many-body Fock space.
-from pandas import read_excel
+"""Library to solve the time dependent schrodinger equation in the many-body Fock space.
+"""
 import numpy as np
 from numpy.linalg import eigh
+
 from scipy.integrate import solve_ivp
 from scipy.interpolate import interp1d
+
+from pandas import read_excel
+
 import matplotlib.pyplot as plt
 
 from qlp.mds.mds_qlpdb import AnnealOffset

### 2020-03-30 qlp/tdse.py
Removing linter warnings for naming conventions and public methods

@@ -1,3 +1,4 @@
+# pylint: disable=C0103, R0903
 """Library to solve the time dependent schrodinger equation in the many-body Fock space.
 """
 import numpy as np

### 2020-03-30 qlp/tdse.py
Documented s_to_offset

@@ -15,25 +15,54 @@ from qlp.mds.mds_qlpdb import AnnealOffset
 
 # Get DWave anneal schedule
 class s_to_offset:
-    def __init__(self, fill_value, anneal_curve):
+    """Class which provides anneal curves for A(s), B(s), C(s) over normalized
+    anneal time s in GHz.
+
+    Attributes:
+        maxB: float
+            Max Dwave magnet field coefficient in GHz.
+        anneal_schedule: Dict[str, List[int, int]]
+            Boundaries for anneal parameters.
+        interpA: np.ndarray
+            Interpolated curve for C(s) in GHz.
+        interpB: np.ndarray
+            Interpolated curve for C(s) in GHz.
+        interpC: np.ndarray
+            Interpolated curve for C(s) in GHz.
+    """
+
+    maxB = 11.8604700
+
+    def __init__(self, fill_value: str, anneal_curve: str):
+        """Allocates offset curves A(s), B(s), C(s) over normalized anneal time s in GHz.
+
+        Arguments:
+            fill_value: If normalized time (s) is extended beyond (0, 1),
+                this option decides whether to extrapolate the anneal schedule,
+                or truncate it at the nearest value.
+                Options are "extrapolate" or "truncate".
+            anneal_curve: Curve normalized time follows.
+                Options are "linear", "logistic" or "dwave" (reads in excel file).
+
+        Raises:
+            KeyError: If one of the inputs is not reckognized
+        """
         if anneal_curve == "linear":
-            # Max Dwave coefficient = 11.8604700 GHz
-            maxB = 11.8604700
+
             self.anneal_schedule = {
                 "s": [0, 1],
                 "C (normalized)": [0, 1],
-                "A(s) (GHz)": [maxB, 0],
-                "B(s) (GHz)": [0, maxB],
+                "A(s) (GHz)": [self.maxB, 0],
+                "B(s) (GHz)": [0, self.maxB],
             }
-        if anneal_curve == "logistic":
-            maxB = 11.8604700
+        elif anneal_curve == "logistic":
             # DWave approx 10 GHz
             s = np.linspace(0, 1)
             self.anneal_schedule = {
                 "s": s,
                 "C (normalized)": s,
-                "A(s) (GHz)": maxB / (1.0 + np.exp(10.0 * (s - 0.5))),
-                "B(s) (GHz)": maxB / (1.0 + np.exp(-10.0 * (s - 0.5))),
[…]

### 2020-03-30 qlp/tdse/__init__.py
Started to refactor schedules

@@ -13,142 +13,7 @@ import matplotlib.pyplot as plt
 
 from qlp.mds.mds_qlpdb import AnnealOffset
 
-# Get DWave anneal schedule
-class s_to_offset:
-    """Class which provides anneal curves for A(s), B(s), C(s) over normalized
-    anneal time s in GHz.
-
-    Attributes:
-        maxB: float
-            Max Dwave magnet field coefficient in GHz.
-        anneal_schedule: Dict[str, List[int, int]]
-            Boundaries for anneal parameters.
-        interpA: np.ndarray
-            Interpolated curve for C(s) in GHz.
-        interpB: np.ndarray
-            Interpolated curve for C(s) in GHz.
-        interpC: np.ndarray
-            Interpolated curve for C(s) in GHz.
-    """
-
-    maxB = 11.8604700
-
-    def __init__(self, fill_value: str, anneal_curve: str):
-        """Allocates offset curves A(s), B(s), C(s) over normalized anneal time s in GHz.
-
-        Arguments:
-            fill_value: If normalized time (s) is extended beyond (0, 1),
-                this option decides whether to extrapolate the anneal schedule,
-                or truncate it at the nearest value.
-                Options are "extrapolate" or "truncate".
-            anneal_curve: Curve normalized time follows.
-                Options are "linear", "logistic" or "dwave" (reads in excel file).
-
-        Raises:
-            KeyError: If one of the inputs is not reckognized
-        """
-        if anneal_curve == "linear":
-
-            self.anneal_schedule = {
-                "s": [0, 1],
-                "C (normalized)": [0, 1],
-                "A(s) (GHz)": [self.maxB, 0],
-                "B(s) (GHz)": [0, self.maxB],
-            }
-        elif anneal_curve == "logistic":
-            # DWave approx 10 GHz
-            s = np.linspace(0, 1)
-            self.anneal_schedule = {
-                "s": s,
-                "C (normalized)": s,
-                "A(s) (GHz)": self.maxB / (1.0 + np.exp(10.0 * (s - 0.5))),
-                "B(s) (GHz)": self.maxB / (1.0 + np.exp(-10.0 * (s - 0.5))),
-            }
-        elif anneal_curve == "dwave":
-            anneal_schedule = read_excel(
-                io="./09-1212A-B_DW_2000Q_5_anneal_schedule.xlsx", sheet_name=1
-            )
-            self.anneal_schedule = {
[…]

### 2020-03-30 qlp/tdse/schedule.py
Started to refactor schedules

@@ -1,0 +1,145 @@
+# pylint: disable=C0103, R0903
+
+"""Functions and classes which define TDSE anneal schedule setups
+"""
+from numpy import linspace, exp
+from scipy.interpolate import interp1d
+from pandas import read_excel
+
+from matplotlib.pyplot import subplots, draw, show
+
+
+class s_to_offset:
+    """Class which provides anneal curves for A(s), B(s), C(s) over normalized
+    anneal time s in GHz.
+
+    Attributes:
+        maxB: float
+            Max Dwave magnet field coefficient in GHz.
+        anneal_schedule: Dict[str, List[int, int]]
+            Boundaries for anneal parameters.
+        interpA: np.ndarray
+            Interpolated curve for C(s) in GHz.
+        interpB: np.ndarray
+            Interpolated curve for C(s) in GHz.
+        interpC: np.ndarray
+            Interpolated curve for C(s) in GHz.
+    """
+
+    maxB = 11.8604700
+
+    def __init__(self, fill_value: str, anneal_curve: str):
+        """Allocates offset curves A(s), B(s), C(s) over normalized anneal time s in GHz.
+
+        Arguments:
+            fill_value: If normalized time (s) is extended beyond (0, 1),
+                this option decides whether to extrapolate the anneal schedule,
+                or truncate it at the nearest value.
+                Options are "extrapolate" or "truncate".
+            anneal_curve: Curve normalized time follows.
+                Options are "linear", "logistic" or "dwave" (reads in excel file).
+
+        Raises:
+            KeyError: If one of the inputs is not reckognized
+        """
+        if anneal_curve == "linear":
+
+            self.anneal_schedule = {
+                "s": [0, 1],
+                "C (normalized)": [0, 1],
+                "A(s) (GHz)": [self.maxB, 0],
+                "B(s) (GHz)": [0, self.maxB],
+            }
+        elif anneal_curve == "logistic":
+            # DWave approx 10 GHz
+            s = linspace(0, 1)
+            self.anneal_schedule = {
+                "s": s,
+                "C (normalized)": s,
+                "A(s) (GHz)": self.maxB / (1.0 + exp(10.0 * (s - 0.5))),
+                "B(s) (GHz)": self.maxB / (1.0 + exp(-10.0 * (s - 0.5))),
+            }
+        elif anneal_curve == "dwave":
+            anneal_schedule = read_excel(
[…]

### 2020-03-30 Notes/Notes.tex
ground states normalization in notes

@@
 \begin{align}
-P =\sum_i | \langle \psi (t)  | \mbox{gnd}_i \rangle |^2 ,
+P =\sum_{i\in G} | \langle \psi (t)  | \mbox{gnd}_i \rangle |^2 ,
 \end{align}
-where the summation runs over degenerated ground states.
+where $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace.
 
@@
 \end{align}
-where the projection operator onto the ground state subspace is $\pi_{\mbox{gnd}}=\sum_i |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
+where the projection operator onto the degenerated ground states subspace is $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
 

### 2020-03-30 qlp/tdse/__init__.py
Moved anneal schedule and plotting of it to schedule submodule

@@ -11,40 +11,7 @@ from pandas import read_excel
 
 import matplotlib.pyplot as plt
 
-from qlp.mds.mds_qlpdb import AnnealOffset
-
-from qlp.tdse.schedule import s_to_offset
-
-
-class AnnealSchedule:
-    def __init__(
-        self,
-        offset,
-        hi_for_offset,
-        offset_min,
-        offset_range,
-        fill_value="extrapolate",
-        anneal_curve="linear",
-        **kwargs,
-    ):
-        AO = AnnealOffset(offset)
-        self.offset_list, self.offset_tag = AO.fcn(
-            hi_for_offset, offset_min, offset_range
-        )
-        self.s2o = s_to_offset(fill_value, anneal_curve)
-
-    def C(self, s):
-        C = self.s2o.interpC(s)
-        C_offset = C + self.offset_list
-        return C_offset
-
-    def A(self, s):
-        C = self.C(s)
-        return self.s2o.interpA(C)
-
-    def B(self, s):
-        C = self.C(s)
-        return self.s2o.interpB(C)
+from qlp.tdse.schedule import AnnealSchedule
 
 
 class TDSE:
@@ -245,22 +212,6 @@ class pure_sol_interface:
     def __init__(self, y1):
         self.t = np.zeros((0))
         self.y = np.zeros((y1.size, 0))
-
-
-def plot_anneal_schedule(tdse, normalized_time):
-    plt.figure()
-    ax = plt.axes()
-    X = np.linspace(*normalized_time)
-    yA = np.array([tdse.AS.A(Xi) for Xi in X])
-    yB = np.array([tdse.AS.B(Xi) for Xi in X])
-    for qubit in range(len(yA[0])):
-        ax.errorbar(x=X, y=yA[:, qubit])
-        ax.errorbar(x=X, y=yB[:, qubit], ls="--")
-    ax.set_xlabel("normalized time")
-    ax.set_ylabel("energy/h [GHz]")
-    plt.savefig("./coefficient.pdf")
-    plt.draw()
-    plt.show()
 
 
 def embed_qubo_example(nvertices):

### 2020-03-30 qlp/tdse/schedule.py

@@ -2,11 +2,15 @@
 
 """Functions and classes which define TDSE anneal schedule setups
 """
-from numpy import linspace, exp
+from typing import Optional
+
+from numpy import linspace, exp, array
 from scipy.interpolate import interp1d
 from pandas import read_excel
 
-from matplotlib.pyplot import subplots, draw, show
+from matplotlib.pyplot import subplots, draw, show, savefig
+
+from qlp.mds.mds_qlpdb import AnnealOffset
 
 
 class s_to_offset:
@@ -141,5 +145,69 @@ class s_to_offset:
             / self.anneal_schedule["B(s) (GHz)"].max(),
         )
         ax.errorbar(x=x, y=self.interpB(self.interpC(x)))
+        draw()
+        show()
+
+
+class AnnealSchedule:
+    def __init__(
+        self,
+        offset,
+        hi_for_offset,
+        offset_min,
+        offset_range,
+        fill_value="extrapolate",
+        anneal_curve="linear",
+        **kwargs,
+    ):
+        AO = AnnealOffset(offset)
+        self.offset_list, self.offset_tag = AO.fcn(
+            hi_for_offset, offset_min, offset_range
+        )
+        self.s2o = s_to_offset(fill_value, anneal_curve)
+
+    def C(self, s):
+        C = self.s2o.interpC(s)
+        C_offset = C + self.offset_list
+        return C_offset
+
+    def A(self, s):
+        C = self.C(s)
+        return self.s2o.interpA(C)
+
+    def B(self, s):
+        C = self.C(s)
+        return self.s2o.interpB(C)
+
+    def plot(
+        self,
+        normalized_time: float,
+        ax: Optional["Axes"] = None,
+        outfile: Optional[str] = "./coefficient.pdf",
+        **kwargs,
+    ):
+        """Plots the anneal schedule for A(s) and B(s).
+
+        Arguments:
+            normalized_time: End value for s
+            ax: Axes to plot in. If not given, creates new one.
+            outfile: Store result to file if given.
+            kwargs: For errorbar plot.
+            """
+        if ax is None:
+            _, ax = subplots()
+
+        X = linspace(*normalized_time)
+        yA = array([self.A(Xi) for Xi in X])
+        yB = array([self.B(Xi) for Xi in X])
+        for qubit in range(len(yA[0])):
+            ax.errorbar(x=X, y=yA[:, qubit], **kwargs)
[…]

### 2020-03-30 qlp/tdse/schedule.py
Updated docs

@@ -1,10 +1,10 @@
-# pylint: disable=C0103, R0903
+# pylint: disable=C0103, R0903, R0913
 
 """Functions and classes which define TDSE anneal schedule setups
 """
 from typing import Optional
 
-from numpy import linspace, exp, array
+from numpy import linspace, exp, array, ndarray
 from scipy.interpolate import interp1d
 from pandas import read_excel
 
@@ -14,7 +14,8 @@ from qlp.mds.mds_qlpdb import AnnealOffset
 
 
 class s_to_offset:
-    """Class which provides anneal curves for A(s), B(s), C(s) over normalized
+    """Class which provides anneal curves for A(s) (original Hamiltonian coefficient),
+    B(s) (final Hamiltonian coefficient) and C(s) (anneal time) over normalized
     anneal time s in GHz.
 
     Attributes:
@@ -23,11 +24,11 @@ class s_to_offset:
         anneal_schedule: Dict[str, List[int, int]]
             Boundaries for anneal parameters.
         interpA: np.ndarray
-            Interpolated curve for C(s) in GHz.
+            Interpolated curve for A(s) in GHz.
         interpB: np.ndarray
-            Interpolated curve for C(s) in GHz.
+            Interpolated curve for B(s) in GHz.
         interpC: np.ndarray
-            Interpolated curve for C(s) in GHz.
+            Interpolated curve for C(s).
     """
 
     maxB = 11.8604700
@@ -150,32 +151,49 @@ class s_to_offset:
 
 
 class AnnealSchedule:
+    """Class for obtaining anneal parameters for given anneal schedule parameters.
+    """
+
     def __init__(
         self,
         offset,
         hi_for_offset,
         offset_min,
         offset_range,
-        fill_value="extrapolate",
-        anneal_curve="linear",
+        fill_value: str = "extrapolate",
+        anneal_curve: str = "linear",
         **kwargs,
     ):
+        """Initializes offset curves
+
+        Arguments:
+            offset, hi_for_offset, offset_min, offset_range: Parameters for AnnealOffset
+            fill_value, anneal_curve: Parameters for s_to_offset
+        """
         AO = AnnealOffset(offset)
         self.offset_list, self.offset_tag = AO.fcn(
             hi_for_offset, offset_min, offset_range
         )
         self.s2o = s_to_offset(fill_value, anneal_curve)
 
-    def C(self, s):
+    def C(self, s: float) -> ndarray:
+        """Returns anneal time for given normalized time including offset
+        """
[…]

### 2020-03-30 qlp/tdse/schedule.py
Linting

@@ -154,7 +154,7 @@ class AnnealSchedule:
     """Class for obtaining anneal parameters for given anneal schedule parameters.
     """
 
-    def __init__(
+    def __init__(  # pylint: disable=W0613
         self,
         offset,
         hi_for_offset,

### 2020-03-30 qlp/tdse/__init__.py
Moved embedding to example module

@@ -12,6 +12,7 @@ from pandas import read_excel
 import matplotlib.pyplot as plt
 
 from qlp.tdse.schedule import AnnealSchedule
+from qlp.tdse.example import embed_qubo_example
 
 
 class TDSE:
@@ -212,35 +213,3 @@ class pure_sol_interface:
     def __init__(self, y1):
         self.t = np.zeros((0))
         self.y = np.zeros((y1.size, 0))
-
-
-def embed_qubo_example(nvertices):
-    if nvertices == 2:
-        """This is a NN(2) graph embedded in Chimera"""
-        q = """640 640 2.5
-641 641 6.0
-643 643 6.0
-645 645 -3.0
-647 647 10.5
-640 645 8.0
-641 645 -4.0
-643 645 -4.0
-640 647 -16.0
-641 647 -4.0
-643 647 -4.0"""
-        embedding = {0: [645], 1: [647, 640], 2: [641], 3: [643]}
-    else:
-        raise ValueError("No embedded graph defined.")
-    q = np.array([[float(i) for i in qn.split(" ")] for qn in q.split("\n")])
-    from scipy.sparse import dok_matrix
-
-    remap = {
-        key: idx
-        for idx, key in enumerate(np.unique(np.concatenate((q[:, 0], q[:, 1]), axis=0)))
-    }
-    qubo = dok_matrix((len(np.unique(q[:, 0])), len(np.unique(q[:, 0]))), dtype=float)
-    for qi in q:
-        i = remap[qi[0]]
-        j = remap[qi[1]]
-        qubo[i, j] = qi[2]
-    return qubo, embedding

### 2020-03-30 qlp/tdse/computation.py
Started to work on computation parts

@@ -1,0 +1,211 @@
+# pylint: disable=C0103, R0903
+"""Library to solve the time dependent schrodinger equation in the many-body Fock space.
+
+This module contains the core computations
+"""
+import numpy as np
+from numpy.linalg import eigh
+
+from scipy.integrate import solve_ivp
+
+from qlp.tdse.schedule import AnnealSchedule
+
+
+class TDSE:
+    def __init__(self, n, ising_params, offset_params, solver_params):
+        self.n = n
+        self.ising = ising_params
+        self.offset_params = offset_params
+        self.solver_params = solver_params
+        self.id2, self.sigx, self.sigz = self.pauli()
+        self.FockX, self.FockZ, self.FockZZ = self.init_Fock()
+        self.AS = AnnealSchedule(**offset_params)
+        self.IsingH = self.constructIsingH(
+            self.Bij(self.AS.B(1)) * self.ising["Jij"], self.AS.B(1) * self.ising["hi"]
+        )
+
+    def tdse(self, t, y):
+        """Define time-dependent Schrodinger equation"""
+        f = -1j * np.dot(self.annealingH(t), y)
+        return f
+
+    def pauli(self):
+        """Pauli matrices"""
+        sigx = np.zeros((2, 2))
+        sigz = np.zeros((2, 2))
+        id2 = np.identity(2)
+        sigx[0, 1] = 1.0
+        sigx[1, 0] = 1.0
+        sigz[0, 0] = 1.0
+        sigz[1, 1] = -1.0
+        return id2, sigx, sigz
+
+    def ground_state_degeneracy(self, H, degeneracy_tol=1e-6, debug=False):
+        eigval, eigv = eigh(H)
+        mask = [abs((ei - eigval[0]) / eigval[0]) < degeneracy_tol for ei in eigval]
+        gs_idx = np.arange(len(eigval))[mask]
+        if debug:
+            print(
+                f"Num. degenerate states @ s={self.offset_params['normalized_time'][1]}: {len(gs_idx)}"
+            )
+        return gs_idx, eigval, eigv
+
+    def calculate_overlap(self, psi1, psi2, degen_idx):
+        overlap = sum(
+            np.absolute([np.dot(np.conj(psi1[:, idx]), psi2) for idx in degen_idx]) ** 2
+        )
+        return overlap
+
+    def init_eigen(self, type):
+        if type == "true":
+            # true ground state
+            eigvalue, eigvector = eigh(
[…]

### 2020-03-30 qlp/tdse/__init__.py
Started to work on computation parts

@@ -1,215 +1,6 @@
-# pylint: disable=C0103, R0903
 """Library to solve the time dependent schrodinger equation in the many-body Fock space.
 """
-import numpy as np
-from numpy.linalg import eigh
-
-from scipy.integrate import solve_ivp
-from scipy.interpolate import interp1d
-
-from pandas import read_excel
-
-import matplotlib.pyplot as plt
 
 from qlp.tdse.schedule import AnnealSchedule
 from qlp.tdse.example import embed_qubo_example
-
-
-class TDSE:
-    def __init__(self, n, ising_params, offset_params, solver_params):
-        self.n = n
-        self.ising = ising_params
-        self.offset_params = offset_params
-        self.solver_params = solver_params
-        self.id2, self.sigx, self.sigz = self.pauli()
-        self.FockX, self.FockZ, self.FockZZ = self.init_Fock()
-        self.AS = AnnealSchedule(**offset_params)
-        self.IsingH = self.constructIsingH(
-            self.Bij(self.AS.B(1)) * self.ising["Jij"], self.AS.B(1) * self.ising["hi"]
-        )
-
-    def tdse(self, t, y):
-        """Define time-dependent Schrodinger equation"""
-        f = -1j * np.dot(self.annealingH(t), y)
-        return f
-
-    def pauli(self):
-        """Pauli matrices"""
-        sigx = np.zeros((2, 2))
-        sigz = np.zeros((2, 2))
-        id2 = np.identity(2)
-        sigx[0, 1] = 1.0
-        sigx[1, 0] = 1.0
-        sigz[0, 0] = 1.0
-        sigz[1, 1] = -1.0
-        return id2, sigx, sigz
-
-    def ground_state_degeneracy(self, H, degeneracy_tol=1e-6, debug=False):
-        eigval, eigv = eigh(H)
-        mask = [abs((ei - eigval[0]) / eigval[0]) < degeneracy_tol for ei in eigval]
-        gs_idx = np.arange(len(eigval))[mask]
-        if debug:
-            print(
-                f"Num. degenerate states @ s={self.offset_params['normalized_time'][1]}: {len(gs_idx)}"
-            )
-        return gs_idx, eigval, eigv
-
-    def calculate_overlap(self, psi1, psi2, degen_idx):
-        overlap = sum(
-            np.absolute([np.dot(np.conj(psi1[:, idx]), psi2) for idx in degen_idx]) ** 2
-        )
-        return overlap
-
-    def init_eigen(self, type):
-        if type == "true":
[…]

### 2020-03-30 qlp/tdse/computation.py
Started to resolve linter warnings

@@ -1,4 +1,4 @@
-# pylint: disable=C0103, R0903
+# pylint: disable=C0103, R0902, R0903
 """Library to solve the time dependent schrodinger equation in the many-body Fock space.
 
 This module contains the core computations
@@ -11,14 +11,30 @@ from scipy.integrate import solve_ivp
 from qlp.tdse.schedule import AnnealSchedule
 
 
+def _set_up_pauli():
+    """Creates Pauli matrices and identity
+    """
+    sigx = np.zeros((2, 2))
+    sigz = np.zeros((2, 2))
+    id2 = np.identity(2)
+    sigx[0, 1] = 1.0
+    sigx[1, 0] = 1.0
+    sigz[0, 0] = 1.0
+    sigz[1, 1] = -1.0
+    return id2, sigx, sigz
+
+
+ID2, SIG_X, SIG_Z = _set_up_pauli()
+
+
 class TDSE:
     def __init__(self, n, ising_params, offset_params, solver_params):
         self.n = n
         self.ising = ising_params
         self.offset_params = offset_params
         self.solver_params = solver_params
-        self.id2, self.sigx, self.sigz = self.pauli()
         self.FockX, self.FockZ, self.FockZZ = self.init_Fock()
+        self.Focksize = None
         self.AS = AnnealSchedule(**offset_params)
         self.IsingH = self.constructIsingH(
             self.Bij(self.AS.B(1)) * self.ising["Jij"], self.AS.B(1) * self.ising["hi"]
@@ -28,17 +44,6 @@ class TDSE:
         """Define time-dependent Schrodinger equation"""
         f = -1j * np.dot(self.annealingH(t), y)
         return f
-
-    def pauli(self):
-        """Pauli matrices"""
-        sigx = np.zeros((2, 2))
-        sigz = np.zeros((2, 2))
-        id2 = np.identity(2)
-        sigx[0, 1] = 1.0
-        sigx[1, 0] = 1.0
-        sigz[0, 0] = 1.0
-        sigz[1, 1] = -1.0
-        return id2, sigx, sigz
 
     def ground_state_degeneracy(self, H, degeneracy_tol=1e-6, debug=False):
         eigval, eigv = eigh(H)
@@ -50,19 +55,19 @@ class TDSE:
             )
         return gs_idx, eigval, eigv
 
-    def calculate_overlap(self, psi1, psi2, degen_idx):
-        overlap = sum(
+    @staticmethod
+    def calculate_overlap(psi1, psi2, degen_idx):
+        return sum(
[…]

### 2020-03-30 qlp/tdse/computation.py
Started documenting main class

@@ -3,6 +3,9 @@
 
 This module contains the core computations
 """
+from typing import Dict, Any
+
+from numpy import ndarray
 import numpy as np
 from numpy.linalg import eigh
 
@@ -28,7 +31,38 @@ ID2, SIG_X, SIG_Z = _set_up_pauli()
 
 
 class TDSE:
-    def __init__(self, n, ising_params, offset_params, solver_params):
+    """Time dependent Schrödinger equation solver class
+
+    Usage:
+    ```
+    tdse = TDSE(n, ising_params, offset_params, solver_params)
+
+    # Get thermodynamical state density
+    temperature=15e-3
+    initial_wavefunction = "true"
+    rho = tdse.init_densitymatrix(temperature, initial_wavefunction)
+
+    # Compute anneal
+    sol_densitymatrix = tdse.solve_mixed(rho)
+    ```
+    """
+
+    def __init__(
+        self,
+        n: int,
+        ising_params: Dict[str, Any],
+        offset_params: Dict[str, Any],
+        solver_params: Dict[str, Any],
+    ):
+        """Init the class with
+
+        Arguments:
+            n: Number of qubits
+            ising_params: Parameters for the ising model, e.g., keys are
+                {"Jij", "hi", "c", "energyscale"}.
+            offset_params: Parameters for AnnealSchedule
+            solver_params: Parameters for solve_ivp
+        """
         self.n = n
         self.ising = ising_params
         self.offset_params = offset_params
@@ -40,10 +74,9 @@ class TDSE:
             self.Bij(self.AS.B(1)) * self.ising["Jij"], self.AS.B(1) * self.ising["hi"]
         )
 
-    def tdse(self, t, y):
-        """Define time-dependent Schrodinger equation"""
-        f = -1j * np.dot(self.annealingH(t), y)
-        return f
+    def apply_H(self, t, psi: ndarray) -> ndarray:
+        """Computes `i H(t) psi`"""
+        return -1j * np.dot(self.annealingH(t), psi)
 
     def ground_state_degeneracy(self, H, degeneracy_tol=1e-6, debug=False):
         eigval, eigv = eigh(H)
@@ -168,7 +201,7 @@ class TDSE:
         for jj in range(ngrid - 1):
             y1 = y1 / (np.sqrt(np.absolute(np.dot(np.conj(y1), y1))))
             tempsol = solve_ivp(
[…]

### 2020-03-30 qlp/tdse/computation.py
Started documenting TDSE class and hiding of memebers which are internal only

@@ -3,7 +3,7 @@
 
 This module contains the core computations
 """
-from typing import Dict, Any
+from typing import Dict, Any, Tuple
 
 from numpy import ndarray
 import numpy as np
@@ -67,14 +67,14 @@ class TDSE:
         self.ising = ising_params
         self.offset_params = offset_params
         self.solver_params = solver_params
-        self.FockX, self.FockZ, self.FockZZ = self.init_Fock()
+        self.FockX, self.FockZ, self.FockZZ = self._init_Fock()
         self.Focksize = None
         self.AS = AnnealSchedule(**offset_params)
-        self.IsingH = self.constructIsingH(
-            self.Bij(self.AS.B(1)) * self.ising["Jij"], self.AS.B(1) * self.ising["hi"]
+        self.IsingH = self._constructIsingH(
+            self._Bij(self.AS.B(1)) * self.ising["Jij"], self.AS.B(1) * self.ising["hi"]
         )
 
-    def apply_H(self, t, psi: ndarray) -> ndarray:
+    def _apply_H(self, t, psi: ndarray) -> ndarray:
         """Computes `i H(t) psi`"""
         return -1j * np.dot(self.annealingH(t), psi)
 
@@ -94,7 +94,11 @@ class TDSE:
             np.absolute([np.dot(np.conj(psi1[:, idx]), psi2) for idx in degen_idx]) ** 2
         )
 
-    def init_eigen(self, dtype):
+    def init_eigen(self, dtype: str) -> Tuple[ndarray, ndarray]:
+        """Computes eigenvalue and vector of initial Hamiltonian either as a pure
+        eigenstate of `H_init` (transverse) or a s a superposition of
+        `A(s) H_init + B(s) H_final` (true).
+        """
         if dtype == "true":
             # true ground state
             eigvalue, eigvector = eigh(
@@ -105,19 +109,31 @@ class TDSE:
             eigvalue, eigvector = eigh(
                 -1
                 * self.ising["energyscale"]
-                * self.constructtransverseH(self.AS.A(0) * np.ones(self.n))
+                * self._constructtransverseH(self.AS.A(0) * np.ones(self.n))
             )
         else:
             raise TypeError("Undefined initial wavefunction.")
         return eigvalue, eigvector
 
-    def init_wavefunction(self, dtype="transverse"):
+    def init_wavefunction(self, dtype="transverse") -> ndarray:
[…]

### 2020-04-02 Notes/Notes.tex
Updated notes to @lastyoru and @cchang5 comments.  This addresses #1

@@
 \begin{align}
-i \partial_t \psi(t) = H(t) \psi(t) .
+i \hbar \partial_t \psi(t) = H(t) \psi(t) .
 \end{align}
@@
 \end{align}
-where $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace.
+where $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis, e.g. $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$,  for the degenerated ground states subspace.
 
@@
 \begin{align}
-i \partial_t \rho (t) = [H(t) , \rho(t)] ,
+i \hbar \partial_t \rho (t) = [H(t) , \rho(t)] ,
 \end{align}
@@
 \subsection{Simulating DWave}
-We allow the ability to define arbitrary annealing schedules as shown in Fig.~\ref{fig:anneal_schedules}.
-We also allow for per qubit offsets as suggested by Eq.~(\ref{eq:annealH}), with an example annealing schedule shown in Fig.~\ref{fig:anneal_offset} as well.
-For DWave's implementation, anneal offset yields systematic errors because the qubits no longer all start and end with the same coefficients.
-For our simulation, we allow for extended anneal schedules, which allow all qubits to undergo the full annealing process, yielding a true temporal offset for inhomogeneous driving fields.
+To simulate DWave, we have to consider multiple systematic effects which cause deviation from exact solutions of the Schrödinger equation.
+For example, interactions of the final Hamiltonian are present at the beginning of the anneal schedule due to non-zero anneal coefficients $B(s)$.
+We expect a contamination of the ground state at the order of $B(0) \sim 5\%$ and allow to include these effects in our simulation by computing the ground state of the pure (only $H_\mathrm{init}$) or mixed (both $A(0) H_\mathrm{init} + B(0) H_\mathrm{final}$) system.
+The Hamiltonian at the end of the anneal is less contaminated with $A(1) \sim 10^{-7}$.
+In our simulation we also allow to define arbitrary annealing schedules as shown in Fig.~\ref{fig:anneal_schedules}.
+
+Another systematic error is introduced when allowing different qubit-wise anneal schedules $A(s) \to A_i(s)$ and $B(s) \to B_i(s)$.
+If $B_i(0) \neq B_j(0)$ for $i \neq j$ the initial Hamiltonian, and if $B_i(1) \neq B_j(1)$ for $i \neq j$ the final Hamiltonian is effectively different from what was implemented.
+Therefore shifted anneal schedules on DWave cannot be set too large.
+It in principle possible to extend the anneal schedule beyond the range $s \in [s_I, s_F]$ with $s_I < 0$ and $s_F > 1$ such that, depending on how the $B_i$ are extrapolated, $B_i(s_I) = B_j(s_I)$ and $B_i(s_F) = B_j(s_F)$ for $i \neq j$ and equivalently for the $A_i$.
+We also allow our simulations to incorporate different qubit offsets as suggested by Eq.~(\ref{eq:annealH}), with an example annealing schedule shown in Fig.~\ref{fig:anneal_offset} as well.
+Additionally, we allow for extended anneal schedules, which allow all qubits to undergo the full annealing process, yielding a true temporal offset for inhomogeneous driving fields.
 

### 2020-04-02 Notes/Notes.tex
small update to Notes

@@
 Therefore shifted anneal schedules on DWave cannot be set too large.
+We also allow our simulations to incorporate different qubit offsets as suggested by Eq.~(\ref{eq:annealH}), with an example annealing schedule shown in Fig.~\ref{fig:anneal_offset} as well.
 It in principle possible to extend the anneal schedule beyond the range $s \in [s_I, s_F]$ with $s_I < 0$ and $s_F > 1$ such that, depending on how the $B_i$ are extrapolated, $B_i(s_I) = B_j(s_I)$ and $B_i(s_F) = B_j(s_F)$ for $i \neq j$ and equivalently for the $A_i$.
-We also allow our simulations to incorporate different qubit offsets as suggested by Eq.~(\ref{eq:annealH}), with an example annealing schedule shown in Fig.~\ref{fig:anneal_offset} as well.
-Additionally, we allow for extended anneal schedules, which allow all qubits to undergo the full annealing process, yielding a true temporal offset for inhomogeneous driving fields.
+Therefore, we allow for extended anneal schedules, which allow all qubits to undergo the full annealing process, yielding a true temporal offset for inhomogeneous driving fields.
 
@@
 A quick study below.
-We run a simulation with anneal offsets similar to what we ran on DWave (Fig.~\ref{dwave_result}).
+We run a simulation with anneal offsets similar to what we ran on DWave (Fig.~\ref{fig:dwave_result}).
 We see that if we apply a delay on qubits with small values and advance qubits with of $h_i$ (binary), then the performance improves.

### 2020-04-02 qlp/tdse/computation.py
moved correlatioin calculation to TDSE class. @ccchen please check

@@ -327,3 +327,44 @@ class TDSE:
         return solve_ivp(
             self._apply_tdse_dense2, self.offset_params["normalized_time"], rho
         )
+
+    # Compute Correlations
+    # One time correlation function
+    def cZ(self, ti, xi, sol_densitymatrix):
+        return np.trace(
+            np.dot(
+                self.FockZ[xi],
+                sol_densitymatrix.y[:, ti].reshape(2 ** self.n, 2 ** self.n),
+            )
+        )
+
+    def cZZ(self, ti, xi, xj, sol_densitymatrix):
+        return np.trace(
+            np.dot(
+                self.FockZZ[xi][xj],
+                sol_densitymatrix.y[:, ti].reshape(2 ** self.n, 2 ** self.n),
+            )
+        )
+
+    def cZZd(self, ti, xi, xj, sol_densitymatrix):
+        return self.cZZ(ti, xi, xj, sol_densitymatrix) - self.cZ(
+            ti, xi, sol_densitymatrix
+        ) * self.cZ(ti, xj, sol_densitymatrix)
+
+    # Two time correlation function
+    # http://qutip.org/docs/latest/guide/guide-correlation.html
+    def cZZt2(self, ti, xi, sol_densitymatrixt2):
+        return np.trace(
+            np.dot(
+                self.FockZ[xi],
+                sol_densitymatrixt2.y[:, ti].reshape(2 ** self.n, 2 ** self.n),
+            )
+        )
+
+    def cZZt2d(self, ti, xi, tj, xj, sol_densitymatrix, sol_densitymatrixt2):
+        return np.trace(
+            np.dot(
+                self.FockZ[xi],
+                sol_densitymatrixt2.y[:, ti].reshape(2 ** self.n, 2 ** self.n),
+            )
+        ) - self.cZ(ti, xi, sol_densitymatrix) * self.cZ(tj, xj, sol_densitymatrix)

### 2020-05-04 Notes/Notes.tex

@@
 
+To include the decoherence effects, we solve for master equation in Lindblad form
+\begin{align}
+i \hbar \partial_t \rho (t) = [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
+\end{align}
+where $L_j$ are the Lindblad operators for decoherence.
+In this study we only include lowest order approximation, i.e., the amplitude damping for non-interacting qubits.
+The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^\pm_j $, where $\gamma=1/T_1$ is the decoherence rate for relaxation time $T_1$.
+For simplicity we assume all qubits having the same relaxation time.
+
 \subsection{unit conversion}

### 2020-05-04 paper/figures/qlpdb_plots.py
plots

@@ -147,3 +147,5 @@ if __name__ == "__main__":
 
     # single_histogram(nndata)
     plot_prob(nndata, nndata2, nndata3)
+
+

### 2020-05-04 qlp/tdse/computation.py

@@ -634,7 +634,18 @@ class TDSE:
                 idx += 1
                 nA += 1
         einidx = einidx1 + einidx2
-        return nA, einidx
+        ridx1 = ''
+        ridx2 = ''
+        for idx, eidx in enumerate(einidx1):
+            if eidx != einidx2[idx]:
+                ridx1 += eidx
+                ridx2 += einidx2[idx]
+            else:
+                pass
+        ridx = ridx1 + ridx2
+        esum = f"{einidx}->{ridx}"
+        print(esum)
+        return nA, esum
 
 
 @jit(nopython=True)

### 2020-05-05 paper/figures/tdse_plots.py
setup pure binary offset run

@@ -1,6 +1,8 @@
 import matplotlib.pyplot as plt
 import pickle
 
+import numpy as np
+
 from qlpdb.tdse.models import Tdse
 
 from qlp.mds.mds_qlpdb import graph_summary
@@ -29,6 +31,7 @@ class Data():
         wave_params = dict()
         wave_params["type"] = "mixed"
         wave_params["temp"] = 50E-3
+        wave_params["gamma"] = 0.05
         wave_params["initial_wavefunction"] = "transverse"
 
         # graph params
@@ -87,28 +90,96 @@ def aggregate():
         data.params["offset"]["offset_min"] = offset
         data.params["offset"]["offset_range"] = abs(offset)*2
         adata[abs(offset)] = data.get_data()
-        with open(f"{settings.MEDIA_ROOT}/{adata[offset].solution}", "rb") as file:
+        with open(f"{settings.MEDIA_ROOT}/{adata[abs(offset)].solution}", "rb") as file:
             adata[abs(offset)].sol = pickle.load(file)
-        with open(f"{settings.MEDIA_ROOT}/{adata[offset].instance}", "rb") as file:
+        with open(f"{settings.MEDIA_ROOT}/{adata[abs(offset)].instance}", "rb") as file:
             adata[abs(offset)].tdse = pickle.load(file)
     return adata
 
+def aggregate_gamma():
+    adata = dict()
+    data = Data()
+    for gamma in [0.001, 0.01, 0.015, 0.02, 0.03, 0.035, 0.04, 0.045, 0.05, 0.055, 0.06, 0.065, 0.07, 0.075, 0.1, 1]:
+        data.params["wave"]["gamma"] = gamma
+        adata[gamma] = data.get_data()
+        with open(f"{settings.MEDIA_ROOT}/{adata[gamma].solution}", "rb") as file:
+            adata[gamma].sol = pickle.load(file)
+        with open(f"{settings.MEDIA_ROOT}/{adata[gamma].instance}", "rb") as file:
+            adata[gamma].tdse = pickle.load(file)
+    return adata
+
 def plot_aggregate(adata):
-    plt.figure("probability")
+    plt.figure("full probability")
     ax = plt.axes([0.15, 0.15, 0.8, 0.8])
     for key in adata:
         ax.errorbar(x=adata[key].time, y=adata[key].prob, label=key)
[…]

### 2020-05-05 qlp/mds/mds_qlpdb.py

@@ -22,6 +22,7 @@ class AnnealOffset:
         self.graph_params = graph_params
 
     def fcn(self, h, offset_min, offset_range):
+        h = np.array(h)
         abshrange = max(abs(h)) - min(abs(h))
         fullrange = max(h) - min(h)
 
@@ -54,7 +55,11 @@ class AnnealOffset:
                 if abs(hi) <= hmid:
                     offset_fcn.append(offset_min)
                 else:
-                    offset_fcn.append(offset_min + offset_range)
+                    if offset_min < 0:
+                        offset_fcn.append(offset_min + offset_range)
+                    else:
+                        offset_fcn.append(offset_min - offset_range)
+            print(offset_fcn, offset_tag)
             return offset_fcn, offset_tag
         if self.tag == "negbinary":
             offset_tag = f"FixEmbedding_NegBinary_{offset_min}_{offset_range}_v3_1"
@@ -64,7 +69,11 @@ class AnnealOffset:
                 if abs(hi) >= hmid:
                     offset_fcn.append(offset_min)
                 else:
-                    offset_fcn.append(offset_min + offset_range)
+                    if offset_min < 0:
+                        offset_fcn.append(offset_min + offset_range)
+                    else:
+                        offset_fcn.append(offset_min - offset_range)
+            print(offset_fcn, offset_tag)
             return offset_fcn, offset_tag
         if self.tag == "shiftlinear":
             offset_tag = f"FixEmbedding_ShiftLinear_{offset_min}_{offset_range}"

### 2020-05-05 qlp/tdse/computation.py

@@ -585,6 +585,7 @@ class TDSE:
         tensorrho = rho.reshape(
             tuple([2 for i in range(2 * self.graph["total_qubits"])])
         )
+        print(self.graph["total_qubits"])
         rhoA = np.einsum(indicesA, tensorrho)
         #print("rhoA")
         #print(type(rhoA))

### 2020-05-05 qlp/mds/mds_qlpdb.py
tag run as v4

@@ -48,7 +48,7 @@ class AnnealOffset:
                 f"FixEmbedding_Constant_{offset_min}_{offset_range}_v3_1",
             )
         if self.tag == "binary":
-            offset_tag = f"FixEmbedding_Binary_{offset_min}_{offset_range}_v3_1"
+            offset_tag = f"FixEmbedding_Binary_{offset_min}_{offset_range}_v4"
             offset_fcn = []
             hmid = abshrange * 0.5 + min(abs(h))
             for hi in h:

### 2020-05-05 qlp/mds/mds_qlpdb.py
spurious print statement

@@ -59,7 +59,6 @@ class AnnealOffset:
                         offset_fcn.append(offset_min + offset_range)
                     else:
                         offset_fcn.append(offset_min - offset_range)
-            print(offset_fcn, offset_tag)
             return offset_fcn, offset_tag
         if self.tag == "negbinary":
             offset_tag = f"FixEmbedding_NegBinary_{offset_min}_{offset_range}_v3_1"

### 2020-05-05 qlp/mds/mds_qlpdb.py
commit for manual scaling runs

@@ -48,7 +48,7 @@ class AnnealOffset:
                 f"FixEmbedding_Constant_{offset_min}_{offset_range}_v3_1",
             )
         if self.tag == "binary":
-            offset_tag = f"FixEmbedding_Binary_{offset_min}_{offset_range}_v4"
+            offset_tag = f"FixEmbedding_Binary_{offset_min}_{offset_range}_v5"
             offset_fcn = []
             hmid = abshrange * 0.5 + min(abs(h))
             for hi in h:
@@ -72,7 +72,6 @@ class AnnealOffset:
                         offset_fcn.append(offset_min + offset_range)
                     else:
                         offset_fcn.append(offset_min - offset_range)
-            print(offset_fcn, offset_tag)
             return offset_fcn, offset_tag
         if self.tag == "shiftlinear":
             offset_tag = f"FixEmbedding_ShiftLinear_{offset_min}_{offset_range}"

### 2020-05-05 qlp/tdse/computation.py

@@ -585,7 +585,6 @@ class TDSE:
         tensorrho = rho.reshape(
             tuple([2 for i in range(2 * self.graph["total_qubits"])])
         )
-        print(self.graph["total_qubits"])
         rhoA = np.einsum(indicesA, tensorrho)
         #print("rhoA")
         #print(type(rhoA))

### 2020-05-07 Notes/Notes.tex
setup pure binary offset run
fix Lindblad notes thanks to Chris

@@
 %opening
-\title{Notes}
+%\title{Notes}
 
@@
 \begin{align}
-i \hbar \partial_t \rho (t) = [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
+  \partial_t \rho (t) = - \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
 \end{align}
@@
 In this study we only include lowest order approximation, i.e., the amplitude damping for non-interacting qubits.
-The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^\pm_j $, where $\gamma=1/T_1$ is the decoherence rate for relaxation time $T_1$.
+The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma=1/T_1$ is the decoherence rate for relaxation time $T_1$.
 For simplicity we assume all qubits having the same relaxation time.

### 2020-05-08 paper/main.tex
paper outline

@@
 
-\subsubsection{Total Dominating Set}
-
 \section{DISCUSSION}
 
-\subsection{ILP Examples}
-
-Simple problems and scaling with problem size for single global solution.
-
-- number of constraint equations (slack variables)
-- range of integer values
-- number of variables
-- precision of problem (decimal places needed)
-
-Problems with degenerate minima
-
-- does D-Wave find them with expected distribution for very small systems?
-- at what problem size does this break?
-
-\subsection{Dominating Set}
+\subsection{Finding the Dominating Set with a Quantum Annealer}
 
@@
 
-\subsection{Total Domination with Quantum Annealing}
-
-Solve the total dominating set problem.
-
 This probably just involves making the inequality constraint > 1 instead of > 0.
 
+\subsection{Simulation Results}
+
+\subsection{Decoherence and Many-Body Localization}
+
 \section{METHODS}
+\subsection{Experiment Details}
+\subsubsection{Annealing Time Optimization}
 
-Might not be necessary to have this section.
+\subsubsection{Spin Reversal Transformation Optimization}
+
+\subsection{Simulation Details}
+\subsubsection{The Lindblad Equation}
+Say what the simulator is solving
+
+With anneal offsets
+
+\subsubsection{Other Simulation Details}
+Temperature
+Initial wave function choices
+RK tolerance
+
+\subsubsection{Decoherence Time}
+Scan over decoherence time
 

### 2020-05-08 paper/figures/tdse_plots.py

@@ -75,17 +75,26 @@ class Data():
 def aggregate():
     adata = dict()
     data = Data()
-    #for offset in [-0.05, -0.04, -0.03, -0.02, -0.01, 0.0]:
-    #    data.params["offset"]["offset"] = "negbinary"
-    #    data.params["offset"]["offset_min"] = offset
-    #    data.params["offset"]["offset_range"] = abs(offset)*2
-    #    adata[offset] = data.get_data()
-    #    with open(f"{settings.MEDIA_ROOT}/{adata[offset].solution}", "rb") as file:
-    #        adata[offset].sol = pickle.load(file)
-    #    with open(f"{settings.MEDIA_ROOT}/{adata[offset].instance}", "rb") as file:
-    #        adata[offset].tdse = pickle.load(file)
-    for offset in [0.05, 0.04, 0.03, 0.02, 0.01, 0.0, -0.0005, -0.001, -0.002,-0.004, -0.005, -0.01, -0.02, -0.03, -0.04, -0.05]:
+    #for offset in [0.05, 0.04, 0.03, 0.02, 0.01, 0.0, -0.0005, -0.001, -0.002,-0.004, -0.005, -0.01, -0.02, -0.03, -0.04, -0.05]:
+    #for offset in [0.04, -0.04]:
+    for offset in [0.0]:
         data.params["offset"]["offset"] = "binary"
+        data.params["offset"]["offset_min"] = offset
+        data.params["offset"]["offset_range"] = abs(offset)*2
+        adata[offset] = data.get_data()
+        with open(f"{settings.MEDIA_ROOT}/{adata[offset].solution}", "rb") as file:
+            adata[offset].sol = pickle.load(file)
+        with open(f"{settings.MEDIA_ROOT}/{adata[offset].instance}", "rb") as file:
+            adata[offset].tdse = pickle.load(file)
+    return adata
+
+def aggregate_nodeco():
+    adata = dict()
+    data = Data()
+    data.params["wave"]["gamma"] = 0.0
+    data.params["offset"]["offset"] = "binary"
+    #for offset in [0.05, 0.04, 0.03, 0.02, 0.01, 0.0, -0.01, -0.02, -0.03, -0.04, -0.05]:
+    for offset in [0.04, -0.04]:
         data.params["offset"]["offset_min"] = offset
         data.params["offset"]["offset_range"] = abs(offset)*2
         adata[offset] = data.get_data()
@@ -114,6 +123,9 @@ def plot_aggregate(adata):
[…]

### 2020-05-08 qlp/tdse/computation.py

@@ -584,7 +584,6 @@ class TDSE:
         tensorrho = rho.reshape(
             tuple([2 for i in range(2 * self.graph["total_qubits"])])
         )
-        print(np.shape(tensorrho))
         rhoA = np.einsum(indicesA, tensorrho)
         #print("rhoA")
         #print(type(rhoA))
@@ -592,9 +591,13 @@ class TDSE:
         matrhoA = rhoA.reshape(2 ** nA, 2 ** nA) + reg * np.identity(2 ** nA)
         #e,v=eigh(matrhoA)
         #print('eig rhoA',e)
-        print(np.shape(matrhoA))
-        raise SystemError
         s = -np.trace(matrhoA @ logm(matrhoA)) / np.log(2)
+        return s
+
+    def vonNeumann_entropy(self, rho, reg):
+        totaln = self.graph["total_qubits"]
+        matrho = rho.reshape(2 ** totaln, 2 ** totaln) + reg * np.identity(2 ** totaln)
+        s = -np.trace(matrho @ logm(matrho)) / np.log(2)
         return s
 
     def find_partition(self) -> Tuple[int, str]:

### 2020-05-08 paper/main.tex
reformat paper using revtex because i dont know how to use anything else

@@
-\documentclass[fleqn,10pt]{wlscirep}
+\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography]{revtex4}
 \usepackage[utf8]{inputenc}
@@
 
+\begin{document}
 \title{Solutions to Integer Programming from Quantum Annealing}
 
-\author[1,*]{Christopher K\"orber}
-\author[2]{Chia~Cheng~Chang}
-\author[3]{Chih-Chieh~Chen}
-\author[4]{Travis~Humble}
-\author[5]{Jim~Ostrowski}
-
-\affil[1]{Department of Physics, University of California, Berkeley, California 94720, USA}
-\affil[1]{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
-\affil[2]{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
-\affil[2]{Department of Physics, University of California, Berkeley, California 94720, USA}
-\affil[3]{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
-\affil[4]{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
-\affil[4]{University of Tennessee}
-\affil[*]{ckoerber@berkeley.edu}
+\author{Chia~Cheng~Chang}
+\affiliation{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
+\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
+\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
+\author{Chih-Chieh~Chen}
+\affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
+\author{Christopher K\"orber}
+\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
+\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
+\author{Travis~Humble}
+\affiliation{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
+\author{Jim~Ostrowski}
+\affiliation{University of Tennessee}
 
 \begin{abstract}
-\cite{Chang:2018uxx}
+Abstract here...
 \end{abstract}
 
-\begin{document}
+\preprint{LLNL-JRNL-809712, RIKEN-iTHEMS-Report-20}
+
+\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\tableofcontents
 
@@
 \begin{align}
-\chi^2 = & \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu + p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
+\chi^2 = & \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right. \nonumber\\
+&\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
 \Psi = & \begin{pmatrix}
@@
 \begin{align}
-Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x + \mathrm{Diag}_{\psi^x}(c) T^x,\\
+Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x \nonumber \\
+&+ \mathrm{Diag}_{\psi^x}(c) T^x,\\
 Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,\\
@@
 The target Hamiltonian can be written in the matrix form
+\begin{widetext}
 \begin{align}
@@
 \end{align}
+\end{widetext}
 where $ |M| \equiv \sum_{\nu} M_{\nu \mu}$.
@@
 \subsection{Finding the Dominating Set with a Quantum Annealer}
+
+\begin{figure}
+	\centering
+		\includegraphics[width=0.5\columnwidth]{./figures/linear_crop.pdf}
+	\caption{
+The
+	}
+	\label{fig:linear}
+\end{figure}
+
+We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.
 

### 2020-05-08 paper/main.tex
macbook wants to update... hopefully nothing breaks

@@
 	\end{tabular}
-	\caption{Example of different dominating sets for the Pleiades constellation $G(V, E)$.
+	\caption{Example of different dominating sets for $G(V, E)$.
 Vertices in the dominating set $D$ are highlighted in blue.
@@
 
-\begin{figure}
+\begin{figure}[b]
 	\centering
 		\includegraphics[width=0.5\columnwidth]{./figures/linear_crop.pdf}
-	\caption{
-The
-	}
+	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
 	\label{fig:linear}
@@
 We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.
+This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer.
+Additionally the MDS solution is known analytically, and contains both unique and degenerate solutions.
+In particular, the domination number for $G(n)$ is $\lceil n/3 \rceil$ while the number of MDS solutions for $n$ vertices is
+\begin{align}
+&1 &&\textrm{if} && n\textrm{ mod }3=0,\nonumber \\
+&2\lfloor n/3 \rfloor + 1 && \textrm{if}&& n\textrm{ mod }3=1,\nonumber \\
+&\lfloor n/3 \rfloor + 2 && \textrm{if} && n \textrm{ mod }3 = 2.
+\end{align}
 

### 2020-05-08 paper/main.tex
push for catalina update

@@
 &2\lfloor n/3 \rfloor + 1 && \textrm{if}&& n\textrm{ mod }3=1,\nonumber \\
-&\lfloor n/3 \rfloor + 2 && \textrm{if} && n \textrm{ mod }3 = 2.
+&\lfloor n/3 \rfloor + 2 && \textrm{if} && n \textrm{ mod }3 = 2,
 \end{align}
+and gives the probability of randomly guessing the MDS of $G(n)$.
 

### 2020-05-08 paper/main.tex
tired..

@@
 
-Demonstrate simple dominating set problem.
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/anneal_time_scaling.pdf}
+	\caption{Probability of finding the MDS for $G(6)$ as a function of total annealing time.}
+	\label{fig:at_scale}
+\end{figure}
 
-Study scaling with random graphs (but fixed number of vertices?)
+For the following studies, we perform experiments on the \texttt{DW\_2000Q\_5} solver.
+The annealing time is optimized to 400$\mu$s after performing a study on the $G(6)$ graph as shown in Fig.~\ref{fig:at_scale}.
+In Fig.~\ref{fig:baseline}, we show results from the baseline experiment, without modification to the default DWave annealing schedule, and observe improvement over random guessing.
+However, the experiment results reflect the same degeneracy structure as random guessing, and scale exponentially poorly for larger number of vertices $n$.
+We explore one avenue towards improving the experiment results by introducing per-qubit annealing offsets into the time evolution.
 
-This probably just involves making the inequality constraint > 1 instead of > 0.
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/scaling_baseline.pdf}
+	\caption{Baseline result of DWave (blue) compared to random guessing (red). The jagged nature of random guessing reflects the degeneracy of the ground state.}
+	\label{fig:baseline}
+\end{figure}
+
+\subsubsection{Modified annealing schedule}
+
+In quantum annealing, the ground state of the problem Hamiltonian is obtained from the evolution of a time-dependent Hamiltonian,
+\begin{equation}
+H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}},
+\end{equation}
+where $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, and $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
+The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ on the DWave.
+On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits.
+In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in addition to the effects of applying positive and negative offsets.
+Note that due to the way the offsets are implemented on the hardware level, systematic errors are introduced since the initial and final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
+Fig.~\ref{fig:anneal_schedule} shows the maximum offset that we use for the study, which translates to approximately (due to non-linearity) a 5\% advancement (blue) or delay (red) in the schedule.
+
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/anneal_schedule.pdf}
+	\caption{asdf}
+	\label{fig:anneal_schedule}
+\end{figure}
+
+The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system in general will exhibit more disorder.
+We define disorder by first recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
+\begin{equation}
+H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
+\end{equation}
+and recognize that in the limit where $h_i$ is randomly drawn from a Bernoulli distribution we recover the spin-glass model.
+The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization.
+
+{\color{red} Should we talk about exponential damping here too? as a competing effect.}
+
+Following this logic, we split the qubits into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific problem.
+We then symmetrically offset the two groups of qubits over a total range between 0\% and 10\% (-5\% to +5\%).
+The results of this study is shown in Fig.~\ref{fig:dwave_offset}.
+
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/scaling_comparison_all.pdf}
+	\caption{The legend labels the total range of the symmetric offset employed.
+A positive range indicates that the group of qubits with small values of $|h_i|$ are advanced (qubits with large values of $|h_i|$ are equivalently delayed), and vice versa for results labeled with a negative range.}
+	\label{fig:dwave_offset}
+\end{figure}
+
+Finally, we note that due to the inherent variance in performance when using different physical qubits, for each graph, we perform the offset study on the same physical qubits.
 
@@
 \section{METHODS}
-\subsection{Experiment Details}
-\subsubsection{Annealing Time Optimization}
-
-\subsubsection{Spin Reversal Transformation Optimization}
-
 \subsection{Simulation Details}

### 2020-05-08 paper/figures/ta_plots.py

@@ -85,7 +85,7 @@ def plotta(data):
     fig = plt.figure("scaling", figsize=(7, 4))
     ax = plt.axes([0.15, 0.15, 0.8, 0.8])
     ax.errorbar(x=X, y=y, marker="o", color=red, **errorbar_params)
-    ax.fill_between(x=X, y1=yerr1, y2=yerr2, color=red, alpha=0.5)
+    #ax.fill_between(x=X, y1=yerr1, y2=yerr2, color=red, alpha=0.5)
     ax.set_xscale("log")
     ax.set_ylabel("MDS probability")
     ax.set_xlabel("anneal time (microseconds)")
@@ -313,16 +313,42 @@ def plot_compare_all(data02, data04, data06, data08, data10):
     fig = plt.figure("scaling compare", figsize=(7, 4))
     ax = plt.axes([0.15, 0.15, 0.8, 0.8])
     X = np.arange(len(data10["Constant"]))+2
-    ax.errorbar(x=X, y=data10["Binary"], label="Binary 0.10", color=red, **errorbar_params)
-    ax.errorbar(x=X, y=data08["Binary"], label="Binary 0.08", color=green, **errorbar_params)
-    ax.errorbar(x=X, y=data06["Binary"], label="Binary 0.06", color=blue, **errorbar_params)
-    ax.errorbar(x=X, y=data04["Binary"], label="Binary 0.04", color=red, ls='--', **errorbar_params)
-    ax.errorbar(x=X, y=data02["Binary"], label="Binary 0.02", color=green, ls='--', **errorbar_params)
-    ax.errorbar(x=X, y=data10["Constant"], label="Constant", color=blue, ls='--', **errorbar_params)
+    ax.errorbar(x=X, y=data10["Binary"], label="-10%", color=green, ls='-', **errorbar_params)
+    ax.errorbar(x=X, y=data08["Binary"], label="-8%", color=red, ls=':', **errorbar_params)
+    ax.errorbar(x=X, y=data06["Binary"], label="-6%", color=red, ls='-.', **errorbar_params)
+    ax.errorbar(x=X, y=data04["Binary"], label="-4%", color=red, ls='--', **errorbar_params)
+    ax.errorbar(x=X, y=data02["Binary"], label="-2%", color=red, ls='-', **errorbar_params)
+    ax.errorbar(x=X, y=data10["Constant"], label="Constant", color='k', ls='-', **errorbar_params)
[…]

### 2020-05-08 paper/figures/tdse_plots.py

@@ -12,6 +12,18 @@ from qlp.tdse import convert_params, embed_qubo_example
 
 from django.conf import settings
 
+label_params = dict()
+label_params["fontsize"] = 7
+tick_params = dict()
+tick_params["labelsize"] = 7
+tick_params["width"] = 0.5
+errorbar_params = dict()
+errorbar_params["mew"] = 0.5
+errorbar_params["markersize"] = 5
+red = '#c82506'
+green = '#70b741'
+blue = '#51a7f9'
+
 class Data():
     def __init__(self):
         self.params = self.parameters()
@@ -76,8 +88,8 @@ def aggregate():
     adata = dict()
     data = Data()
     #for offset in [0.05, 0.04, 0.03, 0.02, 0.01, 0.0, -0.0005, -0.001, -0.002,-0.004, -0.005, -0.01, -0.02, -0.03, -0.04, -0.05]:
-    #for offset in [0.04, -0.04]:
-    for offset in [0.0]:
+    for offset in [-0.05, 0.0]:
+    #for offset in [0.0]:
         data.params["offset"]["offset"] = "binary"
         data.params["offset"]["offset_min"] = offset
         data.params["offset"]["offset_range"] = abs(offset)*2
@@ -205,11 +217,38 @@ def plot_gamma(gdata):
     plt.draw()
     plt.show()
 
+def plot_schedule(adata):
+    X, y1, y2 = adata[-0.05].tdse.AS.plot([0, 1])
+    X, z1, z2 = adata[0.0].tdse.AS.plot([0, 1])
+
+    plt.figure("anneal schedule", figsize=(7, 4))
+    ax = plt.axes([0.15, 0.15, 0.8, 0.8])
+    ax.errorbar(x=X, y=y1[:, 0], ls='-', color=blue, label="Positive offset A(s)")
+    ax.errorbar(x=X, y=z1[:, 0], ls='-', color='k', label="Default A(s)")
+    ax.errorbar(x=X, y=y1[:, -1], ls='-', color=red, label="Negative offset A(s)")
+    ax.errorbar(x=X, y=y2[:, 0], ls='--', color=blue, label="Positive offset B(s)")
+    ax.errorbar(x=X, y=z2[:, 0], ls='--', color='k', label="Default B(s)")
+    ax.errorbar(x=X, y=y2[:, -1], ls='--', color=red, label="Negative offset B(s)")
+    ax.set_xlabel("normalized time") #, **label_params)
[…]

### 2020-05-08 paper/main.tex
some discussion and method (marked in blue)

@@
 \begin{equation}
-H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}},
+H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
 \end{equation}
@@
 
+{\color{blue} (I tried to write something here...) Intuitively, we want the system to explore larger state space to increase the probability for the system to reach the final ground state.
+That is, we want the system to have ergodicity to avoid MBL.
+On the other hand, decoherence in the hardware leads to the loss of quantum information.
+It is desirable to minimize the effect of relaxation.
+The interplay between these two competing effects causing the complications in the results of annealing schedule offsets.
+Insights can be obtained by looking at the mutual information $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition A and partition B of the total system.
+$S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.
+(Should we talk about mutual information here? or in the latter MBL part? )}
+
 Following this logic, we split the qubits into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific problem.
@@
 Say what the simulator is solving
+
+{\color{blue}
+
+To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
+\begin{align}
+\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
+\end{align}
+where $\rho (t)$ is the density matrix at time $t$.
+$H(t)$ is the time-dependent Hamiltonian in Eq.~(\ref{eq:tdhamiltonian}).
+$[,]$ denotes the Lie bracket.
+$L_j$ are the Lindblad operators for decoherence.
+$\{, \}$ denotes the anti-commutator.
+In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
+The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
+For simplicity we assume all qubits having the same relaxation time.
+The initial condition is the Gibbs canonical ensemble
+\begin{equation}
+\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} .
+\end{equation}
+The probability to get the ground state at measurement is
+\begin{align}
+P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
+\end{align}
+where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
+Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
+
+}
 

### 2020-05-09 paper/main.tex
very rough first draft. need to write methods also

@@
 \subsection{Finding the Dominating Set with a Quantum Annealer}
-
+\label{sec:discussion:qa}
 \begin{figure}[b]
@@
 
-{\color{red} Should we talk about exponential damping here too? as a competing effect.}
-
-{\color{blue} (I tried to write something here...) Intuitively, we want the system to explore larger state space to increase the probability for the system to reach the final ground state.
-That is, we want the system to have ergodicity to avoid MBL.
-On the other hand, decoherence in the hardware leads to the loss of quantum information.
-It is desirable to minimize the effect of relaxation.
-The interplay between these two competing effects causing the complications in the results of annealing schedule offsets.
-Insights can be obtained by looking at the mutual information $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition A and partition B of the total system.
-$S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.
-(Should we talk about mutual information here? or in the latter MBL part? )}
-
 Following this logic, we split the qubits into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific problem.
@@
 Finally, we note that due to the inherent variance in performance when using different physical qubits, for each graph, we perform the offset study on the same physical qubits.
+Additionally, the largest offset ranges sampled are at the limits of the hardware capabilities of the DWave annealer.
+
+We observe from Fig.~\ref{fig:dwave_offset} that advancing qubits subject to \textit{larger} final external magnetic fields yields approximately an order of magnitude improvement over the baseline results at the largest offset range.
+In contrast advancing qubits with weaker magnetic fields consistently hurts the performance of the annealer.
+This result is surprising in light of the expectation from many-body localization.
+We provide an explanation of this surprising result by simulating the annealing process of the annealer which are discussed in the following sections.
 
@@
 
+In order to understand the effects of annealing offsets, we simulate the annealing process on 5 qubits for a $G(2)$ graph embedded in chimera topography.
+In order to shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
+The resulting ground state probability as a function of offset measured over 200,000 observations is shown in Fig.~\ref{fig:dwave1us} (Top).
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/dwave1us.pdf}
+	\includegraphics[width=\columnwidth]{./figures/sim_deco.pdf}
+	\includegraphics[width=\columnwidth]{./figures/sim_nodeco.pdf}
+	\caption{ (Top) The probability of finding the MDS for $G(2)$ from DWave.
+The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times.
+(Middle) Result from simulation with decoherence and (Bottom) simulation without decoherence.
+In both simulations, at +10\% offset, the probability of finding the ground state vanishes.
+The red simulation points are not present in the DWave result.}
+	\label{fig:dwave1us}
+\end{figure}
+
+For the simulation, the QUBO is obtained from the output of the DWave such that the same embedding is used.
+The time-dependence is obtained by solving the Lindblad equation subject to the DWave annealing schedule with offsets allowing us to incorporate a decoherence model in our simulation.
+The details of the Lindbladian are given in Sec.~\ref{sec:methods:lindblad}.
+Following Ref.~\cite{}, we fix the temperature of the simulation to 15 milliKelvins to reflect the reported operating temperature of the DWave.
+Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian is approximately 2 Kelvins as shown in Fig.~\ref{fig:spectrum}.
+As a result, the DWave operates at effectively zero-temperature for this example problem.
+
+We then set an effective $T_1$ coherence time to 20 $ns$ in order to match the DWave probability of finding the MDS of $G(2)$ at approximately 86\%.
+A detailed study of $T_1$ is given in Sec.~\ref{sec:methods:deco}.
+We emphasize that the effective coherence time is much longer than the single qubit coherence time of 0.5 $ns$ reported by DWave, while still being orders of magnitude shorter than the total anneal time.
+The simulation and the experiment however, both are able to recover the ground state with high probability regardless, and exemplifies the robustness of quantum annealing.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/spectrum.pdf}
+	\includegraphics[width=\columnwidth]{./figures/spectrum_offset.pdf}
+	\caption{The energy spectrum of the first 5 states of the time-dependent Hamiltonian (Top) without annealing offsets and (Bottom) -10\% annealing offset.
+The spectrum in dimensionless units at the end of the anneal is an integer spectrum and correspond to the number of vertices in the dominating set.
+For $G(2)$, the MDS has 1 vertex.
+Annealing offsets lift the ground-state degeneracy.}
+	\label{fig:spectrum}
+\end{figure}
+
+The probability of finding the MDS from the simulation with and without decoherence are given in Fig.~\ref{fig:dwave_offset} (Middle) and (Bottom).
+We observe that with decoherence, the simulation captures the rough features of the experiment, including a steady improvement for negative offsets, and similar non-linear behavior at positive offsets.
+Additionally, the range of probabilities in the simulation non-trivially match the range observed in experiment.
+In contrast, simulations without decoherence exemplify the opposite behavior with respect to offsets, in line with expectation from many-body localization.
+Therefore, the simulation provides evidence in relating the improvement seen on the DWave to the effects of decoherence rather than many-body localization, while for idealized annealing, the effects of many-body localization become important.
+
+In both simulations, the system experience a relatively large jump in probability, at -10\% and +30\% respectively.
+For the simulation with decoherence, this behavior is inconsistent with experiment.
+{\color{red} eh..
+guess a reason?} Additionally, both simulations experience vanishing probability at +10\% offset.
+This behavior is expected to happen eventually in experiment as well when the two sets of qubits become too aggressively staggered and effectively decouple.
+The simulation however, incorrectly predicts when the decoupling happens.
+
 \subsection{Decoherence and Many-Body Localization}
+
+We provide further evidence of the competing effects between decoherence and many-body localization in this section.
+
+Intuitively, we want the system to explore a larger state space to increase the probability for the system to reach the final ground state.
+That is, we want the system to have ergodicity in order to avoid MBL.
+On the other hand, decoherence in the hardware leads to the loss of quantum information.
+It is therefore desirable to minimize the effect of relaxation.
+The interplay between these two competing effects can be observed by looking at the time-dependent probability of reaching the final ground state, and the mutual information.
+The mutual information is defined as $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition $A$ and partition $B$ of the total system.
+$S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/full_prob_deco.pdf}
+	\includegraphics[width=\columnwidth]{./figures/mutual_info_deco.pdf}
+	\includegraphics[width=\columnwidth]{./figures/full_prob_nodeco.pdf}
+	\includegraphics[width=\columnwidth]{./figures/mutual_info_nodeco.pdf}
+	\caption{(Left) The time-dependent probability of resolving the ground state and (Right) the corresponding mutual information.
+(Top) Simulation with decoherence included and (Bottom) without decoherence.}
+	\label{fig:prob_mi}
+\end{figure*}
+
+From Fig.~\ref{fig:prob_mi} we observe that when the anneal schedule is modified to delay stronger external magnetic fields, the phase transition is delayed, yielding larger mutual information, and in turn probes a larger state space.
+This observation is independent of the effects of decoherence, and only relies on delaying the phase transition later in the annealing process.
+It then follows that the effects of decoherence is in competition with delocalization because the system is required to exhibit its quantum mechanical nature for longer.
+In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and become unaffected by decoherence.
+This phenomena is demonstrated by the left panels in Fig.~\ref{fig:prob_mi} where in the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this.
+top one the red is always below blue, the bottom one, the red crosses the blue after the phase transition).
+
+Things to do:
+
+Compute dwave mutual information
+
+Study ground state degeneracy by plotting distribution of states.
 
@@
 \subsubsection{The Lindblad Equation}
+\label{sec:methods:lindblad}
 Say what the simulator is solving
@@
 \subsubsection{Decoherence Time}
+\label{sec:methods:deco}
 Scan over decoherence time

### 2020-05-09 paper/figures/ta_plots.py

@@ -356,8 +356,13 @@ def plot_tdse(data):
     ax = plt.axes([0.15, 0.15, 0.8, 0.8])
     X = [-0.05, -0.04, -0.03, -0.02, -0.01, 0.0, 0.01, 0.02, 0.03, 0.04, 0.05]
     y = data["Binary"]
-    ax.errorbar(x=X, y=y, ls="none", marker='^')
+    ax.errorbar(x=X, y=y, ls="none", marker='o', color='k')
+    ax.set_xticks([-0.05, -0.04, -0.03, -0.02, -0.01, 0.0, 0.01, 0.02, 0.03, 0.04, 0.05])
+    ax.set_xticklabels(["-10%", "-8%", "-6%", "-4%", "-2%", "0%", "2%", "4%", "6%", "8%", "10%"])
+    ax.set_xlabel("offset range")
+    ax.set_ylabel("MDS probability")
     plt.draw()
+    plt.savefig("./dwave1us.pdf", transparent=True)
     plt.show()
 
 if __name__ == "__main__":
@@ -390,8 +395,8 @@ if __name__ == "__main__":
     #plot_baseline(data10)
 
     # compare offset plot
-    plot_compare_all(data02, data04, data06, data08, data10)
+    #plot_compare_all(data02, data04, data06, data08, data10)
 
     # plot tdse comparison plots
-    #tdsedata = get_tdse_data()
-    #plot_tdse(tdsedata)
+    tdsedata = get_tdse_data()
+    plot_tdse(tdsedata)

### 2020-05-09 paper/figures/tdse_plots.py

@@ -20,11 +20,12 @@ tick_params["width"] = 0.5
 errorbar_params = dict()
 errorbar_params["mew"] = 0.5
 errorbar_params["markersize"] = 5
-red = '#c82506'
-green = '#70b741'
-blue = '#51a7f9'
+red = "#c82506"
+green = "#70b741"
+blue = "#51a7f9"
 
-class Data():
+
+class Data:
     def __init__(self):
         self.params = self.parameters()
 
@@ -42,7 +43,7 @@ class Data():
         # wave params
         wave_params = dict()
         wave_params["type"] = "mixed"
-        wave_params["temp"] = 15E-3
+        wave_params["temp"] = 15e-3
         wave_params["gamma"] = 0.05
         wave_params["initial_wavefunction"] = "transverse"
 
@@ -84,31 +85,62 @@ class Data():
         ).first()
         return query
 
+
 def aggregate():
     adata = dict()
     data = Data()
-    #for offset in [0.05, 0.04, 0.03, 0.02, 0.01, 0.0, -0.0005, -0.001, -0.002,-0.004, -0.005, -0.01, -0.02, -0.03, -0.04, -0.05]:
-    for offset in [-0.05, 0.0]:
-    #for offset in [0.0]:
+    #for offset in [
+    #    0.05,
+    #    0.04,
+    #    0.03,
+    #    0.02,
+    #    0.01,
+    #    0.0,
+    #    -0.0005,
+    #    -0.001,
+    #    -0.002,
+    #    -0.004,
+    #    -0.005,
+    #    -0.01,
+    #    -0.02,
+    #    -0.03,
+    #    -0.04,
+    #    -0.05,
+    #]:
+        # for offset in [-0.04, 0.04]:
+    for offset in [-0.04, 0.04]:
         data.params["offset"]["offset"] = "binary"
         data.params["offset"]["offset_min"] = offset
-        data.params["offset"]["offset_range"] = abs(offset)*2
+        data.params["offset"]["offset_range"] = abs(offset) * 2
         adata[offset] = data.get_data()
         with open(f"{settings.MEDIA_ROOT}/{adata[offset].solution}", "rb") as file:
             adata[offset].sol = pickle.load(file)
         with open(f"{settings.MEDIA_ROOT}/{adata[offset].instance}", "rb") as file:
             adata[offset].tdse = pickle.load(file)
     return adata
+
 
[…]

### 2020-05-09 paper/main.tex
fix some summations and other things (marked in blue)

@@
 Formally, ILP is defined as the optimization of a linear function
+{\color{blue}
 \begin{align}
-f(x) = &\min\limits_{x}(c_i x_i),\\
-\textrm{subject to} \quad & A_{aj}x_i +b_a \leq 0 \\
+f(x) = &\min\limits_{x}(\sum_i c_i x_i),\\
+\textrm{subject to} \quad & \sum_i A_{ai}x_i +b_a \leq 0 \\
 & x_i \geq 0,\\
@@
 \end{align}
+}
 where $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
 The inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
+{\color{blue}
 \begin{align}
-f(x) = &\min(c_i x_i),\\
-\textrm{subject to} \quad & A_{a i}x_i + s_a + b_a = 0,\\
+f(x) = &\min(\sum_i c_i x_i),\\
+\textrm{subject to} \quad & \sum_i A_{a i}x_i + s_a + b_a = 0,\\
 & s_a \geq 0,\\
@@
 \end{align}
-
+}
 Since quantum annealing solves the QUBO problem, we extend the proposed algorithm to solve integer quadratic optimization problems such that
+{\color{blue}
 \begin{align}
-f(x) = \min\limits_{x}(x_i d_{ij} x_j + c_i x_i)
+f(x) = \min\limits_{x}(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i)
 \end{align}
+}
 without the introduction of auxiliary qubits.
@@
 $S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.
+{\color{blue} $\rho_{A,B}$ is the density matrix for the total system.
+$\rho_{A}=\mbox{Tr}_{B} (\rho_{A,B})$ is the reduced density matrix for the subsystem A.}
 
@@
 \end{align}
-where $\rho (t)$ is the density matrix at time $t$.
-$H(t)$ is the time-dependent Hamiltonian in Eq.~(\ref{eq:tdhamiltonian}).
+where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian 
+\begin{align}
+\label{eq:annealH}
+ H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\ 
+ +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
+\end{align}
+where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
+The site dependency takes into account of the annealing offset.
 $[,]$ denotes the Lie bracket.
@@
 \begin{equation}
-\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} .
+\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
 \end{equation}
+where $\beta$ is the inverse temperature.
 The probability to get the ground state at measurement is

### 2020-05-10 paper/main.tex
minor words changed for dephasing

@@
 It then follows that the effects of decoherence is in competition with delocalization because the system is required to exhibit its quantum mechanical nature for longer.
-In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and become unaffected by decoherence.
-This phenomena is demonstrated by the left panels in Fig.~\ref{fig:prob_mi} where in the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this.
+In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and {\color{blue}become unaffected by dephasing.} This phenomena is demonstrated by the left panels in Fig.~\ref{fig:prob_mi} where in the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this.
 top one the red is always below blue, the bottom one, the red crosses the blue after the phase transition).
@@
 The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
+The amplitude damping model also includes the dephasing effect, where the dephasing time is fixed to $T_2=\frac{T_1}{2}$.
 For simplicity we assume all qubits having the same relaxation time.

### 2020-05-10 paper/main.tex
add coherence plot

@@
 \label{sec:methods:deco}
-Scan over decoherence time
+
+Mention long coherence time asymptote to right value.
+
+Scan coherence time, match to DWave.
+
+Some more discussion about short coherence time and why it makes sense?
+
+Travis said: Regarding T1 << T effecting the state at time T, I am thinking more about the point that the very short T1 dephasing time has the effect of quenching any coherence.
+In this regard, a very short T1 is pushing the systems toward a classical annealing model.
+The absence of any dephasing is then the best-case quantum annealing model.
+Consequently, the difference in outcome would trace back to this coherence being present.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/coherence.pdf}
+	\caption{asdf}
+	\label{fig:prob_mi}
+\end{figure}
 

### 2020-05-11 paper/main.tex
remove one sentence about dephasing
Started to write abstract

@@
 \begin{abstract}
-Abstract here...
+While quantum computing proposes promising solutions to computational problems not accessible with classical approaches, due to current hardware constraints, most quantum algorithms are not yet capable of computing systems of practical relevance, and classical counterparts outperform them.
+To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
+For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA) and investigated problem and hardware-specific limitations.
+This work presents the formalism of how to map ILP problems to the annealing architectures.
+It illustrates the effects of decorrelation and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
+We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.
+%Conclusion: What do these findings mean to us?
+[Rephrase] We need better hardware to challenge heuristic solvers but we identified how to optimize hardware.
+%Perspectives: What should be done next?
+[Rephrase] Better understand correlations and localizations and improve simulation to scale to larger problems.
+
 \end{abstract}
@@
 		Connected nodes are neighbors of the DS (turquoise) or already in the DS.
-		In (a), one finds three unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
+		In (a), one finds three maximally unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
 		In the first step $a\to b$, randomly the node (4) is picked.
-		In (b), one has two unconnected choices [(1), (2)] with each adjacent to another unconnected node.
+		In (b), one has three unconnected choices [(1), (2)] with each adjacent to another unconnected node and one node [(6)] which is only adjacent to neighbors of the DS.
 		After randomly selecting (2) when going from $b \to c$, only one unconnected node is remaining (6).
@@
 \begin{align}
-f(x) = &\min(\sum_{\nu \in V} \psi^x_{\nu}),\\
+f(x) = &\min\left(\sum_{\nu \in V} \psi^x_{\nu}\right),\\
 \textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1,\\
@@
 where $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, and $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
-The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ on the DWave.
+The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ (CK: time unit mapping) on the DWave.
 On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits.
@@
 The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
-The amplitude damping model also includes the dephasing effect, where the dephasing time is fixed to $T_2=\frac{T_1}{2}$.
 For simplicity we assume all qubits having the same relaxation time.

### 2020-05-11 paper/main.tex
Formatting
First reordering

@@
-\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography]{revtex4}
+-\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography]{revtex4}
 \usepackage[utf8]{inputenc}
@@
 
+%========================================================================================
 \section{INTRODUCTION}
 \label{sec:introduction}
+%========================================================================================
 
@@
 where $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
+
+{\color{red} Paragraph on how this is solved classically.
+Include strengths and drawbacks of classical solution.}
+
+%========================================================================================
+\section{METHODS}
+\label{sec:methods}
+%========================================================================================
+
+%----------------------------------------------------------------------------------------
+\subsection{Integer Programming Mapping to QUBO}
+\label{sec:methods:ilp}
+%----------------------------------------------------------------------------------------
+
 The inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
@@
 
-{\color{red} Paragraph on how this is solved classically. Include strengths and drawbacks of classical solution.}
+%----------------------------------------------------------------------------------------
+\subsection{QUBO}
+\label{sec:methods:qubo}
+%----------------------------------------------------------------------------------------
 
-\section{RESULTS}
-\label{sec:results}
 We map integer variables $z_i$ to qubits under the following transformation~\cite{Chang:2018uoc}
@@
 
+%----------------------------------------------------------------------------------------
 \subsection{Integer Programming Mapping to QUBO}
-\label{sec:results:ilp}
+\label{sec:methods:ilp}
+%----------------------------------------------------------------------------------------
+
 The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
 \begin{align}
-\chi^2 = & \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right. \nonumber\\
+    \chi^2 = & \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
+    \nonumber\\
     &\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
@@
 
+%----------------------------------------------------------------------------------------
 \subsection{Application to the Dominating Set Problem}
-\label{sec:results:mds}
+\label{sec:methods:mds}
+%----------------------------------------------------------------------------------------
 
@@
 
+%----------------------------------------------------------------------------------------
 \subsubsection{Minimum Dominating Set}
+%----------------------------------------------------------------------------------------
+
 The solution to the minimum independent set can be expressed as an integer optimization problem given by,
@@
 
-\section{DISCUSSION}
+%----------------------------------------------------------------------------------------
+\subsubsection{Modified annealing schedule}
+%----------------------------------------------------------------------------------------
 
+In quantum annealing, the ground state of the problem Hamiltonian is obtained from the evolution of a time-dependent Hamiltonian,
+\begin{equation}
+    H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
+\end{equation}
+where $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, and $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
+The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ (CK: time unit mapping) on the DWave.
+On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits.
+In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in addition to the effects of applying positive and negative offsets.
+Note that due to the way the offsets are implemented on the hardware level, systematic errors are introduced since the initial and final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
+Fig.~\ref{fig:anneal_schedule} shows the maximum offset that we use for the study, which translates to approximately (due to non-linearity) a 5\% advancement (blue) or delay (red) in the schedule.
+
+\begin{figure}[b]
+    \centering
+    \includegraphics[width=\columnwidth]{./figures/anneal_schedule.pdf}
+    \caption{asdf}
+    \label{fig:anneal_schedule}
+\end{figure}
+
+The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system in general will exhibit more disorder.
+We define disorder by first recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
+\begin{equation}
+    H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
+\end{equation}
+and recognize that in the limit where $h_i$ is randomly drawn from a Bernoulli distribution we recover the spin-glass model.
+The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization.
+
+%----------------------------------------------------------------------------------------
+\subsection{Simulation Results}
+%----------------------------------------------------------------------------------------
+
+In order to understand the effects of annealing offsets, we simulate the annealing process on 5 qubits for a $G(2)$ graph embedded in chimera topography.
+In order to shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
+The resulting ground state probability as a function of offset measured over 200,000 observations is shown in Fig.~\ref{fig:dwave1us} (Top).
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{./figures/dwave1us.pdf}
+    \includegraphics[width=\columnwidth]{./figures/sim_deco.pdf}
+    \includegraphics[width=\columnwidth]{./figures/sim_nodeco.pdf}
+    \caption{ (Top) The probability of finding the MDS for $G(2)$ from DWave.
+The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times.
+(Middle) Result from simulation with decoherence and (Bottom) simulation without decoherence.
+In both simulations, at +10\% offset, the probability of finding the ground state vanishes.
+The red simulation points are not present in the DWave result.}
+    \label{fig:dwave1us}
+\end{figure}
+
+For the simulation, the QUBO is obtained from the output of the DWave such that the same embedding is used.
+The time-dependence is obtained by solving the Lindblad equation subject to the DWave annealing schedule with offsets allowing us to incorporate a decoherence model in our simulation.
+The details of the Lindbladian are given in Sec.~\ref{sec:methods:lindblad}.
+Following Ref.~\cite{}, we fix the temperature of the simulation to 15 milliKelvins to reflect the reported operating temperature of the DWave.
+Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian is approximately 2 Kelvins as shown in Fig.~\ref{fig:spectrum}.
+As a result, the DWave operates at effectively zero-temperature for this example problem.
+
+We then set an effective $T_1$ coherence time to 20 $ns$ in order to match the DWave probability of finding the MDS of $G(2)$ at approximately 86\%.
+A detailed study of $T_1$ is given in Sec.~\ref{sec:methods:deco}.
+We emphasize that the effective coherence time is much longer than the single qubit coherence time of 0.5 $ns$ reported by DWave, while still being orders of magnitude shorter than the total anneal time.
+The simulation and the experiment however, both are able to recover the ground state with high probability regardless, and exemplifies the robustness of quantum annealing.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{./figures/spectrum.pdf}
+    \includegraphics[width=\columnwidth]{./figures/spectrum_offset.pdf}
+    \caption{The energy spectrum of the first 5 states of the time-dependent Hamiltonian (Top) without annealing offsets and (Bottom) -10\% annealing offset.
+The spectrum in dimensionless units at the end of the anneal is an integer spectrum and correspond to the number of vertices in the dominating set.
+For $G(2)$, the MDS has 1 vertex.
+Annealing offsets lift the ground-state degeneracy.}
+    \label{fig:spectrum}
+\end{figure}
+
+%----------------------------------------------------------------------------------------
+\subsection{Simulation Details}
+%----------------------------------------------------------------------------------------
+
+%----------------------------------------------------------------------------------------
+\subsubsection{The Lindblad Equation}
+\label{sec:methods:lindblad}
+%----------------------------------------------------------------------------------------
+Say what the simulator is solving
+
+{\color{blue}
+
+To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
+\begin{align}
+    \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
+\end{align}
+where $\rho (t)$ is the density matrix at time $t$.
+$H(t)$ is the time-dependent Hamiltonian
+\begin{align}
+    \label{eq:annealH}
+     H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\
+     +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
+\end{align}
+where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
+The site dependency takes into account of the annealing offset.
+$[,]$ denotes the Lie bracket.
+$L_j$ are the Lindblad operators for decoherence.
+$\{, \}$ denotes the anti-commutator.
+In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
+The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
+For simplicity we assume all qubits having the same relaxation time.
+The initial condition is the Gibbs canonical ensemble
+\begin{equation}
+    \rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
+\end{equation}
+where $\beta$ is the inverse temperature.
+The probability to get the ground state at measurement is
+\begin{align}
+    P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
+\end{align}
+where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
+Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
+
+}
+
+With anneal offsets
+%----------------------------------------------------------------------------------------
+\subsubsection{Other Simulation Details}
+%----------------------------------------------------------------------------------------
+Temperature
+Initial wave function choices
+RK tolerance
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Decoherence Time}
+\label{sec:methods:deco}
+%----------------------------------------------------------------------------------------
+
+Mention long coherence time asymptote to right value.
+
+Scan coherence time, match to DWave.
+
+Some more discussion about short coherence time and why it makes sense?
+
+Travis said: Regarding T1 << T effecting the state at time T, I am thinking more about the point that the very short T1 dephasing time has the effect of quenching any coherence.
+In this regard, a very short T1 is pushing the systems toward a classical annealing model.
+The absence of any dephasing is then the best-case quantum annealing model.
+Consequently, the difference in outcome would trace back to this coherence being present.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{./figures/coherence.pdf}
+    \caption{asdf}
+    \label{fig:prob_mi}
+\end{figure}
+
+%========================================================================================
+\section{RESULTS \& DISCUSSION}
+\label{sec:results}
+%========================================================================================
+
+%----------------------------------------------------------------------------------------
 \subsection{Finding the Dominating Set with a Quantum Annealer}
 \label{sec:discussion:qa}
+%----------------------------------------------------------------------------------------
+
 \begin{figure}[b]
@@
         \includegraphics[width=0.5\columnwidth]{./figures/linear_crop.pdf}
-	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
+    \caption{Linear graphs $G(n)$ used in this study.
+Nodes denote vertices of the graphs and lines are undirected edges.}
     \label{fig:linear}
@@
     \includegraphics[width=\columnwidth]{./figures/scaling_baseline.pdf}
-	\caption{Baseline result of DWave (blue) compared to random guessing (red). The jagged nature of random guessing reflects the degeneracy of the ground state.}
+    \caption{Baseline result of DWave (blue) compared to random guessing (red).
+The jagged nature of random guessing reflects the degeneracy of the ground state.}
     \label{fig:baseline}
@@
 
+%----------------------------------------------------------------------------------------
 \subsubsection{Modified annealing schedule}
-
-In quantum annealing, the ground state of the problem Hamiltonian is obtained from the evolution of a time-dependent Hamiltonian,
-\begin{equation}
-H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
-\end{equation}
-where $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, and $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
-The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ (CK: time unit mapping) on the DWave.
-On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits.
-In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in addition to the effects of applying positive and negative offsets.
-Note that due to the way the offsets are implemented on the hardware level, systematic errors are introduced since the initial and final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
-Fig.~\ref{fig:anneal_schedule} shows the maximum offset that we use for the study, which translates to approximately (due to non-linearity) a 5\% advancement (blue) or delay (red) in the schedule.
-
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=\columnwidth]{./figures/anneal_schedule.pdf}
-	\caption{asdf}
-	\label{fig:anneal_schedule}
-\end{figure}
-
-The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system in general will exhibit more disorder.
-We define disorder by first recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
-\begin{equation}
-H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
-\end{equation}
-and recognize that in the limit where $h_i$ is randomly drawn from a Bernoulli distribution we recover the spin-glass model.
-The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization.
+%----------------------------------------------------------------------------------------
 
@@
 
+%----------------------------------------------------------------------------------------
 \subsection{Simulation Results}
+%----------------------------------------------------------------------------------------
 
@@
 
+%----------------------------------------------------------------------------------------
 \subsection{Decoherence and Many-Body Localization}
+%----------------------------------------------------------------------------------------
 
@@
 
-\section{METHODS}
-\subsection{Simulation Details}
-\subsubsection{The Lindblad Equation}
-\label{sec:methods:lindblad}
-Say what the simulator is solving
-
-{\color{blue}
-
-To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
-\begin{align}
-\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
-\end{align}
-where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian 
-\begin{align}
-\label{eq:annealH}
- H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\ 
- +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
-\end{align}
-where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
-The site dependency takes into account of the annealing offset.
-$[,]$ denotes the Lie bracket.
-$L_j$ are the Lindblad operators for decoherence.
-$\{, \}$ denotes the anti-commutator.
-In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
-The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
-For simplicity we assume all qubits having the same relaxation time.
-The initial condition is the Gibbs canonical ensemble
-\begin{equation}
-\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
-\end{equation}
-where $\beta$ is the inverse temperature.
-The probability to get the ground state at measurement is
-\begin{align}
-P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
-\end{align}
-where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
-Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
-
-}
-
-With anneal offsets
-
-\subsubsection{Other Simulation Details}
-Temperature
-Initial wave function choices
-RK tolerance
-
-\subsubsection{Decoherence Time}
-\label{sec:methods:deco}
-
-Mention long coherence time asymptote to right value.
-
-Scan coherence time, match to DWave.
-
-Some more discussion about short coherence time and why it makes sense?
-
-Travis said: Regarding T1 << T effecting the state at time T, I am thinking more about the point that the very short T1 dephasing time has the effect of quenching any coherence.
-In this regard, a very short T1 is pushing the systems toward a classical annealing model.
-The absence of any dephasing is then the best-case quantum annealing model.
-Consequently, the difference in outcome would trace back to this coherence being present.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./figures/coherence.pdf}
-	\caption{asdf}
-	\label{fig:prob_mi}
-\end{figure}
-
+%========================================================================================
 \section{DATA AVAILABILITY}
+%========================================================================================
 
@@
 
+%========================================================================================
 \section{ACKNOWLEDGEMENTS}
+%========================================================================================
 
@@
 
+%========================================================================================
 \section{AUTHOR CONTRIBUTIONS}
+%========================================================================================
 
@@
 
+%========================================================================================
 \section{ADDITIONAL INFORMATION}
+%========================================================================================
 
@@
 
+%========================================================================================
 \bibliography{qilp}
+%========================================================================================
 

### 2020-05-11 paper/main.tex
Reshuffle adjustments

@@
--\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography]{revtex4}
+\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography]{revtex4}
+
 \usepackage[utf8]{inputenc}
@@
 }
+
+% disable subsections and subsubsections in the TOC
+\makeatletter
+\def\l@subsubsection#1#2{}
+\makeatother
 
@@
 
+%----------------------------------------------------------------------------------------
+\subsubsection{Slack variables}
+\label{sec:methods:slack}
+%----------------------------------------------------------------------------------------
+
 The inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
@@
 %----------------------------------------------------------------------------------------
-\subsection{QUBO}
-\label{sec:methods:qubo}
+\subsubsection{Bit basis}
+\label{sec:methods:bit-basis}
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\subsection{Integer Programming Mapping to QUBO}
-\label{sec:methods:ilp}
+\subsubsection{Integer Programming Mapping QUBO}
+\label{sec:methods:ilp-qubo}
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\subsection{Application to the Dominating Set Problem}
+\subsubsection{Minimum Dominating Set Problem}
 \label{sec:methods:mds}
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{Minimum Dominating Set}
+\subsubsection{Minimum Dominating Set Qubo}
+\label{sec:methods:mds-qubo}
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
+\subsection{Quantum Annealing}
+\label{methods:annealing}
+%----------------------------------------------------------------------------------------
+
+%----------------------------------------------------------------------------------------
 \subsubsection{Modified annealing schedule}
+\label{methods:annealing-schedule}
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\subsection{Simulation Results}
-%----------------------------------------------------------------------------------------
-
-In order to understand the effects of annealing offsets, we simulate the annealing process on 5 qubits for a $G(2)$ graph embedded in chimera topography.
-In order to shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
-The resulting ground state probability as a function of offset measured over 200,000 observations is shown in Fig.~\ref{fig:dwave1us} (Top).
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{./figures/dwave1us.pdf}
-    \includegraphics[width=\columnwidth]{./figures/sim_deco.pdf}
-    \includegraphics[width=\columnwidth]{./figures/sim_nodeco.pdf}
-    \caption{ (Top) The probability of finding the MDS for $G(2)$ from DWave.
-The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times.
-(Middle) Result from simulation with decoherence and (Bottom) simulation without decoherence.
-In both simulations, at +10\% offset, the probability of finding the ground state vanishes.
-The red simulation points are not present in the DWave result.}
-    \label{fig:dwave1us}
-\end{figure}
-
-For the simulation, the QUBO is obtained from the output of the DWave such that the same embedding is used.
-The time-dependence is obtained by solving the Lindblad equation subject to the DWave annealing schedule with offsets allowing us to incorporate a decoherence model in our simulation.
-The details of the Lindbladian are given in Sec.~\ref{sec:methods:lindblad}.
-Following Ref.~\cite{}, we fix the temperature of the simulation to 15 milliKelvins to reflect the reported operating temperature of the DWave.
-Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian is approximately 2 Kelvins as shown in Fig.~\ref{fig:spectrum}.
-As a result, the DWave operates at effectively zero-temperature for this example problem.
-
-We then set an effective $T_1$ coherence time to 20 $ns$ in order to match the DWave probability of finding the MDS of $G(2)$ at approximately 86\%.
-A detailed study of $T_1$ is given in Sec.~\ref{sec:methods:deco}.
-We emphasize that the effective coherence time is much longer than the single qubit coherence time of 0.5 $ns$ reported by DWave, while still being orders of magnitude shorter than the total anneal time.
-The simulation and the experiment however, both are able to recover the ground state with high probability regardless, and exemplifies the robustness of quantum annealing.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{./figures/spectrum.pdf}
-    \includegraphics[width=\columnwidth]{./figures/spectrum_offset.pdf}
-    \caption{The energy spectrum of the first 5 states of the time-dependent Hamiltonian (Top) without annealing offsets and (Bottom) -10\% annealing offset.
-The spectrum in dimensionless units at the end of the anneal is an integer spectrum and correspond to the number of vertices in the dominating set.
-For $G(2)$, the MDS has 1 vertex.
-Annealing offsets lift the ground-state degeneracy.}
-    \label{fig:spectrum}
-\end{figure}
-
-%----------------------------------------------------------------------------------------
-\subsection{Simulation Details}
+\subsection{Simulation of a Quantum Annealer}
+\label{sec:methods:simulation}
 %----------------------------------------------------------------------------------------
@@
 %========================================================================================
+\section{CONCLUSION}
+%========================================================================================
+
+%========================================================================================
 \section{DATA AVAILABILITY}
@@
 
-...
+C.K. drank a lot of coffee.
 

### 2020-05-12 paper/main.tex
change annealing time in paper.. it is 600us instead of 400us

--- 2020-05-11 paper/main.tex
@@
 \begin{abstract}
-While quantum computing proposes promising solutions to computational problems not accessible with classical approaches, due to current hardware constraints, most quantum algorithms are not yet capable of computing systems of practical relevance, and classical counterparts outperform them.
-To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
-For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA) and investigated problem and hardware-specific limitations.
-This work presents the formalism of how to map ILP problems to the annealing architectures.
-It illustrates the effects of decorrelation and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
-We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.
-%Conclusion: What do these findings mean to us?
-[Rephrase] We need better hardware to challenge heuristic solvers but we identified how to optimize hardware.
-%Perspectives: What should be done next?
-[Rephrase] Better understand correlations and localizations and improve simulation to scale to larger problems.
-
+Abstract here...
 \end{abstract}
@@
 		Connected nodes are neighbors of the DS (turquoise) or already in the DS.
-		In (a), one finds three maximally unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
+		In (a), one finds three unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
 		In the first step $a\to b$, randomly the node (4) is picked.
-		In (b), one has three unconnected choices [(1), (2)] with each adjacent to another unconnected node and one node [(6)] which is only adjacent to neighbors of the DS.
+		In (b), one has two unconnected choices [(1), (2)] with each adjacent to another unconnected node.
 		After randomly selecting (2) when going from $b \to c$, only one unconnected node is remaining (6).
@@
 \begin{align}
-f(x) = &\min\left(\sum_{\nu \in V} \psi^x_{\nu}\right),\\
+f(x) = &\min(\sum_{\nu \in V} \psi^x_{\nu}),\\
 \textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1,\\
@@
 For the following studies, we perform experiments on the \texttt{DW\_2000Q\_5} solver.
-The annealing time is optimized to 400$\mu$s after performing a study on the $G(6)$ graph as shown in Fig.~\ref{fig:at_scale}.
+The annealing time is optimized to 600$\mu$s after performing a study on the $G(6)$ graph as shown in Fig.~\ref{fig:at_scale}.
 In Fig.~\ref{fig:baseline}, we show results from the baseline experiment, without modification to the default DWave annealing schedule, and observe improvement over random guessing.
@@
 where $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, and $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
-The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ (CK: time unit mapping) on the DWave.
+The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ on the DWave.
 On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits.

### 2020-05-12 paper/figures/ta_plots.py

@@ -351,6 +351,17 @@ def plot_baseline(data10):
     plt.savefig("./scaling_baseline.pdf")
     plt.show()
 
+    plt.figure("const/rando", figsize=(7, 4))
+    ax = plt.axes([0.15, 0.15, 0.8, 0.8])
+    ax.errorbar(x=X, y=data10["Constant"]/rguess, label="DWave/Random", marker='o', color='k', **errorbar_params)
+    ax.legend()
+    ax.set_yscale("log")
+    ax.set_ylabel("improvement ratio")
+    ax.set_xlabel("number of vertices")
+    plt.draw()
+    plt.savefig("./ratio_baseline.pdf", transparent=True)
+    plt.show()
+
 def plot_tdse(data):
     fig = plt.figure("tdse", figsize=(7,4))
     ax = plt.axes([0.15, 0.15, 0.8, 0.8])
@@ -392,11 +403,11 @@ if __name__ == "__main__":
     #plot_full(data10, "0p10")
 
     # baseline
-    #plot_baseline(data10)
+    plot_baseline(data10)
 
     # compare offset plot
     #plot_compare_all(data02, data04, data06, data08, data10)
 
     # plot tdse comparison plots
-    tdsedata = get_tdse_data()
-    plot_tdse(tdsedata)
+    #tdsedata = get_tdse_data()
+    #plot_tdse(tdsedata)

### 2020-05-12 paper/figures/ta_plots.py
dwave mi

@@ -168,6 +168,59 @@ def getdata_full(min, rangex):
         print(y)
     return y
 
+def get_spin_config():
+    import pickle
+    vrange = [-0.05, -0.04, -0.03, -0.02, -0.01, 0.0, 0.01, 0.02, 0.03, 0.04, 0.05]
+    offlist = ["Binary"]
+    try:
+        y =dict()
+        for offx in offlist:
+            y[offx] = dict()
+            for v in vrange:
+                with open(f"./temp/{offx}_{v}.pickle", "rb") as file:
+                    y[offx][v] = pickle.load(file)
+    except:
+        data = {
+            offx: {
+                v: data_Data.objects.filter(
+                    experiment__graph__tag=f"NN(2)",
+                    experiment__tag=f"FixEmbedding_{offx}_{v}_{2*abs(v)}_v5",
+                    experiment__settings__annealing_time=1,
+                    experiment__settings__num_spin_reversal_transforms=5,
+                ).to_dataframe()
+                for v in vrange
+            }
+            for offx in offlist
+        }
+        y = dict()
+        for offset in data.keys():
+            y[offset] = dict()
+            X = list(data[offset].keys())
+            for v in X:
+                spin = data[offset][v]["spin_config"]
+                with open(f"./temp/{offset}_{v}.pickle", "wb") as file:
+                    pickle.dump(spin, file)
+                y[offset][v] = spin
+    # remap y
+    remap = [1, 2, 3, 0, 1]
+    for offset in y.keys():
+        X = list(y[offset].keys())
+        for v in X:
+            temp = []
+            for yi in y[offset][v]:
+                temp.append([yi[idx] for idx in remap])
+            y[offset][v] = np.array(temp)
+    basis = [(i, j, k, l, m) for i in [0, 1] for j in [0, 1] for k in [0, 1] for l in [0, 1] for m in [0, 1]]
+    scount = dict()
+    for offset in y.keys():
+        X = list(y[offset].keys())
+        scount[offset] = dict()
+        for v in X:
+            scount[offset][v] = {b: 0 for b in basis}
+            for yi in y[offset][v]:
+                scount[offset][v][tuple(yi)] += 1
+    return scount
+
 def get_tdse_data():
     if True:
[…]

### 2020-05-22 qlp/tdse/computation.py
full counting statistics done

@@ -490,7 +490,7 @@ class TDSE:
         return lindblad
 
     def get_lindblad(self,ymat,gamma,H):
-        '''full counting statistics
+        '''full counting statistics under wide-band-limit
         '''
         value,vector=np.linalg.eigh(H.toarray())
         lindblad=np.zeros((len(value),len(value)),dtype=complex)
@@ -510,7 +510,7 @@ class TDSE:
                 loweringrho=(lowering)@(ymat)
 
                 # re-factored lindblad operator
-                lindblad+=(lowering)@(2.0*rhoraising-e*(raisingrho))+(raising)@(2.0*e*(rholowering)-loweringrho)-(rhoraising)@(lowering)-e*(rholowering)@(raising)
+                lindblad+=((lowering)@(2.0*rhoraising-e*(raisingrho))+(raising)@(2.0*e*(rholowering)-loweringrho)-(rhoraising)@(lowering)-e*(rholowering)@(raising))/(1.0+e)
 
         #lindblad=(1-p)*lower+p*np.conjugate(np.transpose(lower))
         #lindblad=(1-p)*( 2.0*(lower)@(ymat)@(raiseop)-raiseop@(lower)@(ymat)-(ymat)@(raiseop)@(lower) )

### 2020-05-22 Notes/Notes.tex
notes updated for full counting statistics

@@
 %opening
-%\title{Notes}
+\title{Notes}
 
@@
 
+The Lindblad operators from full counting statistics under wide-band limit is given by (arXiv:1312.3476 [quant-ph])
+\begin{align}
+  L_{2j}=(\sqrt{\gamma p_j}) a_j \\
+  L_{2j+1}=(\sqrt{\gamma (1-p_j)} )a_j^\dagger ,
+\end{align}
+, where $j=(\mu,\nu)$ runs through all the level spacing between all the many-body eigen states of the system Hamiltonian for $E_\mu > E_\nu$.
+$p_j=\frac{1}{1+e^{-\beta (E_\mu-E_\nu)}}$.
+$a_j=|\nu \rangle \langle \mu |$ is the lowering operator for many-body states in the qubits system.
+
 \subsection{unit conversion}

### 2020-05-22 qlp/tdse/computation.py
move to ref paper's convention

@@ -510,7 +510,7 @@ class TDSE:
                 loweringrho=(lowering)@(ymat)
 
                 # re-factored lindblad operator
-                lindblad+=((lowering)@(2.0*rhoraising-e*(raisingrho))+(raising)@(2.0*e*(rholowering)-loweringrho)-(rhoraising)@(lowering)-e*(rholowering)@(raising))/(1.0+e)
+                lindblad+=((lowering)@(2.0*rhoraising-e*(raisingrho))+(raising)@(2.0*e*(rholowering)-loweringrho)-(rhoraising)@(lowering)-e*(rholowering)@(raising))
 
         #lindblad=(1-p)*lower+p*np.conjugate(np.transpose(lower))
         #lindblad=(1-p)*( 2.0*(lower)@(ymat)@(raiseop)-raiseop@(lower)@(ymat)-(ymat)@(raiseop)@(lower) )

### 2020-05-25 Notes/Notes.tex

--- 2020-05-07 Notes/Notes.tex
@@
 \begin{align}
-  \partial_t \rho (t) = - \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
+  \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
 \end{align}
@@
 For simplicity we assume all qubits having the same relaxation time.
+
+The Lindblad master equation from full counting statistics is given by (arXiv:1312.3476 [quant-ph])
+\begin{align}
+\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_{\mu>\nu,x\in \pm} (2L^x_{\mu \nu} \rho(t) L_{\mu \nu}^{x\dagger} - \{ L^{x\dagger}_{\mu \nu} L^x_{\mu \nu}, \rho(t) \}) ,
+\end{align}
+and
+\begin{align}
+  L^-_{\mu \nu}=(\sqrt{\gamma}) a_{\mu \nu} \\
+  L^+_{\mu \nu}=(\sqrt{\gamma p_{\mu \nu}} )a_{\mu \nu}^\dagger ,
+\end{align}
+, where indices $\mu$ and $\nu$ run through all pairs of the many-body eigenstates of the system Hamiltonian for $\mu > \nu$ and $E_0 \le E_1 \le ...
+\le E_{dim(\mbox{Hilbert space})}$.
+$p_{\mu \nu}=e^{-\beta (E_\mu-E_\nu)}$.
+$a_{\mu \nu}=|\nu \rangle \langle \mu |$ is the lowering operator for many-body eigen states in the qubits system.
 

### 2020-05-25 paper/main.tex
First intro adjustments

--- 2020-05-11 paper/main.tex
@@
 
+\newcommand{\alert}[1]{\textbf{\color{red}{#1}}}
+\renewcommand{\vec}[1]{\boldsymbol{#1}}
+
 \begin{abstract}
@@
 
-Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints and is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and z~\cite{}.
+Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints and is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}.
 In general however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
 The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem can be obtained in polynomial time, the optimal integer solution in general must be found in the $2^n$ integer solutions which surround the real number solution.
+Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
+While greedy algorithms do not guarantee optimal global solutions, they find approximate solutions in polynomial time, which can be utilized in further computations.
 Due to the importance and difficulty, in this work we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.
@@
 
-Formally, ILP is defined as the optimization of a linear function
-{\color{blue}
-\begin{align}
-    f(x) = &\min\limits_{x}(\sum_i c_i x_i),\\
-    \textrm{subject to} \quad & \sum_i A_{ai}x_i +b_a \leq 0 \\
-    & x_i \geq 0,\\
-    & x_i \in \mathbb{Z}
-\end{align}
-}
-where $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
+\alert{[Formulate: Decoherence \& Localization]}
+Hardware suffers from...
+For this reason one is not guaranteed to find optimal solutions
 
-{\color{red} Paragraph on how this is solved classically.
-Include strengths and drawbacks of classical solution.}
+\alert{[Formulate: Simulations]}
+To understand findings and limitations, we mimic the hardware
+
+In section \ref{sec:methods} we propose an algorithm that maps ILP problems to QA hardware (\ref{sec:methods:ilp}) and present an example implementation in case of the Minimial Dominating Set problem (\ref{sec:methods:mds}).
+We review the annealing process on the utilized hardware (\ref{sec:methods:annealing}) and describe the computational framework which we used to simulate the annealing process (\ref{sec:methods:simulation}).
+Section \ref{sec:results} summarizes our findings and presents...
+We conclude this report in \ref{sec:conclusion}.
+All algorithms used and data obtained are publicly available (\ref{sec:open-source})
 
@@
 
+This section presents how a general ILP is mapped to a QUBO.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Integer linear programming}
+\label{sec:methods:ilp-def}
+%----------------------------------------------------------------------------------------
+Formally, ILP is defined as the optimization of a linear function
+\begin{align}
+    \label{eq:initial-ip-def}
+    \vec x_0 = \mathrm{arg} &\min\limits_{x}(\sum_i c_i x_i)
+\end{align}
+subject to
+\begin{align}
+    \label{eq:ilp-constraints}
+    &\sum_i A_{ai}x_i +b_a \leq 0 \,,\\
+    & x_i  \in \mathbbm{N}
+\end{align}
+
+where the natural numbers $\mathbbm{N}$ include zero, $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
+
 %----------------------------------------------------------------------------------------
@@
 
-The inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
-{\color{blue}
+The inequality constraints in eq.~\eqref{eq:ilp-constraints} can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
 \begin{align}
-    f(x) = &\min(\sum_i c_i x_i),\\
-    \textrm{subject to} \quad & \sum_i A_{a i}x_i + s_a + b_a = 0,\\
-    & s_a \geq 0,\\
-    & s_a \in \mathbb{Z},\\
-    & x_i \geq 0,\\
-    & x_i \in \mathbb{Z}.
+    \vec x_0 = \mathrm{arg} &\min(\sum_i c_i x_i)\,,
 \end{align}
-}
-Since quantum annealing solves the QUBO problem, we extend the proposed algorithm to solve integer quadratic optimization problems such that
-{\color{blue}
+subject to
+\begin{align}& \sum_i A_{a i}x_i + s_a + b_a = 0,\\
+    & s_a \in \mathbb{N},\\
+    & x_i \in \mathbb{N}.
+\end{align}
+While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).
+
+Because quantum annealing is capable of solving quadratic problems, we extend the proposed algorithm to solve integer quadratic optimization problems as well such that
 \begin{align}
-    f(x) = \min\limits_{x}(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i)
+    \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
 \end{align}
-}
 without the introduction of auxiliary qubits.
@@
 
-We map integer variables $z_i$ to qubits under the following transformation~\cite{Chang:2018uoc}
+We map integer variables $\vec z = \vec x, \vec s$ to qubits under the following transformation~\cite{Chang:2018uoc}
 \begin{align}
@@
 \end{align}
-where $\psi_{ri} \in \{0, 1\}$ while the number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
-The transformation can in general be express as a rectangular matrix.
+where $\psi_{ri} \in \{0, 1\}$.
+The number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
+This transformation can be expressed as a rectangular matrix.
 For example, a vector of two integer variables $z_0$ and $z_1$ represented by one and two qubits respectively is given as
@@
 \end{align}
-The transformation can be reduced to a tensor product if $R_i$ is a constant for all $i$ such that
+If all variables are represented by the same number of qubits--$R_i$ is a constant for all $i$--then one can express the transformation as tensor product of bit vectors
 \begin{align}
@@
 \end{align}
-
-While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbb{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
-As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).
 
@@
     \chi^2 = & \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
-    \nonumber\\
+    \nonumber\\ \label{eq:qubo-min}
     &\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
-    \Psi = & \begin{pmatrix}
-    \Psi^x\\
-    \Psi^s
-    \end{pmatrix},
+    \vec x_0 =&  T^x \vec \Psi^x_0 \, , 
+    \qquad (\vec \Psi^x_0, \vec \Psi^s_0) = \mathrm{arg}\min\limits_{\vec{\Psi}^x, \vec \Psi^s}(\chi^2) \,, &
 \end{align}
-where $p$ is the strength of the penalty factor which must be set large enough such that the constraints are satisfied under minimization.
+where $p$ is an external parameter representing the strength of the penalty when violating constraints.
 The objective function can be represented as a QUBO Hamiltonian
@@
 %----------------------------------------------------------------------------------------
+\subsubsection{Comment on penalty term}
+\label{sec:methods:ilp-qubo-comments}
+%----------------------------------------------------------------------------------------
+
+The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
+Thus some knowledge of the problem is required.
+In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
+After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
+Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
+
+%----------------------------------------------------------------------------------------
+\subsection{Example: Minimum Dominating Set Problem}
+\label{sec:methods:mds}
+%----------------------------------------------------------------------------------------
+
+%----------------------------------------------------------------------------------------
 \subsubsection{Minimum Dominating Set Problem}
-\label{sec:methods:mds}
+\label{sec:methods:mds-def}
 %----------------------------------------------------------------------------------------
@@
 \subsection{Quantum Annealing}
-\label{methods:annealing}
+\label{sec:methods:annealing}
 %----------------------------------------------------------------------------------------
@@
 \subsubsection{Modified annealing schedule}
-\label{methods:annealing-schedule}
+\label{sec:methods:annealing-schedule}
 %----------------------------------------------------------------------------------------
@@
 \section{CONCLUSION}
+\label{sec:conclusion}
 %========================================================================================
@@
 \section{DATA AVAILABILITY}
+\label{sec:open-source}
 %========================================================================================

### 2020-05-25 paper/figures/tdse_plots.py
Prettified anneal schedule plot

@@ -108,7 +108,7 @@ def aggregate():
         -0.05,
     ]:
         # for offset in [-0.04, 0.04]:
-        #for offset in [-0.04, 0.04]:
+        # for offset in [-0.04, 0.04]:
         data.params["offset"]["offset"] = "binary"
         data.params["offset"]["offset_min"] = offset
         data.params["offset"]["offset_range"] = abs(offset) * 2
@@ -139,7 +139,7 @@ def aggregate_nodeco():
         -0.04,
         -0.05,
     ]:
-        #for offset in [0.04, -0.04]:
+        # for offset in [0.04, -0.04]:
         data.params["offset"]["offset_min"] = offset
         data.params["offset"]["offset_range"] = abs(offset) * 2
         adata[offset] = data.get_data()
@@ -192,7 +192,12 @@ def plot_aggregate(adata, tag):
             color = blue
         tdse = adata[key].tdse
         idx, en, evec = tdse.ground_state_degeneracy(tdse.IsingH, 2e-2, debug=False)
-        ax.errorbar(x=adata[key].time, y=adata[key].prob, color=color, label=f"{int(key*2*100)}%")
+        ax.errorbar(
+            x=adata[key].time,
+            y=adata[key].prob,
+            color=color,
+            label=f"{int(key*2*100)}%",
+        )
     ax.set_xlabel("normalized time")
     ax.set_ylabel("MDS probability")
     ax.legend()
@@ -208,7 +213,7 @@ def plot_aggregate(adata, tag):
             color = red
         else:
             color = blue
-        ax.errorbar(x=2*xi, y=y[idx], ls="none", marker="o", color=color)
+        ax.errorbar(x=2 * xi, y=y[idx], ls="none", marker="o", color=color)
     ax.set_xlabel("offset range (%)")
     ax.set_ylabel("MDS probability")
     if tag == "deco":
@@ -216,7 +221,7 @@ def plot_aggregate(adata, tag):
     else:
         ax.set_ylim([0.9938, 0.99485])
     plt.draw()
-    #plt.savefig(f"./sim_{tag}.pdf", transparent=True)
+    # plt.savefig(f"./sim_{tag}.pdf", transparent=True)
 
     reg = 1e-9
     plt.figure(f"mutual information", figsize=(7, 4))
[…]

### 2020-05-25 paper/figures/tdse_plots.py
Prettified anneal schedule plot

@@ -108,7 +108,7 @@ def aggregate():
         -0.05,
     ]:
         # for offset in [-0.04, 0.04]:
-        #for offset in [-0.04, 0.04]:
+        # for offset in [-0.04, 0.04]:
         data.params["offset"]["offset"] = "binary"
         data.params["offset"]["offset_min"] = offset
         data.params["offset"]["offset_range"] = abs(offset) * 2
@@ -125,7 +125,7 @@ def aggregate_nodeco():
     data = Data()
     data.params["wave"]["gamma"] = 0.0
     data.params["offset"]["offset"] = "binary"
-    #for offset in [
+    # for offset in [
     #    0.05,
     #    0.04,
     #    0.03,
@@ -137,7 +137,7 @@ def aggregate_nodeco():
     #    -0.03,
     #    -0.04,
     #    -0.05,
-    #]:
+    # ]:
     for offset in [0.04, -0.04]:
         data.params["offset"]["offset_min"] = offset
         data.params["offset"]["offset_range"] = abs(offset) * 2
@@ -191,7 +191,12 @@ def plot_aggregate(adata, tag):
             color = blue
         tdse = adata[key].tdse
         idx, en, evec = tdse.ground_state_degeneracy(tdse.IsingH, 2e-2, debug=False)
-        ax.errorbar(x=adata[key].time, y=adata[key].prob, color=color, label=f"{int(key*2*100)}%")
+        ax.errorbar(
+            x=adata[key].time,
+            y=adata[key].prob,
+            color=color,
+            label=f"{int(key*2*100)}%",
+        )
     ax.set_xlabel("normalized time")
     ax.set_ylabel("MDS probability")
     ax.legend()
@@ -240,7 +245,12 @@ def plot_aggregate(adata, tag):
             [tdse.vonNeumann_entropy(sol.y[:, i], reg) for i in range(sol.t.size)]
         ).real
         mutual_information = entropyA + entropyB - entropyAB
-        ax.errorbar(x=adata[key].time, y=mutual_information, color=color, label=f"{int(key*2*100)}%")
+        ax.errorbar(
+            x=adata[key].time,
+            y=mutual_information,
+            color=color,
+            label=f"{int(key*2*100)}%",
+        )
[…]

### 2020-05-25 paper/figures/tdse_plots.py
Added anotation to schedule plot

@@ -312,6 +312,10 @@ def plot_schedule(adata):
     ax.errorbar(x=X, y=z2[:, 0], ls="--", color="k")
     ax.errorbar(x=X, y=y2[:, -1], ls="--", color=red)
 
+    ax.annotate(s=f"{y2[-1,  0]:1.2f}", xy=(X[-1], y2[-1, 0]), color=blue, va="bottom")
+    ax.annotate(s=f"{z2[-1,  0]:1.2f}", xy=(X[-1], z2[-1, 0]), color="k", va="center")
+    ax.annotate(s=f"{y2[-1, -1]:1.2f}", xy=(X[-1], y2[-1, -1]), color=red, va="top")
+
     l1 = ax.plot(np.nan, np.nan, ls="-", color="black")[0]
     l2 = ax.plot(np.nan, np.nan, ls="--", color="black")[0]
 

### 2020-05-25 paper/figures/tdse_plots.py
Added anotation to schedule plot

@@ -313,6 +313,10 @@ def plot_schedule(adata):
     ax.errorbar(x=X, y=z2[:, 0], ls="--", color="k")
     ax.errorbar(x=X, y=y2[:, -1], ls="--", color=red)
 
+    ax.annotate(s=f"{y2[-1,  0]:1.2f}", xy=(X[-1], y2[-1, 0]), color=blue, va="bottom")
+    ax.annotate(s=f"{z2[-1,  0]:1.2f}", xy=(X[-1], z2[-1, 0]), color="k", va="center")
+    ax.annotate(s=f"{y2[-1, -1]:1.2f}", xy=(X[-1], y2[-1, -1]), color=red, va="top")
+
     l1 = ax.plot(np.nan, np.nan, ls="-", color="black")[0]
     l2 = ax.plot(np.nan, np.nan, ls="--", color="black")[0]
 

### 2020-05-25 paper/figures/tdse_plots.py
Added initial anneal annotation

@@ -317,6 +317,14 @@ def plot_schedule(adata):
     ax.annotate(s=f"{z2[-1,  0]:1.2f}", xy=(X[-1], z2[-1, 0]), color="k", va="center")
     ax.annotate(s=f"{y2[-1, -1]:1.2f}", xy=(X[-1], y2[-1, -1]), color=red, va="top")
 
+    ax.annotate(
+        s=f"{z2[0, 0]:1.2f}",
+        xy=(X[0], z2[0, 0] + 0.2),
+        color="k",
+        va="bottom",
+        ha="left",
+    )
+
     l1 = ax.plot(np.nan, np.nan, ls="-", color="black")[0]
     l2 = ax.plot(np.nan, np.nan, ls="--", color="black")[0]
 

### 2020-05-25 paper/figures/tdse_plots.py
Added initial anneal annotation

@@ -316,6 +316,14 @@ def plot_schedule(adata):
     ax.annotate(s=f"{z2[-1,  0]:1.2f}", xy=(X[-1], z2[-1, 0]), color="k", va="center")
     ax.annotate(s=f"{y2[-1, -1]:1.2f}", xy=(X[-1], y2[-1, -1]), color=red, va="top")
 
+    ax.annotate(
+        s=f"{z2[0, 0]:1.2f}",
+        xy=(X[0], z2[0, 0] + 0.2),
+        color="k",
+        va="bottom",
+        ha="left",
+    )
+
     l1 = ax.plot(np.nan, np.nan, ls="-", color="black")[0]
     l2 = ax.plot(np.nan, np.nan, ls="--", color="black")[0]
 

### 2020-05-25 paper/figures/tdse_plots.py
[Debug] Corrected color / offset order of anneal plot

@@ -341,9 +341,9 @@ def plot_schedule(adata):
             "B(s)",
             "",
             r"$\it{Offset}$",
-            "Negative",
-            "Default",
             "Positive",
+            "Default",
+            "Negative",
         ],
         frameon=False,
         ncol=2,

### 2020-05-25 paper/figures/tdse_plots.py
[Debug] Corrected color / offset order of anneal plot

@@ -342,9 +342,9 @@ def plot_schedule(adata):
             "B(s)",
             "",
             r"$\it{Offset}$",
-            "Negative",
-            "Default",
             "Positive",
+            "Default",
+            "Negative",
         ],
         frameon=False,
         ncol=2,

### 2020-05-26 paper/main.tex

@@
 
+This sections demonstrates the formalism in case of an example ILP: the Minimum Dominating Set problem.
+
 %----------------------------------------------------------------------------------------
-\subsubsection{Minimum Dominating Set Problem}
+\subsubsection{Definition of the Minimum Dominating Set Problem}
 \label{sec:methods:mds-def}
@@
 
-The target Hamiltonian can be written in the matrix form
-\begin{widetext}
+The target QUBO in the notation of eq.~\eqref{eq:matrix_form} reads
+{\small
 \begin{align}
-    E = &
-    \begin{pmatrix}
-    \Psi^x & \Psi^s
-    \end{pmatrix}
-    \begin{pmatrix}
-    \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] & - p(\mathbbm{1}+J^T)T^s\\
-    - p{T^s}^T(\mathbbm{1}+J)& p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]
-    \end{pmatrix}
-    \begin{pmatrix}
-    \Psi^x\\ \Psi^s
-    \end{pmatrix} + p \overline{\overline{V}}
-    \label{eq:matrix_form}
-\end{align}
-\end{widetext}
+    Q_{xx} &= \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] \,,\\
+    Q_{sx} &= - p(\mathbbm{1}+J^T)T^s\,,\\
+    Q_{ss} &= p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]\,,\\
+    C &=  p \overline{\overline{V}}\,,
+\end{align}}
 where $ |M| \equiv \sum_{\nu} M_{\nu \mu}$.
@@
 
-In quantum annealing, the ground state of the problem Hamiltonian is obtained from the evolution of a time-dependent Hamiltonian,
+A quantum annealer evolves the ground state of an initial Hamiltonian into the ground state of the problem Hamiltonian by adiabatically changing the hardware which implements Hamiltonian.
+Thus, the implemented Hamiltonian is explicitly time dependent
 \begin{equation}
@@
 \end{equation}
-where $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, and $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
-The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ (CK: time unit mapping) on the DWave.
-On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits.
+and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
+The variable $s\in [0, 1]$ is the normalized annealing time and, in physical units, is allowed to vary between 1$\mu s$ to 2$ms$ on DWave.
+
+On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
 In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in addition to the effects of applying positive and negative offsets.
-Note that due to the way the offsets are implemented on the hardware level, systematic errors are introduced since the initial and final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
+Note that due to the way the offsets are implemented on the hardware level, systematic errors are introduced since the initial and final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets ($B_i(s) \neq B_j(s)$).
 Fig.~\ref{fig:anneal_schedule} shows the maximum offset that we use for the study, which translates to approximately (due to non-linearity) a 5\% advancement (blue) or delay (red) in the schedule.
 
-\begin{figure}[b]
+\begin{figure}[htb]
     \centering
@@
 The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system in general will exhibit more disorder.
-We define disorder by first recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
+When recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
 \begin{equation}
@@
 \end{equation}
-and recognize that in the limit where $h_i$ is randomly drawn from a Bernoulli distribution we recover the spin-glass model.
+we recognize that if $h_i$ is randomly drawn from a Bernoulli distribution we recover the spin-glass model.
 The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization.
@@
 %----------------------------------------------------------------------------------------
-Say what the simulator is solving
-
-{\color{blue}
 
@@
 $\{, \}$ denotes the anti-commutator.
-In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
+In this study, we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
 The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
-For simplicity we assume all qubits having the same relaxation time.
+For simplicity, we assume all qubits have the same relaxation time.
 The initial condition is the Gibbs canonical ensemble
@@
 where $\beta$ is the inverse temperature.
-The probability to get the ground state at measurement is
+The probability to obtain the ground state at for a single measurement is
 \begin{align}
-    P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
+    P_{\mbox{gnd}} =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
 \end{align}
-where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
+where the projection operator onto the degenerated ground states subspace is defined as
+\begin{equation}
+	\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i|
+	\, .
+\end{equation}
 Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
 
-}
-
-With anneal offsets
 %----------------------------------------------------------------------------------------

### 2020-05-26 paper/main.tex
Wording

@@
 To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
-For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA) and investigated problem and hardware-specific limitations.
+For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA), and investigated problem and hardware-specific limitations.
 This work presents the formalism of how to map ILP problems to the annealing architectures.
@@
 Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints and is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}.
-In general however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
+In general, however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
+Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
 The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem can be obtained in polynomial time, the optimal integer solution in general must be found in the $2^n$ integer solutions which surround the real number solution.
-Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
 While greedy algorithms do not guarantee optimal global solutions, they find approximate solutions in polynomial time, which can be utilized in further computations.
-Due to the importance and difficulty, in this work we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.
+Due to the importance and difficulty, in this work, we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.
 
 Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{}.
-Through the adiabatic theorem of quantum mechanics, the annealer is prepared initially in a trivial ground state while the solution to ILP is encoded in the target Hamiltonian.
+Through the adiabatic theorem of quantum mechanics, the annealer is initially prepared in a trivial ground state while the final Hamiltonian encodes the solution to the ILP.
 Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems~\cite{2018Glover}.
@@
 
-In section \ref{sec:methods} we propose an algorithm that maps ILP problems to QA hardware (\ref{sec:methods:ilp}) and present an example implementation in case of the Minimial Dominating Set problem (\ref{sec:methods:mds}).
+In section \ref{sec:methods} we propose an algorithm that maps ILP problems to QA hardware (\ref{sec:methods:ilp}) and present an example implementation in case of the Minimal Dominating Set problem (\ref{sec:methods:mds}).
 We review the annealing process on the utilized hardware (\ref{sec:methods:annealing}) and describe the computational framework which we used to simulate the annealing process (\ref{sec:methods:simulation}).
@@
 
-This section presents how a general ILP is mapped to a QUBO.
+This section presents the formalism which maps a general ILP to a QUBO.
 
@@
 
-This sections demonstrates the formalism in case of an example ILP: the Minimum Dominating Set problem.
+This section demonstrates the formalism in case of an example ILP: the Minimum Dominating Set problem.
 
@@
 Fig.~\ref{fig:dominating_sets}c shows an example of the minimum dominating set of $G(V, E)$ and is different from the minimal dominating set.
-We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set in general can have a smaller domination number.
+We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
 As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a problem that is well studied for quantum annealers~\cite{}.
@@
 
-The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system in general will exhibit more disorder.
+The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system, in general, will exhibit more disorder.
 When recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
@@
 \end{equation}
-we recognize that if $h_i$ is randomly drawn from a Bernoulli distribution we recover the spin-glass model.
-The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization.
+we recognize that if $h_i$ is randomly drawn from a Bernoulli distribution, we recover the spin-glass model.
+The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analog of Anderson Localization.
 
@@
 For the following studies, we perform experiments on the \texttt{DW\_2000Q\_5} solver.
-The annealing time is optimized to 600$\mu$s after performing a study on the $G(6)$ graph as shown in Fig.~\ref{fig:at_scale}.
+After performing a study on the $G(6)$wgraph, We selected an annealing time is of 600$\mu$s that optimizes the probability of finding the ground state, as shown in Fig.~\ref{fig:at_scale}.
 In Fig.~\ref{fig:baseline}, we show results from the baseline experiment, without modification to the default DWave annealing schedule, and observe improvement over random guessing.
-However, the experiment results reflect the same degeneracy structure as random guessing, and scale exponentially poorly for larger number of vertices $n$.
+However, the experiment results reflect the same degeneracy structure as random guessing and scale exponentially poorly for a larger number of vertices $n$.
 We explore one avenue towards improving the experiment results by introducing per-qubit annealing offsets into the time evolution.
@@
 We then symmetrically offset the two groups of qubits over a total range between 0\% and 10\% (-5\% to +5\%).
-The results of this study is shown in Fig.~\ref{fig:dwave_offset}.
+The results of this study are shown in Fig.~\ref{fig:dwave_offset}.
 
@@
     \includegraphics[width=\columnwidth]{./figures/scaling_comparison_all.pdf}
-    \caption{The legend labels the total range of the symmetric offset employed.
+    \caption{The legend labels the entire range of the symmetric offset employed.
 A positive range indicates that the group of qubits with small values of $|h_i|$ are advanced (qubits with large values of $|h_i|$ are equivalently delayed), and vice versa for results labeled with a negative range.}
@@
 
-Finally, we note that due to the inherent variance in performance when using different physical qubits, for each graph, we perform the offset study on the same physical qubits.
+Finally, we note that due to the inherent variance in performance when using different physical qubits, we perform the offset study on the same physical qubits for each graph.
 Additionally, the largest offset ranges sampled are at the limits of the hardware capabilities of the DWave annealer.
@@
 We observe from Fig.~\ref{fig:dwave_offset} that advancing qubits subject to \textit{larger} final external magnetic fields yields approximately an order of magnitude improvement over the baseline results at the largest offset range.
-In contrast advancing qubits with weaker magnetic fields consistently hurts the performance of the annealer.
+In contrast, advancing qubits with weaker magnetic fields consistently hurts the performance of the annealer.
 This result is surprising in light of the expectation from many-body localization.
-We provide an explanation of this surprising result by simulating the annealing process of the annealer which are discussed in the following sections.
+We explain this surprising result by simulating the annealing process of the annealer, which we discuss in the following sections.
 
@@
 
-In order to understand the effects of annealing offsets, we simulate the annealing process on 5 qubits for a $G(2)$ graph embedded in chimera topography.
-In order to shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
+In order to understand the effects of annealing offsets, we simulate the annealing process on five qubits for a $G(2)$ graph embedded in chimera topography.
+To shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
 The resulting ground state probability as a function of offset measured over 200,000 observations is shown in Fig.~\ref{fig:dwave1us} (Top).
@@
 
-For the simulation, the QUBO is obtained from the output of the DWave such that the same embedding is used.
-The time-dependence is obtained by solving the Lindblad equation subject to the DWave annealing schedule with offsets allowing us to incorporate a decoherence model in our simulation.
+The simulation utilizes the same Hamiltonian as DWave, which corresponds to the embedded original MDS QUBO.
+The time-dependent solution is obtained by solving the Lindblad equation subject to the DWave annealing schedule with offsets allowing us to incorporate a decoherence model in our simulation.
 The details of the Lindbladian are given in Sec.~\ref{sec:methods:lindblad}.
 Following Ref.~\cite{}, we fix the temperature of the simulation to 15 milliKelvins to reflect the reported operating temperature of the DWave.
-Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian is approximately 2 Kelvins as shown in Fig.~\ref{fig:spectrum}.
+Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian is approximately 2 Kelvins, as shown in Fig.~\ref{fig:spectrum}.
 As a result, the DWave operates at effectively zero-temperature for this example problem.
 
-We then set an effective $T_1$ coherence time to 20 $ns$ in order to match the DWave probability of finding the MDS of $G(2)$ at approximately 86\%.
+We then set an effective $T_1$ coherence time to 20 $ns$ to match the DWave probability of finding the MDS of $G(2)$ at approximately 86\%.
 A detailed study of $T_1$ is given in Sec.~\ref{sec:methods:deco}.
 We emphasize that the effective coherence time is much longer than the single qubit coherence time of 0.5 $ns$ reported by DWave, while still being orders of magnitude shorter than the total anneal time.
-The simulation and the experiment however, both are able to recover the ground state with high probability regardless, and exemplifies the robustness of quantum annealing.
+The simulation and the experiment, however, both can recover the ground state with high probability regardless and exemplify quantum annealing's robustness.
 
@@
 
-The probability of finding the MDS from the simulation with and without decoherence are given in Fig.~\ref{fig:dwave_offset} (Middle) and (Bottom).
+We present the simulated probability of finding the MDS with and without decoherence in Fig.~\ref{fig:dwave_offset} (Middle) and (Bottom).
 We observe that with decoherence, the simulation captures the rough features of the experiment, including a steady improvement for negative offsets, and similar non-linear behavior at positive offsets.
-Additionally, the range of probabilities in the simulation non-trivially match the range observed in experiment.
-In contrast, simulations without decoherence exemplify the opposite behavior with respect to offsets, in line with expectation from many-body localization.
-Therefore, the simulation provides evidence in relating the improvement seen on the DWave to the effects of decoherence rather than many-body localization, while for idealized annealing, the effects of many-body localization become important.
+Additionally, the range of probabilities in the simulation non-trivially matches the range observed in the experiment.
+In contrast, simulations without decoherence exemplify the opposite behavior concerning offsets, in line with expectations from many-body localization.
+Therefore, the simulation provides evidence in relating the improvement seen on the DWave to the effects of decoherence rather than many-body localization, while for idealized annealing, the effects of many-body localization become essential.
 
-In both simulations, the system experience a relatively large jump in probability, at -10\% and +30\% respectively.
+In both simulations, the system experience a relatively big jump in probability, at -10\% and +30\%, respectively.
 For the simulation with decoherence, this behavior is inconsistent with experiment.
 {\color{red} eh..
-guess a reason?} Additionally, both simulations experience vanishing probability at +10\% offset.
-This behavior is expected to happen eventually in experiment as well when the two sets of qubits become too aggressively staggered and effectively decouple.
-The simulation however, incorrectly predicts when the decoupling happens.
+guess a reason?} Additionally, both simulations experience vanishing probability at a +10\% offset.
+This behavior is expected to happen eventually in the experiment as well when the two sets of qubits become too aggressively staggered and effectively decouple.
+The simulation, however, incorrectly predicts when the decoupling happens.
 
@@
 
-Intuitively, we want the system to explore a larger state space to increase the probability for the system to reach the final ground state.
+Intuitively, we want the system to explore a more extensive state space to increase the probability for the system to reach the final ground state.
 That is, we want the system to have ergodicity in order to avoid MBL.
 On the other hand, decoherence in the hardware leads to the loss of quantum information.
-It is therefore desirable to minimize the effect of relaxation.
+It is, therefore, desirable to minimize the effect of relaxation.
 The interplay between these two competing effects can be observed by looking at the time-dependent probability of reaching the final ground state, and the mutual information.
@@
 
-From Fig.~\ref{fig:prob_mi} we observe that when the anneal schedule is modified to delay stronger external magnetic fields, the phase transition is delayed, yielding larger mutual information, and in turn probes a larger state space.
+From Fig.~\ref{fig:prob_mi}, we observe that when the annealing schedule is modified to delay stronger external magnetic fields, the phase transition is delayed, yielding larger mutual information, and in turn probes a larger state space.
 This observation is independent of the effects of decoherence, and only relies on delaying the phase transition later in the annealing process.
-It then follows that the effects of decoherence is in competition with delocalization because the system is required to exhibit its quantum mechanical nature for longer.
-In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and {\color{blue}become unaffected by dephasing.} This phenomena is demonstrated by the left panels in Fig.~\ref{fig:prob_mi} where in the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this.
+It then follows that the effects of decoherence competes with delocalization because the system is required to exhibit its quantum mechanical nature for longer.
+In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and become unaffected by dephasing.
+The left panels in Fig.~\ref{fig:prob_mi} demonstrate this phenomenon wherein the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this.
 top one the red is always below blue, the bottom one, the red crosses the blue after the phase transition).

### 2020-05-26 paper/main.tex
Added MBL section

@@
 \begin{align}
-    \chi^2 = & \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
+    \chi^2 &= \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
     \nonumber\\ \label{eq:qubo-min}
-    &\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
-    \vec x_0 =&  T^x \vec \Psi^x_0 \, ,
-    \qquad (\vec \Psi^x_0, \vec \Psi^s_0) = \mathrm{arg}\min\limits_{\vec{\Psi}^x, \vec \Psi^s}(\chi^2) \,, &
+    &\qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
+    \vec x_0 &=  T^x \vec \Psi^x_0 \, ,
+    \\
+    (\vec \Psi^x_0, \vec \Psi^s_0) &= \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,, &
 \end{align}
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{Other Simulation Details}
-%----------------------------------------------------------------------------------------
-Temperature
-Initial wave function choices
-RK tolerance
-
-%----------------------------------------------------------------------------------------
 \subsubsection{Decoherence Time}
@@
 \end{figure}
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Many-Body Localization}
+\label{sec:methods:mbl}
+%----------------------------------------------------------------------------------------
+
+If the annealer does not reach thermal equilibrium, for example, strong external magnetic fields freeze in individual qubits, the final solution of the annealing process might not encode the ground state of the final Hamiltonian.
+It is thus essential to prepare the system such that Many-Body Localizations are absent, and thus one must define a measure for MBL.
+
+We consider the mutual information as a measure for shared information between different partitions (sets of qubits) of the entire system.
+Given two partitions $A$ and $B$, the mutual information is defined as 
+\begin{equation}
+    I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B}) \geq 0\,,
+\end{equation}
+which is only zero if partitions $A$ and $B$ do not share information.
+We describe individual density information measures by the von Neumann entropy $S(\rho)=-\mbox{Tr}\rho \log_2 \rho$.
+The density matrix $\rho_{A,B}$ represents the entire system while $\rho_{A}=\mbox{Tr}_{B} (\rho_{A,B})$ is the reduced density matrix for the subsystem A (and equivalent $B$ for exchanged indicies).
+
+We note that this measure depends on the choice of partitions, which is, in principle, arbitrary.
+To define a measure for MBL, the choice for partitions should encode the likelihood of frozen qubits. 
+Thus a natural choice for partitions are regions of different external magnetic fields.
+For this choice, at the beginning of the anneal, the mutual information will be zero as all spins start orthogonal to the external field, and, in the end, the mutual information will be constant once a final solution is obtained.
+Intermediate values for the mutual information encode the communication probability of different spin alignments.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Decoherence and Many-Body Localization}
+\label{sec:methods:decoherence-and-mbl}
+%----------------------------------------------------------------------------------------
+
+Intuitively, to find a final state which globally minimizes the energy, we want the system to explore the entire state space.
+That is, we want the system to have ergodicity in order to avoid Many-Body Localizations.
+Thus the annealing process should be sufficiently slow to not introduce potential barriers which freeze in intermediate spin configurations.
+On the other hand, decoherence in the hardware leads to the loss of quantum information.
+It is, therefore, desirable to minimize the effect of relaxation and shorten the annealing process.
+The interplay between these two competing effects can be observed by looking at the non-monotonous time dependency of the probability for reaching the global ground state.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Other Simulation Details}
+%----------------------------------------------------------------------------------------
+Temperature
+Initial wave function choices
+RK tolerance
 
@@
 For the following studies, we perform experiments on the \texttt{DW\_2000Q\_5} solver.
-After performing a study on the $G(6)$wgraph, We selected an annealing time is of 600$\mu$s that optimizes the probability of finding the ground state, as shown in Fig.~\ref{fig:at_scale}.
+After performing a study on the $G(6)$ graph, We selected an annealing time is of 600$\mu$s that optimizes the probability of finding the ground state, as shown in Fig.~\ref{fig:at_scale}.
 In Fig.~\ref{fig:baseline}, we show results from the baseline experiment, without modification to the default DWave annealing schedule, and observe improvement over random guessing.
@@
 
-Following this logic, we split the qubits into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific problem.
+Following this logic, we split the qubits into two groups depending on the value of $h_i$ relative to $(\max(h_i) - \min(h_i)) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific problem.
 We then symmetrically offset the two groups of qubits over a total range between 0\% and 10\% (-5\% to +5\%).
@@
 
-\begin{figure}[b]
+\begin{figure}[htb]
     \centering
@@
 
-We present the simulated probability of finding the MDS with and without decoherence in Fig.~\ref{fig:dwave_offset} (Middle) and (Bottom).
+We present the simulated probability of finding the MDS with and without decoherence in Fig.~\ref{fig:dwave1us} (Middle) and (Bottom).
 We observe that with decoherence, the simulation captures the rough features of the experiment, including a steady improvement for negative offsets, and similar non-linear behavior at positive offsets.
@@
 We provide further evidence of the competing effects between decoherence and many-body localization in this section.
-
-Intuitively, we want the system to explore a more extensive state space to increase the probability for the system to reach the final ground state.
-That is, we want the system to have ergodicity in order to avoid MBL.
-On the other hand, decoherence in the hardware leads to the loss of quantum information.
-It is, therefore, desirable to minimize the effect of relaxation.
-The interplay between these two competing effects can be observed by looking at the time-dependent probability of reaching the final ground state, and the mutual information.
-The mutual information is defined as $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition $A$ and partition $B$ of the total system.
-$S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.
-{\color{blue} $\rho_{A,B}$ is the density matrix for the total system.
-$\rho_{A}=\mbox{Tr}_{B} (\rho_{A,B})$ is the reduced density matrix for the subsystem A.}
 

### 2020-05-28 paper/main.tex
Formatting

@@
  \label{eq:initial-ip-def}
-    \vec x_0 = \mathrm{arg} &\min\limits_{x}(\sum_i c_i x_i)
+ \vec x_0 = \mathrm{arg} & \min\limits_{x}(\sum_i c_i x_i)
 \end{align}
@@
  \label{eq:ilp-constraints}
-    &\sum_i A_{ai}x_i +b_a \leq 0 \,,\\
+  & \sum_i A_{ai}x_i +b_a \leq 0 \,, \\
   & x_i  \in \mathbbm{N}
@@
 \begin{align}
-    \vec x_0 = \mathrm{arg} &\min(\sum_i c_i x_i)\,,
+ \vec x_0 = \mathrm{arg} & \min(\sum_i c_i x_i)\,,
 \end{align}
 subject to
-\begin{align}& \sum_i A_{a i}x_i + s_a + b_a = 0,\\
-    & s_a \in \mathbb{N},\\
+\begin{align}              & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
+  & s_a \in \mathbb{N},                \\
   & x_i \in \mathbb{N}.
@@
  \begin{pmatrix}
-    z_0\\
+  z_0 \\
   z_1
@@
  \begin{pmatrix}
-    2^0 & 0 & 0\\
+  2^0 & 0   & 0   \\
   0   & 2^0 & 2^1
@@
  \begin{pmatrix}
-    \psi_{00}\\
-    \psi_{01}\\
+  \psi_{00} \\
+  \psi_{01} \\
   \psi_{11}
@@
  \equiv T^z \begin{pmatrix}
-    \psi_{00}\\
-    \psi_{01}\\
+  \psi_{00} \\
+  \psi_{01} \\
   \psi_{11}
@@
 \begin{align}
-    \mathcal{R} = & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},\\
-    \mathcal{Z} = & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},\\
-    |\mathds{1}| = & |\mathcal{Z}|,\\
+ \mathcal{R} =  & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},    \\
+ \mathcal{Z} =  & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},    \\
+ |\mathds{1}| = & |\mathcal{Z}|,                 \\
  T^z =          & \mathds{1}\otimes \mathcal{R}.
@@
 \begin{align}
-    \chi^2 &= \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
-    \nonumber\\ \label{eq:qubo-min}
-    &\qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
-    \vec x_0 &=  T^x \vec \Psi^x_0 \, ,
+ \chi^2                         & = \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
+ \nonumber                                                                                                                             \\ \label{eq:qubo-min}
+                                & \qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],   \\
+ \vec x_0                       & =  T^x \vec \Psi^x_0 \, ,
  \\
-    (\vec \Psi^x_0, \vec \Psi^s_0) &= \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,, &
+ (\vec \Psi^x_0, \vec \Psi^s_0) & = \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,,                                                 &
 \end{align}
@@
  \begin{pmatrix}
-    Q_{xx} & Q_{xs}\\
+  Q_{xx} & Q_{xs} \\
   Q_{sx} & Q_{ss}
@@
  \begin{pmatrix}
-    \Psi^x\\ \Psi^s
-    \end{pmatrix} + pb^2,\\
+  \Psi^x \\ \Psi^s
+ \end{pmatrix} + pb^2, \\
  \equiv & \Psi^T Q \Psi + C,
@@
  Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x \nonumber \\
-    &+ \mathrm{Diag}_{\psi^x}(c) T^x,\\
-    Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,\\
+          & + \mathrm{Diag}_{\psi^x}(c) T^x,                                                                    \\
+ Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,                                                                     \\
  Q_{ss} = & p\left[ {T^{s}}^T T^s + \mathrm{Diag}_{\psi^s}\left( {T^{s}}^T b + b^T T^s\right) \right].
@@
                    &
-    \includegraphics[width=0.20\textwidth]{./figures/subaru_mds2.pdf}\\
+  \includegraphics[width=0.20\textwidth]{./figures/subaru_mds2.pdf} \\
   \centering\bf{a} & \centering\bf{b} & \centering\bf{c}
@@
                    &
-    \includegraphics[width=0.20\textwidth]{./figures/greedy-4.pdf}\\
+  \includegraphics[width=0.20\textwidth]{./figures/greedy-4.pdf}            \\
   \centering\bf{a} & \centering\bf{b} & \centering\bf{c} & \centering\bf{d}
@@
 \begin{align}
-    f(x) = &\min\left(\sum_{\nu \in V} \psi^x_{\nu}\right),\\
-    \textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1,\\
+ f(x) =                    & \min\left(\sum_{\nu \in V} \psi^x_{\nu}\right),                    \\
+ \textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1, \\
                            & \psi^x_{\nu} \in \{0, 1\}
@@
 \begin{align}
-    f(x) = &\min(\sum_{\nu\in V} \psi^x_{\nu}),\\
-    \textrm{subject to} \quad & \psi^x_{\nu} + J_{\nu \mu} \psi^x_{\mu}- T^s_{\nu \alpha} \psi^s_{\alpha}  - 1 = 0,\\
-    & \psi_{\nu} \in \{0, 1\},\\
-    & 0 \leq s_{\nu} \leq |\mathrm{N}(\nu)|\\
+ f(x) =                    & \min(\sum_{\nu\in V} \psi^x_{\nu}),                                                 \\
+ \textrm{subject to} \quad & \psi^x_{\nu} + J_{\nu \mu} \psi^x_{\mu}- T^s_{\nu \alpha} \psi^s_{\alpha}  - 1 = 0, \\
+                           & \psi_{\nu} \in \{0, 1\},                                                            \\
+                           & 0 \leq s_{\nu} \leq |\mathrm{N}(\nu)|                                               \\
                            & s_{\nu} \in \mathbb{Z},
@@
   \begin{align}
-    Q_{xx} &= \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] \,,\\
-    Q_{sx} &= - p(\mathbbm{1}+J^T)T^s\,,\\
-    Q_{ss} &= p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]\,,\\
-    C &=  p \overline{\overline{V}}\,,
+   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] \,, \\
+   Q_{sx} & = - p(\mathbbm{1}+J^T)T^s\,,                                                                     \\
+   Q_{ss} & = p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]\,,                                  \\
+   C      & =  p \overline{\overline{V}}\,,
   \end{align}}
@@
  \label{eq:annealH}
-     H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\
-     +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
+ H_{anneal}(t) & =  - \sum_i  A_i(t)\sigma^x_i                                                                      & \notag \\
+ +             & \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  , &
 \end{align}
@@
 \begin{align}
-    &1 &&\textrm{if} && n\textrm{ mod }3=0,\nonumber \\
-    &2\lfloor n/3 \rfloor + 1 && \textrm{if}&& n\textrm{ mod }3=1,\nonumber \\
-    &\lfloor n/3 \rfloor + 2 && \textrm{if} && n \textrm{ mod }3 = 2,
+  & 1                        &  & \textrm{if} &  & n\textrm{ mod }3=0,\nonumber \\
+  & 2\lfloor n/3 \rfloor + 1 &  & \textrm{if} &  & n\textrm{ mod }3=1,\nonumber \\
+  & \lfloor n/3 \rfloor + 2  &  & \textrm{if} &  & n \textrm{ mod }3 = 2,
 \end{align}
@@
 \end{figure}
+
+cpan -i File::HomeDir Unicode::GCString
 

### 2020-05-28 paper/main.tex
Added links to GH issues

@@
 
+\newcommand{\ghissue}[2]{
+ \noindent\fbox{\parbox{0.49\textwidth}{
+   \alert{[#1]}%
+   \\%
+   \href{https://github.com/cchang5/quantum\_linear\_programming/pull/#2}{See GitHub issue #2}}%
+ }}
+}
+
 \begin{abstract}
@@
  We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.
-  %Conclusion: What do these findings mean to us?
-  [Rephrase] We need better hardware to challenge heuristic solvers but we identified how to optimize hardware.
-  %Perspectives: What should be done next?
-  [Rephrase] Better understand correlations and localizations and improve simulation to scale to larger problems.
+
+ \ghissue{Finalize abstract}{13}
 
@@
 
-\alert{[Formulate: Decoherence \& Localization]}
-Hardware suffers from...
-For this reason one is not guaranteed to find optimal solutions
+\ghissue{Decoherence \& Localization}{14}
 
-\alert{[Formulate: Simulations]}
-To understand findings and limitations, we mimic the hardware
+\ghissue{Simulations}{15}
 
@@
  \includegraphics[width=\columnwidth]{./figures/anneal_schedule.pdf}
- \caption{asdf}
+ \caption{
+  Anneal schedules for amplitudes of initial Hamiltonian (solid) and final Hamiltonian (dashed) are displayed for a complete anneal schedule.
+  Different colors represent different offesets: advanced (blue), default (black) and delayed (red).
+ }
  \label{fig:anneal_schedule}
@@
 
-Mention long coherence time asymptote to right value.
-
-Scan coherence time, match to DWave.
-
-Some more discussion about short coherence time and why it makes sense?
-
-Travis said: Regarding T1 << T effecting the state at time T, I am thinking more about the point that the very short T1 dephasing time has the effect of quenching any coherence.
-In this regard, a very short T1 is pushing the systems toward a classical annealing model.
-The absence of any dephasing is then the best-case quantum annealing model.
-Consequently, the difference in outcome would trace back to this coherence being present.
+\ghissue{Decoherence section}{#16}
 
@@
  \includegraphics[width=\columnwidth]{./figures/coherence.pdf}
- \caption{asdf}
+ \caption{To be updated}
  \label{fig:prob_mi}
@@
 %----------------------------------------------------------------------------------------
-Temperature
-Initial wave function choices
-RK tolerance
+
+\ghissue{Simulation details}{#18}
 
@@
 
-Things to do:
-
-Compute dwave mutual information
-
-Study ground state degeneracy by plotting distribution of states.
+\ghissue{Finalize results}{#19}
 
@@
 
+\ghissue{Conclusion}{#20}
+
 %========================================================================================
@@
 
-Link to GitHub.
+\ghissue{Data availability}{#21}
 
@@
 
+\ghissue{Acknowledgements}{#22}
 We thank x, y, z...
@@
 
+\ghissue{Author contributions}{#23}
 C.K. drank a lot of coffee.
@@
 \bibliography{qilp}
+\ghissue{References}{#24}
 %========================================================================================

### 2020-06-01 paper/main.tex
[Debug] Syntax
push for runs

--- 2020-05-26 paper/main.tex
@@
 \documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography]{revtex4}
-
 \usepackage[utf8]{inputenc}
@@
 }
-
-% disable subsections and subsubsections in the TOC
-\makeatletter
-\def\l@subsubsection#1#2{}
-\makeatother
 
@@
 
-\newcommand{\alert}[1]{\textbf{\color{red}{#1}}}
-\renewcommand{\vec}[1]{\boldsymbol{#1}}
-
 \begin{abstract}
-While quantum computing proposes promising solutions to computational problems not accessible with classical approaches, due to current hardware constraints, most quantum algorithms are not yet capable of computing systems of practical relevance, and classical counterparts outperform them.
-To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
-For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA), and investigated problem and hardware-specific limitations.
-This work presents the formalism of how to map ILP problems to the annealing architectures.
-It illustrates the effects of decorrelation and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
-We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.
-%Conclusion: What do these findings mean to us?
-[Rephrase] We need better hardware to challenge heuristic solvers but we identified how to optimize hardware.
-%Perspectives: What should be done next?
-[Rephrase] Better understand correlations and localizations and improve simulation to scale to larger problems.
-
+Abstract here...
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\tableofcontents
+%\tableofcontents
 
@@
 
-%========================================================================================
 \section{INTRODUCTION}
 \label{sec:introduction}
-%========================================================================================
 
-Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints and is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}.
-In general, however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
-Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
+Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints and is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and z~\cite{}.
+In general however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
 The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem can be obtained in polynomial time, the optimal integer solution in general must be found in the $2^n$ integer solutions which surround the real number solution.
-While greedy algorithms do not guarantee optimal global solutions, they find approximate solutions in polynomial time, which can be utilized in further computations.
-Due to the importance and difficulty, in this work, we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.
+Due to the importance and difficulty, in this work we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.
 
 Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{}.
-Through the adiabatic theorem of quantum mechanics, the annealer is initially prepared in a trivial ground state while the final Hamiltonian encodes the solution to the ILP.
+Through the adiabatic theorem of quantum mechanics, the annealer is prepared initially in a trivial ground state while the solution to ILP is encoded in the target Hamiltonian.
 Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems~\cite{2018Glover}.
 
-\alert{[Formulate: Decoherence \& Localization]}
-Hardware suffers from...
-For this reason one is not guaranteed to find optimal solutions
-
-\alert{[Formulate: Simulations]}
-To understand findings and limitations, we mimic the hardware
-
-In section \ref{sec:methods} we propose an algorithm that maps ILP problems to QA hardware (\ref{sec:methods:ilp}) and present an example implementation in case of the Minimal Dominating Set problem (\ref{sec:methods:mds}).
-We review the annealing process on the utilized hardware (\ref{sec:methods:annealing}) and describe the computational framework which we used to simulate the annealing process (\ref{sec:methods:simulation}).
-Section \ref{sec:results} summarizes our findings and presents...
-We conclude this report in \ref{sec:conclusion}.
-All algorithms used and data obtained are publicly available (\ref{sec:open-source})
-
-%========================================================================================
-\section{METHODS}
-\label{sec:methods}
-%========================================================================================
-
-%----------------------------------------------------------------------------------------
-\subsection{Integer Programming Mapping to QUBO}
-\label{sec:methods:ilp}
-%----------------------------------------------------------------------------------------
-
-This section presents the formalism which maps a general ILP to a QUBO.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Integer linear programming}
-\label{sec:methods:ilp-def}
-%----------------------------------------------------------------------------------------
 Formally, ILP is defined as the optimization of a linear function
+{\color{blue}
 \begin{align}
-    \label{eq:initial-ip-def}
-    \vec x_0 = \mathrm{arg} &\min\limits_{x}(\sum_i c_i x_i)
+f(x) = &\min\limits_{x}(\sum_i c_i x_i),\\
+\textrm{subject to} \quad & \sum_i A_{ai}x_i +b_a \leq 0 \\
+& x_i \geq 0,\\
+& x_i \in \mathbb{Z}
 \end{align}
-subject to
+}
+where $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
+The inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
+{\color{blue}
 \begin{align}
-    \label{eq:ilp-constraints}
-    &\sum_i A_{ai}x_i +b_a \leq 0 \,,\\
-    & x_i  \in \mathbbm{N}
+f(x) = &\min(\sum_i c_i x_i),\\
+\textrm{subject to} \quad & \sum_i A_{a i}x_i + s_a + b_a = 0,\\
+& s_a \geq 0,\\
+& s_a \in \mathbb{Z},\\
+& x_i \geq 0,\\
+& x_i \in \mathbb{Z}.
 \end{align}
-
-where the natural numbers $\mathbbm{N}$ include zero, $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Slack variables}
-\label{sec:methods:slack}
-%----------------------------------------------------------------------------------------
-
-The inequality constraints in eq.~\eqref{eq:ilp-constraints} can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
+}
+Since quantum annealing solves the QUBO problem, we extend the proposed algorithm to solve integer quadratic optimization problems such that
+{\color{blue}
 \begin{align}
-    \vec x_0 = \mathrm{arg} &\min(\sum_i c_i x_i)\,,
+f(x) = \min\limits_{x}(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i)
 \end{align}
-subject to
-\begin{align}& \sum_i A_{a i}x_i + s_a + b_a = 0,\\
-    & s_a \in \mathbb{N},\\
-    & x_i \in \mathbb{N}.
-\end{align}
-While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
-As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).
-
-Because quantum annealing is capable of solving quadratic problems, we extend the proposed algorithm to solve integer quadratic optimization problems as well such that
-\begin{align}
-    \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
-\end{align}
+}
 without the introduction of auxiliary qubits.
 
-%----------------------------------------------------------------------------------------
-\subsubsection{Bit basis}
-\label{sec:methods:bit-basis}
-%----------------------------------------------------------------------------------------
+{\color{red} Paragraph on how this is solved classically. Include strengths and drawbacks of classical solution.}
 
-We map integer variables $\vec z = \vec x, \vec s$ to qubits under the following transformation~\cite{Chang:2018uoc}
+\section{RESULTS}
+\label{sec:results}
+We map integer variables $z_i$ to qubits under the following transformation~\cite{Chang:2018uoc}
 \begin{align}
@@
 \end{align}
-where $\psi_{ri} \in \{0, 1\}$.
-The number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
-This transformation can be expressed as a rectangular matrix.
+where $\psi_{ri} \in \{0, 1\}$ while the number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
+The transformation can in general be express as a rectangular matrix.
 For example, a vector of two integer variables $z_0$ and $z_1$ represented by one and two qubits respectively is given as
@@
 \end{align}
-If all variables are represented by the same number of qubits--$R_i$ is a constant for all $i$--then one can express the transformation as tensor product of bit vectors
+The transformation can be reduced to a tensor product if $R_i$ is a constant for all $i$ such that
 \begin{align}
@@
 
-%----------------------------------------------------------------------------------------
-\subsubsection{Integer Programming Mapping QUBO}
-\label{sec:methods:ilp-qubo}
-%----------------------------------------------------------------------------------------
+While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbb{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).
 
+\subsection{Integer Programming Mapping to QUBO}
+\label{sec:results:ilp}
 The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
 \begin{align}
-    \chi^2 &= \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
-    \nonumber\\ \label{eq:qubo-min}
-    &\qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
-    \vec x_0 &=  T^x \vec \Psi^x_0 \, ,
-    \\
-    (\vec \Psi^x_0, \vec \Psi^s_0) &= \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,, &
+\chi^2 = & \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right. \nonumber\\
+&\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
+\Psi = & \begin{pmatrix}
+\Psi^x\\
+\Psi^s
+\end{pmatrix},
 \end{align}
-where $p$ is an external parameter representing the strength of the penalty when violating constraints.
+where $p$ is the strength of the penalty factor which must be set large enough such that the constraints are satisfied under minimization.
 The objective function can be represented as a QUBO Hamiltonian
@@
 
-%----------------------------------------------------------------------------------------
-\subsubsection{Comment on penalty term}
-\label{sec:methods:ilp-qubo-comments}
-%----------------------------------------------------------------------------------------
-
-The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
-Thus some knowledge of the problem is required.
-In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
-After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
-Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
-
-%----------------------------------------------------------------------------------------
-\subsection{Example: Minimum Dominating Set Problem}
-\label{sec:methods:mds}
-%----------------------------------------------------------------------------------------
-
-This section demonstrates the formalism in case of an example ILP: the Minimum Dominating Set problem.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Definition of the Minimum Dominating Set Problem}
-\label{sec:methods:mds-def}
-%----------------------------------------------------------------------------------------
+\subsection{Application to the Dominating Set Problem}
+\label{sec:results:mds}
 
@@
 Fig.~\ref{fig:dominating_sets}c shows an example of the minimum dominating set of $G(V, E)$ and is different from the minimal dominating set.
-We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
+We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set in general can have a smaller domination number.
 As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a problem that is well studied for quantum annealers~\cite{}.
@@
 		Connected nodes are neighbors of the DS (turquoise) or already in the DS.
-        In (a), one finds three maximally unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
+		In (a), one finds three unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
 		In the first step $a\to b$, randomly the node (4) is picked.
-        In (b), one has three unconnected choices [(1), (2)] with each adjacent to another unconnected node and one node [(6)] which is only adjacent to neighbors of the DS.
+		In (b), one has two unconnected choices [(1), (2)] with each adjacent to another unconnected node.
 		After randomly selecting (2) when going from $b \to c$, only one unconnected node is remaining (6).
@@
 
-%----------------------------------------------------------------------------------------
-\subsubsection{Minimum Dominating Set Qubo}
-\label{sec:methods:mds-qubo}
-%----------------------------------------------------------------------------------------
-
+\subsubsection{Minimum Dominating Set}
 The solution to the minimum independent set can be expressed as an integer optimization problem given by,
 \begin{align}
-    f(x) = &\min\left(\sum_{\nu \in V} \psi^x_{\nu}\right),\\
+f(x) = &\min(\sum_{\nu \in V} \psi^x_{\nu}),\\
 \textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1,\\
@@
 
-The target QUBO in the notation of eq.~\eqref{eq:matrix_form} reads
-{\small
+The target Hamiltonian can be written in the matrix form
+\begin{widetext}
 \begin{align}
-    Q_{xx} &= \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] \,,\\
-    Q_{sx} &= - p(\mathbbm{1}+J^T)T^s\,,\\
-    Q_{ss} &= p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]\,,\\
-    C &=  p \overline{\overline{V}}\,,
-\end{align}}
+E = &
+\begin{pmatrix}
+\Psi^x & \Psi^s
+\end{pmatrix}
+\begin{pmatrix}
+\mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] & - p(\mathbbm{1}+J^T)T^s\\
+- p{T^s}^T(\mathbbm{1}+J)& p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]
+\end{pmatrix}
+\begin{pmatrix}
+\Psi^x\\ \Psi^s
+\end{pmatrix} + p \overline{\overline{V}}
+\label{eq:matrix_form}
+\end{align}
+\end{widetext}
 where $ |M| \equiv \sum_{\nu} M_{\nu \mu}$.
 
-%----------------------------------------------------------------------------------------
-\subsection{Quantum Annealing}
-\label{sec:methods:annealing}
-%----------------------------------------------------------------------------------------
+\section{DISCUSSION}
 
-%----------------------------------------------------------------------------------------
-\subsubsection{Modified annealing schedule}
-\label{sec:methods:annealing-schedule}
-%----------------------------------------------------------------------------------------
-
-A quantum annealer evolves the ground state of an initial Hamiltonian into the ground state of the problem Hamiltonian by adiabatically changing the hardware which implements Hamiltonian.
-Thus, the implemented Hamiltonian is explicitly time dependent
-\begin{equation}
-    H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
-\end{equation}
-and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
-The variable $s\in [0, 1]$ is the normalized annealing time and, in physical units, is allowed to vary between 1$\mu s$ to 2$ms$ on DWave.
-
-On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
-In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in addition to the effects of applying positive and negative offsets.
-Note that due to the way the offsets are implemented on the hardware level, systematic errors are introduced since the initial and final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets ($B_i(s) \neq B_j(s)$).
-Fig.~\ref{fig:anneal_schedule} shows the maximum offset that we use for the study, which translates to approximately (due to non-linearity) a 5\% advancement (blue) or delay (red) in the schedule.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{./figures/anneal_schedule.pdf}
-    \caption{asdf}
-    \label{fig:anneal_schedule}
-\end{figure}
-
-The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system, in general, will exhibit more disorder.
-When recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
-\begin{equation}
-    H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
-\end{equation}
-we recognize that if $h_i$ is randomly drawn from a Bernoulli distribution, we recover the spin-glass model.
-The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analog of Anderson Localization.
-
-%----------------------------------------------------------------------------------------
-\subsection{Simulation of a Quantum Annealer}
-\label{sec:methods:simulation}
-%----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-\subsubsection{The Lindblad Equation}
-\label{sec:methods:lindblad}
-%----------------------------------------------------------------------------------------
-
-To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
-\begin{align}
-    \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
-\end{align}
-where $\rho (t)$ is the density matrix at time $t$.
-$H(t)$ is the time-dependent Hamiltonian
-\begin{align}
-    \label{eq:annealH}
-     H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\
-     +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
-\end{align}
-where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
-The site dependency takes into account of the annealing offset.
-$[,]$ denotes the Lie bracket.
-$L_j$ are the Lindblad operators for decoherence.
-$\{, \}$ denotes the anti-commutator.
-In this study, we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
-The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
-For simplicity, we assume all qubits have the same relaxation time.
-The initial condition is the Gibbs canonical ensemble
-\begin{equation}
-    \rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
-\end{equation}
-where $\beta$ is the inverse temperature.
-The probability to obtain the ground state at for a single measurement is
-\begin{align}
-    P_{\mbox{gnd}} =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
-\end{align}
-where the projection operator onto the degenerated ground states subspace is defined as
-\begin{equation}
-	\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i|
-	\, .
-\end{equation}
-Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Decoherence Time}
-\label{sec:methods:deco}
-%----------------------------------------------------------------------------------------
-
-Mention long coherence time asymptote to right value.
-
-Scan coherence time, match to DWave.
-
-Some more discussion about short coherence time and why it makes sense?
-
-Travis said: Regarding T1 << T effecting the state at time T, I am thinking more about the point that the very short T1 dephasing time has the effect of quenching any coherence.
-In this regard, a very short T1 is pushing the systems toward a classical annealing model.
-The absence of any dephasing is then the best-case quantum annealing model.
-Consequently, the difference in outcome would trace back to this coherence being present.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{./figures/coherence.pdf}
-    \caption{asdf}
-    \label{fig:prob_mi}
-\end{figure}
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Many-Body Localization}
-\label{sec:methods:mbl}
-%----------------------------------------------------------------------------------------
-
-If the annealer does not reach thermal equilibrium, for example, strong external magnetic fields freeze in individual qubits, the final solution of the annealing process might not encode the ground state of the final Hamiltonian.
-It is thus essential to prepare the system such that Many-Body Localizations are absent, and thus one must define a measure for MBL.
-
-We consider the mutual information as a measure for shared information between different partitions (sets of qubits) of the entire system.
-Given two partitions $A$ and $B$, the mutual information is defined as 
-\begin{equation}
-    I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B}) \geq 0\,,
-\end{equation}
-which is only zero if partitions $A$ and $B$ do not share information.
-We describe individual density information measures by the von Neumann entropy $S(\rho)=-\mbox{Tr}\rho \log_2 \rho$.
-The density matrix $\rho_{A,B}$ represents the entire system while $\rho_{A}=\mbox{Tr}_{B} (\rho_{A,B})$ is the reduced density matrix for the subsystem A (and equivalent $B$ for exchanged indicies).
-
-We note that this measure depends on the choice of partitions, which is, in principle, arbitrary.
-To define a measure for MBL, the choice for partitions should encode the likelihood of frozen qubits. 
-Thus a natural choice for partitions are regions of different external magnetic fields.
-For this choice, at the beginning of the anneal, the mutual information will be zero as all spins start orthogonal to the external field, and, in the end, the mutual information will be constant once a final solution is obtained.
-Intermediate values for the mutual information encode the communication probability of different spin alignments.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Decoherence and Many-Body Localization}
-\label{sec:methods:decoherence-and-mbl}
-%----------------------------------------------------------------------------------------
-
-Intuitively, to find a final state which globally minimizes the energy, we want the system to explore the entire state space.
-That is, we want the system to have ergodicity in order to avoid Many-Body Localizations.
-Thus the annealing process should be sufficiently slow to not introduce potential barriers which freeze in intermediate spin configurations.
-On the other hand, decoherence in the hardware leads to the loss of quantum information.
-It is, therefore, desirable to minimize the effect of relaxation and shorten the annealing process.
-The interplay between these two competing effects can be observed by looking at the non-monotonous time dependency of the probability for reaching the global ground state.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Other Simulation Details}
-%----------------------------------------------------------------------------------------
-Temperature
-Initial wave function choices
-RK tolerance
-
-%========================================================================================
-\section{RESULTS \& DISCUSSION}
-\label{sec:results}
-%========================================================================================
-
-%----------------------------------------------------------------------------------------
 \subsection{Finding the Dominating Set with a Quantum Annealer}
 \label{sec:discussion:qa}
-%----------------------------------------------------------------------------------------
-
 \begin{figure}[b]
@@
 		\includegraphics[width=0.5\columnwidth]{./figures/linear_crop.pdf}
-    \caption{Linear graphs $G(n)$ used in this study.
-Nodes denote vertices of the graphs and lines are undirected edges.}
+	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
 	\label{fig:linear}
@@
 For the following studies, we perform experiments on the \texttt{DW\_2000Q\_5} solver.
-After performing a study on the $G(6)$ graph, We selected an annealing time is of 600$\mu$s that optimizes the probability of finding the ground state, as shown in Fig.~\ref{fig:at_scale}.
+The annealing time is optimized to 600$\mu$s after performing a study on the $G(6)$ graph as shown in Fig.~\ref{fig:at_scale}.
 In Fig.~\ref{fig:baseline}, we show results from the baseline experiment, without modification to the default DWave annealing schedule, and observe improvement over random guessing.
-However, the experiment results reflect the same degeneracy structure as random guessing and scale exponentially poorly for a larger number of vertices $n$.
+However, the experiment results reflect the same degeneracy structure as random guessing, and scale exponentially poorly for larger number of vertices $n$.
 We explore one avenue towards improving the experiment results by introducing per-qubit annealing offsets into the time evolution.
@@
 	\includegraphics[width=\columnwidth]{./figures/scaling_baseline.pdf}
-    \caption{Baseline result of DWave (blue) compared to random guessing (red).
-The jagged nature of random guessing reflects the degeneracy of the ground state.}
+	\caption{Baseline result of DWave (blue) compared to random guessing (red). The jagged nature of random guessing reflects the degeneracy of the ground state.}
 	\label{fig:baseline}
@@
 
-%----------------------------------------------------------------------------------------
 \subsubsection{Modified annealing schedule}
-%----------------------------------------------------------------------------------------
 
-Following this logic, we split the qubits into two groups depending on the value of $h_i$ relative to $(\max(h_i) - \min(h_i)) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific problem.
+In quantum annealing, the ground state of the problem Hamiltonian is obtained from the evolution of a time-dependent Hamiltonian,
+\begin{equation}
+H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
+\end{equation}
+where $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, and $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
+The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ on the DWave.
+On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits.
+In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in addition to the effects of applying positive and negative offsets.
+Note that due to the way the offsets are implemented on the hardware level, systematic errors are introduced since the initial and final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
+Fig.~\ref{fig:anneal_schedule} shows the maximum offset that we use for the study, which translates to approximately (due to non-linearity) a 5\% advancement (blue) or delay (red) in the schedule.
+
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/anneal_schedule.pdf}
+	\caption{asdf}
+	\label{fig:anneal_schedule}
+\end{figure}
+
+The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system in general will exhibit more disorder.
+We define disorder by first recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
+\begin{equation}
+H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
+\end{equation}
+and recognize that in the limit where $h_i$ is randomly drawn from a Bernoulli distribution we recover the spin-glass model.
+The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization.
+
+Following this logic, we split the qubits into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific problem.
 We then symmetrically offset the two groups of qubits over a total range between 0\% and 10\% (-5\% to +5\%).
-The results of this study are shown in Fig.~\ref{fig:dwave_offset}.
+The results of this study is shown in Fig.~\ref{fig:dwave_offset}.
 
-\begin{figure}[htb]
+\begin{figure}[b]
 	\centering
 	\includegraphics[width=\columnwidth]{./figures/scaling_comparison_all.pdf}
-    \caption{The legend labels the entire range of the symmetric offset employed.
+	\caption{The legend labels the total range of the symmetric offset employed.
 A positive range indicates that the group of qubits with small values of $|h_i|$ are advanced (qubits with large values of $|h_i|$ are equivalently delayed), and vice versa for results labeled with a negative range.}
@@
 
-Finally, we note that due to the inherent variance in performance when using different physical qubits, we perform the offset study on the same physical qubits for each graph.
+Finally, we note that due to the inherent variance in performance when using different physical qubits, for each graph, we perform the offset study on the same physical qubits.
 Additionally, the largest offset ranges sampled are at the limits of the hardware capabilities of the DWave annealer.
@@
 We observe from Fig.~\ref{fig:dwave_offset} that advancing qubits subject to \textit{larger} final external magnetic fields yields approximately an order of magnitude improvement over the baseline results at the largest offset range.
-In contrast, advancing qubits with weaker magnetic fields consistently hurts the performance of the annealer.
+In contrast advancing qubits with weaker magnetic fields consistently hurts the performance of the annealer.
 This result is surprising in light of the expectation from many-body localization.
-We explain this surprising result by simulating the annealing process of the annealer, which we discuss in the following sections.
+We provide an explanation of this surprising result by simulating the annealing process of the annealer which are discussed in the following sections.
 
-%----------------------------------------------------------------------------------------
 \subsection{Simulation Results}
-%----------------------------------------------------------------------------------------
 
-In order to understand the effects of annealing offsets, we simulate the annealing process on five qubits for a $G(2)$ graph embedded in chimera topography.
-To shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
+In order to understand the effects of annealing offsets, we simulate the annealing process on 5 qubits for a $G(2)$ graph embedded in chimera topography.
+In order to shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
 The resulting ground state probability as a function of offset measured over 200,000 observations is shown in Fig.~\ref{fig:dwave1us} (Top).
@@
 
-The simulation utilizes the same Hamiltonian as DWave, which corresponds to the embedded original MDS QUBO.
-The time-dependent solution is obtained by solving the Lindblad equation subject to the DWave annealing schedule with offsets allowing us to incorporate a decoherence model in our simulation.
+For the simulation, the QUBO is obtained from the output of the DWave such that the same embedding is used.
+The time-dependence is obtained by solving the Lindblad equation subject to the DWave annealing schedule with offsets allowing us to incorporate a decoherence model in our simulation.
 The details of the Lindbladian are given in Sec.~\ref{sec:methods:lindblad}.
 Following Ref.~\cite{}, we fix the temperature of the simulation to 15 milliKelvins to reflect the reported operating temperature of the DWave.
-Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian is approximately 2 Kelvins, as shown in Fig.~\ref{fig:spectrum}.
+Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian is approximately 2 Kelvins as shown in Fig.~\ref{fig:spectrum}.
 As a result, the DWave operates at effectively zero-temperature for this example problem.
 
-We then set an effective $T_1$ coherence time to 20 $ns$ to match the DWave probability of finding the MDS of $G(2)$ at approximately 86\%.
+We then set an effective $T_1$ coherence time to 20 $ns$ in order to match the DWave probability of finding the MDS of $G(2)$ at approximately 86\%.
 A detailed study of $T_1$ is given in Sec.~\ref{sec:methods:deco}.
 We emphasize that the effective coherence time is much longer than the single qubit coherence time of 0.5 $ns$ reported by DWave, while still being orders of magnitude shorter than the total anneal time.
-The simulation and the experiment, however, both can recover the ground state with high probability regardless and exemplify quantum annealing's robustness.
+The simulation and the experiment however, both are able to recover the ground state with high probability regardless, and exemplifies the robustness of quantum annealing.
 
@@
 
-We present the simulated probability of finding the MDS with and without decoherence in Fig.~\ref{fig:dwave1us} (Middle) and (Bottom).
+The probability of finding the MDS from the simulation with and without decoherence are given in Fig.~\ref{fig:dwave_offset} (Middle) and (Bottom).
 We observe that with decoherence, the simulation captures the rough features of the experiment, including a steady improvement for negative offsets, and similar non-linear behavior at positive offsets.
-Additionally, the range of probabilities in the simulation non-trivially matches the range observed in the experiment.
-In contrast, simulations without decoherence exemplify the opposite behavior concerning offsets, in line with expectations from many-body localization.
-Therefore, the simulation provides evidence in relating the improvement seen on the DWave to the effects of decoherence rather than many-body localization, while for idealized annealing, the effects of many-body localization become essential.
+Additionally, the range of probabilities in the simulation non-trivially match the range observed in experiment.
+In contrast, simulations without decoherence exemplify the opposite behavior with respect to offsets, in line with expectation from many-body localization.
+Therefore, the simulation provides evidence in relating the improvement seen on the DWave to the effects of decoherence rather than many-body localization, while for idealized annealing, the effects of many-body localization become important.
 
-In both simulations, the system experience a relatively big jump in probability, at -10\% and +30\%, respectively.
+In both simulations, the system experience a relatively large jump in probability, at -10\% and +30\% respectively.
 For the simulation with decoherence, this behavior is inconsistent with experiment.
 {\color{red} eh..
-guess a reason?} Additionally, both simulations experience vanishing probability at a +10\% offset.
-This behavior is expected to happen eventually in the experiment as well when the two sets of qubits become too aggressively staggered and effectively decouple.
-The simulation, however, incorrectly predicts when the decoupling happens.
+guess a reason?} Additionally, both simulations experience vanishing probability at +10\% offset.
+This behavior is expected to happen eventually in experiment as well when the two sets of qubits become too aggressively staggered and effectively decouple.
+The simulation however, incorrectly predicts when the decoupling happens.
 
-%----------------------------------------------------------------------------------------
 \subsection{Decoherence and Many-Body Localization}
-%----------------------------------------------------------------------------------------
 
 We provide further evidence of the competing effects between decoherence and many-body localization in this section.
+
+Intuitively, we want the system to explore a larger state space to increase the probability for the system to reach the final ground state.
+That is, we want the system to have ergodicity in order to avoid MBL.
+On the other hand, decoherence in the hardware leads to the loss of quantum information.
+It is therefore desirable to minimize the effect of relaxation.
+The interplay between these two competing effects can be observed by looking at the time-dependent probability of reaching the final ground state, and the mutual information.
+The mutual information is defined as $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition $A$ and partition $B$ of the total system.
+$S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.
+{\color{blue} $\rho_{A,B}$ is the density matrix for the total system.
+$\rho_{A}=\mbox{Tr}_{B} (\rho_{A,B})$ is the reduced density matrix for the subsystem A.}
 
@@
 
-From Fig.~\ref{fig:prob_mi}, we observe that when the annealing schedule is modified to delay stronger external magnetic fields, the phase transition is delayed, yielding larger mutual information, and in turn probes a larger state space.
+From Fig.~\ref{fig:prob_mi} we observe that when the anneal schedule is modified to delay stronger external magnetic fields, the phase transition is delayed, yielding larger mutual information, and in turn probes a larger state space.
 This observation is independent of the effects of decoherence, and only relies on delaying the phase transition later in the annealing process.
-It then follows that the effects of decoherence competes with delocalization because the system is required to exhibit its quantum mechanical nature for longer.
-In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and become unaffected by dephasing.
-The left panels in Fig.~\ref{fig:prob_mi} demonstrate this phenomenon wherein the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this.
+It then follows that the effects of decoherence is in competition with delocalization because the system is required to exhibit its quantum mechanical nature for longer.
+In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and {\color{blue}become unaffected by dephasing.} This phenomena is demonstrated by the left panels in Fig.~\ref{fig:prob_mi} where in the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this.
 top one the red is always below blue, the bottom one, the red crosses the blue after the phase transition).
@@
 
-%========================================================================================
-\section{CONCLUSION}
-\label{sec:conclusion}
-%========================================================================================
+\section{METHODS}
+\subsection{Simulation Details}
+\subsubsection{The Lindblad Equation}
+\label{sec:methods:lindblad}
+Say what the simulator is solving
 
-%========================================================================================
+{\color{blue}
+
+To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
+\begin{align}
+\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
+\end{align}
+where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian 
+\begin{align}
+\label{eq:annealH}
+ H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\ 
+ +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
+\end{align}
+where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
+The site dependency takes into account of the annealing offset.
+$[,]$ denotes the Lie bracket.
+$L_j$ are the Lindblad operators for decoherence.
+$\{, \}$ denotes the anti-commutator.
+In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
+The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
+For simplicity we assume all qubits having the same relaxation time.
+The initial condition is the Gibbs canonical ensemble
+\begin{equation}
+\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
+\end{equation}
+where $\beta$ is the inverse temperature.
+The probability to get the ground state at measurement is
+\begin{align}
+P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
+\end{align}
+where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
+Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
+
+}
+
+With anneal offsets
+
+\subsubsection{Other Simulation Details}
+Temperature
+Initial wave function choices
+RK tolerance
+
+\subsubsection{Decoherence Time}
+\label{sec:methods:deco}
+
+Mention long coherence time asymptote to right value.
+
+Scan coherence time, match to DWave.
+
+Some more discussion about short coherence time and why it makes sense?
+
+Travis said: Regarding T1 << T effecting the state at time T, I am thinking more about the point that the very short T1 dephasing time has the effect of quenching any coherence.
+In this regard, a very short T1 is pushing the systems toward a classical annealing model.
+The absence of any dephasing is then the best-case quantum annealing model.
+Consequently, the difference in outcome would trace back to this coherence being present.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/coherence.pdf}
+	\caption{asdf}
+	\label{fig:prob_mi}
+\end{figure}
+
 \section{DATA AVAILABILITY}
-\label{sec:open-source}
-%========================================================================================
 
@@
 
-%========================================================================================
 \section{ACKNOWLEDGEMENTS}
-%========================================================================================
 
@@
 
-%========================================================================================
 \section{AUTHOR CONTRIBUTIONS}
-%========================================================================================
 
-C.K. drank a lot of coffee.
+...
 
-%========================================================================================
 \section{ADDITIONAL INFORMATION}
-%========================================================================================
 
@@
 
-%========================================================================================
 \bibliography{qilp}
-%========================================================================================
 

### 2020-06-01 paper/figures/ta_plots.py

@@ -480,7 +480,9 @@ def plot_dwave_mi(scount,opt):
     return pr
 
 def get_tdse_densitymatrix():
-    from tdse_plots import aggregate
+    #from tdse_plots import aggregate
+    from tdse_plots import aggregate_nodeco as aggregate
+
     tdata = aggregate()
     finalstate = {"Binary": {}}
     for key in tdata.keys():
@@ -488,13 +490,89 @@ def get_tdse_densitymatrix():
         finalstate["Binary"][key] = np.diag(temp[:,-1].reshape(32, 32))
     return finalstate
 
-def plot_final_state(dwpr, simpr, offset=0.0):
+def plot_final_state(dwpr=None, simpr=None, offset=0.0):
     fig = plt.figure("final state pr", figsize=(7,4))
     ax = plt.axes([0.15, 0.15, 0.7, 0.7])
-    ax.errorbar(x=range(len(dwpr[offset])), y = dwpr[offset], color=blue)
-    ax.errorbar(x=range(len(simpr[offset])), y = simpr[offset], color=red)
+    if dwpr:
+        ax.errorbar(x=range(len(dwpr[offset])), y = dwpr[offset], color=blue)
+    if simpr:
+        ax.errorbar(x=range(len(simpr[offset])), y = simpr[offset], color=red)
     plt.draw()
     plt.show()
+
+def plot_final_state_vs_at(prdict, offset=0.0):
+    fig = plt.figure("final state pr", figsize=(7,4))
+    ax = plt.axes([0.15, 0.15, 0.7, 0.7])
+    anneal_time =  [1, 10, 100, 1000] #[1,2,3,4,5,6,7,8,9,10,20,30,40,50,60,70,80,90,100,200,300,400,500,600,700,800,900,1000]
+    for at in anneal_time:
+        ax.errorbar(x=range(len(prdict[at][offset])), y = prdict[at][offset])
+    plt.draw()
+    plt.show()
+
+def getallspinconfig():
+    import pickle
+    vrange = [-0.05, -0.04, -0.03, -0.02, -0.01, 0.0, 0.01, 0.02, 0.03, 0.04, 0.05]
+    anneal_time = [1,2,3,4,5,6,7,8,9,10,20,30,40,50,60,70,80,90,100,200,300,400,500,600,700,800,900,1000]
+    try:
+        y =dict()
+        for at in anneal_time:
+            y[at] = dict()
+            for v in vrange:
[…]

### 2020-06-01 paper/figures/tdse_plots.py

@@ -124,21 +124,22 @@ def aggregate_nodeco():
     adata = dict()
     data = Data()
     data.params["wave"]["gamma"] = 0.0
+    data.params["offset"]["annealing_time"] = 0.001
     data.params["offset"]["offset"] = "binary"
-    #for offset in [
-    #    0.05,
-    #    0.04,
-    #    0.03,
-    #    0.02,
-    #    0.01,
-    #    0.0,
-    #    -0.01,
-    #    -0.02,
-    #    -0.03,
-    #    -0.04,
-    #    -0.05,
-    #]:
-    for offset in [0.04, -0.04]:
+    for offset in [
+        0.05,
+        0.04,
+        0.03,
+        0.02,
+        0.01,
+        0.0,
+        -0.01,
+        -0.02,
+        -0.03,
+        -0.04,
+        -0.05,
+    ]:
+        #for offset in [0.04, -0.04]:
         data.params["offset"]["offset_min"] = offset
         data.params["offset"]["offset_range"] = abs(offset) * 2
         adata[offset] = data.get_data()
@@ -197,7 +198,7 @@ def plot_aggregate(adata, tag):
     ax.legend()
     plt.draw()
     plt.savefig(f"full_prob_{tag}.pdf", transparent=True)
-    """
+
     plt.figure("prob", figsize=(7, 4))
     ax = plt.axes([0.15, 0.15, 0.8, 0.8])
     x = list(adata.keys())
@@ -215,8 +216,8 @@ def plot_aggregate(adata, tag):
     else:
         ax.set_ylim([0.9938, 0.99485])
     plt.draw()
-    plt.savefig(f"./sim_{tag}.pdf", transparent=True)
-    """
+    #plt.savefig(f"./sim_{tag}.pdf", transparent=True)
+
     reg = 1e-9
     plt.figure(f"mutual information", figsize=(7, 4))
     ax = plt.axes([0.15, 0.15, 0.8, 0.8])
@@ -435,9 +436,9 @@ if __name__ == "__main__":
     # plot_spectrum(adata)
 
     # vs offset no decoherence
-    #bdata = aggregate_nodeco()
-    #plot_aggregate(bdata, "nodeco")
+    bdata = aggregate_nodeco()
+    plot_aggregate(bdata, "nodeco")
 
     # vs gamma
-    gdata = aggregate_gamma()
-    plot_gamma(gdata)
+    #gdata = aggregate_gamma()
+    #plot_gamma(gdata)

### 2020-06-01 qlp/mds/mds_qlpdb.py
update tag

@@ -48,7 +48,7 @@ class AnnealOffset:
                 f"FixEmbedding_Constant_{offset_min}_{offset_range}_v3_1",
             )
         if self.tag == "binary":
-            offset_tag = f"FixEmbedding_Binary_{offset_min}_{offset_range}_v5"
+            offset_tag = f"FixEmbedding_Binary_{offset_min}_{offset_range}_FS_v1"
             offset_fcn = []
             hmid = abshrange * 0.5 + min(abs(h))
             for hi in h:

### 2020-07-11 paper/main.tex
update plots in paper

@@
 	\includegraphics[width=\columnwidth]{./figures/sim_deco.pdf}
-	\includegraphics[width=\columnwidth]{./figures/sim_nodeco.pdf}
 	\caption{ (Top) The probability of finding the MDS for $G(2)$ from DWave.
@@
 The details of the Lindbladian are given in Sec.~\ref{sec:methods:lindblad}.
-Following Ref.~\cite{}, we fix the temperature of the simulation to 15 milliKelvins to reflect the reported operating temperature of the DWave.
-Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian is approximately 2 Kelvins as shown in Fig.~\ref{fig:spectrum}.
-As a result, the DWave operates at effectively zero-temperature for this example problem.
+Following Ref.~\cite{}, we fix the temperature of the simulation to 40 milliKelvins to reflect approximately the reported operating temperature of the DWave.
+Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian ranges from 13 mK to 90 mK depending on the offset as shown in Fig.~\ref{fig:spectrum}.
+We account for the thermal effects through full-counting statistics~\ref{}.
+{\color{red}some more words about this?}
 
-We then set an effective $T_1$ coherence time to 20 $ns$ in order to match the DWave probability of finding the MDS of $G(2)$ at approximately 86\%.
+We then set an effective $T_1$ coherence time to 60 $ns$ in order to match the DWave probability of finding the MDS of $G(2)$ at approximately 85\%.
 A detailed study of $T_1$ is given in Sec.~\ref{sec:methods:deco}.
@@
 
-The probability of finding the MDS from the simulation with and without decoherence are given in Fig.~\ref{fig:dwave_offset} (Middle) and (Bottom).
-We observe that with decoherence, the simulation captures the rough features of the experiment, including a steady improvement for negative offsets, and similar non-linear behavior at positive offsets.
-Additionally, the range of probabilities in the simulation non-trivially match the range observed in experiment.
-In contrast, simulations without decoherence exemplify the opposite behavior with respect to offsets, in line with expectation from many-body localization.
-Therefore, the simulation provides evidence in relating the improvement seen on the DWave to the effects of decoherence rather than many-body localization, while for idealized annealing, the effects of many-body localization become important.
+The probability of finding the MDS from simulation is given in Fig.~\ref{fig:dwave_offset} (Bottom).
+We observe that the simulation captures the rough features of the experiment, including a steady improvement for negative offsets.
+Additionally, the range of probabilities in the simulation non-trivially match the range observed in experiment suggesting that the temperature and coherence time parameters are consistent with experiment.
 
-In both simulations, the system experience a relatively large jump in probability, at -10\% and +30\% respectively.
-For the simulation with decoherence, this behavior is inconsistent with experiment.
-{\color{red} eh..
-guess a reason?} Additionally, both simulations experience vanishing probability at +10\% offset.
-This behavior is expected to happen eventually in experiment as well when the two sets of qubits become too aggressively staggered and effectively decouple.
-The simulation however, incorrectly predicts when the decoupling happens.
-
-\subsection{Decoherence and Many-Body Localization}
+\subsection{Many-Body Localization}
 
@@
 	\includegraphics[width=\columnwidth]{./figures/full_prob_deco.pdf}
-	\includegraphics[width=\columnwidth]{./figures/mutual_info_deco.pdf}
-	\includegraphics[width=\columnwidth]{./figures/full_prob_nodeco.pdf}
-	\includegraphics[width=\columnwidth]{./figures/mutual_info_nodeco.pdf}
+	\includegraphics[width=\columnwidth]{./figures/hybridization.pdf}
 	\caption{(Left) The time-dependent probability of resolving the ground state and (Right) the corresponding mutual information.
@@
 \end{figure*}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/final_state_distribution.pdf}
+	\caption{caption}
+	\label{fig:final_state_distribution}
+\end{figure}
 

### 2020-07-12 paper/main.tex
new plots and comments to paper

@@
 	\centering
-	\includegraphics[width=\columnwidth]{./figures/dwave1us.pdf}
+	%\includegraphics[width=\columnwidth]{./figures/dwave1us.pdf}
 	\includegraphics[width=\columnwidth]{./figures/sim_deco.pdf}
-	\caption{ (Top) The probability of finding the MDS for $G(2)$ from DWave.
+	\caption{ {\color{red} New figure, Dwave on top of simulation (black).} The probability of finding the MDS for $G(2)$ from DWave.
 The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times.
@@
 	\includegraphics[width=\columnwidth]{./figures/spectrum_offset.pdf}
-	\caption{The energy spectrum of the first 5 states of the time-dependent Hamiltonian (Top) without annealing offsets and (Bottom) -10\% annealing offset.
+	\caption{{\color{red} Maybe combine these 2 plots to 1 as well?
+same color for same offset.} The energy spectrum of the first 5 states of the time-dependent Hamiltonian (Top) without annealing offsets and (Bottom) -10\% annealing offset.
 The spectrum in dimensionless units at the end of the anneal is an integer spectrum and correspond to the number of vertices in the dominating set.
@@
 
+{\color{red} Talk about final state distribution here. Reference figure, make figure prettier, add DWave final state distribution to figure.}
+
 \subsection{Many-Body Localization}
 
-We provide further evidence of the competing effects between decoherence and many-body localization in this section.
+We provide further evidence that suggests the advancement of strong external fields leads to a delay in the phase transition, and increase in many-body localization, and results in a higher probability to recover the true ground state in this section.
 
+{\color{red} The following paragraphs are not relevant now. Need new story.}
 Intuitively, we want the system to explore a larger state space to increase the probability for the system to reach the final ground state.
@@
 	\includegraphics[width=\columnwidth]{./figures/final_state_distribution.pdf}
-	\caption{caption}
+	\caption{{\color{red}I need to add dwave final state distribution here too.}}
 	\label{fig:final_state_distribution}
@@
 Say what the simulator is solving
-
+{\color{red} Need to change to talk about full counting statistics.}
 {\color{blue}

### 2020-07-12 paper/figures/tdse_plots.py

@@ -11,6 +11,8 @@ from qlp.mds.qubo import get_mds_qubo
 from qlp.tdse import convert_params, embed_qubo_example
 
 from django.conf import settings
+from ta_plots import get_tdse_data, plot_tdse
+
 
 label_params = dict()
 label_params["fontsize"] = 7
@@ -358,27 +360,29 @@ def plot_distribution(adata):
 
 
 def plot_aggregate(adata, tag):
-    plt.figure("full probability", figsize=(7, 4))
-    ax = plt.axes([0.15, 0.15, 0.8, 0.8])
-    for idx, key in enumerate(adata):
-        if key > 0:
-            color = red
-        else:
-            color = blue
-        tdse = adata[key].tdse
-        idx, en, evec = tdse.ground_state_degeneracy(tdse.IsingH, 2e-2, debug=False)
-        ax.errorbar(
-            x=adata[key].time,
-            y=adata[key].prob,
-            color=color,
-            label=f"{int(key*2*100)}%",
-        )
-    ax.set_xlabel("normalized time")
-    ax.set_ylabel("MDS probability")
-    ax.legend()
-    plt.draw()
-    plt.savefig(f"full_prob_{tag}.pdf", transparent=True)
+    if False:
+        plt.figure("full probability", figsize=(7, 4))
+        ax = plt.axes([0.15, 0.15, 0.8, 0.8])
+        for idx, key in enumerate(adata):
+            if key > 0:
+                color = red
+            else:
+                color = blue
+            tdse = adata[key].tdse
+            idx, en, evec = tdse.ground_state_degeneracy(tdse.IsingH, 2e-2, debug=False)
+            ax.errorbar(
+                x=adata[key].time,
+                y=adata[key].prob,
+                color=color,
+                label=f"{int(key*2*100)}%",
+            )
+        ax.set_xlabel("normalized time")
+        ax.set_ylabel("MDS probability")
+        ax.legend()
+        plt.draw()
+        plt.savefig(f"full_prob_{tag}.pdf", transparent=True)
 
+    dwave_data = get_tdse_data()
     plt.figure("prob", figsize=(7, 4))
     ax = plt.axes([0.15, 0.15, 0.8, 0.8])
     x = list(adata.keys())
@@ -389,58 +393,62 @@ def plot_aggregate(adata, tag):
         else:
             color = "k"
[…]

### 2020-07-12 paper/main.tex
new spectrum plot
update simulator section  in paper

@@
 {\color{red} Need to change to talk about full counting statistics.}
-{\color{blue}
+{\color{red}
 
@@
 \begin{align}
-\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
+\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}[\rho (t)] ,
 \end{align}
@@
 The site dependency takes into account of the annealing offset.
-$[,]$ denotes the Lie bracket.
-$L_j$ are the Lindblad operators for decoherence.
-$\{, \}$ denotes the anti-commutator.
-In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
-The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$.
-For simplicity we assume all qubits having the same relaxation time.
+$[,]$ denotes the Lie bracket and $\mathcal{L}$ is the Lindblad operator.
+
+For full counting statistics the Lindblad operator is 
+\begin{align}
+\mathcal{L}[\rho (t)] &=& \Gamma \sum_j   (2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}) \\
+&& + e^{-\beta \Delta E_j} (2 S_j^\dagger \rho(t) S_j - \{ S_j S^\dagger_j, \rho(t) \} )
+\end{align}
+where $j$ index the inter-level spacing for energy difference $\Delta E_j$, $\{, \}$ denotes the anti-commutator, $\Gamma = 1/T_c$ is the decoherence rate for coherence time $T_c$.
+
+%In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
+The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where
+
+}
+
+ {\color{blue}
 The initial condition is the Gibbs canonical ensemble
@@
 RK tolerance
+
+{\color{red}
+
+To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e.
+$A(s)=A(0)$ and $B(s)=0$.
+The initial state is pure zero state $\rho=|00...0\rangle \langle 00...0|$.
+In this case the analytical solution can be obtained for the wave function oscillation.
+The time-dependent probability is $P_{0}=\cos^{2n}(s)=\cos^{2n}(t/T)$ where $n$ is the number of qubits and $T$ is the annealing time.
+For annealing time $T=1/A(0)$, we expect to see perfect one-period oscillation.
+The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/check.png}
+	\caption{check}
+	\label{fig:check}
+\end{figure}
+
+}
 

### 2020-07-12 paper/figures/ta_plots.py
update final state distribution

@@ -562,11 +562,11 @@ def getallspinconfig():
                 scount[at][v][tuple(yi)] += 1
     # get prob vs computational basis
     n=5
-    pr = np.zeros(2 ** n)
     prdict = dict()
     for at in anneal_time:
         prdict[at] = dict()
         for v in vrange:
+            pr = np.zeros(2 ** n)
             for I in range(2 ** n):
                 dwstate = np.abs(np.array([int(i) for i in '{0:05b}'.format(I)]) - 1)  # map 0 <-> 1
                 pr[I] = scount[at][v][(tuple(dwstate))]

### 2020-07-12 paper/figures/tdse_plots.py

@@ -11,7 +11,7 @@ from qlp.mds.qubo import get_mds_qubo
 from qlp.tdse import convert_params, embed_qubo_example
 
 from django.conf import settings
-from ta_plots import get_tdse_data, plot_tdse
+from ta_plots import get_tdse_data, plot_tdse, getallspinconfig
 
 
 label_params = dict()
@@ -220,15 +220,19 @@ def plot_centropy(adata):
 
 
 def plot_distribution(adata):
+    prdict = getallspinconfig()
+
     plt.figure("distribution", figsize=(7, 11))
     rhodim = 2 ** 5
-    height = 0.08
-    top = 0.95
+    height = 0.085
+    top = 0.98
     ax0 = plt.axes([0.15, top - height, 0.8, height])
     ax0.bar(
         x=np.linspace(0, rhodim - 1, rhodim),
         height=np.diagonal(adata[-0.05].sol.y[:, -1].reshape((rhodim, rhodim))).real,
         width=1,
+        color=red,
+        label="simulation"
     )
     ax0.get_xaxis().set_ticks([])
     ax0.set_ylim([0, 1.1])
@@ -241,6 +245,8 @@ def plot_distribution(adata):
         x=np.linspace(0, rhodim - 1, rhodim),
         height=np.diagonal(adata[-0.04].sol.y[:, -1].reshape((rhodim, rhodim))).real,
         width=1,
+        color=red
+
     )
     ax1.set_ylim([0, 1.1])
     ax1.text(
@@ -253,6 +259,7 @@ def plot_distribution(adata):
         x=np.linspace(0, rhodim - 1, rhodim),
         height=np.diagonal(adata[-0.03].sol.y[:, -1].reshape((rhodim, rhodim))).real,
         width=1,
+        color=red
     )
     ax2.set_ylim([0, 1.1])
     ax2.text(
@@ -265,6 +272,7 @@ def plot_distribution(adata):
         x=np.linspace(0, rhodim - 1, rhodim),
         height=np.diagonal(adata[-0.02].sol.y[:, -1].reshape((rhodim, rhodim))).real,
         width=1,
+        color=red
     )
     ax3.set_ylim([0, 1.1])
     ax3.text(
@@ -277,6 +285,7 @@ def plot_distribution(adata):
         x=np.linspace(0, rhodim - 1, rhodim),
[…]

### 2020-08-26 paper/main.tex
update paper

@@
-\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography]{revtex4}
+\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,
+floatfix,longbibliography]{revtex4-2}
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-\usepackage{amsmath,amssymb}
+\usepackage{amsmath}
+\usepackage{mathtools}
+\usepackage{amsfonts}
 \usepackage{bm,bbm}
 \usepackage{graphicx}
-\usepackage{color}
-\usepackage{dsfont}
+\usepackage{xcolor}
 
@@
 Formally, ILP is defined as the optimization of a linear function
-{\color{blue}
 \begin{align}
 f(x) = &\min\limits_{x}(\sum_i c_i x_i),\\
-\textrm{subject to} \quad & \sum_i A_{ai}x_i +b_a \leq 0 \\
-& x_i \geq 0,\\
-& x_i \in \mathbb{Z}
+\textrm{subject to } &\left \{
+\begin{matrix*}[l]
+	&\sum_i A_{ai}x_i +b_a \leq 0 \\
+	&x_i \geq 0,\\
+	&x_i \in \mathbb{Z}
+\end{matrix*} \right.
 \end{align}
-}
 where $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
 The inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
-{\color{blue}
 \begin{align}
 f(x) = &\min(\sum_i c_i x_i),\\
-\textrm{subject to} \quad & \sum_i A_{a i}x_i + s_a + b_a = 0,\\
-& s_a \geq 0,\\
-& s_a \in \mathbb{Z},\\
-& x_i \geq 0,\\
-& x_i \in \mathbb{Z}.
+\textrm{subject to } &\left \{
+\begin{matrix*}[l]
+	&\sum_i A_{a i}x_i + s_a + b_a = 0,\\
+	&s_a \geq 0,\\
+	&s_a \in \mathbb{Z},\\
+	&x_i \geq 0,\\
+	&x_i \in \mathbb{Z}.
+\end{matrix*} \right.
 \end{align}
-}
 Since quantum annealing solves the QUBO problem, we extend the proposed algorithm to solve integer quadratic optimization problems such that
-{\color{blue}
 \begin{align}
-f(x) = \min\limits_{x}(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i)
+f(x) = \min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
 \end{align}
-}
 without the introduction of auxiliary qubits.
-
-{\color{red} Paragraph on how this is solved classically. Include strengths and drawbacks of classical solution.}
 
@@
 	\centering
-	\begin{tabular}{p{0.3\textwidth}p{0.3\textwidth}p{0.3\textwidth}}
-	\includegraphics[width=0.20\textwidth]{./figures/subaru_ds.pdf}
-&
-	\includegraphics[width=0.20\textwidth]{./figures/subaru_mds4.pdf}
-&
-	\includegraphics[width=0.20\textwidth]{./figures/subaru_mds2.pdf}\\
-	\centering\bf{a} & \centering\bf{b} & \centering\bf{c}
+	\begin{tabular}{p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
+	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds0.pdf}
+&&
+	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds1.pdf}
+&&
+	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds2.pdf}\\
+	\centering\bf{a} && \centering\bf{b} && \centering\bf{c}
 	\end{tabular}
@@
 Vertices in the dominating set $D$ are highlighted in blue.
-{\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 5$.
-{\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 4$.
-We note that $D$ is also the maximum independent set of $G$.
-{\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.}
+{\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 2$.
+{\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.
+{\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 1$.}
 	\label{fig:dominating_sets}
@@
 For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
-Thus one is guaranteed to find a dominating set but not necessarily a MDS.
-We demonstrate an example greedy algorithm in figure Fig.~\ref{fig:mds-greedy}.
+Thus one is guaranteed to find a dominating set but not necessarily a MDS. {\color{red} Write some pseudo code for greedy search.}
+%We demonstrate an example greedy algorithm in figure Fig.~\ref{fig:mds-greedy}.
+
+\iffalse
 \begin{figure*}
@@
 \end{figure*}
+\fi
 
@@
 \end{pmatrix} + p \overline{\overline{V}}
-\label{eq:matrix_form}
+\label{eq:matrix_form2}
 \end{align}
@@
 	\centering
-		\includegraphics[width=0.5\columnwidth]{./figures/linear_crop.pdf}
+	\begin{tabular}{cc}
+	$G(n):$ &
+	\raisebox{-.4\height}{\includegraphics[width=0.8\columnwidth]{./new_figures/linear_graph.pdf}}
+	\end{tabular}
 	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
@@
 
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=\columnwidth]{./figures/anneal_time_scaling.pdf}
-	\caption{Probability of finding the MDS for $G(6)$ as a function of total annealing time.}
-	\label{fig:at_scale}
-\end{figure}
-
-For the following studies, we perform experiments on the \texttt{DW\_2000Q\_5} solver.
-The annealing time is optimized to 600$\mu$s after performing a study on the $G(6)$ graph as shown in Fig.~\ref{fig:at_scale}.
+For the following studies, we perform experiments on the \texttt{DW\_2000Q\_6} solver.
+The annealing time is set to 500$\mu$s after performing a study on various annealing times the $G(6)$ graph.
 In Fig.~\ref{fig:baseline}, we show results from the baseline experiment, without modification to the default DWave annealing schedule, and observe improvement over random guessing.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./figures/scaling_baseline.pdf}
-	\caption{Baseline result of DWave (blue) compared to random guessing (red). The jagged nature of random guessing reflects the degeneracy of the ground state.}
+	\includegraphics[width=\columnwidth]{./new_figures/DWave_scaling.pdf}
+	\caption{Baseline result of DWave (black) compared to random guessing (blue).
+The jagged nature of random guessing reflects the degeneracy of the ground state.
+The legend labels the values of annealing offsets employed.
+A positive offsets (yellow) indicates that qubits with large values of $|h_i|$ are annealing with a delayed schedule, while negative offsets (green) delay the schedule of qubits with small values of $h_i$.}
 	\label{fig:baseline}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./figures/anneal_schedule.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
 	\caption{asdf}
@@
 The results of this study is shown in Fig.~\ref{fig:dwave_offset}.
-
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=\columnwidth]{./figures/scaling_comparison_all.pdf}
-	\caption{The legend labels the total range of the symmetric offset employed.
-A positive range indicates that the group of qubits with small values of $|h_i|$ are advanced (qubits with large values of $|h_i|$ are equivalently delayed), and vice versa for results labeled with a negative range.}
-	\label{fig:dwave_offset}
-\end{figure}
 
@@
 	\centering
-	%\includegraphics[width=\columnwidth]{./figures/dwave1us.pdf}
-	\includegraphics[width=\columnwidth]{./figures/sim_deco.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
 	\caption{ {\color{red} New figure, Dwave on top of simulation (black).} The probability of finding the MDS for $G(2)$ from DWave.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./figures/spectrum.pdf}
-	\includegraphics[width=\columnwidth]{./figures/spectrum_offset.pdf}
-	\caption{{\color{red} Maybe combine these 2 plots to 1 as well?
+	\includegraphics[width=\columnwidth]{./figures/spectrum_all.pdf}
+	%\includegraphics[width=\columnwidth]{./figures/spectrum_offset.pdf}
+	\caption{{\color{red} NEED NEW PLOTS.
+Maybe combine these 2 plots to 1 as well?
 same color for same offset.} The energy spectrum of the first 5 states of the time-dependent Hamiltonian (Top) without annealing offsets and (Bottom) -10\% annealing offset.
@@
 \subsection{Many-Body Localization}
-
+{\color{red} Probably need to rerwite this...}
 We provide further evidence that suggests the advancement of strong external fields leads to a delay in the phase transition, and increase in many-body localization, and results in a higher probability to recover the true ground state in this section.
@@
 
-\begin{figure*}
+\begin{figure}
 	\centering
-	\includegraphics[width=\columnwidth]{./figures/full_prob_deco.pdf}
-	\includegraphics[width=\columnwidth]{./figures/hybridization.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
 	\caption{(Left) The time-dependent probability of resolving the ground state and (Right) the corresponding mutual information.
 (Top) Simulation with decoherence included and (Bottom) without decoherence.}
-	\label{fig:prob_mi}
-\end{figure*}
+	\label{fig:td_prob}
+\end{figure}
 
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./figures/final_state_distribution.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/final_state_distribution.pdf}
 	\caption{{\color{red}I need to add dwave final state distribution here too.}}
@@
 	\caption{asdf}
-	\label{fig:prob_mi}
+	\label{fig:prob_mi2}
 \end{figure}

### 2020-08-26 paper/figures/clean_plots.py

@@ -78,7 +78,7 @@ class Sim:
         """==============================="""
         wave_params["temp"] = 0.0225
         wave_params["gamma"] = 1 / 1
-        wave_params["gamma_local"] = 1 / 20
+        wave_params["gamma_local"] = 1 / 15 # 1/15 or 1/20
         """==============================="""
         wave_params["initial_wavefunction"] = "transverse"
 
@@ -665,17 +665,23 @@ def plot_hybridization():
     # plt.yscale("log")
     plt.savefig("../new_figures/hybridization.pdf", transparent=True)
 
+"""
+###########################
+#####  level spacing  #####
+###########################
+"""
+
 def getlevelspacing(offset=0.05):
     sim = Sim()
     query, sol, tdse = sim.get_data(offset)
     ngrid = 1000
-    fockn=tdse.Focksize
+    fockn= tdse.Focksize
     timegrid = np.linspace(0, 1, ngrid)
     r = np.zeros(ngrid)
     for i in range(ngrid):
         H = tdse.annealingH(timegrid[i]).todense()
         val, evec = eigh(H)
-        spacing = val[1:]-val[0:fockn-1]
+        spacing = val[1:fockn]-val[0:fockn-1]
         temp=np.asarray([min((spacing[n],spacing[n+1]))/max((spacing[n],spacing[n+1])) for n in range(fockn-2)])
         r[i]=np.sum(temp)/(fockn-2)
     return timegrid, r
@@ -688,7 +694,7 @@ def plot_levelspacing():
         timegrid, r = getlevelspacing(os)
         all_levels.append(r)
     print(np.shape(all_levels))
-    sns.heatmap(all_levels)
+    sns.heatmap(all_levels, yticklabels=offset)
     #ax.legend()
     #plt.yscale("log")
     #plt.savefig("../new_figures/levelspacing.pdf", transparent=True)
@@ -699,6 +705,42 @@ def plot_levelspacing():
 #####  time-dependent energy spectrum  #####
 ############################################
 """
+
+def getspectrum(offset=0.05):
+    sim = Sim()
+    query, sol, tdse = sim.get_data(offset)
+    ngrid = 100
+    es= 3
+    timegrid = np.linspace(0, 1, ngrid)
+    r = {idx: [] for idx in range(es)}
+    gap = {0: [], 1: []}
+    gap_density = []
+    for i in range(ngrid):
[…]

### 2020-08-27 paper/main.tex
explain decoherence in paper

@@
 \usepackage{xcolor}
+\usepackage{dsfont}
 
@@
 
-For full counting statistics the Lindblad operator is 
+We consider two types of decoherence models: full counting statistics and local damping.
+The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
+The local damping term models the decoherence of each qubit independently.
+For full counting statistics, the Lindblad operator is 
 \begin{align}
-\mathcal{L}[\rho (t)] &=& \Gamma \sum_j   (2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}) \\
+\mathcal{L}[\rho (t)] &=& \Gamma_{fc} \sum_j   (2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}) \notag \\
 && + e^{-\beta \Delta E_j} (2 S_j^\dagger \rho(t) S_j - \{ S_j S^\dagger_j, \rho(t) \} )
 \end{align}
-where $j$ index the inter-level spacing for energy difference $\Delta E_j$, $\{, \}$ denotes the anti-commutator, $\Gamma = 1/T_c$ is the decoherence rate for coherence time $T_c$.
-
-%In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits.
-The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where
+where $j$ is the index for the inter-level spacing $\Delta E_j=E_\mu-E_\nu>0$.
+$S_j=|E_\nu \rangle \langle E_\mu|$ denotes the many-body lowering operator.
+$\{, \}$ denotes the anti-commutator.
+$\Gamma = 1/T_c$ is the decoherence rate for coherence time $T_c$.
+That is, due to the interaction with the classical thermal bath, there is a probability that the system hops from each higher-energy many-body state to a lower-energy many-body state.
+The probability of the inverse process is given by a Boltzmann factor.
+To model the local decoherence of each qubits in the non-interacting limit, we also consider the amplitude damping for non-interacting qubits.
+The Lindblad operator is
+\begin{align}
+\mathcal{L}[\rho (t)] &=&  \Gamma_{loc} \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \notag \\
+&& + e^{-\beta 2|h_j| }  (2L_j^\dagger \rho(t) L_j - \{ L_j L_j^\dagger, \rho(t) \}) ),
+\end{align}
+where $j$ is the index for qubit.
+$L_j= \sigma^{+}_j=|1\rangle \langle 0|$ for $h_j>0$ and $L_j= \sigma^{-}_j=|0\rangle \langle 1|$ for $h_j<0$.
+That is, each qubit is damped toward its local ground state if we ignore all the interactions.
 

### 2020-08-27 paper/main.tex
clean up discussion

@@
+%! suppress = LineBreak
 \documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,
@@
 \usepackage{xcolor}
-\usepackage{dsfont}
 
@@
 
-\preprint{LLNL-JRNL-809712, RIKEN-iTHEMS-Report-20}
+\preprint{RIKEN-iTHEMS-Report-20}
 
@@
 The annealing time is set to 500$\mu$s after performing a study on various annealing times the $G(6)$ graph.
-In Fig.~\ref{fig:baseline}, we show results from the baseline experiment, without modification to the default DWave annealing schedule, and observe improvement over random guessing.
-However, the experiment results reflect the same degeneracy structure as random guessing, and scale exponentially poorly for larger number of vertices $n$.
-We explore one avenue towards improving the experiment results by introducing per-qubit annealing offsets into the time evolution.
+The black line (offset$=0.0$) in Fig.~\ref{fig:baseline} shows results from the baseline experiment, without modification to the DWave annealing schedule, and observe improvement over random guessing (blue).
+However, We explore one avenue towards improving the experiment results by introducing per-qubit annealing offsets into the time evolution.
 
@@
 
+\noindent\textit{Annealing offsets}
+
 In quantum annealing, the ground state of the problem Hamiltonian is obtained from the evolution of a time-dependent Hamiltonian,
@@
 On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits.
-In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in addition to the effects of applying positive and negative offsets.
-Note that due to the way the offsets are implemented on the hardware level, systematic errors are introduced since the initial and final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
-Fig.~\ref{fig:anneal_schedule} shows the maximum offset that we use for the study, which translates to approximately (due to non-linearity) a 5\% advancement (blue) or delay (red) in the schedule.
+In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
+The time dependent coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
+The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
+As a result, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
+Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
+We extrapolate their values by a linear extrapolation, and only employ negative offsets such that this effect only enters at the beginning of the annealing process rather than the end.
+Details of the DWave annealing schedule use to generate Fig.~\ref{fig:anneal_schedule} and further documentation are provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.
 
@@
 and recognize that in the limit where $h_i$ is randomly drawn from a Bernoulli distribution we recover the spin-glass model.
-The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization.
+The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.
+\\\\
+\noindent\textit{Implementation of annealing offsets}
 
-Following this logic, we split the qubits into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific problem.
-We then symmetrically offset the two groups of qubits over a total range between 0\% and 10\% (-5\% to +5\%).
+For even the smallest graph $NN(2)$, the MDS problem is not native to the chimera graph and must be embedded.
+Following the hypothesis of MBL, we therefore, must look at the values of $h_i$ after embedding.
+The qubits then split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding.
+Further detail is given in Sec.~\ref{sec:methods:minor_embedding} {\color{red} put in methods more details}.
+We study the effects offset the two groups of qubits over a total range between 0\% and 5\% of $c$.
 The results of this study is shown in Fig.~\ref{fig:dwave_offset}.
 
-Finally, we note that due to the inherent variance in performance when using different physical qubits, for each graph, we perform the offset study on the same physical qubits.
-Additionally, the largest offset ranges sampled are at the limits of the hardware capabilities of the DWave annealer.
-
-We observe from Fig.~\ref{fig:dwave_offset} that advancing qubits subject to \textit{larger} final external magnetic fields yields approximately an order of magnitude improvement over the baseline results at the largest offset range.
-In contrast advancing qubits with weaker magnetic fields consistently hurts the performance of the annealer.
-This result is surprising in light of the expectation from many-body localization.
-We provide an explanation of this surprising result by simulating the annealing process of the annealer which are discussed in the following sections.
+The results in yellow (green) delays the annealing of qubits subject to stronger (weaker) external fields.
+We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the anneal schedule, in agreement with the MBL hypothesis.
+The phenomena is observed across different problem sizes and hints at the possibility of a generic improvement strategy.
+In the following section, we provide evidence that the improvement is rooted in quantum mechanics, and not other causes such as imperfections in hardware~\cite{} {\color{red} cite dwave's use of annealing offsets}.
+The master equation for quantum annealing is solved subject to the DWave anneal schedule with annealing offsets in order to reproduce the observed phenomenon.
 
@@
 
-In order to understand the effects of annealing offsets, we simulate the annealing process on 5 qubits for a $G(2)$ graph embedded in chimera topography.
+In order to understand the effects of annealing offsets, we simulate the annealing process for the $G(2)$ graph embedded in chimera topography.
 In order to shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
-The resulting ground state probability as a function of offset measured over 200,000 observations is shown in Fig.~\ref{fig:dwave1us} (Top).
+The resulting ground state probability as a function of offset measured over 100,000 observations is shown in Fig.~\ref{fig:dwave1us}.
 
@@
 	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
-	\caption{ {\color{red} New figure, Dwave on top of simulation (black).} The probability of finding the MDS for $G(2)$ from DWave.
-The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times.
-(Middle) Result from simulation with decoherence and (Bottom) simulation without decoherence.
-In both simulations, at +10\% offset, the probability of finding the ground state vanishes.
-The red simulation points are not present in the DWave result.}
+	\caption{ {\color{red} new caption}}
 	\label{fig:dwave1us}
@@
 
-For the simulation, the QUBO is obtained from the output of the DWave such that the same embedding is used.
-The time-dependence is obtained by solving the Lindblad equation subject to the DWave annealing schedule with offsets allowing us to incorporate a decoherence model in our simulation.
-The details of the Lindbladian are given in Sec.~\ref{sec:methods:lindblad}.
-Following Ref.~\cite{}, we fix the temperature of the simulation to 40 milliKelvins to reflect approximately the reported operating temperature of the DWave.
-Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian ranges from 13 mK to 90 mK depending on the offset as shown in Fig.~\ref{fig:spectrum}.
-We account for the thermal effects through full-counting statistics~\ref{}.
-{\color{red}some more words about this?}
+Simulation results are obtained by solving the von Neumann equation subject to two decoherence models: local damping and full-counting statistics.
+Details of the master equation are given in Sec.~\ref{sec:methods:lindblad}.
+The time dependence of $A(s)$ and $B(s)$ are given by the DWave annealing schedule with offsets in Fig.~\ref{fig:anneal_schedule}.
+The graph $G(2)$ has the interesting feature of having a degenerate ground state depending on whether qubit 0 or 1 is chosen to be the MDS solution.
+This degeneracy is reflected in the experimental result and provides a non-trivial benchmark for our simulation.
+Fig.~\ref{fig:final_state_distribution} show the final state distribution of the three lowest lying state.
+The states $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ are the two degenerate ground states of the embedded Hamiltonian, while $(1, 1, 1, 1, 1)$ is the first excited state which yields an incorrect solution.
+All other states receive negligible probability at the end of annealing.
+The simulation (black) captures main features of the experimental result: 1) significant probability to populate both ground states (rather than populating only one), 2) asymmetry in ground state population due to systematic effects of offset lifting the final state degeneracy spanning approximately the correct range, 3) population of first excited state with systematically lower probability when the strong field is delayed.
+This result can be obtained by tuning three free parameters: the simulation temperature to the order of 10 milliKelvin, and the two coefficients of the two decoherence models at the order of 1 to 10 $ns$.
+Additional insights of the simulation are given in Sec.~\ref{sec:methods:simulation_details}.
 
-We then set an effective $T_1$ coherence time to 60 $ns$ in order to match the DWave probability of finding the MDS of $G(2)$ at approximately 85\%.
-A detailed study of $T_1$ is given in Sec.~\ref{sec:methods:deco}.
-We emphasize that the effective coherence time is much longer than the single qubit coherence time of 0.5 $ns$ reported by DWave, while still being orders of magnitude shorter than the total anneal time.
-The simulation and the experiment however, both are able to recover the ground state with high probability regardless, and exemplifies the robustness of quantum annealing.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./figures/spectrum_all.pdf}
-	%\includegraphics[width=\columnwidth]{./figures/spectrum_offset.pdf}
-	\caption{{\color{red} NEED NEW PLOTS.
-Maybe combine these 2 plots to 1 as well?
-same color for same offset.} The energy spectrum of the first 5 states of the time-dependent Hamiltonian (Top) without annealing offsets and (Bottom) -10\% annealing offset.
-The spectrum in dimensionless units at the end of the anneal is an integer spectrum and correspond to the number of vertices in the dominating set.
-For $G(2)$, the MDS has 1 vertex.
-Annealing offsets lift the ground-state degeneracy.}
-	\label{fig:spectrum}
-\end{figure}
-
-The probability of finding the MDS from simulation is given in Fig.~\ref{fig:dwave_offset} (Bottom).
-We observe that the simulation captures the rough features of the experiment, including a steady improvement for negative offsets.
-Additionally, the range of probabilities in the simulation non-trivially match the range observed in experiment suggesting that the temperature and coherence time parameters are consistent with experiment.
-
-{\color{red} Talk about final state distribution here. Reference figure, make figure prettier, add DWave final state distribution to figure.}
-
-\subsection{Many-Body Localization}
-{\color{red} Probably need to rerwite this...}
-We provide further evidence that suggests the advancement of strong external fields leads to a delay in the phase transition, and increase in many-body localization, and results in a higher probability to recover the true ground state in this section.
-
-{\color{red} The following paragraphs are not relevant now. Need new story.}
-Intuitively, we want the system to explore a larger state space to increase the probability for the system to reach the final ground state.
-That is, we want the system to have ergodicity in order to avoid MBL.
-On the other hand, decoherence in the hardware leads to the loss of quantum information.
-It is therefore desirable to minimize the effect of relaxation.
-The interplay between these two competing effects can be observed by looking at the time-dependent probability of reaching the final ground state, and the mutual information.
-The mutual information is defined as $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition $A$ and partition $B$ of the total system.
-$S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.
-{\color{blue} $\rho_{A,B}$ is the density matrix for the total system.
-$\rho_{A}=\mbox{Tr}_{B} (\rho_{A,B})$ is the reduced density matrix for the subsystem A.}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
-	\caption{(Left) The time-dependent probability of resolving the ground state and (Right) the corresponding mutual information.
-(Top) Simulation with decoherence included and (Bottom) without decoherence.}
-	\label{fig:td_prob}
-\end{figure}
+The resulting probability of recovering the correct solution as a function of annealing offset is given in Fig.~\ref{fig:dwave1us}.
+We confirm that scaling with respect to offset from the simulation matches what is observed from experiment.
+Furthermore, in Sec.~\ref{}, we provide the results of an ideal quantum annealer, where the annealing schedule is faithfully delayed (all qubits start and end with the same values of $A$ and $B$) and all decoherence terms are removed.
+The scaling with respect to offset is preserved indicating that the improvements are related to quantum mechanics.
 
@@
 
-From Fig.~\ref{fig:prob_mi} we observe that when the anneal schedule is modified to delay stronger external magnetic fields, the phase transition is delayed, yielding larger mutual information, and in turn probes a larger state space.
-This observation is independent of the effects of decoherence, and only relies on delaying the phase transition later in the annealing process.
-It then follows that the effects of decoherence is in competition with delocalization because the system is required to exhibit its quantum mechanical nature for longer.
-In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and {\color{blue}become unaffected by dephasing.} This phenomena is demonstrated by the left panels in Fig.~\ref{fig:prob_mi} where in the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this.
-top one the red is always below blue, the bottom one, the red crosses the blue after the phase transition).
-
-Things to do:
-
-Compute dwave mutual information
-
-Study ground state degeneracy by plotting distribution of states.
+\subsection{Final remarks}
+We would like to emphasize that while the annealing offsets are motivated by the MBL hypothesis, and the results also follow those expectations, we do not have definitive proof that MBL plays a crucial role.
+The reason is because observations of MBL inevitably require the study of finite-size scaling, and our current simulation while being extremely thorough and explicit, is exponentially slow to evaluate making evaluations of even $G(3)$ untenable.
+However, the intersection of time-dependent quantum mechanics and emergent phenomena such at MBL is an exciting direction that is pertinent to adiabatic quantum computing.
 
 \section{METHODS}
-\subsection{Simulation Details}
-\subsubsection{The Lindblad Equation}
+\subsection{The Lindblad Equation}
 \label{sec:methods:lindblad}
-Say what the simulator is solving
-{\color{red} Need to change to talk about full counting statistics.}
-{\color{red}
 
@@
 
-}
-
- {\color{blue}
 The initial condition is the Gibbs canonical ensemble
@@
 
-}
+\subsection{Minor Embedding}
+\label{sec:methods:minor_embedding}
 
-With anneal offsets
-
-\subsubsection{Other Simulation Details}
-Temperature
-Initial wave function choices
-RK tolerance
-
-{\color{red}
-
+\subsection{Simulation Details}
+\label{sec:methods:simulation_details}
 To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e.
@@
 The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction.
+{\color{red} Are you suppose to reference Fig.
+7 here?}
 
@@
 
-}
-
-\subsubsection{Decoherence Time}
-\label{sec:methods:deco}
-
-Mention long coherence time asymptote to right value.
-
-Scan coherence time, match to DWave.
-
-Some more discussion about short coherence time and why it makes sense?
-
-Travis said: Regarding T1 << T effecting the state at time T, I am thinking more about the point that the very short T1 dephasing time has the effect of quenching any coherence.
-In this regard, a very short T1 is pushing the systems toward a classical annealing model.
-The absence of any dephasing is then the best-case quantum annealing model.
-Consequently, the difference in outcome would trace back to this coherence being present.
-
 \begin{figure}
 	\centering
-	\includegraphics[width=\columnwidth]{./figures/coherence.pdf}
-	\caption{asdf}
-	\label{fig:prob_mi2}
+	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
+	\caption{(Left) The time-dependent probability of resolving the ground state and (Right) the corresponding mutual information.
+(Top) Simulation with decoherence included and (Bottom) without decoherence.}
+	\label{fig:td_prob}
 \end{figure}
@@
 
+\bibliographystyle{naturemag-doi}
 \bibliography{qilp}

### 2020-08-27 paper/main.tex
first draft

@@
 \noindent\textit{Implementation of annealing offsets}
+\label{sec:discussion:offsets}
 
@@
 \label{sec:methods:minor_embedding}
+Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
+As a result, details of the embedding are important.
+We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the DWave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module.
+The same embedding is used for all DWave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
+Additionally, solving the same graph as a function of offset on the exact same qubits removes (or at least keeps consistent) the systematic effects due to solving a problem on different physical qubits.
+We note that comparisons between different graphs in Fig.~\ref{fig:baseline} are subject to this uncontrolled systematic.
+
+After embedding the QUBO for $G(2)$ requires 5 qubits (an increase from 4), where by construction, qubits 0 and 3 form the qubit chain.
+We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by DWave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the minimum dominating set.
+
+The resulting Ising Hamiltonian has external field equal to $h = (2.75, 1.5, -1.0, -1.25, -1.0)$.
+Following the offset strategy described in Sec.~\ref{sec:discussion:offsets}, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
+This imbalance in the two groups may perhaps explain the reason why effects of delaying the weaker fields are more pronounced, since delaying the strong fields only differs from the baseline by a single qubit.
 
@@
 
+Next, the simulator is applied to the $G(2)$ problem and the result is summarized in Fig.~\ref{fig:td_prob} where the time-dependent overlap with the exact Ising ground state is shown.
+We observe for all cases that the system undergoes what is analogous to a magnetic phase transition around $s\sim 0.4$.
+After the phase transition, we are able to confirm that the system collapses to effectively a classical state in the sense that the density matrix becomes a diagonal matrix.
+The steady increase in probability after the phase transition is a sensitive balance between the competing effects between full-counting statistics and local damping.
+In our example, full-counting statistics is tuned to be slightly stronger, resulting in what amounts to a final thermal annealing step.
+If local damping is relatively stronger, then the probability after the phase transition will slowly decrease as the system decoheres into its local ground state.
+While we believe both effects are important in DWave, the experimental results are not precise enough for us to conclude which is the dominant effect.
+We emphasize however, that the simulation suggests that the ground state is recovered predominantly due to the quantum phase transition.
+
 \begin{figure}
@@
 \end{figure}
+
+Finally, we comment that in order for the simulation to obtain the final state distribution shown in Fig.~\ref{fig:final_state_distribution}, effects of full-counting statistics are required.
+Absent some dynamical thermalization effect, the $G(2)$ problem is too small such that at a total annealing time of 1$\mu s$, the annealing offsets lift the ground state degeneracy by an amount such that diabatic transitions are absent, and the simulation is populated predominantly by the unique ground state.
+The final state distribution gives us a very sensitive observable to tune the simulation temperature, and agrees well with the experimental operating temperature.
 

### 2020-08-29 paper/figures/clean_plots.py
new figures

@@ -68,21 +68,21 @@ class Sim:
         wave_params = dict()
         wave_params["type"] = "mixed"
         """==============================="""
-        #wave_params["temp"] = 0.015
-        #wave_params["gamma"] = 1 / 1
-        #wave_params["gamma_local"] = 1 / 10
+        # wave_params["temp"] = 0.015
+        # wave_params["gamma"] = 1 / 1
+        # wave_params["gamma_local"] = 1 / 10
         """==============================="""
-        #wave_params["temp"] = 0.03
-        #wave_params["gamma"] = 1 / 1
-        #wave_params["gamma_local"] = 1 / 30
+        # wave_params["temp"] = 0.03
+        # wave_params["gamma"] = 1 / 1
+        # wave_params["gamma_local"] = 1 / 30
         """==============================="""
         wave_params["temp"] = 0.0225
         wave_params["gamma"] = 1 / 1
-        wave_params["gamma_local"] = 1 / 15 # 1/15 or 1/20
+        wave_params["gamma_local"] = 1 / 15  # 1/15 or 1/20
         """==============================="""
-        #wave_params["temp"] = 0.04
-        #wave_params["gamma"] = 1 / 10
-        #wave_params["gamma_local"] = 1 / 10 # 1/15 or 1/20
+        # wave_params["temp"] = 0.04
+        # wave_params["gamma"] = 1 / 10
+        # wave_params["gamma_local"] = 1 / 10 # 1/15 or 1/20
         """==============================="""
         wave_params["initial_wavefunction"] = "transverse"
 
@@ -401,15 +401,16 @@ def getall(offset=-0.05, graphsize=2):
     return prob
 
 
-def plot_all():
-    def degenfcn(n):
-        if n % 3 == 2:
-            return n // 3 + 2
-        if n % 3 == 1:
-            return 2 * (n // 3 + 1)
-        if n % 3 == 0:
-            return 1
+def degenfcn(n):
+    if n % 3 == 2:
+        return n // 3 + 2
+    if n % 3 == 1:
+        return 2 * (n // 3 + 1)
+    if n % 3 == 0:
+        return 1
 
+
+def plot_all():
     plt.figure(figsize=p["figsize"])
     ax = plt.axes(p["aspect_ratio"])
     """dwave result
[…]

### 2020-08-29 paper/figures/clean_plots.py
some plots for talks

@@ -59,11 +59,11 @@ class Sim:
         # offset params
         offset_params = dict()
         offset_params["annealing_time"] = 1
+        offset_params["normalized_time"] = "[0, 1]"
         offset_params["offset"] = "single_sided_binary"
         offset_params["offset_min"] = 0
-        offset_params["fill_value"] = "extrapolate"
         offset_params["anneal_curve"] = "dwave"
-
+        print(offset_params)
         # wave params
         wave_params = dict()
         wave_params["type"] = "mixed"
@@ -106,8 +106,9 @@ class Sim:
         }
         return params
 
-    def get_data(self, offset):
+    def get_data(self, offset, normalized_time = [0.0, 1.0]):
         self.params["offset"]["offset_min"] = offset
+        self.params["offset"]["normalized_time"] = normalized_time
         print(self.params["graph"]["tag"])
         print(convert_params(self.params["offset"]))
         print(self.params["solver"])
@@ -118,6 +119,8 @@ class Sim:
             solver__contains=self.params["solver"],
             wave__contains=self.params["wave"],
         ).first()
+        from django.db import connection
+        print(connection.queries)
         with open(f"{settings.MEDIA_ROOT}/{query.solution}", "rb") as file:
             sol = pickle.load(file)
         with open(f"{settings.MEDIA_ROOT}/{query.instance}", "rb") as file:
@@ -491,9 +494,9 @@ def gettdse(offset=0.0):
     return prob
 
 
-def gettdsetheory(offset=0.0):
+def gettdsetheory(offset=0.0, normalized_time = "[0, 1]"):
     sim = Sim()
-    query, sol, tdse = sim.get_data(offset)
+    query, sol, tdse = sim.get_data(offset, normalized_time)
     H = tdse._constructIsingH(np.array(tdse.ising["Jij"]), np.array(tdse.ising["hi"])).todense().tolist()
     eval, evec = eigh(H)
     project = sum([np.kron(evec[:, idx], np.conj(evec[:, idx])) for idx in [0, 1]])
@@ -523,6 +526,24 @@ def plot_tdse():
     plt.legend()
     plt.savefig("../new_figures/NN2_offset_scaling.pdf", transparent=True)
 
+def plot_tdse_extended():
+    plt.figure(figsize=p["figsize"])
+    ax = plt.axes(p["aspect_ratio"])
+    """simulation result
[…]

### 2020-08-30 paper/main.tex
fancy names
add offset section in appendix

@@
 floatfix,longbibliography]{revtex4-2}
+\usepackage{CJK}
 \usepackage[utf8]{inputenc}
@@
 
-\author{Chia~Cheng~Chang}
+\author{Chia~Cheng~Chang (\begin{CJK*}{UTF8}{bsmi}張家丞\end{CJK*})}
 \affiliation{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
@@
 \affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
-\author{Chih-Chieh~Chen}
+	\author{Chih-Chieh~Chen (\begin{CJK*}{UTF8}{bsmi}\mbox{陳志傑}\end{CJK*})}
 \affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
@@
 The resulting probability of recovering the correct solution as a function of annealing offset is given in Fig.~\ref{fig:dwave1us}.
-We confirm that scaling with respect to offset from the simulation matches what is observed from experiment.
-Furthermore, in Sec.~\ref{}, we provide the results of an ideal quantum annealer, where the annealing schedule is faithfully delayed (all qubits start and end with the same values of $A$ and $B$) and all decoherence terms are removed.
-The scaling with respect to offset is preserved indicating that the improvements are related to quantum mechanics.
+We confirm that scaling with respect to offset from the simulation matches what is observed from experiment, and provides evidence suggesting that the improvements are related to quantum mechanics.
+An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets is presented in Sec.~\ref{sec:app:offset}, and further supports this observation.
 
@@
 \end{align}
-where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian 
+where $\rho (t)$ is the density matrix at time $t$. The time-dependent Hamiltonian $H(t)$ solved by DWave as documented in Ref.~\cite{dwave_offset} is
 \begin{align}
 \label{eq:annealH}
- H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\ 
- +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
+ H^{\textrm{anneal}}(t)  =&  - \sum_i  A_i(t)\sigma^x_i +\sum_i B_{i}(t) h_i \sigma^z_i \notag \\
+ +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j ,&
 \end{align}
@@
 Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
+
+\subsection{Systematic effects of annealing offsets}
+\label{sec:app:offset}
+We verify that our implementation of annealing offsets on the simulator is consistent with DWave by solving the following three qubit Hamiltonian
+\begin{align}
+	\label{eq:offset_test_hamiltonian}
+	H^{\textrm{problem}} =
+	\begin{pmatrix}
+		-0.25 & 1 & 0 \\
+		0 & -0.25 & 0 \\
+		0 & 0 & -0.25
+	\end{pmatrix}
+\end{align}
+which has a doubly-degenerate ground state of $(0, 1, 1)$ and $(1, 0, 1)$.
+An annealing offset is then applied to either qubit 0 or 1, and breaks the ground state degeneracy of the system.
+Because of the systematic error introduced when assigning an offset to a qubit, the final Hamiltonian given by Eq.~(\ref{eq:annealH}) will have small deviations from the input problem Hamiltonian.
+For example, we expect a negative offset to qubit 0 to Eq.~(\ref{eq:offset_test_hamiltonian}) will yield $(1, 0, 1)$ as the unique ground state given Eq.~(\ref{eq:annealH}).
+
+We confirm that with different combinations of annealing offsets, the degeneracy is lifted on the DWave results as expected by solving for the modified problem Hamiltonian spectrum, as well as dialing in annealing offset in the simulation of this three qubit test case.
+
+In the simulation, we are also reserve the ability to remove the systematic errors by extending the annealing schedule as shown in Fig.~\ref{fig:anneal_schedule_ext}.
+With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians.
+The dependence on offset for $G(2)$ (Fig.~(\ref{fig:dwave1us})) remains the same under the extended anneal schedule (Fig.~\ref{fig:anneal_schedule_ext}), confirming that the behavior is not a systematic artifact.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./new_figures/anneal_schedule_extended.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling_extended.pdf}
+	\caption{{\color{red}I need to add dwave final state distribution here too.}}
+	\label{fig:anneal_schedule_ext}
+\end{figure}
 

### 2020-08-30 paper/figures/clean_plots.py

@@ -533,16 +533,16 @@ def plot_tdse_extended():
     """
     offset = list(0.01 * (np.arange(11) - 5))
     prob = [gettdsetheory(os, normalized_time = [-0.1, 1.1]) for os in offset]
-    ax.errorbar(x=offset, y=prob, ls="-", marker="o", color="k", alpha=0.5, label="extended")
+    ax.errorbar(x=offset, y=prob, ls="-", marker="o", color="k", alpha=0.5)
 
-    prob = [gettdsetheory(os, normalized_time = [0.0, 1.0]) for os in offset]
-    ax.errorbar(x=offset, y=prob, ls="--", marker="o", color=os_color["sim"], label="truncated")
+    #prob = [gettdsetheory(os, normalized_time = [0.0, 1.0]) for os in offset]
+    #ax.errorbar(x=offset, y=prob, ls="--", marker="o", color=os_color["sim"], label="truncated")
     """labels
     """
     ax.set_xlabel("offset", p["textargs"])
     ax.set_ylabel("probability", p["textargs"])
 
-    plt.legend()
+    #plt.legend()
     plt.savefig("../new_figures/NN2_offset_scaling_extended.pdf", transparent=True)
 
 """
@@ -552,9 +552,9 @@ def plot_tdse_extended():
 """
 
 
-def getannealcurve(offset=0.05):
+def getannealcurve(offset=0.05, normalized_time=[0.0, 1.0]):
     sim = Sim()
-    query, sol, tdse = sim.get_data(offset)
+    query, sol, tdse = sim.get_data(offset, normalized_time)
     X = np.linspace(*query.offset["normalized_time"])
     yA = np.array([tdse.AS.A(Xi) for Xi in X])[:, 0]
     yB = np.array([tdse.AS.B(Xi) for Xi in X])[:, 0]
@@ -562,7 +562,7 @@ def getannealcurve(offset=0.05):
 
 
 def plot_annealcurve():
-    offset = list(np.arange(6) / 100)
+    offset = [0.0, 0.05] #list(np.arange(6) / 100)
     plt.figure(figsize=p["figsize"])
     ax = plt.axes(p["aspect_ratio"])
     for os in offset:
@@ -576,7 +576,7 @@ def plot_annealcurve():
             colorA = blue
             colorB = blue
             alpha = os_alpha[os]
-        s, yA, yB = getannealcurve(os)
[…]

### 2020-09-04 paper/main.tex
Cleanup repo

@@
 \documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,
-floatfix,longbibliography]{revtex4-2}
+floatfix,longbibliography,aps,10pt]{revtex4-2}
 \usepackage{CJK}
@@
 \usepackage{mathtools}
-\usepackage{amsfonts}
+\usepackage{amsfonts,dsfont}
 \usepackage{bm,bbm}
@@
 
-\bibliographystyle{naturemag-doi}
+\bibliographystyle{apsrev4-1}
 \bibliography{qilp}

### 2020-09-04 paper/main.tex

@@
 %! suppress = LineBreak
-\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,
-floatfix,longbibliography,aps,10pt]{revtex4-2}
+\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography,aps,10pt]{revtex4-2}
 \usepackage{CJK}
@@
 
+% disable subsections and subsubsections in the TOC
+\makeatletter
+\def\l@subsubsection#1#2{}
+\makeatother
+
 \begin{document}
@@
 
+\newcommand{\alert}[1]{\textbf{\color{red}{#1}}}
+\renewcommand{\vec}[1]{\boldsymbol{#1}}
+
+\newcommand{\ghissue}[2]{
+ \noindent\fbox{\parbox{0.49\textwidth}{
+   \alert{[#1]}%
+   \\%
+   \href{https://github.com/cchang5/quantum\_linear\_programming/pull/#2}{See GitHub issue #2}}%
+ }
+}
+
 \begin{abstract}
-Abstract here...
+ While quantum computing proposes promising solutions to computational problems not accessible with classical approaches, due to current hardware constraints, most quantum algorithms are not yet capable of computing systems of practical relevance, and classical counterparts outperform them.
+ To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
+ For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA), and investigated problem and hardware-specific limitations.
+ This work presents the formalism of how to map ILP problems to the annealing architectures.
+ It illustrates the effects of decorrelation and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
+ We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.
+
+ \ghissue{Finalize abstract}{13}
+
 \end{abstract}
@@
 
+%========================================================================================
 \section{INTRODUCTION}
 \label{sec:introduction}
+%========================================================================================
 
-Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints and is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and z~\cite{}.
-In general however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
+Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints and is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}.
+In general, however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
+Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
 The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem can be obtained in polynomial time, the optimal integer solution in general must be found in the $2^n$ integer solutions which surround the real number solution.
-Due to the importance and difficulty, in this work we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.
+While greedy algorithms do not guarantee optimal global solutions, they find approximate solutions in polynomial time, which can be utilized in further computations.
+Due to the importance and difficulty, in this work, we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.
 
 Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{}.
-Through the adiabatic theorem of quantum mechanics, the annealer is prepared initially in a trivial ground state while the solution to ILP is encoded in the target Hamiltonian.
+Through the adiabatic theorem of quantum mechanics, the annealer is initially prepared in a trivial ground state while the final Hamiltonian encodes the solution to the ILP.
 Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems~\cite{2018Glover}.
 
+\ghissue{Decoherence \& Localization}{14}
+
+\ghissue{Simulations}{15}
+
+In section \ref{sec:methods} we propose an algorithm that maps ILP problems to QA hardware (\ref{sec:methods:ilp}) and present an example implementation in case of the Minimal Dominating Set problem (\ref{sec:methods:mds}).
+We review the annealing process on the utilized hardware (\ref{sec:methods:annealing}) and describe the computational framework which we used to simulate the annealing process (\ref{sec:methods:simulation}).
+Section \ref{sec:results} summarizes our findings and presents...
+We conclude this report in \ref{sec:conclusion}.
+All algorithms used and data obtained are publicly available (\ref{sec:open-source})
+
+%========================================================================================
+\section{METHODS}
+\label{sec:methods}
+%========================================================================================
+
+%----------------------------------------------------------------------------------------
+\subsection{Integer Programming Mapping to QUBO}
+\label{sec:methods:ilp}
+%----------------------------------------------------------------------------------------
+
+This section presents the formalism which maps a general ILP to a QUBO.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Integer linear programming}
+\label{sec:methods:ilp-def}
+%----------------------------------------------------------------------------------------
 Formally, ILP is defined as the optimization of a linear function
 \begin{align}
-f(x) = &\min\limits_{x}(\sum_i c_i x_i),\\
-\textrm{subject to } &\left \{
-\begin{matrix*}[l]
-	&\sum_i A_{ai}x_i +b_a \leq 0 \\
-	&x_i \geq 0,\\
-	&x_i \in \mathbb{Z}
-\end{matrix*} \right.
+ \label{eq:initial-ip-def}
+ \vec x_0 = \mathrm{arg} & \min\limits_{x}(\sum_i c_i x_i)
 \end{align}
-where $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
-The inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
+subject to
 \begin{align}
-f(x) = &\min(\sum_i c_i x_i),\\
-\textrm{subject to } &\left \{
-\begin{matrix*}[l]
-	&\sum_i A_{a i}x_i + s_a + b_a = 0,\\
-	&s_a \geq 0,\\
-	&s_a \in \mathbb{Z},\\
-	&x_i \geq 0,\\
-	&x_i \in \mathbb{Z}.
-\end{matrix*} \right.
+ \label{eq:ilp-constraints}
+  & \sum_i A_{ai}x_i +b_a \leq 0 \,, \\
+  & x_i  \in \mathbbm{N}
 \end{align}
-Since quantum annealing solves the QUBO problem, we extend the proposed algorithm to solve integer quadratic optimization problems such that
+
+where the natural numbers $\mathbbm{N}$ include zero, $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Slack variables}
+\label{sec:methods:slack}
+%----------------------------------------------------------------------------------------
+
+The inequality constraints in eq.~\eqref{eq:ilp-constraints} can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
 \begin{align}
-f(x) = \min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
+ \vec x_0 = \mathrm{arg} & \min(\sum_i c_i x_i)\,,
+\end{align}
+subject to
+\begin{align}                                                 & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
+  & s_a \in \mathbb{N},                \\
+  & x_i \in \mathbb{N}.
+\end{align}
+While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).
+
+Because quantum annealing is capable of solving quadratic problems, we extend the proposed algorithm to solve integer quadratic optimization problems as well such that
+\begin{align}
+ \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
 \end{align}
@@
 
-\section{RESULTS}
-\label{sec:results}
-We map integer variables $z_i$ to qubits under the following transformation~\cite{Chang:2018uoc}
+%----------------------------------------------------------------------------------------
+\subsubsection{Bit basis}
+\label{sec:methods:bit-basis}
+%----------------------------------------------------------------------------------------
+
+We map integer variables $\vec z = \vec x, \vec s$ to qubits under the following transformation~\cite{Chang:2018uoc}
 \begin{align}
@@
  \begin{pmatrix}
-z_0\\
+  z_0 \\
   z_1
@@
  \begin{pmatrix}
-2^0 & 0 & 0\\
+  2^0 & 0   & 0   \\
   0   & 2^0 & 2^1
@@
  \begin{pmatrix}
-\psi_{00}\\
-\psi_{01}\\
+  \psi_{00} \\
+  \psi_{01} \\
   \psi_{11}
@@
  \equiv T^z \begin{pmatrix}
-\psi_{00}\\
-\psi_{01}\\
+  \psi_{00} \\
+  \psi_{01} \\
   \psi_{11}
@@
 \end{align}
-The transformation can be reduced to a tensor product if $R_i$ is a constant for all $i$ such that
+If all variables are represented by the same number of qubits--$R_i$ is a constant for all $i$--then one can express the transformation as tensor product of bit vectors
 \begin{align}
-\mathcal{R} = & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},\\
-\mathcal{Z} = & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},\\
-|\mathds{1}| = & |\mathcal{Z}|,\\
+ \mathcal{R} =  & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},    \\
+ \mathcal{Z} =  & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},    \\
+ |\mathds{1}| = & |\mathcal{Z}|,                 \\
  T^z =          & \mathds{1}\otimes \mathcal{R}.
@@
 
-While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbb{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
-As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).
+%----------------------------------------------------------------------------------------
+\subsubsection{Integer Programming Mapping QUBO}
+\label{sec:methods:ilp-qubo}
+%----------------------------------------------------------------------------------------
 
-\subsection{Integer Programming Mapping to QUBO}
-\label{sec:results:ilp}
 The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
 \begin{align}
-\chi^2 = & \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right. \nonumber\\
-&\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],\\
-\Psi = & \begin{pmatrix}
-\Psi^x\\
-\Psi^s
-\end{pmatrix},
+ \chi^2                         & = \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
+ \nonumber                                                                                                                             \\ \label{eq:qubo-min}
+                                & \qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],   \\
+ \vec x_0                       & =  T^x \vec \Psi^x_0 \, ,
+ \\
+ (\vec \Psi^x_0, \vec \Psi^s_0) & = \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,,                                                 &
 \end{align}
-where $p$ is the strength of the penalty factor which must be set large enough such that the constraints are satisfied under minimization.
+where $p$ is an external parameter representing the strength of the penalty when violating constraints.
 The objective function can be represented as a QUBO Hamiltonian
@@
  \begin{pmatrix}
-Q_{xx} & Q_{xs}\\
+  Q_{xx} & Q_{xs} \\
   Q_{sx} & Q_{ss}
@@
  \begin{pmatrix}
-\Psi^x\\ \Psi^s
-\end{pmatrix} + pb^2,\\
+  \Psi^x \\ \Psi^s
+ \end{pmatrix} + pb^2, \\
  \equiv & \Psi^T Q \Psi + C,
@@
  Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x \nonumber \\
-&+ \mathrm{Diag}_{\psi^x}(c) T^x,\\
-Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,\\
+          & + \mathrm{Diag}_{\psi^x}(c) T^x,                                                                    \\
+ Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,                                                                     \\
  Q_{ss} = & p\left[ {T^{s}}^T T^s + \mathrm{Diag}_{\psi^s}\left( {T^{s}}^T b + b^T T^s\right) \right].
@@
 
-\subsection{Application to the Dominating Set Problem}
-\label{sec:results:mds}
+%----------------------------------------------------------------------------------------
+\subsubsection{Comment on penalty term}
+\label{sec:methods:ilp-qubo-comments}
+%----------------------------------------------------------------------------------------
+
+The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
+Thus some knowledge of the problem is required.
+In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
+After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
+Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
+
+%----------------------------------------------------------------------------------------
+\subsection{Example: Minimum Dominating Set Problem}
+\label{sec:methods:mds}
+%----------------------------------------------------------------------------------------
+
+This section demonstrates the formalism in case of an example ILP: the Minimum Dominating Set problem.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Definition of the Minimum Dominating Set Problem}
+\label{sec:methods:mds-def}
+%----------------------------------------------------------------------------------------
 
@@
                    &
-	\includegraphics[width=0.20\textwidth]{./figures/greedy-4.pdf}\\
+  \includegraphics[width=0.20\textwidth]{./figures/greedy-4.pdf}            \\
   \centering\bf{a} & \centering\bf{b} & \centering\bf{c} & \centering\bf{d}
@@
   Connected nodes are neighbors of the DS (turquoise) or already in the DS.
-		In (a), one finds three unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
+  In (a), one finds three maximally unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
   In the first step $a\to b$, randomly the node (4) is picked.
-		In (b), one has two unconnected choices [(1), (2)] with each adjacent to another unconnected node.
+  In (b), one has three unconnected choices [(1), (2)] with each adjacent to another unconnected node and one node [(6)] which is only adjacent to neighbors of the DS.
   After randomly selecting (2) when going from $b \to c$, only one unconnected node is remaining (6).
@@
 
-\subsubsection{Minimum Dominating Set}
+%----------------------------------------------------------------------------------------
+\subsubsection{Minimum Dominating Set Qubo}
+\label{sec:methods:mds-qubo}
+%----------------------------------------------------------------------------------------
+
 The solution to the minimum independent set can be expressed as an integer optimization problem given by,
 \begin{align}
-f(x) = &\min(\sum_{\nu \in V} \psi^x_{\nu}),\\
-\textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1,\\
+ f(x) =                    & \min\left(\sum_{\nu \in V} \psi^x_{\nu}\right),                    \\
+ \textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1, \\
                            & \psi^x_{\nu} \in \{0, 1\}
@@
 \begin{align}
-f(x) = &\min(\sum_{\nu\in V} \psi^x_{\nu}),\\
-\textrm{subject to} \quad & \psi^x_{\nu} + J_{\nu \mu} \psi^x_{\mu}- T^s_{\nu \alpha} \psi^s_{\alpha}  - 1 = 0,\\
-& \psi_{\nu} \in \{0, 1\},\\
-& 0 \leq s_{\nu} \leq |\mathrm{N}(\nu)|\\
+ f(x) =                    & \min(\sum_{\nu\in V} \psi^x_{\nu}),                                                 \\
+ \textrm{subject to} \quad & \psi^x_{\nu} + J_{\nu \mu} \psi^x_{\mu}- T^s_{\nu \alpha} \psi^s_{\alpha}  - 1 = 0, \\
+                           & \psi_{\nu} \in \{0, 1\},                                                            \\
+                           & 0 \leq s_{\nu} \leq |\mathrm{N}(\nu)|                                               \\
                            & s_{\nu} \in \mathbb{Z},
@@
 
-The target Hamiltonian can be written in the matrix form
-\begin{widetext}
+The target QUBO in the notation of eq.~\eqref{eq:matrix_form} reads
+ {\small
   \begin{align}
-E = &
-\begin{pmatrix}
-\Psi^x & \Psi^s
-\end{pmatrix}
-\begin{pmatrix}
-\mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] & - p(\mathbbm{1}+J^T)T^s\\
-- p{T^s}^T(\mathbbm{1}+J)& p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]
-\end{pmatrix}
-\begin{pmatrix}
-\Psi^x\\ \Psi^s
-\end{pmatrix} + p \overline{\overline{V}}
-\label{eq:matrix_form2}
-\end{align}
-\end{widetext}
+   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] \,, \\
+   Q_{sx} & = - p(\mathbbm{1}+J^T)T^s\,,                                                                     \\
+   Q_{ss} & = p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]\,,                                  \\
+   C      & =  p \overline{\overline{V}}\,,
+  \end{align}}
 where $ |M| \equiv \sum_{\nu} M_{\nu \mu}$.
 
-\section{DISCUSSION}
+%----------------------------------------------------------------------------------------
+\subsection{Quantum Annealing}
+\label{sec:methods:annealing}
+%----------------------------------------------------------------------------------------
 
+%----------------------------------------------------------------------------------------
+\subsubsection{Modified annealing schedule}
+\label{sec:methods:annealing-schedule}
+%----------------------------------------------------------------------------------------
+
+A quantum annealer evolves the ground state of an initial Hamiltonian into the ground state of the problem Hamiltonian by adiabatically changing the hardware which implements Hamiltonian.
+Thus, the implemented Hamiltonian is explicitly time dependent
+\begin{equation}
+ H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
+\end{equation}
+and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
+The variable $s\in [0, 1]$ is the normalized annealing time and, in physical units, is allowed to vary between 1$\mu s$ to 2$ms$ on DWave.
+
+On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
+In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
+The time dependent coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
+The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
+As a result, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
+Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
+We extrapolate their values by a linear extrapolation, and only employ negative offsets such that this effect only enters at the beginning of the annealing process rather than the end.
+Details of the DWave annealing schedule use to generate Fig.~\ref{fig:anneal_schedule} and further documentation are provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.
+
+\begin{figure}[htb]
+ \centering
+  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
+  \caption{
+  Anneal schedules for amplitudes of initial Hamiltonian (top left to bottom right) and final Hamiltonian (bottom left to top right) are displayed for a complete anneal schedule.
+  Different colors represent different offesets: delayed (light to dark), default (black).
+ }
+ \label{fig:anneal_schedule}
+\end{figure}
+
+The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system, in general, will exhibit more disorder.
+When recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
+\begin{equation}
+ H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
+\end{equation}
+we recognize that if $h_i$ is randomly drawn from a Bernoulli distribution, we recover the spin-glass model.
+The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Implementation of annealing offsets}
+\label{sec:methods:annealing-schedule}
+%----------------------------------------------------------------------------------------
+
+For even the smallest graph $NN(2)$, the MDS problem is not native to the chimera graph and must be embedded.
+Following the hypothesis of MBL, we therefore, must look at the values of $h_i$ after embedding.
+The qubits then split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding.
+Further detail is given in Sec.~\ref{sec:methods:minor_embedding} {\color{red} put in methods more details}.
+We study the effects offset the two groups of qubits over a total range between 0\% and 5\% of $c$.
+The results of this study is shown in Fig.~\ref{fig:dwave_offset}.
+
+The results in yellow (green) delays the annealing of qubits subject to stronger (weaker) external fields.
+We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the anneal schedule, in agreement with the MBL hypothesis.
+The phenomena is observed across different problem sizes and hints at the possibility of a generic improvement strategy.
+In the following section, we provide evidence that the improvement is rooted in quantum mechanics, and not other causes such as imperfections in hardware~\cite{} {\color{red} cite dwave's use of annealing offsets}.
+The master equation for quantum annealing is solved subject to the DWave anneal schedule with annealing offsets in order to reproduce the observed phenomenon.
+
+%----------------------------------------------------------------------------------------
+\subsection{Simulation of a Quantum Annealer}
+\label{sec:methods:simulation}
+%----------------------------------------------------------------------------------------
+
+%----------------------------------------------------------------------------------------
+\subsubsection{The Lindblad Equation}
+\label{sec:methods:lindblad}
+%----------------------------------------------------------------------------------------
+
+To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
+\begin{align}
+ \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
+\end{align}
+where $\rho (t)$ is the density matrix at time $t$.
+$H(t)$ is the time-dependent Hamiltonian
+\begin{align}
+ \label{eq:annealH}
+ H_{anneal}(t) & =  - \sum_i  A_i(t)\sigma^x_i                                                                      & \notag \\
+ +             & \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  , &
+\end{align}
+where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
+The site dependency takes into account of the annealing offset.
+$[,]$ denotes the Lie bracket.
+$L_j$ are the Lindblad operators for decoherence.
+$\{, \}$ denotes the anti-commutator.
+
+We consider two types of decoherence models: full counting statistics and local damping.
+The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
+The local damping term models the decoherence of each qubit independently.
+For full counting statistics, the Lindblad operator is
+\begin{align}
+\mathcal{L}[\rho (t)] &=& \Gamma_{fc} \sum_j   (2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}) \notag \\
+&& + e^{-\beta \Delta E_j} (2 S_j^\dagger \rho(t) S_j - \{ S_j S^\dagger_j, \rho(t) \} )
+\end{align}
+where $j$ is the index for the inter-level spacing $\Delta E_j=E_\mu-E_\nu>0$. $S_j=|E_\nu \rangle \langle E_\mu|$ denotes the many-body lowering operator.
+$\{, \}$ denotes the anti-commutator. $\Gamma = 1/T_c$ is the decoherence rate for coherence time $T_c$.
+That is, due to the interaction with the classical thermal bath, there is a probability that the system hops from each higher-energy many-body state to a lower-energy many-body state.
+The probability of the inverse process is given by a Boltzmann factor.
+To model the local decoherence of each qubits in the non-interacting limit, we also consider the amplitude damping for non-interacting qubits.
+The Lindblad operator is
+\begin{align}
+\mathcal{L}[\rho (t)] &=&  \Gamma_{loc} \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \notag \\
+&& + e^{-\beta 2|h_j| }  (2L_j^\dagger \rho(t) L_j - \{ L_j L_j^\dagger, \rho(t) \}) ),
+\end{align}
+where $j$ is the index for qubit.
+$L_j= \sigma^{+}_j=|1\rangle \langle 0|$ for $h_j>0$ and $L_j= \sigma^{-}_j=|0\rangle \langle 1|$ for $h_j<0$.
+That is, each qubit is damped toward its local ground state if we ignore all the interactions.
+
+The initial condition is the Gibbs canonical ensemble
+\begin{equation}
+\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
+\end{equation}
+where $\beta$ is the inverse temperature.
+The probability to get the ground state at measurement is
+\begin{align}
+P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
+\end{align}
+where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
+Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Decoherence Time}
+\label{sec:methods:deco}
+%----------------------------------------------------------------------------------------
+
+\ghissue{Decoherence section}{16}
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Many-Body Localization}
+\label{sec:methods:mbl}
+%----------------------------------------------------------------------------------------
+
+If the annealer does not reach thermal equilibrium, for example, strong external magnetic fields freeze in individual qubits, the final solution of the annealing process might not encode the ground state of the final Hamiltonian.
+It is thus essential to prepare the system such that Many-Body Localizations are absent, and thus one must define a measure for MBL.
+
+We note that this measure depends on the choice of partitions, which is, in principle, arbitrary.
+To define a measure for MBL, the choice for partitions should encode the likelihood of frozen qubits.
+Thus a natural choice for partitions are regions of different external magnetic fields.
+For this choice, at the beginning of the anneal, the mutual information will be zero as all spins start orthogonal to the external field, and, in the end, the mutual information will be constant once a final solution is obtained.
+Intermediate values for the mutual information encode the communication probability of different spin alignments.
+
+Intuitively, to find a final state which globally minimizes the energy, we want the system to explore the entire state space.
+That is, we want the system to have ergodicity in order to avoid Many-Body Localizations.
+Thus the annealing process should be sufficiently slow to not introduce potential barriers which freeze in intermediate spin configurations.
+On the other hand, decoherence in the hardware leads to the loss of quantum information.
+It is, therefore, desirable to minimize the effect of relaxation and shorten the annealing process.
+The interplay between these two competing effects can be observed by looking at the non-monotonous time dependency of the probability for reaching the global ground state.
+
+%----------------------------------------------------------------------------------------
+
+\subsubsection{Systematic effects of annealing offsets}
+\label{sec:app:offset}
+%----------------------------------------------------------------------------------------
+
+We verify that our implementation of annealing offsets on the simulator is consistent with DWave by solving the following three qubit Hamiltonian
+\begin{align}
+	\label{eq:offset_test_hamiltonian}
+	H^{\textrm{problem}} =
+	\begin{pmatrix}
+		-0.25 & 1 & 0 \\
+		0 & -0.25 & 0 \\
+		0 & 0 & -0.25
+	\end{pmatrix}
+\end{align}
+which has a doubly-degenerate ground state of $(0, 1, 1)$ and $(1, 0, 1)$.
+An annealing offset is then applied to either qubit 0 or 1, and breaks the ground state degeneracy of the system.
+Because of the systematic error introduced when assigning an offset to a qubit, the final Hamiltonian given by Eq.~(\ref{eq:annealH}) will have small deviations from the input problem Hamiltonian.
+For example, we expect a negative offset to qubit 0 to Eq.~(\ref{eq:offset_test_hamiltonian}) will yield $(1, 0, 1)$ as the unique ground state given Eq.~(\ref{eq:annealH}).
+
+We confirm that with different combinations of annealing offsets, the degeneracy is lifted on the DWave results as expected by solving for the modified problem Hamiltonian spectrum, as well as dialing in annealing offset in the simulation of this three qubit test case.
+
+In the simulation, we are also reserve the ability to remove the systematic errors by extending the annealing schedule as shown in Fig.~\ref{fig:anneal_schedule_ext}.
+With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians.
+The dependence on offset for $G(2)$ (Fig.~(\ref{fig:dwave1us})) remains the same under the extended anneal schedule (Fig.~\ref{fig:anneal_schedule_ext}), confirming that the behavior is not a systematic artifact.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./new_figures/anneal_schedule_extended.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling_extended.pdf}
+	\caption{{\color{red}I need to add dwave final state distribution here too.}}
+	\label{fig:anneal_schedule_ext}
+\end{figure}
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Minor Embedding}
+\label{sec:methods:minor_embedding}
+%----------------------------------------------------------------------------------------
+Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
+As a result, details of the embedding are important.
+We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the DWave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module.
+The same embedding is used for all DWave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
+Additionally, solving the same graph as a function of offset on the exact same qubits removes (or at least keeps consistent) the systematic effects due to solving a problem on different physical qubits.
+We note that comparisons between different graphs in Fig.~\ref{fig:baseline} are subject to this uncontrolled systematic.
+
+After embedding the QUBO for $G(2)$ requires 5 qubits (an increase from 4), where by construction, qubits 0 and 3 form the qubit chain.
+We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by DWave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the minimum dominating set.
+
+The resulting Ising Hamiltonian has external field equal to $h = (2.75, 1.5, -1.0, -1.25, -1.0)$.
+Following the offset strategy described in Sec.~\ref{sec:discussion:offsets}, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
+This imbalance in the two groups may perhaps explain the reason why effects of delaying the weaker fields are more pronounced, since delaying the strong fields only differs from the baseline by a single qubit.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Other Simulation Details}
+\label{sec:methods:simulation_details}
+%----------------------------------------------------------------------------------------
+To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e. $A(s)=A(0)$ and $B(s)=0$.
+The initial state is pure zero state $\rho=|00...0\rangle \langle 00...0|$.
+In this case the analytical solution can be obtained for the wave function oscillation.
+The time-dependent probability is $P_{0}=\cos^{2n}(s)=\cos^{2n}(t/T)$ where $n$ is the number of qubits and $T$ is the annealing time.
+For annealing time $T=1/A(0)$, we expect to see perfect one-period oscillation.
+The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction.
+{\color{red} Are you suppose to reference Fig. 7 here?}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./figures/check.png}
+	\caption{check}
+	\label{fig:check}
+\end{figure}
+
+Next, the simulator is applied to the $G(2)$ problem and the result is summarized in Fig.~\ref{fig:td_prob} where the time-dependent overlap with the exact Ising ground state is shown.
+We observe for all cases that the system undergoes what is analogous to a magnetic phase transition around $s\sim 0.4$.
+After the phase transition, we are able to confirm that the system collapses to effectively a classical state in the sense that the density matrix becomes a diagonal matrix.
+The steady increase in probability after the phase transition is a sensitive balance between the competing effects between full-counting statistics and local damping.
+In our example, full-counting statistics is tuned to be slightly stronger, resulting in what amounts to a final thermal annealing step.
+If local damping is relatively stronger, then the probability after the phase transition will slowly decrease as the system decoheres into its local ground state.
+While we believe both effects are important in DWave, the experimental results are not precise enough for us to conclude which is the dominant effect.
+We emphasize however, that the simulation suggests that the ground state is recovered predominantly due to the quantum phase transition.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
+	\caption{(Left) The time-dependent probability of resolving the ground state and (Right) the corresponding mutual information.
+(Top) Simulation with decoherence included and (Bottom) without decoherence.}
+	\label{fig:td_prob}
+\end{figure}
+
+Finally, we comment that in order for the simulation to obtain the final state distribution shown in Fig.~\ref{fig:final_state_distribution}, effects of full-counting statistics are required.
+Absent some dynamical thermalization effect, the $G(2)$ problem is too small such that at a total annealing time of 1$\mu s$, the annealing offsets lift the ground state degeneracy by an amount such that diabatic transitions are absent, and the simulation is populated predominantly by the unique ground state.
+The final state distribution gives us a very sensitive observable to tune the simulation temperature, and agrees well with the experimental operating temperature.
+
+\ghissue{Simulation details}{18}
+
+%========================================================================================
+\section{RESULTS}
+\label{sec:results}
+%========================================================================================
+
+%----------------------------------------------------------------------------------------
 \subsection{Finding the Dominating Set with a Quantum Annealer}
 \label{sec:discussion:qa}
+%----------------------------------------------------------------------------------------
 \begin{figure}[b]
@@
 
-\subsubsection{Modified annealing schedule}
-
-\noindent\textit{Annealing offsets}
-
-In quantum annealing, the ground state of the problem Hamiltonian is obtained from the evolution of a time-dependent Hamiltonian,
-\begin{equation}
-H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
-\end{equation}
-where $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, and $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
-The variable $s\in [0, 1]$ is the normalized annealing time and is allowed to vary between 1$\mu s$ to 2$ms$ on the DWave.
-On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits.
-In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
-The time dependent coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
-The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
-As a result, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
-Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
-We extrapolate their values by a linear extrapolation, and only employ negative offsets such that this effect only enters at the beginning of the annealing process rather than the end.
-Details of the DWave annealing schedule use to generate Fig.~\ref{fig:anneal_schedule} and further documentation are provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.
-
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
-	\caption{asdf}
-	\label{fig:anneal_schedule}
-\end{figure}
-
-The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system in general will exhibit more disorder.
-We define disorder by first recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
-\begin{equation}
-H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
-\end{equation}
-and recognize that in the limit where $h_i$ is randomly drawn from a Bernoulli distribution we recover the spin-glass model.
-The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.
-\\\\
-\noindent\textit{Implementation of annealing offsets}
-\label{sec:discussion:offsets}
-
-For even the smallest graph $NN(2)$, the MDS problem is not native to the chimera graph and must be embedded.
-Following the hypothesis of MBL, we therefore, must look at the values of $h_i$ after embedding.
-The qubits then split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding.
-Further detail is given in Sec.~\ref{sec:methods:minor_embedding} {\color{red} put in methods more details}.
-We study the effects offset the two groups of qubits over a total range between 0\% and 5\% of $c$.
-The results of this study is shown in Fig.~\ref{fig:dwave_offset}.
-
-The results in yellow (green) delays the annealing of qubits subject to stronger (weaker) external fields.
-We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the anneal schedule, in agreement with the MBL hypothesis.
-The phenomena is observed across different problem sizes and hints at the possibility of a generic improvement strategy.
-In the following section, we provide evidence that the improvement is rooted in quantum mechanics, and not other causes such as imperfections in hardware~\cite{} {\color{red} cite dwave's use of annealing offsets}.
-The master equation for quantum annealing is solved subject to the DWave anneal schedule with annealing offsets in order to reproduce the observed phenomenon.
-
+%----------------------------------------------------------------------------------------
 \subsection{Simulation Results}
+%----------------------------------------------------------------------------------------
 
@@
 	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
-	\caption{ {\color{red} new caption}}
+	\caption{The probability of finding the MDS for $G(2)$ from DWave (orange) and results from simulation with both decoherence terms (blue).
+     The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times.}
 	\label{fig:dwave1us}
@@
 
+%----------------------------------------------------------------------------------------
+\subsection{Decoherence and Many-Body Localization}
+%----------------------------------------------------------------------------------------
+
+\ghissue{Finalize results}{19}
+
+%========================================================================================
+\section{DISCUSSION}
+\label{sec:discussion}
+%========================================================================================
+
 \subsection{Final remarks}
@@
 
-\section{METHODS}
-\subsection{The Lindblad Equation}
-\label{sec:methods:lindblad}
+\ghissue{Conclusion}{20}
 
-To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
-\begin{align}
-\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}[\rho (t)] ,
-\end{align}
-where $\rho (t)$ is the density matrix at time $t$. The time-dependent Hamiltonian $H(t)$ solved by DWave as documented in Ref.~\cite{dwave_offset} is
-\begin{align}
-\label{eq:annealH}
- H^{\textrm{anneal}}(t)  =&  - \sum_i  A_i(t)\sigma^x_i +\sum_i B_{i}(t) h_i \sigma^z_i \notag \\
- +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j ,&
-\end{align}
-where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
-The site dependency takes into account of the annealing offset.
-$[,]$ denotes the Lie bracket and $\mathcal{L}$ is the Lindblad operator.
+%========================================================================================
+\section{DATA AVAILABILITY}
+\label{sec:open-source}
+%========================================================================================
 
-We consider two types of decoherence models: full counting statistics and local damping.
-The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
-The local damping term models the decoherence of each qubit independently.
-For full counting statistics, the Lindblad operator is
-\begin{align}
-\mathcal{L}[\rho (t)] &=& \Gamma_{fc} \sum_j   (2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}) \notag \\
-&& + e^{-\beta \Delta E_j} (2 S_j^\dagger \rho(t) S_j - \{ S_j S^\dagger_j, \rho(t) \} )
-\end{align}
-where $j$ is the index for the inter-level spacing $\Delta E_j=E_\mu-E_\nu>0$.
-$S_j=|E_\nu \rangle \langle E_\mu|$ denotes the many-body lowering operator.
-$\{, \}$ denotes the anti-commutator.
-$\Gamma = 1/T_c$ is the decoherence rate for coherence time $T_c$.
-That is, due to the interaction with the classical thermal bath, there is a probability that the system hops from each higher-energy many-body state to a lower-energy many-body state.
-The probability of the inverse process is given by a Boltzmann factor.
-To model the local decoherence of each qubits in the non-interacting limit, we also consider the amplitude damping for non-interacting qubits.
-The Lindblad operator is
-\begin{align}
-\mathcal{L}[\rho (t)] &=&  \Gamma_{loc} \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \notag \\
-&& + e^{-\beta 2|h_j| }  (2L_j^\dagger \rho(t) L_j - \{ L_j L_j^\dagger, \rho(t) \}) ),
-\end{align}
-where $j$ is the index for qubit.
-$L_j= \sigma^{+}_j=|1\rangle \langle 0|$ for $h_j>0$ and $L_j= \sigma^{-}_j=|0\rangle \langle 1|$ for $h_j<0$.
-That is, each qubit is damped toward its local ground state if we ignore all the interactions.
+\ghissue{Data availability}{21}
 
-The initial condition is the Gibbs canonical ensemble
-\begin{equation}
-\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
-\end{equation}
-where $\beta$ is the inverse temperature.
-The probability to get the ground state at measurement is
-\begin{align}
-P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
-\end{align}
-where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
-Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
+%========================================================================================
+\section{ACKNOWLEDGEMENTS}
+%========================================================================================
 
-\subsection{Systematic effects of annealing offsets}
-\label{sec:app:offset}
-We verify that our implementation of annealing offsets on the simulator is consistent with DWave by solving the following three qubit Hamiltonian
-\begin{align}
-	\label{eq:offset_test_hamiltonian}
-	H^{\textrm{problem}} =
-	\begin{pmatrix}
-		-0.25 & 1 & 0 \\
-		0 & -0.25 & 0 \\
-		0 & 0 & -0.25
-	\end{pmatrix}
-\end{align}
-which has a doubly-degenerate ground state of $(0, 1, 1)$ and $(1, 0, 1)$.
-An annealing offset is then applied to either qubit 0 or 1, and breaks the ground state degeneracy of the system.
-Because of the systematic error introduced when assigning an offset to a qubit, the final Hamiltonian given by Eq.~(\ref{eq:annealH}) will have small deviations from the input problem Hamiltonian.
-For example, we expect a negative offset to qubit 0 to Eq.~(\ref{eq:offset_test_hamiltonian}) will yield $(1, 0, 1)$ as the unique ground state given Eq.~(\ref{eq:annealH}).
-
-We confirm that with different combinations of annealing offsets, the degeneracy is lifted on the DWave results as expected by solving for the modified problem Hamiltonian spectrum, as well as dialing in annealing offset in the simulation of this three qubit test case.
-
-In the simulation, we are also reserve the ability to remove the systematic errors by extending the annealing schedule as shown in Fig.~\ref{fig:anneal_schedule_ext}.
-With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians.
-The dependence on offset for $G(2)$ (Fig.~(\ref{fig:dwave1us})) remains the same under the extended anneal schedule (Fig.~\ref{fig:anneal_schedule_ext}), confirming that the behavior is not a systematic artifact.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/anneal_schedule_extended.pdf}
-	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling_extended.pdf}
-	\caption{{\color{red}I need to add dwave final state distribution here too.}}
-	\label{fig:anneal_schedule_ext}
-\end{figure}
-
-\subsection{Minor Embedding}
-\label{sec:methods:minor_embedding}
-Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
-As a result, details of the embedding are important.
-We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the DWave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module.
-The same embedding is used for all DWave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
-Additionally, solving the same graph as a function of offset on the exact same qubits removes (or at least keeps consistent) the systematic effects due to solving a problem on different physical qubits.
-We note that comparisons between different graphs in Fig.~\ref{fig:baseline} are subject to this uncontrolled systematic.
-
-After embedding the QUBO for $G(2)$ requires 5 qubits (an increase from 4), where by construction, qubits 0 and 3 form the qubit chain.
-We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by DWave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the minimum dominating set.
-
-The resulting Ising Hamiltonian has external field equal to $h = (2.75, 1.5, -1.0, -1.25, -1.0)$.
-Following the offset strategy described in Sec.~\ref{sec:discussion:offsets}, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
-This imbalance in the two groups may perhaps explain the reason why effects of delaying the weaker fields are more pronounced, since delaying the strong fields only differs from the baseline by a single qubit.
-
-\subsection{Simulation Details}
-\label{sec:methods:simulation_details}
-To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e.
-$A(s)=A(0)$ and $B(s)=0$.
-The initial state is pure zero state $\rho=|00...0\rangle \langle 00...0|$.
-In this case the analytical solution can be obtained for the wave function oscillation.
-The time-dependent probability is $P_{0}=\cos^{2n}(s)=\cos^{2n}(t/T)$ where $n$ is the number of qubits and $T$ is the annealing time.
-For annealing time $T=1/A(0)$, we expect to see perfect one-period oscillation.
-The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction.
-{\color{red} Are you suppose to reference Fig.
-7 here?}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./figures/check.png}
-	\caption{check}
-	\label{fig:check}
-\end{figure}
-
-Next, the simulator is applied to the $G(2)$ problem and the result is summarized in Fig.~\ref{fig:td_prob} where the time-dependent overlap with the exact Ising ground state is shown.
-We observe for all cases that the system undergoes what is analogous to a magnetic phase transition around $s\sim 0.4$.
-After the phase transition, we are able to confirm that the system collapses to effectively a classical state in the sense that the density matrix becomes a diagonal matrix.
-The steady increase in probability after the phase transition is a sensitive balance between the competing effects between full-counting statistics and local damping.
-In our example, full-counting statistics is tuned to be slightly stronger, resulting in what amounts to a final thermal annealing step.
-If local damping is relatively stronger, then the probability after the phase transition will slowly decrease as the system decoheres into its local ground state.
-While we believe both effects are important in DWave, the experimental results are not precise enough for us to conclude which is the dominant effect.
-We emphasize however, that the simulation suggests that the ground state is recovered predominantly due to the quantum phase transition.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
-	\caption{(Left) The time-dependent probability of resolving the ground state and (Right) the corresponding mutual information.
-(Top) Simulation with decoherence included and (Bottom) without decoherence.}
-	\label{fig:td_prob}
-\end{figure}
-
-Finally, we comment that in order for the simulation to obtain the final state distribution shown in Fig.~\ref{fig:final_state_distribution}, effects of full-counting statistics are required.
-Absent some dynamical thermalization effect, the $G(2)$ problem is too small such that at a total annealing time of 1$\mu s$, the annealing offsets lift the ground state degeneracy by an amount such that diabatic transitions are absent, and the simulation is populated predominantly by the unique ground state.
-The final state distribution gives us a very sensitive observable to tune the simulation temperature, and agrees well with the experimental operating temperature.
-
-\section{DATA AVAILABILITY}
-
-Link to GitHub.
-
-\section{ACKNOWLEDGEMENTS}
-
+\ghissue{Acknowledgements}{22}
 We thank x, y, z...
 
+%========================================================================================
 \section{AUTHOR CONTRIBUTIONS}
+%========================================================================================
 
-...
+\ghissue{Author contributions}{23}
+C.K. drank a lot of coffee.
 
+%========================================================================================
 \section{ADDITIONAL INFORMATION}
+%========================================================================================
 
@@
 \bibliography{qilp}
+\ghissue{References}{24}
+%========================================================================================
 

### 2020-09-04 paper/main.tex
Placing methods in the end
Major section refactor

@@
 
-Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints and is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}.
+Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints
+\begin{align}
+ \label{eq:initial-ip-def}
+ \vec x_0 = \mathrm{arg} & \min\limits_{x}(\sum_i c_i x_i)
+\end{align}
+subject to
+\begin{align}
+ \label{eq:ilp-constraints}
+  & \sum_i A_{ai}x_i +b_a \leq 0 \,, \\
+  & x_i  \in \mathbbm{N}\, ,
+\end{align}
+where the natural numbers $\mathbbm{N}$ include zero, $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
+
+ILP is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}.
 In general, however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
@@
 While greedy algorithms do not guarantee optimal global solutions, they find approximate solutions in polynomial time, which can be utilized in further computations.
+
+An important ILP is the Minimum Dominating Set problem which is represantivly considered in this work.
+For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, and a dominating set $D$ is a specific subset of vertices $D \subseteq V$.
+In particluar $D$ is a dominating set if all vertices in $V$ but not in $D$ are adjacent to at least one vertex in $D$.
+This is equivalent to requiring the set of nearest-neighbor vertices of $D$ (exclusive) and $D$ cover all vertices $N(D) \cup D = V$ (an example is given by Fig.~\ref{fig:dominating_sets}a).
+The set $D$ is a minimal dominating set if there is no proper subset of $D$ that is a dominating set, {\it{i.e.}}, the removal of any vertex in $D$ results in $N(D) \cup D  \neq V$.
+An example is given by Fig.~\ref{fig:dominating_sets}b.
+The domination number of $D$ is given by the cardinality of $|D| \equiv \overline{\overline{D}}$.
+The minimum dominating set (MDS) is defined by $D$ with the smallest domination number.
+Fig.~\ref{fig:dominating_sets}c shows an example of the minimum dominating set of $G(V, E)$ and is different from the minimal dominating set.
+We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
+As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a problem that is well studied for quantum annealers~\cite{}.
+
+\begin{figure*}
+	\centering
+	\begin{tabular}{p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
+	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds0.pdf}
+&&
+	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds1.pdf}
+&&
+	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds2.pdf}\\
+	\centering\bf{a} && \centering\bf{b} && \centering\bf{c}
+	\end{tabular}
+	\caption{Example of different dominating sets for $G(V, E)$.
+Vertices in the dominating set $D$ are highlighted in blue.
+{\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 2$.
+{\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.
+{\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 1$.}
+	\label{fig:dominating_sets}
+\end{figure*}
+
+For general graphs, existing "classical" algorithms either find MDS solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or approximate solutions in polynomial time.
+For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
+Thus one is guaranteed to find a dominating set but not necessarily a MDS.
+
 Due to the importance and difficulty, in this work, we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.
@@
 
+In this paper, we propose a new algorithm that maps ILP problems to QUBOs.
+This is achieved by the introduction of slack variables $s$ which turn the inequalities eq.~\eqref{eq:ilp-constraints} to equalities
+\begin{align}
+  & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
+  & s_a \in \mathbb{N},                \\
+  & x_i \in \mathbb{N}.
+\end{align}
+As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values.
+
 \ghissue{Decoherence \& Localization}{14}
+
+A quantum annealer evolves the ground state of an initial Hamiltonian into the ground state of the problem Hamiltonian by adiabatically changing the hardware which implements Hamiltonian.
+Thus, the implemented Hamiltonian is explicitly time dependent
+\begin{equation}
+ H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
+\end{equation}
+and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ encodes the problem to be solved.
+The variable $s\in [0, 1]$ is the normalized annealing time and, in physical units, is allowed to vary between 1$\mu s$ to 2$ms$ on DWave.
+
+On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
+In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
+Details of the DWave annealing schedule use to generate Fig.~\ref{fig:anneal_schedule} and further documentation are provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.
+
+\begin{figure}[htb]
+ \centering
+  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
+  \caption{
+  Anneal schedules for amplitudes of initial Hamiltonian (top left to bottom right) and final Hamiltonian (bottom left to top right) are displayed for a complete anneal schedule.
+  Different colors represent different offesets: delayed (light to dark), default (black).
+ }
+ \label{fig:anneal_schedule}
+\end{figure}
+
+If the annealer does not reach thermal equilibrium, for example, strong external magnetic fields freeze in individual qubits, the final solution of the annealing process might not encode the ground state of the final Hamiltonian.
+It is thus essential to prepare the system such that Many-Body Localizations are absent, and thus one must define a measure for MBL.
+
+We note that this measure depends on the choice of partitions, which is, in principle, arbitrary.
+To define a measure for MBL, the choice for partitions should encode the likelihood of frozen qubits.
+Thus a natural choice for partitions are regions of different external magnetic fields.
+For this choice, at the beginning of the anneal, the mutual information will be zero as all spins start orthogonal to the external field, and, in the end, the mutual information will be constant once a final solution is obtained.
+Intermediate values for the mutual information encode the communication probability of different spin alignments.
+
+Intuitively, to find a final state which globally minimizes the energy, we want the system to explore the entire state space.
+That is, we want the system to have ergodicity in order to avoid Many-Body Localizations.
+Thus the annealing process should be sufficiently slow to not introduce potential barriers which freeze in intermediate spin configurations.
+On the other hand, decoherence in the hardware leads to the loss of quantum information.
+It is, therefore, desirable to minimize the effect of relaxation and shorten the annealing process.
+The interplay between these two competing effects can be observed by looking at the non-monotonous time dependency of the probability for reaching the global ground state.
+
+To improve annealing results we propose a qubitwise offsets associated with exeternal field alignments.
+The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system, in general, will exhibit more disorder.
+When recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
+\begin{equation}
+ H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
+\end{equation}
+we recognize that if $h_i$ is randomly drawn from a Bernoulli distribution, we recover the spin-glass model.
+The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.
 
@@
 
-In section \ref{sec:methods} we propose an algorithm that maps ILP problems to QA hardware (\ref{sec:methods:ilp}) and present an example implementation in case of the Minimal Dominating Set problem (\ref{sec:methods:mds}).
+ and present an example implementation in case of the Minimal Dominating Set problem (\ref{sec:methods:mds}).
 We review the annealing process on the utilized hardware (\ref{sec:methods:annealing}) and describe the computational framework which we used to simulate the annealing process (\ref{sec:methods:simulation}).
@@
 All algorithms used and data obtained are publicly available (\ref{sec:open-source})
+
+%========================================================================================
+\section{RESULTS}
+\label{sec:results}
+%========================================================================================
+
+%----------------------------------------------------------------------------------------
+\subsection{ILP QUBO}
+\label{sec:results:qa}
+%----------------------------------------------------------------------------------------
+
+The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
+\begin{align}
+ \chi^2                         & = \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
+ \nonumber                                                                                                                             \\ \label{eq:qubo-min}
+                                & \qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],   \\
+ \vec x_0                       & =  T^x \vec \Psi^x_0 \, ,
+ \\
+ (\vec \Psi^x_0, \vec \Psi^s_0) & = \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,,                                                 &
+\end{align}
+where $p$ is an external parameter representing the strength of the penalty when violating constraints and $T^{x,z}$ is a matrix mapping qubits to integers (see also section \ref{sec:methods:bit-basis}).
+The objective function can be represented as a QUBO Hamiltonian
+\begin{align}
+ E =    &
+ \begin{pmatrix}
+  \Psi^x & \Psi^s
+ \end{pmatrix}
+ \begin{pmatrix}
+  Q_{xx} & Q_{xs} \\
+  Q_{sx} & Q_{ss}
+ \end{pmatrix}
+ \begin{pmatrix}
+  \Psi^x \\ \Psi^s
+ \end{pmatrix} + pb^2, \\
+ \equiv & \Psi^T Q \Psi + C,
+ \label{eq:matrix_form}
+\end{align}
+where
+\begin{align}
+ Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x \nonumber \\
+          & + \mathrm{Diag}_{\psi^x}(c) T^x,                                                                    \\
+ Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,                                                                     \\
+ Q_{ss} = & p\left[ {T^{s}}^T T^s + \mathrm{Diag}_{\psi^s}\left( {T^{s}}^T b + b^T T^s\right) \right].
+\end{align}
+The function $\mathrm{Diag}_{z}(v)$ embeds a vector $v$ into a diagonal matrix in subspace $z$, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.
+
+A solution to the ILP is found by obtaining the qubit vector $\psi$ which minimizes $E$.
+The integer solution to the original ILP is computed by $\vec x = T^x \vec \psi^x$ and the original energy is computed by shifting the annealer extracted energy by $pb^2$.
+The slack components of this vector $\psi^s$ can be utilized to check if the contraints are indeed fulfilled.
+
+%----------------------------------------------------------------------------------------
+\subsection{Dominating Set scaling \& offset study}
+\label{sec:results:qa}
+%----------------------------------------------------------------------------------------
+\begin{figure}[b]
+	\centering
+	\begin{tabular}{cc}
+	$G(n):$ &
+	\raisebox{-.4\height}{\includegraphics[width=0.8\columnwidth]{./new_figures/linear_graph.pdf}}
+	\end{tabular}
+	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
+\label{fig:linear}
+\end{figure}
+
+We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.
+This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer.
+Additionally the MDS solution is known analytically, and contains both unique and degenerate solutions.
+In particular, the domination number for $G(n)$ is $\lceil n/3 \rceil$ while the number of MDS solutions for $n$ vertices is
+\begin{align}
+&1 &&\textrm{if} && n\textrm{ mod }3=0,\nonumber \\
+&2\lfloor n/3 \rfloor + 1 && \textrm{if}&& n\textrm{ mod }3=1,\nonumber \\
+&\lfloor n/3 \rfloor + 2 && \textrm{if} && n \textrm{ mod }3 = 2,
+\end{align}
+and gives the probability of randomly guessing the MDS of $G(n)$.
+
+For even the smallest graph $G(2)$, the MDS problem is not native to the chimera graph and must be embedded.
+Following the hypothesis of MBL, we therefore, must look at the values of $h_i$ after embedding.
+The qubits then split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| + \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding.
+Further detail is given in Sec.~\ref{sec:methods:minor_embedding} {\color{red} put in methods more details}.
+We study the effects offset the two groups of qubits over a total range between 0\% and 5\% of $c$.
+The results of this study is shown in Fig.~\ref{fig:dwave_offset}.
+
+For the following studies, we perform experiments on the \texttt{DW\_2000Q\_6} solver.
+The annealing time is set to 500$\mu$s after performing a study on various annealing times the $G(6)$ graph.
+The black line (offset$=0.0$) in Fig.~\ref{fig:baseline} shows results from the baseline experiment, without modification to the DWave annealing schedule, and observe improvement over random guessing (blue).
+However, We explore one avenue towards improving the experiment results by introducing per-qubit annealing offsets into the time evolution.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./new_figures/DWave_scaling.pdf}
+	\caption{Baseline result of DWave (black) compared to random guessing (blue).
+The jagged nature of random guessing reflects the degeneracy of the ground state.
+The legend labels the values of annealing offsets employed.
+A positive offsets (yellow) indicates that qubits with large values of $|h_i|$ are annealing with a delayed schedule, while negative offsets (green) delay the schedule of qubits with small values of $h_i$.}
+	\label{fig:baseline}
+\end{figure}
+
+The results in yellow (green) delays the annealing of qubits subject to stronger (weaker) external fields.
+We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the anneal schedule, in agreement with the MBL hypothesis.
+The phenomena is observed across different problem sizes and hints at the possibility of a generic improvement strategy.
+
+%----------------------------------------------------------------------------------------
+\subsection{Simulation Results}
+%----------------------------------------------------------------------------------------
+
+In order to understand the effects of annealing offsets, we simulate the annealing process for the $G(2)$ graph embedded in chimera topography.
+In order to shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
+The resulting ground state probability as a function of offset measured over 100,000 observations is shown in Fig.~\ref{fig:dwave1us}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
+	\caption{The probability of finding the MDS for $G(2)$ from DWave (orange) and results from simulation with both decoherence terms (blue).
+     The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times.}
+	\label{fig:dwave1us}
+\end{figure}
+
+Simulation results are obtained by solving the von Neumann equation subject to two decoherence models: local damping and full-counting statistics.
+Details of the master equation are given in Sec.~\ref{sec:methods:lindblad}.
+The time dependence of $A(s)$ and $B(s)$ are given by the DWave annealing schedule with offsets in Fig.~\ref{fig:anneal_schedule}.
+The graph $G(2)$ has the interesting feature of having a degenerate ground state depending on whether qubit 0 or 1 is chosen to be the MDS solution.
+This degeneracy is reflected in the experimental result and provides a non-trivial benchmark for our simulation.
+Fig.~\ref{fig:final_state_distribution} show the final state distribution of the three lowest lying state.
+The states $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ are the two degenerate ground states of the embedded Hamiltonian, while $(1, 1, 1, 1, 1)$ is the first excited state which yields an incorrect solution.
+All other states receive negligible probability at the end of annealing.
+The simulation (black) captures main features of the experimental result: 1) significant probability to populate both ground states (rather than populating only one), 2) asymmetry in ground state population due to systematic effects of offset lifting the final state degeneracy spanning approximately the correct range, 3) population of first excited state with systematically lower probability when the strong field is delayed.
+This result can be obtained by tuning three free parameters: the simulation temperature to the order of 10 milliKelvin, and the two coefficients of the two decoherence models at the order of 1 to 10 $ns$.
+Additional insights of the simulation are given in Sec.~\ref{sec:methods:simulation_details}.
+
+The resulting probability of recovering the correct solution as a function of annealing offset is given in Fig.~\ref{fig:dwave1us}.
+We confirm that scaling with respect to offset from the simulation matches what is observed from experiment, and provides evidence suggesting that the improvements are related to quantum mechanics.
+An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets is presented in Sec.~\ref{sec:app:offset}, and further supports this observation.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./new_figures/final_state_distribution.pdf}
+	\caption{{\color{red}I need to add dwave final state distribution here too.}}
+	\label{fig:final_state_distribution}
+\end{figure}
+
+\ghissue{Finalize results}{19}
+
+%========================================================================================
+\section{DISCUSSION}
+\label{sec:discussion}
+%========================================================================================
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Comment on ILP QUBO penalty term}
+\label{sec:methods:ilp-qubo-comments}
+%----------------------------------------------------------------------------------------
+
+The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
+Thus some knowledge of the problem is required.
+In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
+After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
+Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
+
+\subsection{Final remarks}
+We would like to emphasize that while the annealing offsets are motivated by the MBL hypothesis, and the results also follow those expectations, we do not have definitive proof that MBL plays a crucial role.
+The reason is because observations of MBL inevitably require the study of finite-size scaling, and our current simulation while being extremely thorough and explicit, is exponentially slow to evaluate making evaluations of even $G(3)$ untenable.
+However, the intersection of time-dependent quantum mechanics and emergent phenomena such at MBL is an exciting direction that is pertinent to adiabatic quantum computing.
+
+\ghissue{Conclusion}{20}
 
@@
 \label{sec:methods:ilp}
-%----------------------------------------------------------------------------------------
-
-This section presents the formalism which maps a general ILP to a QUBO.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Integer linear programming}
-\label{sec:methods:ilp-def}
-%----------------------------------------------------------------------------------------
-Formally, ILP is defined as the optimization of a linear function
-\begin{align}
- \label{eq:initial-ip-def}
- \vec x_0 = \mathrm{arg} & \min\limits_{x}(\sum_i c_i x_i)
-\end{align}
-subject to
-\begin{align}
- \label{eq:ilp-constraints}
-  & \sum_i A_{ai}x_i +b_a \leq 0 \,, \\
-  & x_i  \in \mathbbm{N}
-\end{align}
-
-where the natural numbers $\mathbbm{N}$ include zero, $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Slack variables}
-\label{sec:methods:slack}
-%----------------------------------------------------------------------------------------
-
-The inequality constraints in eq.~\eqref{eq:ilp-constraints} can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
-\begin{align}
- \vec x_0 = \mathrm{arg} & \min(\sum_i c_i x_i)\,,
-\end{align}
-subject to
-\begin{align}                                                 & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
-  & s_a \in \mathbb{N},                \\
-  & x_i \in \mathbb{N}.
-\end{align}
-While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
-As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).
-
-Because quantum annealing is capable of solving quadratic problems, we extend the proposed algorithm to solve integer quadratic optimization problems as well such that
-\begin{align}
- \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
-\end{align}
-without the introduction of auxiliary qubits.
 
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{Integer Programming Mapping QUBO}
-\label{sec:methods:ilp-qubo}
-%----------------------------------------------------------------------------------------
-
-The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
-\begin{align}
- \chi^2                         & = \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
- \nonumber                                                                                                                             \\ \label{eq:qubo-min}
-                                & \qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],   \\
- \vec x_0                       & =  T^x \vec \Psi^x_0 \, ,
- \\
- (\vec \Psi^x_0, \vec \Psi^s_0) & = \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,,                                                 &
-\end{align}
-where $p$ is an external parameter representing the strength of the penalty when violating constraints.
-The objective function can be represented as a QUBO Hamiltonian
-\begin{align}
- E =    &
- \begin{pmatrix}
-  \Psi^x & \Psi^s
- \end{pmatrix}
- \begin{pmatrix}
-  Q_{xx} & Q_{xs} \\
-  Q_{sx} & Q_{ss}
- \end{pmatrix}
- \begin{pmatrix}
-  \Psi^x \\ \Psi^s
- \end{pmatrix} + pb^2, \\
- \equiv & \Psi^T Q \Psi + C,
- \label{eq:matrix_form}
-\end{align}
-where
-\begin{align}
- Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x \nonumber \\
-          & + \mathrm{Diag}_{\psi^x}(c) T^x,                                                                    \\
- Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,                                                                     \\
- Q_{ss} = & p\left[ {T^{s}}^T T^s + \mathrm{Diag}_{\psi^s}\left( {T^{s}}^T b + b^T T^s\right) \right].
-\end{align}
-The function $\mathrm{Diag}_{z}(v)$ embeds a vector $v$ into a diagonal matrix in subspace $z$, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Comment on penalty term}
-\label{sec:methods:ilp-qubo-comments}
-%----------------------------------------------------------------------------------------
-
-The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
-Thus some knowledge of the problem is required.
-In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
-After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
-Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
-
-%----------------------------------------------------------------------------------------
-\subsection{Example: Minimum Dominating Set Problem}
-\label{sec:methods:mds}
-%----------------------------------------------------------------------------------------
-
-This section demonstrates the formalism in case of an example ILP: the Minimum Dominating Set problem.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Definition of the Minimum Dominating Set Problem}
-\label{sec:methods:mds-def}
-%----------------------------------------------------------------------------------------
-
-Given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, and a subset of vertices $D \subseteq V$.
-If the set of all vertices not in $D$ is adjacent to at least one vertex in $D$, then $D$ is a dominating set.
-This is equivalent to requiring the set of nearest-neighbor vertices of $D$ (exclusive) and $D$ cover all vertices $N(D) \cup D = V$ (an example is given by Fig.~\ref{fig:dominating_sets}a).
-The set $D$ is a minimal dominating set if there is no proper subset of $D$ that is a dominating set, {\it{i.e.}}, the removal of any vertex in $D$ results in $N(D) \cup D  \neq V$.
-An example is given by Fig.~\ref{fig:dominating_sets}b.
-The domination number of $D$ is given by the cardinality of $|D| \equiv \overline{\overline{D}}$.
-The minimum dominating set (MDS) is defined by $D$ with the smallest domination number.
-Fig.~\ref{fig:dominating_sets}c shows an example of the minimum dominating set of $G(V, E)$ and is different from the minimal dominating set.
-We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
-As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a problem that is well studied for quantum annealers~\cite{}.
-
-\begin{figure*}
-	\centering
-	\begin{tabular}{p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
-	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds0.pdf}
-&&
-	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds1.pdf}
-&&
-	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds2.pdf}\\
-	\centering\bf{a} && \centering\bf{b} && \centering\bf{c}
-	\end{tabular}
-	\caption{Example of different dominating sets for $G(V, E)$.
-Vertices in the dominating set $D$ are highlighted in blue.
-{\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 2$.
-{\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.
-{\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 1$.}
-	\label{fig:dominating_sets}
-\end{figure*}
-
-For general graphs, existing "classical" algorithms either find minimal solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or approximate solutions in polynomial time.
-For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
-Thus one is guaranteed to find a dominating set but not necessarily a MDS. {\color{red} Write some pseudo code for greedy search.}
-%We demonstrate an example greedy algorithm in figure Fig.~\ref{fig:mds-greedy}.
-
-\iffalse
-\begin{figure*}
- \centering
- \begin{tabular}{p{0.22\textwidth}p{0.22\textwidth}p{0.22\textwidth}p{0.22\textwidth}}
-  \includegraphics[width=0.20\textwidth]{./figures/greedy-1.pdf}
-                   &
-  \includegraphics[width=0.20\textwidth]{./figures/greedy-2.pdf}
-                   &
-  \includegraphics[width=0.20\textwidth]{./figures/greedy-3.pdf}
-                   &
-  \includegraphics[width=0.20\textwidth]{./figures/greedy-4.pdf}            \\
-  \centering\bf{a} & \centering\bf{b} & \centering\bf{c} & \centering\bf{d}
- \end{tabular}
- \caption{
-  Example of greedy MDS algorithm:
-  The algorithm iteratively adds vertices to the dominating set (black nodes) such that newly added nodes are maximally unconnected (white nodes).
-  Connected nodes are neighbors of the DS (turquoise) or already in the DS.
-  In (a), one finds three maximally unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
-  In the first step $a\to b$, randomly the node (4) is picked.
-  In (b), one has three unconnected choices [(1), (2)] with each adjacent to another unconnected node and one node [(6)] which is only adjacent to neighbors of the DS.
-  After randomly selecting (2) when going from $b \to c$, only one unconnected node is remaining (6).
-  The found solution is a (minimal) dominating set but not a MDS.
-  To find the MDS using this greedy algorithm, the first node choice must be either (2) or (5).
- }
- \label{fig:mds-greedy}
-\end{figure*}
-\fi
-
-%----------------------------------------------------------------------------------------
 \subsubsection{Minimum Dominating Set Qubo}
@@
 %----------------------------------------------------------------------------------------
+\subsection{Notes}
+\label{sec:methods:ilp:notes}
+%----------------------------------------------------------------------------------------
+
+Because quantum annealing is capable of solving quadratic problems, we extend the proposed algorithm to solve integer quadratic optimization problems as well such that
+\begin{align}
+ \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
+\end{align}
+without the introduction of auxiliary qubits.
+
+While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+
+%----------------------------------------------------------------------------------------
 \subsection{Quantum Annealing}
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{Modified annealing schedule}
+\subsubsection{Finite Annealing Schedules}
 \label{sec:methods:annealing-schedule}
 %----------------------------------------------------------------------------------------
-
-A quantum annealer evolves the ground state of an initial Hamiltonian into the ground state of the problem Hamiltonian by adiabatically changing the hardware which implements Hamiltonian.
-Thus, the implemented Hamiltonian is explicitly time dependent
-\begin{equation}
- H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
-\end{equation}
-and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
-The variable $s\in [0, 1]$ is the normalized annealing time and, in physical units, is allowed to vary between 1$\mu s$ to 2$ms$ on DWave.
-
-On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
-In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
 The time dependent coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
@@
 We extrapolate their values by a linear extrapolation, and only employ negative offsets such that this effect only enters at the beginning of the annealing process rather than the end.
-Details of the DWave annealing schedule use to generate Fig.~\ref{fig:anneal_schedule} and further documentation are provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.
-
-\begin{figure}[htb]
- \centering
-  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
-  \caption{
-  Anneal schedules for amplitudes of initial Hamiltonian (top left to bottom right) and final Hamiltonian (bottom left to top right) are displayed for a complete anneal schedule.
-  Different colors represent different offesets: delayed (light to dark), default (black).
- }
- \label{fig:anneal_schedule}
-\end{figure}
-
-The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system, in general, will exhibit more disorder.
-When recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
-\begin{equation}
- H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
-\end{equation}
-we recognize that if $h_i$ is randomly drawn from a Bernoulli distribution, we recover the spin-glass model.
-The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Implementation of annealing offsets}
-\label{sec:methods:annealing-schedule}
-%----------------------------------------------------------------------------------------
-
-For even the smallest graph $NN(2)$, the MDS problem is not native to the chimera graph and must be embedded.
-Following the hypothesis of MBL, we therefore, must look at the values of $h_i$ after embedding.
-The qubits then split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding.
-Further detail is given in Sec.~\ref{sec:methods:minor_embedding} {\color{red} put in methods more details}.
-We study the effects offset the two groups of qubits over a total range between 0\% and 5\% of $c$.
-The results of this study is shown in Fig.~\ref{fig:dwave_offset}.
-
-The results in yellow (green) delays the annealing of qubits subject to stronger (weaker) external fields.
-We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the anneal schedule, in agreement with the MBL hypothesis.
-The phenomena is observed across different problem sizes and hints at the possibility of a generic improvement strategy.
-In the following section, we provide evidence that the improvement is rooted in quantum mechanics, and not other causes such as imperfections in hardware~\cite{} {\color{red} cite dwave's use of annealing offsets}.
-The master equation for quantum annealing is solved subject to the DWave anneal schedule with annealing offsets in order to reproduce the observed phenomenon.
 
@@
 %----------------------------------------------------------------------------------------
-
-If the annealer does not reach thermal equilibrium, for example, strong external magnetic fields freeze in individual qubits, the final solution of the annealing process might not encode the ground state of the final Hamiltonian.
-It is thus essential to prepare the system such that Many-Body Localizations are absent, and thus one must define a measure for MBL.
-
-We note that this measure depends on the choice of partitions, which is, in principle, arbitrary.
-To define a measure for MBL, the choice for partitions should encode the likelihood of frozen qubits.
-Thus a natural choice for partitions are regions of different external magnetic fields.
-For this choice, at the beginning of the anneal, the mutual information will be zero as all spins start orthogonal to the external field, and, in the end, the mutual information will be constant once a final solution is obtained.
-Intermediate values for the mutual information encode the communication probability of different spin alignments.
-
-Intuitively, to find a final state which globally minimizes the energy, we want the system to explore the entire state space.
-That is, we want the system to have ergodicity in order to avoid Many-Body Localizations.
-Thus the annealing process should be sufficiently slow to not introduce potential barriers which freeze in intermediate spin configurations.
-On the other hand, decoherence in the hardware leads to the loss of quantum information.
-It is, therefore, desirable to minimize the effect of relaxation and shorten the annealing process.
-The interplay between these two competing effects can be observed by looking at the non-monotonous time dependency of the probability for reaching the global ground state.
 
@@
 %========================================================================================
-\section{RESULTS}
-\label{sec:results}
-%========================================================================================
-
-%----------------------------------------------------------------------------------------
-\subsection{Finding the Dominating Set with a Quantum Annealer}
-\label{sec:discussion:qa}
-%----------------------------------------------------------------------------------------
-\begin{figure}[b]
-	\centering
-	\begin{tabular}{cc}
-	$G(n):$ &
-	\raisebox{-.4\height}{\includegraphics[width=0.8\columnwidth]{./new_figures/linear_graph.pdf}}
-	\end{tabular}
-	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
-\label{fig:linear}
-\end{figure}
-
-We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.
-This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer.
-Additionally the MDS solution is known analytically, and contains both unique and degenerate solutions.
-In particular, the domination number for $G(n)$ is $\lceil n/3 \rceil$ while the number of MDS solutions for $n$ vertices is
-\begin{align}
-&1 &&\textrm{if} && n\textrm{ mod }3=0,\nonumber \\
-&2\lfloor n/3 \rfloor + 1 && \textrm{if}&& n\textrm{ mod }3=1,\nonumber \\
-&\lfloor n/3 \rfloor + 2 && \textrm{if} && n \textrm{ mod }3 = 2,
-\end{align}
-and gives the probability of randomly guessing the MDS of $G(n)$.
-
-For the following studies, we perform experiments on the \texttt{DW\_2000Q\_6} solver.
-The annealing time is set to 500$\mu$s after performing a study on various annealing times the $G(6)$ graph.
-The black line (offset$=0.0$) in Fig.~\ref{fig:baseline} shows results from the baseline experiment, without modification to the DWave annealing schedule, and observe improvement over random guessing (blue).
-However, We explore one avenue towards improving the experiment results by introducing per-qubit annealing offsets into the time evolution.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/DWave_scaling.pdf}
-	\caption{Baseline result of DWave (black) compared to random guessing (blue).
-The jagged nature of random guessing reflects the degeneracy of the ground state.
-The legend labels the values of annealing offsets employed.
-A positive offsets (yellow) indicates that qubits with large values of $|h_i|$ are annealing with a delayed schedule, while negative offsets (green) delay the schedule of qubits with small values of $h_i$.}
-	\label{fig:baseline}
-\end{figure}
-
-%----------------------------------------------------------------------------------------
-\subsection{Simulation Results}
-%----------------------------------------------------------------------------------------
-
-In order to understand the effects of annealing offsets, we simulate the annealing process for the $G(2)$ graph embedded in chimera topography.
-In order to shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
-The resulting ground state probability as a function of offset measured over 100,000 observations is shown in Fig.~\ref{fig:dwave1us}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
-	\caption{The probability of finding the MDS for $G(2)$ from DWave (orange) and results from simulation with both decoherence terms (blue).
-     The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times.}
-	\label{fig:dwave1us}
-\end{figure}
-
-Simulation results are obtained by solving the von Neumann equation subject to two decoherence models: local damping and full-counting statistics.
-Details of the master equation are given in Sec.~\ref{sec:methods:lindblad}.
-The time dependence of $A(s)$ and $B(s)$ are given by the DWave annealing schedule with offsets in Fig.~\ref{fig:anneal_schedule}.
-The graph $G(2)$ has the interesting feature of having a degenerate ground state depending on whether qubit 0 or 1 is chosen to be the MDS solution.
-This degeneracy is reflected in the experimental result and provides a non-trivial benchmark for our simulation.
-Fig.~\ref{fig:final_state_distribution} show the final state distribution of the three lowest lying state.
-The states $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ are the two degenerate ground states of the embedded Hamiltonian, while $(1, 1, 1, 1, 1)$ is the first excited state which yields an incorrect solution.
-All other states receive negligible probability at the end of annealing.
-The simulation (black) captures main features of the experimental result: 1) significant probability to populate both ground states (rather than populating only one), 2) asymmetry in ground state population due to systematic effects of offset lifting the final state degeneracy spanning approximately the correct range, 3) population of first excited state with systematically lower probability when the strong field is delayed.
-This result can be obtained by tuning three free parameters: the simulation temperature to the order of 10 milliKelvin, and the two coefficients of the two decoherence models at the order of 1 to 10 $ns$.
-Additional insights of the simulation are given in Sec.~\ref{sec:methods:simulation_details}.
-
-The resulting probability of recovering the correct solution as a function of annealing offset is given in Fig.~\ref{fig:dwave1us}.
-We confirm that scaling with respect to offset from the simulation matches what is observed from experiment, and provides evidence suggesting that the improvements are related to quantum mechanics.
-An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets is presented in Sec.~\ref{sec:app:offset}, and further supports this observation.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/final_state_distribution.pdf}
-	\caption{{\color{red}I need to add dwave final state distribution here too.}}
-	\label{fig:final_state_distribution}
-\end{figure}
-
-%----------------------------------------------------------------------------------------
-\subsection{Decoherence and Many-Body Localization}
-%----------------------------------------------------------------------------------------
-
-\ghissue{Finalize results}{19}
-
-%========================================================================================
-\section{DISCUSSION}
-\label{sec:discussion}
-%========================================================================================
-
-\subsection{Final remarks}
-We would like to emphasize that while the annealing offsets are motivated by the MBL hypothesis, and the results also follow those expectations, we do not have definitive proof that MBL plays a crucial role.
-The reason is because observations of MBL inevitably require the study of finite-size scaling, and our current simulation while being extremely thorough and explicit, is exponentially slow to evaluate making evaluations of even $G(3)$ untenable.
-However, the intersection of time-dependent quantum mechanics and emergent phenomena such at MBL is an exciting direction that is pertinent to adiabatic quantum computing.
-
-\ghissue{Conclusion}{20}
-
-%========================================================================================
 \section{DATA AVAILABILITY}

### 2020-09-04 paper/main.tex
Brought simulation into intro

@@
  We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.
+ {\color{red}Furthermore we find evidence for Many-body localization effects ... and find that FC decoherence is more relevant than local decoherence...}
 
@@
 \ghissue{Simulations}{15}
+
+To understand which quantum phenomena are relevant for describing the scaling behavior of the proposed offset study, we simulate the anneal for a small MDS problem.
+This requires solving the von Neumann equations of the time dependent problem.
+To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
+\begin{align}
+ \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}(\rho(t), H(t))
+\end{align}
+where $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
+In this work, we consider two types of decoherence models: full counting statistics and local damping.
+The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
+The local damping term models the decoherence of each qubit independently.
 

### 2020-09-04 paper/main.tex
comments

@@
  This work presents the formalism of how to map ILP problems to the annealing architectures.
- It illustrates the effects of decorrelation and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
- We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decorrelation--which is qualitatively confirmed by simulations.
+ It illustrates the effects of decoherence and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
+ We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decoherence--which is qualitatively confirmed by simulations.
  {\color{red}Furthermore we find evidence for Many-body localization effects ... and find that FC decoherence is more relevant than local decoherence...}
@@
 where the natural numbers $\mathbbm{N}$ include zero, $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
+{\color{red} I don't actually understand this sentence.}
 
@@
 
-An important ILP is the Minimum Dominating Set problem which is represantivly considered in this work.
-For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, and a dominating set $D$ is a specific subset of vertices $D \subseteq V$.
-In particluar $D$ is a dominating set if all vertices in $V$ but not in $D$ are adjacent to at least one vertex in $D$.
+An important ILP is the Minimum Dominating Set problem which is represantivly {\color{red} this is a typo, but i can't guess what word you're trying to use also...} considered in this work.
+For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, a dominating set $D$ is a specific subset of vertices $D \subseteq V$.
+In particular $D$ is a dominating set if all vertices in $V$ but not in $D$ are adjacent to at least one vertex in $D$.
 This is equivalent to requiring the set of nearest-neighbor vertices of $D$ (exclusive) and $D$ cover all vertices $N(D) \cup D = V$ (an example is given by Fig.~\ref{fig:dominating_sets}a).
@@
 As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values.
+{\color{blue} In general, $s$ can be relaxed to span a fixed-point decimal number following Ref.~\cite{Chang:2018uoc} if the constraint equation is defined by non-integer coefficients.}
 
@@
 If the annealer does not reach thermal equilibrium, for example, strong external magnetic fields freeze in individual qubits, the final solution of the annealing process might not encode the ground state of the final Hamiltonian.
+{\color{red} @CC is this statement actually correct?}
 It is thus essential to prepare the system such that Many-Body Localizations are absent, and thus one must define a measure for MBL.
 
+{\color{blue} These two paragraphs need to be changed (softened).
+The mutual information does not paint the story we need.
+Or more specifically, the MI we plot is not useful yet because we have no finite size scaling.
+In general, we do not have a good observable for MBL without finite size scaling.
+This is future work.
+The problem size is too small also to really see this effect.
+The best we can say is that we have this MBL hypothesis, and we set offsets with respect to that.
+So I think the paragraph above, and below should be changed to a short summary of Anderson Localization, and how our system is like a spin-glass, so we follow the AL logic.
+We then observe that the simulation agrees with DWave, and in the absense of unknown hardware effects like qubits freezing due to hardware limitations (this is a hardware problem actually, not a QM problem), that this scaling holds.
+So DWave claims offset is good to cure ``freezing'' problems cuz of hardware issues.
+We can claim this is more than hardware, but rooted in QM.
+This is the strongest statement we can make without getting skewered.}
+{\color{red}
 We note that this measure depends on the choice of partitions, which is, in principle, arbitrary.
@@
 The interplay between these two competing effects can be observed by looking at the non-monotonous time dependency of the probability for reaching the global ground state.
+}
 
@@
 
- and present an example implementation in case of the Minimal Dominating Set problem (\ref{sec:methods:mds}).
-We review the annealing process on the utilized hardware (\ref{sec:methods:annealing}) and describe the computational framework which we used to simulate the annealing process (\ref{sec:methods:simulation}).
-Section \ref{sec:results} summarizes our findings and presents...
-We conclude this report in \ref{sec:conclusion}.
-All algorithms used and data obtained are publicly available (\ref{sec:open-source})
+We first present the QUBO mapping for ILP (\ref{sec:results:qa1}), and demonstrate the methodology on an example implementation in case of the Minimal Dominating Set problem (\ref{sec:results:qa}) on the DWave quantum annealer.
+Results from quantum annealing are compared and discussed in contrast to simulations (\ref{sec:results:simulation}).
+All algorithms used and data obtained are publicly available (\ref{sec:open-source}).
 
@@
 \subsection{ILP QUBO}
-\label{sec:results:qa}
+\label{sec:results:qa1}
 %----------------------------------------------------------------------------------------
+{\color{red} This section and the methods section reads very disjoint. You also don't define everything here and then Reference the Methods for more information.}
 
@@
 The qubits then split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| + \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding.
-Further detail is given in Sec.~\ref{sec:methods:minor_embedding} {\color{red} put in methods more details}.
+Further detail is given in Sec.~\ref{sec:methods:minor_embedding}.
 We study the effects offset the two groups of qubits over a total range between 0\% and 5\% of $c$.
-The results of this study is shown in Fig.~\ref{fig:dwave_offset}.
+The results of this study is shown in Fig.~\ref{fig:baseline}.
 
@@
 %----------------------------------------------------------------------------------------
-
+\label{sec:results:simulation}
 In order to understand the effects of annealing offsets, we simulate the annealing process for the $G(2)$ graph embedded in chimera topography.
@@
 
-%========================================================================================
-\section{DISCUSSION}
-\label{sec:discussion}
-%========================================================================================
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Comment on ILP QUBO penalty term}
-\label{sec:methods:ilp-qubo-comments}
-%----------------------------------------------------------------------------------------
-
-The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
-Thus some knowledge of the problem is required.
-In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
-After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
-Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
-
 \subsection{Final remarks}
+\label{sec:results:final}
 We would like to emphasize that while the annealing offsets are motivated by the MBL hypothesis, and the results also follow those expectations, we do not have definitive proof that MBL plays a crucial role.
@@
 %----------------------------------------------------------------------------------------
-\subsection{Notes}
+\subsubsection{Comment on ILP QUBO penalty term}
+\label{sec:methods:ilp-qubo-comments}
+%----------------------------------------------------------------------------------------
+
+The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
+Thus some knowledge of the problem is required.
+In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
+After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
+Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Notes}
 \label{sec:methods:ilp:notes}
@@
 While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
-
-%----------------------------------------------------------------------------------------
-\subsection{Quantum Annealing}
-\label{sec:methods:annealing}
-%----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Finite Annealing Schedules}
-\label{sec:methods:annealing-schedule}
-%----------------------------------------------------------------------------------------
-The time dependent coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
-The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
-As a result, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
-Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
-We extrapolate their values by a linear extrapolation, and only employ negative offsets such that this effect only enters at the beginning of the annealing process rather than the end.
 
@@
 %----------------------------------------------------------------------------------------
+\subsubsection{Finite Annealing Schedules}
+\label{sec:methods:annealing-schedule}
+%----------------------------------------------------------------------------------------
+The time dependent coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
+The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
+As a result, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
+Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
+We extrapolate their values by a linear extrapolation, and only employ negative offsets such that this effect only enters at the beginning of the annealing process rather than the end.
+
+%----------------------------------------------------------------------------------------
 \subsubsection{Decoherence Time}
@@
 
+FC gives correct distribution.
+Local the simplest relaxation mode.
+Maybe run a plot showing we turn of local, and see same scaling.
+So offset is not directly tackling only this.
+Can show that in Fig.
+7.
+
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
+{\color{red} I think we discussed enough about this in the main text. There's no need to talk about this here.}
 

### 2020-09-04 paper/figures/clean_plots.py

@@ -722,7 +722,7 @@ def getlevelspacing(offset=0.05):
     sim = Sim()
     query, sol, tdse = sim.get_data(offset)
     ngrid = 1000
-    fockn = tdse.Focksize
+    fockn = 3 #tdse.Focksize
     timegrid = np.linspace(0, 1, ngrid)
     r = np.zeros(ngrid)
     for i in range(ngrid):
@@ -745,8 +745,8 @@ def plot_levelspacing():
     sns.heatmap(all_levels, yticklabels=offset)
     # ax.legend()
     # plt.yscale("log")
-    # plt.savefig("../new_figures/levelspacing.pdf", transparent=True)
-    plt.show()
+    plt.savefig("../new_figures/levelspacing.pdf", transparent=True)
+    #plt.show()
 
 
 """
@@ -954,12 +954,12 @@ if __name__ == "__main__":
     For TDSE simulation
     """
     #plot_tdse()
-    plot_tdse_extended()
+    #plot_tdse_extended()
     # plot_distribution()
     #plot_annealcurve()
     # plot_timedepprob()
     # plot_hybridization()
     # plot_mi()
     # plot_timedepsz()
-    # plot_levelspacing()
+    plot_levelspacing()
     #plot_spectrum()

### 2020-09-04 paper/main.tex
edits

@@
   & \sum_i A_{ai}x_i +b_a \leq 0 \,, \\
-  & x_i  \in \mathbbm{N}\, ,
+  & x_i  \in \mathbbm{Z} \geq 0\, ,
 \end{align}
-where the natural numbers $\mathbbm{N}$ include zero, $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
-{\color{red} I don't actually understand this sentence.}
+where $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.
 
@@
 
-For general graphs, existing "classical" algorithms either find MDS solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or approximate solutions in polynomial time.
+For general graphs, existing algorithms on classical computers find MDS solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or approximate solutions in polynomial time.
 For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
@@
   & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
-  & s_a \in \mathbb{N},                \\
-  & x_i \in \mathbb{N}.
+  & s_a \geq 0,                \\
+  & x_i \in \mathbb{Z} \geq 0.
 \end{align}
-As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values.
-{\color{blue} In general, $s$ can be relaxed to span a fixed-point decimal number following Ref.~\cite{Chang:2018uoc} if the constraint equation is defined by non-integer coefficients.}
 
@@
 \begin{equation}
- H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
+ H(t) = A(t) H^{\textrm{init}} + B(t) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
 \end{equation}
 and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ encodes the problem to be solved.
-The variable $s\in [0, 1]$ is the normalized annealing time and, in physical units, is allowed to vary between 1$\mu s$ to 2$ms$ on DWave.
 
-On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
-In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
-Details of the DWave annealing schedule use to generate Fig.~\ref{fig:anneal_schedule} and further documentation are provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.
-
-\begin{figure}[htb]
- \centering
-  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
-  \caption{
-  Anneal schedules for amplitudes of initial Hamiltonian (top left to bottom right) and final Hamiltonian (bottom left to top right) are displayed for a complete anneal schedule.
-  Different colors represent different offesets: delayed (light to dark), default (black).
- }
- \label{fig:anneal_schedule}
-\end{figure}
-
-If the annealer does not reach thermal equilibrium, for example, strong external magnetic fields freeze in individual qubits, the final solution of the annealing process might not encode the ground state of the final Hamiltonian.
-{\color{red} @CC is this statement actually correct?}
-It is thus essential to prepare the system such that Many-Body Localizations are absent, and thus one must define a measure for MBL.
+{\color{red} If the annealer does not reach thermal equilibrium, for example, strong external magnetic fields freeze in individual qubits, the final solution of the annealing process might not encode the ground state of the final Hamiltonian.
+It is thus essential to prepare the system such that Many-Body Localizations are absent, and thus one must define a measure for MBL. }
 
@@
 }
-
-To improve annealing results we propose a qubitwise offsets associated with exeternal field alignments.
-The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system, in general, will exhibit more disorder.
-When recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
+{\color{green} We further improve the performance of the quantum annealer by utilizing annealing offsets which effectively delays the annealing schedule on a per-qubit basis.
+The improvement strategy is motivated by recognizing that a general QUBO exhibits properties of a spin-glass model.
+Explicilty, the Ising representation of the the problem Hamiltonian has the form
 \begin{equation}
@@
 \end{equation}
-we recognize that if $h_i$ is randomly drawn from a Bernoulli distribution, we recover the spin-glass model.
-The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.
-
+where in the case that $h_i$ is randomly drawn from a Bernoulli distribution, we recover the spin-glass model.
+The spin-glass model enters its glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.
+In the case of quantum annealing, when an algorithm is mapped to its QUBO representation, the values of $h_i$ will often times take on various values, mimicking spin-glass like behavior.
+As a result, the system of qubits can be interpreted to posses more disordered over time, and guides our choice of annealing offsets.
+}
 \ghissue{Simulations}{15}
@@
 We confirm that scaling with respect to offset from the simulation matches what is observed from experiment, and provides evidence suggesting that the improvements are related to quantum mechanics.
-An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets is presented in Sec.~\ref{sec:app:offset}, and further supports this observation.
+An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets and effects of local damping are presented in Sec.~\ref{sec:app:offset}, and further supports this observation.
 
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{Notes}
+\subsubsection{{\color{green} Integer quadratic optimization}}
 \label{sec:methods:ilp:notes}
@@
 While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Minor Embedding}
+\label{sec:methods:minor_embedding}
+%----------------------------------------------------------------------------------------
+Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
+As a result, details of the embedding are important.
+We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the DWave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module.
+The same embedding is used for all DWave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
+Additionally, solving the same graph as a function of offset on the exact same qubits removes (or at least keeps consistent) the systematic effects due to solving a problem on different physical qubits.
+We note that comparisons between different graphs in Fig.~\ref{fig:baseline} are subject to this uncontrolled systematic.
+
+After embedding the QUBO for $G(2)$ requires 5 qubits (an increase from 4), where by construction, qubits 0 and 3 form the qubit chain.
+We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by DWave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the minimum dominating set.
+
+The resulting Ising Hamiltonian has external field equal to $h = (2.75, 1.5, -1.0, -1.25, -1.0)$.
+Following the offset strategy described in Sec.~\ref{sec:discussion:offsets}, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
+This imbalance in the two groups may perhaps explain the reason why effects of delaying the weaker fields are more pronounced, since delaying the strong fields only differs from the baseline by a single qubit.
 
@@
 
+{\color{green}For the simulation results presented, we set the temperature to 22.5 milliKelvin. The coherence time for local decoherence is set to 15$ns$, and 1$ns$ for full-counting statistics.
+}
 %----------------------------------------------------------------------------------------
-\subsubsection{Finite Annealing Schedules}
+\subsubsection{Annealing schedule and offsets}
 \label{sec:methods:annealing-schedule}
 %----------------------------------------------------------------------------------------
-The time dependent coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
+{\color{red} I moved the details of annealing schedules here. This doesn't belong in the main text. This is way too detailed.}
+In this section, we discuss the details of the annealing schedule with respect to the dimensionless normalized time $s$.
+On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
+In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
+Details of the DWave annealing schedule use to generate Fig.~\ref{fig:anneal_schedule} and further documentation are provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.
+
+\begin{figure}[htb]
+ \centering
+  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
+  \caption{
+  Anneal schedules for amplitudes of initial Hamiltonian (top left to bottom right) and final Hamiltonian (bottom left to top right) are displayed for a complete anneal schedule.
+  Different colors represent different offesets: delayed (light to dark), default (black).
+ }
+ \label{fig:anneal_schedule}
+\end{figure}
+
+The coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
 The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
@@
 We extrapolate their values by a linear extrapolation, and only employ negative offsets such that this effect only enters at the beginning of the annealing process rather than the end.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Decoherence Time}
-\label{sec:methods:deco}
-%----------------------------------------------------------------------------------------
-
-\ghissue{Decoherence section}{16}
-
-FC gives correct distribution.
-Local the simplest relaxation mode.
-Maybe run a plot showing we turn of local, and see same scaling.
-So offset is not directly tackling only this.
-Can show that in Fig.
-7.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Many-Body Localization}
-\label{sec:methods:mbl}
-%----------------------------------------------------------------------------------------
-{\color{red} I think we discussed enough about this in the main text. There's no need to talk about this here.}
-
-%----------------------------------------------------------------------------------------
-
-\subsubsection{Systematic effects of annealing offsets}
-\label{sec:app:offset}
-%----------------------------------------------------------------------------------------
 
@@
 \end{figure}
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Minor Embedding}
-\label{sec:methods:minor_embedding}
-%----------------------------------------------------------------------------------------
-Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
-As a result, details of the embedding are important.
-We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the DWave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module.
-The same embedding is used for all DWave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
-Additionally, solving the same graph as a function of offset on the exact same qubits removes (or at least keeps consistent) the systematic effects due to solving a problem on different physical qubits.
-We note that comparisons between different graphs in Fig.~\ref{fig:baseline} are subject to this uncontrolled systematic.
-
-After embedding the QUBO for $G(2)$ requires 5 qubits (an increase from 4), where by construction, qubits 0 and 3 form the qubit chain.
-We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by DWave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the minimum dominating set.
-
-The resulting Ising Hamiltonian has external field equal to $h = (2.75, 1.5, -1.0, -1.25, -1.0)$.
-Following the offset strategy described in Sec.~\ref{sec:discussion:offsets}, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
-This imbalance in the two groups may perhaps explain the reason why effects of delaying the weaker fields are more pronounced, since delaying the strong fields only differs from the baseline by a single qubit.
 
@@
 
+{\color{red}
+%----------------------------------------------------------------------------------------
+\subsubsection{Decoherence Time}
+\label{sec:methods:deco}
+%----------------------------------------------------------------------------------------
+
+\ghissue{Decoherence section}{16}
+I think the following two sections can be merged / removed.
+
+I talk about this in the section above.
+
+The AL discussion is a bit too textbooky for a paper I think.
+
+FC gives correct distribution.
+Local the simplest relaxation mode.
+Maybe run a plot showing we turn of local, and see same scaling.
+So offset is not directly tackling only this.
+Can show that in Fig.
+7.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Anderson Localization}
+\label{sec:methods:mbl}
+%----------------------------------------------------------------------------------------
+{\color{green} If we want, we can write a short summary of Anderson Localization. Anderson Hamiltonian -> spin representation. This requires some more reading though I think.}
+%----------------------------------------------------------------------------------------
+
+}
 %========================================================================================

### 2020-09-10 paper/main.tex
Added more context to first result section and simplified qubo notation

@@
 \begin{align}
+  \label{eq:ilp:slack}
   & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
-  & s_a \geq 0,                \\
-  & x_i \in \mathbb{Z} \geq 0.
+  & x_i, s_a \in \mathbb{Z} \geq 0.
 \end{align}
+While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+Furthermore, this formalism can be generalized to constrained quadratic optimizations \ref{sec:methods:ilp:quadratic}.
 
@@
 %----------------------------------------------------------------------------------------
-{\color{red} This section and the methods section reads very disjoint. You also don't define everything here and then Reference the Methods for more information.}
+We map the integer variables $\vec z = \vec x, \vec s$ appearing in eq.~\eqref{eq:ilp:slack} to qubits under the following transformation~\cite{Chang:2018uoc}
+\begin{align}
+ z_i = & \sum_{r=0}^{R_i-1} 2^r \psi_{ri}
+ \label{eq:int_to_bin}
+\end{align}
+where $\psi_{ri} \in \{0, 1\}$.
+The number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$ (see also section \ref{sec:methods:bit-basis}).
+This transformation can be expressed as a rectangular matrix $T_z$ such that
+\begin{equation}
+    \begin{pmatrix}
+        \vec x \\ \vec s
+    \end{pmatrix}
+    =
+    \begin{pmatrix}
+        T_x & 0 \\ 0 & T_s
+    \end{pmatrix}
+    \begin{pmatrix}
+        \vec \Psi_x \\ \vec \Psi_s
+    \end{pmatrix}
+    =
+    T
+    \vec \Psi
+\end{equation}
 
-The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
+The integer linear (and quadratic equivalently, see section \ref{sec:methods:ilp:quadratic}) optimization problem can be mapped to a minimization of the quadratic objective function
 \begin{align}
- \chi^2                         & = \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
- \nonumber                                                                                                                             \\ \label{eq:qubo-min}
-                                & \qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],   \\
- \vec x_0                       & =  T^x \vec \Psi^x_0 \, ,
- \\
- (\vec \Psi^x_0, \vec \Psi^s_0) & = \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,,                                                 &
+ \chi^2(\vec \Psi)
+ &=
+ \vec c^T T_x \vec \Psi_x + p \left\| A T_s \vec \Psi_x + T_s \vec \Psi_s + \vec b \right\|^2
 \end{align}
-where $p$ is an external parameter representing the strength of the penalty when violating constraints and $T^{x,z}$ is a matrix mapping qubits to integers (see also section \ref{sec:methods:bit-basis}).
-The objective function can be represented as a QUBO Hamiltonian
+where $p$ is an external parameter representing the strength of the penalty when violating constraints.
+This parameter needs to be sufficiently large, e.g., $p \geq \vec c \cdot \vec x$, to ensure the constraints are indeed fulfilled\footnote{Depending on the problem, $p$ can be smaller as well.
+For example, in the case of the MDS, $p\geq 1$ suffices.}.
+The objective function $\chi^2$ can be represented as a QUBO Hamiltonian
 \begin{align}
- E =    &
- \begin{pmatrix}
-  \Psi^x & \Psi^s
- \end{pmatrix}
+ \chi^2(\vec \Psi) =    &
+ \vec \Psi^T
  \begin{pmatrix}
@@
  \end{pmatrix}
- \begin{pmatrix}
-  \Psi^x \\ \Psi^s
- \end{pmatrix} + pb^2, \\
- \equiv & \Psi^T Q \Psi + C,
+ \vec \Psi + p\left \| \vec b \right\|^2, \\
+ \equiv &  \vec \Psi^T Q  \vec \Psi + C,
  \label{eq:matrix_form}
@@
 where
+{\small
 \begin{align}
- Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x \nonumber \\
-          & + \mathrm{Diag}_{\psi^x}(c) T^x,                                                                    \\
- Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,                                                                     \\
- Q_{ss} = & p\left[ {T^{s}}^T T^s + \mathrm{Diag}_{\psi^s}\left( {T^{s}}^T b + b^T T^s\right) \right].
-\end{align}
-The function $\mathrm{Diag}_{z}(v)$ embeds a vector $v$ into a diagonal matrix in subspace $z$, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.
+ \label{eq:qubo:components}
+ Q_{xx} = & p {T_{x}}^T \left[ A^T A + \mathrm{diag} \left(A^T \vec b + \vec b^T A\right) \right] T_x + \mathrm{diag}(\vec c) T_x,                                                                    \\
+ Q_{xs} = & Q_{sx}^T = p {T_{x}}^T A^T T_s,                                                                     \\
+ Q_{ss} = & p\left[ {T_{s}}^T T_s + \mathrm{diag}\left( {T_{s}}^T \vec b + \vec b^T T_s\right) \right].
+\end{align}}
+The function $\mathrm{diag}(\vec v)$ transforms a vector $\vec v$ into a diagonal matrix, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.
 
-A solution to the ILP is found by obtaining the qubit vector $\psi$ which minimizes $E$.
-The integer solution to the original ILP is computed by $\vec x = T^x \vec \psi^x$ and the original energy is computed by shifting the annealer extracted energy by $pb^2$.
-The slack components of this vector $\psi^s$ can be utilized to check if the contraints are indeed fulfilled.
+A solution to the ILP is found by identifying the qubit vector $\vec \Psi^{(0)}$ which minimizes $ \chi^2$.
+The integer solution to the original ILP is computed by $\vec x^{(0)} = T_x \vec \Psi_x^{(0)}$ and the original solution to the problem is computed by shifting the annealer extracted energy $E \equiv  \chi^2(\vec \Psi^{(0)}) $ by $p \left \| \vec b \right\|^2$.
+The slack components of this vector $\vec \Psi_s$ can be utilized to check if the contraints are indeed fulfilled.
 
@@
 \begin{align}
- f(x) =                    & \min\left(\sum_{\nu \in V} \psi^x_{\nu}\right),                    \\
- \textrm{subject to} \quad & \psi^x_{\nu} + \sum_{\mu \in \mathit{N}(\nu)} \psi^x_{\mu} \geq 1, \\
-                           & \psi^x_{\nu} \in \{0, 1\}
+ f(\vec x) = & \min\left(\sum_{v \in V} x_v\right),                    \\
 \end{align}
-where the dimension of the dependent variable $x$ is the number of vertices $\overline{\overline{V}}$.
-The problem minimizes the number of vertices in $D$ with a binary variable $\psi^x$ encoded by a single qubit, subject to the constraint that at least one vertex in $\mathit{N}(\nu)$ is in $D$.
-For each vertex in $V$ we introduce slack variables $s_{\nu} = T^s_{\nu \alpha} \psi^s_{\alpha}$ to encode the inequality constraint such that
+subject to
 \begin{align}
- f(x) =                    & \min(\sum_{\nu\in V} \psi^x_{\nu}),                                                 \\
- \textrm{subject to} \quad & \psi^x_{\nu} + J_{\nu \mu} \psi^x_{\mu}- T^s_{\nu \alpha} \psi^s_{\alpha}  - 1 = 0, \\
-                           & \psi_{\nu} \in \{0, 1\},                                                            \\
-                           & 0 \leq s_{\nu} \leq |\mathrm{N}(\nu)|                                               \\
-                           & s_{\nu} \in \mathbb{Z},
+ & x_v + \sum_{j \in \mathcal{N}(v)} x_j \geq 1, \\
+ & x_v \in \{0, 1\}
 \end{align}
-where the nearest-neighbor sum is expressed by $J$ (symmetric and zero diagonal), the adjacency matrix for $G$.
-The algorithm uses $N_q = \overline{\overline{V}} + \sum_{\nu \in V} \log_2 \mathit(N(\nu))$ qubits---$\overline{\overline{V}}$ qubits to encode the vertices and another $\sum_{\nu \in V} \log_2 \mathit(N(\nu))$ qubits to embed the slack variables.
-Therefore, the embedding at worse scales with $\overline{\overline{V}} \log_2 |\overline{\overline{V}}|$ qubits for fully connected graphs.
+where $\mathcal{N}(v)}$ represents the set of all direct neighbors of vertex $v$ and the dimension of the dependent variable $x$ is the number of vertices $n_V \equiv \overline{\overline{V}}$.
+The problem minimizes the number of vertices in $D$ with a binary variable $\vec x = \vec \Psi_x$ encoded by single qubit, subject to the constraint that at least one vertex in $\mathcal{N}(\nu)$ is in $D$.
+For each vertex in $V$ we introduce slack variables
+\begin{equation}
+    \vec s \in \left\{ \mathbb{Z}^{n_V} \, \middle| \, 0 \leq s_{v} \leq |\mathcal{N}(v)| \quad \forall v\in V \right\} \, ,
+\end{equation}
+which is related to the qubit vector $\vec \Psi_s$ by $\vec s = T_s \vec \Psi_s$, to encode the inequality constraint such that
+\begin{align}
+ f(\vec \Psi_x)
+ =
+ & \min\left(\vec 1 \cdot \vec \Psi_x \right) \, ,
+\end{align}
+subject to
+\begin{align}
+ &
+ \vec \Psi_x + J \vec \Psi_x - T_s \Psi_s  - \vec 1 = 0\,,
+ \\
+ &
+ (\vec \Psi_s)_\nu \in \{ 0, 1\}
+\end{align}
+where the nearest-neighbor sum is expressed by $J$ (zero diagonal and symmetric for non-directional graphs), the adjacency matrix for $G$.
+The algorithm uses
+\begin{equation}
+    N_q = \overline{\overline{V}} + \sum_{\nu \in V} \log_2 \mathit(N(\nu))
+\end{equation}
+qubits to encode the vertices and to embed the slack variables.
+Therefore, the embedding at worse scales with $n_V \log_2 n_V$ qubits for fully connected graphs.
 
@@
   \begin{align}
-   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{Diag}_{\psi^x}(|J|) - \mathbbm{1} \right] \,, \\
-   Q_{sx} & = - p(\mathbbm{1}+J^T)T^s\,,                                                                     \\
-   Q_{ss} & = p\left[{T^s}^T T^s + 2\mathrm{Diag}_{\psi^s}(|T^s|)\right]\,,                                  \\
+   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{diag}(|J|) - \mathbbm{1} \right] \,, \\
+   Q_{sx} & = - p(\mathbbm{1}+J^T)T_s\,,                                                                     \\
+   Q_{ss} & = p\left[{T_s}^T T_s + 2\mathrm{diag}(|T_s|)\right]\,,                                  \\
    C      & =  p \overline{\overline{V}}\,,
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{{\color{green} Integer quadratic optimization}}
-\label{sec:methods:ilp:notes}
+\subsubsection{Integer quadratic optimization}
+\label{sec:methods:ilp:quadratic}
 %----------------------------------------------------------------------------------------
@@
 
-While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+In this case the $Q_{xx}$ component of the Qubo, eq.~\eqref{eq:qubo:components} obtains a new term
+\begin{equation}
+    Q_{xx} \to Q_{xx} + T_x^T d T_x \, .
+\end{equation}
 

### 2020-09-10 paper/main.tex
Fixed typo

@@
 \end{align}
-where $\mathcal{N}(v)}$ represents the set of all direct neighbors of vertex $v$ and the dimension of the dependent variable $x$ is the number of vertices $n_V \equiv \overline{\overline{V}}$.
+where $\mathcal{N}(v)$ represents the set of all direct neighbors of vertex $v$ and the dimension of the dependent variable $x$ is the number of vertices $n_V \equiv \overline{\overline{V}}$.
 The problem minimizes the number of vertices in $D$ with a binary variable $\vec x = \vec \Psi_x$ encoded by single qubit, subject to the constraint that at least one vertex in $\mathcal{N}(\nu)$ is in $D$.
@@
 \begin{equation}
-    N_q = \overline{\overline{V}} + \sum_{\nu \in V} \log_2 \mathit(N(\nu))
+    N_q = \overline{\overline{V}} + \sum_{v \in V} \log_2 \mathcal{N}(v)
 \end{equation}

### 2020-09-10 paper/main.tex
Updated intro / merged jsons edits.
Also removed a few issues which seemed answered by the intro.

@@
 
-Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints
+Integer Linear Programming (ILP) is an integer optimization problem subject to inequality constraints
 \begin{align}
@@
 ILP is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}.
-In general, however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
+In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
 Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
@@
 
-An important ILP is the Minimum Dominating Set problem which is represantivly {\color{red} this is a typo, but i can't guess what word you're trying to use also...} considered in this work.
+An important ILP is the Minimum Dominating Set problem, which is representatively considered in this work.
 For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, a dominating set $D$ is a specific subset of vertices $D \subseteq V$.
-In particular $D$ is a dominating set if all vertices in $V$ but not in $D$ are adjacent to at least one vertex in $D$.
+In particular, $D$ is a dominating set if all vertices in $V$ but not in $D$ are adjacent to at least one vertex in $D$.
 This is equivalent to requiring the set of nearest-neighbor vertices of $D$ (exclusive) and $D$ cover all vertices $N(D) \cup D = V$ (an example is given by Fig.~\ref{fig:dominating_sets}a).
@@
 The domination number of $D$ is given by the cardinality of $|D| \equiv \overline{\overline{D}}$.
-The minimum dominating set (MDS) is defined by $D$ with the smallest domination number.
+The Minimum Dominating Set (MDS) is defined by $D$ with the smallest domination number.
 Fig.~\ref{fig:dominating_sets}c shows an example of the minimum dominating set of $G(V, E)$ and is different from the minimal dominating set.
 We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
-As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a problem that is well studied for quantum annealers~\cite{}.
+As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a well-studied problem for quantum annealers~\cite{}.
 
@@
 For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
-Thus one is guaranteed to find a dominating set but not necessarily a MDS.
+Thus one is guaranteed to find a dominating set but not necessarily an MDS.
 
-Due to the importance and difficulty, in this work, we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.
+Due to the importance and difficulty in this work, we present a method to obtain optimal solutions to ILP by employing quantum annealing methods.
 
@@
 Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems~\cite{2018Glover}.
+
+A quantum annealer evolves the ground state of an initial Hamiltonian into the problems Hamiltonian's ground state by adiabatically changing the hardware that implements Hamiltonian.
+Thus, the implemented Hamiltonian is explicitly time dependent
+\begin{equation}
+ H(t) = A(t) H^{\textrm{init}} + B(t) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
+\end{equation}
+and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ encodes the problem to be solved.
+The Ising representation of the the problem Hamiltonian has the form
+\begin{equation}
+ H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i \, .
+\end{equation}
+Intuitively, to find a final state that globally minimizes the energy, the annealer needs to explore the entire state.
+If the annealer does not reach thermal equilibrium, the annealing process's final solution might not encode the final Hamiltonian's ground state.
+Thus the annealing process should be sufficiently slow not to introduce potential barriers that freeze in intermediate spin configurations.
+On the other hand, decoherence in the hardware leads to the loss of quantum information.
+It is, therefore, desirable to minimize the effect of relaxation and shorten the annealing process.
+
+While such spin-freezing effects may be related to systematic hardware constraints, they are hypothetically related to quantum localization phenomena.
+Recognizing that a general QUBO exhibits a spin-glass model's properties--if the were $h_i$ coefficients are randomly drawn from a Bernoulli distribution--one may expect spin-localization behavior influencing the outcome of the anneal.
+In the case of quantum annealing, when an algorithm is mapped to its QUBO representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
+Explicitly, the spin-glass model enters its glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization effects, the many-body analog of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.
 
@@
 
-\ghissue{Decoherence \& Localization}{14}
+We further improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis.
+The improvement strategy is motivated by the MBL hypothesis.
+That is, we want the system to have ergodicity in order to avoid Many-Body Localizations.
+We prepare the system such that Many-Body Localizations are minimized by partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.
 
-A quantum annealer evolves the ground state of an initial Hamiltonian into the ground state of the problem Hamiltonian by adiabatically changing the hardware which implements Hamiltonian.
-Thus, the implemented Hamiltonian is explicitly time dependent
-\begin{equation}
- H(t) = A(t) H^{\textrm{init}} + B(t) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
-\end{equation}
-and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ encodes the problem to be solved.
-
-{\color{red} If the annealer does not reach thermal equilibrium, for example, strong external magnetic fields freeze in individual qubits, the final solution of the annealing process might not encode the ground state of the final Hamiltonian.
-It is thus essential to prepare the system such that Many-Body Localizations are absent, and thus one must define a measure for MBL. }
-
-{\color{blue} These two paragraphs need to be changed (softened).
-The mutual information does not paint the story we need.
-Or more specifically, the MI we plot is not useful yet because we have no finite size scaling.
-In general, we do not have a good observable for MBL without finite size scaling.
-This is future work.
-The problem size is too small also to really see this effect.
-The best we can say is that we have this MBL hypothesis, and we set offsets with respect to that.
-So I think the paragraph above, and below should be changed to a short summary of Anderson Localization, and how our system is like a spin-glass, so we follow the AL logic.
-We then observe that the simulation agrees with DWave, and in the absense of unknown hardware effects like qubits freezing due to hardware limitations (this is a hardware problem actually, not a QM problem), that this scaling holds.
-So DWave claims offset is good to cure ``freezing'' problems cuz of hardware issues.
-We can claim this is more than hardware, but rooted in QM.
-This is the strongest statement we can make without getting skewered.}
-{\color{red}
-We note that this measure depends on the choice of partitions, which is, in principle, arbitrary.
-To define a measure for MBL, the choice for partitions should encode the likelihood of frozen qubits.
-Thus a natural choice for partitions are regions of different external magnetic fields.
-For this choice, at the beginning of the anneal, the mutual information will be zero as all spins start orthogonal to the external field, and, in the end, the mutual information will be constant once a final solution is obtained.
-Intermediate values for the mutual information encode the communication probability of different spin alignments.
-
-Intuitively, to find a final state which globally minimizes the energy, we want the system to explore the entire state space.
-That is, we want the system to have ergodicity in order to avoid Many-Body Localizations.
-Thus the annealing process should be sufficiently slow to not introduce potential barriers which freeze in intermediate spin configurations.
-On the other hand, decoherence in the hardware leads to the loss of quantum information.
-It is, therefore, desirable to minimize the effect of relaxation and shorten the annealing process.
-The interplay between these two competing effects can be observed by looking at the non-monotonous time dependency of the probability for reaching the global ground state.
-}
-{\color{green} We further improve the performance of the quantum annealer by utilizing annealing offsets which effectively delays the annealing schedule on a per-qubit basis.
-The improvement strategy is motivated by recognizing that a general QUBO exhibits properties of a spin-glass model.
-Explicilty, the Ising representation of the the problem Hamiltonian has the form
-\begin{equation}
- H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
-\end{equation}
-where in the case that $h_i$ is randomly drawn from a Bernoulli distribution, we recover the spin-glass model.
-The spin-glass model enters its glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.
-In the case of quantum annealing, when an algorithm is mapped to its QUBO representation, the values of $h_i$ will often times take on various values, mimicking spin-glass like behavior.
-As a result, the system of qubits can be interpreted to posses more disordered over time, and guides our choice of annealing offsets.
-}
-\ghissue{Simulations}{15}
-
-To understand which quantum phenomena are relevant for describing the scaling behavior of the proposed offset study, we simulate the anneal for a small MDS problem.
-This requires solving the von Neumann equations of the time dependent problem.
+To understand which phenomena are relevant for describing the proposed offset study's scaling behavior, whether they are rooted in the quantum nature or related to hardware constraints, we simulate the anneal for a small MDS problem.
+This simulation requires solving the von Neumann equations of the time-dependent problem.
 To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
@@
 
-We first present the QUBO mapping for ILP (\ref{sec:results:qa1}), and demonstrate the methodology on an example implementation in case of the Minimal Dominating Set problem (\ref{sec:results:qa}) on the DWave quantum annealer.
-Results from quantum annealing are compared and discussed in contrast to simulations (\ref{sec:results:simulation}).
-All algorithms used and data obtained are publicly available (\ref{sec:open-source}).
-
 %========================================================================================
@@
 %========================================================================================
+
+We first present the QUBO mapping for ILP (\ref{sec:results:qa1}), and demonstrate the methodology on an example implementation in case of the Minimal Dominating Set problem (\ref{sec:results:qa}) on the DWave quantum annealer.
+Results from quantum annealing are compared and discussed in contrast to simulations (\ref{sec:results:simulation}).
+All algorithms used and data obtained are publicly available (\ref{sec:open-source}).
 
@@
 
+%========================================================================================
+\section{CONCLUSION}
+\label{sec:conclusion}
+%========================================================================================
+
 \ghissue{Finalize results}{19}
@@
 
-We map integer variables $\vec z = \vec x, \vec s$ to qubits under the following transformation~\cite{Chang:2018uoc}
-\begin{align}
- z_i = & \sum_{r=0}^{R_i-1} 2^r \psi_{ri}
- \label{eq:int_to_bin}
-\end{align}
-where $\psi_{ri} \in \{0, 1\}$.
-The number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
-This transformation can be expressed as a rectangular matrix.
+The integer-vector qubit transformation, eq.~\eqref{eq}, can be expressed as a rectangular matrix.
 For example, a vector of two integer variables $z_0$ and $z_1$ represented by one and two qubits respectively is given as
@@
 \end{align}
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Comment on ILP QUBO penalty term}
+\label{sec:methods:ilp-qubo-comments}
+%----------------------------------------------------------------------------------------
+
+The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
+Thus some knowledge of the problem is required.
+In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
+After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
+Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Integer quadratic optimization}
+\label{sec:methods:ilp:quadratic}
+%----------------------------------------------------------------------------------------
+
+Because quantum annealing is capable of solving quadratic problems, we extend the proposed algorithm to solve integer quadratic optimization problems as well such that
+\begin{align}
+ \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
+\end{align}
+without the introduction of auxiliary qubits.
+
+In this case the $Q_{xx}$ component of the Qubo, eq.~\eqref{eq:qubo:components} obtains a new term
+\begin{equation}
+    Q_{xx} \to Q_{xx} + T_x^T d T_x \, .
+\end{equation}
 
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{Comment on ILP QUBO penalty term}
-\label{sec:methods:ilp-qubo-comments}
+\subsection{Offset study}
+\label{sec:methods:experiment}
 %----------------------------------------------------------------------------------------
-
-The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
-Thus some knowledge of the problem is required.
-In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
-After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
-Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Integer quadratic optimization}
-\label{sec:methods:ilp:quadratic}
-%----------------------------------------------------------------------------------------
-
-Because quantum annealing is capable of solving quadratic problems, we extend the proposed algorithm to solve integer quadratic optimization problems as well such that
-\begin{align}
- \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
-\end{align}
-without the introduction of auxiliary qubits.
-
-In this case the $Q_{xx}$ component of the Qubo, eq.~\eqref{eq:qubo:components} obtains a new term
-\begin{equation}
-    Q_{xx} \to Q_{xx} + T_x^T d T_x \, .
-\end{equation}
 
@@
 
-{\color{green}For the simulation results presented, we set the temperature to 22.5 milliKelvin. The coherence time for local decoherence is set to 15$ns$, and 1$ns$ for full-counting statistics.
-}
+For the simulation results presented, we set the temperature to 22.5 milliKelvin.
+The coherence time for local decoherence is set to 15$ns$, and 1$ns$ for full-counting statistics.
+
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-{\color{red} I moved the details of annealing schedules here. This doesn't belong in the main text. This is way too detailed.}
 In this section, we discuss the details of the annealing schedule with respect to the dimensionless normalized time $s$.
@@
 
-{\color{red}
-%----------------------------------------------------------------------------------------
-\subsubsection{Decoherence Time}
-\label{sec:methods:deco}
-%----------------------------------------------------------------------------------------
-
-\ghissue{Decoherence section}{16}
-I think the following two sections can be merged / removed.
-
-I talk about this in the section above.
-
-The AL discussion is a bit too textbooky for a paper I think.
-
-FC gives correct distribution.
-Local the simplest relaxation mode.
-Maybe run a plot showing we turn of local, and see same scaling.
-So offset is not directly tackling only this.
-Can show that in Fig.
-7.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Anderson Localization}
-\label{sec:methods:mbl}
-%----------------------------------------------------------------------------------------
-{\color{green} If we want, we can write a short summary of Anderson Localization. Anderson Hamiltonian -> spin representation. This requires some more reading though I think.}
-%----------------------------------------------------------------------------------------
-
-}
 %========================================================================================

### 2020-09-10 paper/main.tex
Updated abstract

@@
  For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA), and investigated problem and hardware-specific limitations.
- This work presents the formalism of how to map ILP problems to the annealing architectures.
- It illustrates the effects of decoherence and many-body localization, for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
- We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decoherence--which is qualitatively confirmed by simulations.
- {\color{red}Furthermore we find evidence for Many-body localization effects ... and find that FC decoherence is more relevant than local decoherence...}
-
- \ghissue{Finalize abstract}{13}
-
+ This work presents the formalism of how to map ILP problems to the annealing architectures, how to systematically improve computations utilizing optmizied anneal schedules and models the anneal process through a simmulation.
+ It illustrates the effects of decoherence and Many-Body Localization, for the Minimum Dominating Set problem, and compares annealing results against numerical simulations of the quantum architecture.
+ We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decoherence.
+ Simulations qualitatively reproduce the offset study, suggesting the improvements are at least partially caused by quantum effects.
 \end{abstract}

### 2020-09-10 paper/main.tex
Updates based on issues

@@
 In order to understand the effects of annealing offsets, we simulate the annealing process for the $G(2)$ graph embedded in chimera topography.
-In order to shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$.
+In order to shorten the simulation time, we repeat the same anneal process with a total annealing time of 1 $\mu s$ and count the number of correct ground state occurances.
 The resulting ground state probability as a function of offset measured over 100,000 observations is shown in Fig.~\ref{fig:dwave1us}.
@@
 
+\ghissue{Decoherance study}{31}
+
 %========================================================================================
@@
 %========================================================================================
-
-\ghissue{Finalize results}{19}
 
@@
 
-The solution to the minimum independent set can be expressed as an integer optimization problem given by,
+The solution to the Minimum Dominating Set problem can be expressed as an integer optimization problem given by,
 \begin{align}
@@
 qubits to encode the vertices and to embed the slack variables.
-Therefore, the embedding at worse scales with $n_V \log_2 n_V$ qubits for fully connected graphs.
+Therefore, the (logical) qubit vector $\vec \Psi$ at worst scales with $n_V \log_2 n_V$ qubits for fully connected graphs.
 
@@
 
-\ghissue{Simulation details}{18}
-
 %========================================================================================

### 2020-09-10 paper/main.tex
edits

@@
  We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decoherence.
- Simulations qualitatively reproduce the offset study, suggesting the improvements are at least partially caused by quantum effects.
+ Simulations qualitatively reproduce algorithmic improvements of the modified annealing schedule, suggesting the improvements have origins from quantum effects.
 \end{abstract}
@@
  \label{eq:initial-ip-def}
- \vec x_0 = \mathrm{arg} & \min\limits_{x}(\sum_i c_i x_i)
+ \vec x_0 = \mathrm{arg} & \min\limits_{x}\left(\sum_i c_i x_i\right)
 \end{align}
@@
 
-An important ILP is the Minimum Dominating Set problem, which is representatively considered in this work.
+An important ILP application is the Minimum Dominating Set problem, which is representatively considered in this work.
 For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, a dominating set $D$ is a specific subset of vertices $D \subseteq V$.
@@
 and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ encodes the problem to be solved.
-The Ising representation of the the problem Hamiltonian has the form
-\begin{equation}
- H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i \, .
-\end{equation}
-Intuitively, to find a final state that globally minimizes the energy, the annealer needs to explore the entire state.
-If the annealer does not reach thermal equilibrium, the annealing process's final solution might not encode the final Hamiltonian's ground state.
-Thus the annealing process should be sufficiently slow not to introduce potential barriers that freeze in intermediate spin configurations.
-On the other hand, decoherence in the hardware leads to the loss of quantum information.
-It is, therefore, desirable to minimize the effect of relaxation and shorten the annealing process.
 
-While such spin-freezing effects may be related to systematic hardware constraints, they are hypothetically related to quantum localization phenomena.
-Recognizing that a general QUBO exhibits a spin-glass model's properties--if the were $h_i$ coefficients are randomly drawn from a Bernoulli distribution--one may expect spin-localization behavior influencing the outcome of the anneal.
-In the case of quantum annealing, when an algorithm is mapped to its QUBO representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
-Explicitly, the spin-glass model enters its glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization effects, the many-body analog of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.
-
-In this paper, we propose a new algorithm that maps ILP problems to QUBOs.
+In this paper, we propose an algorithm that maps ILP problems to QUBO.
 This is achieved by the introduction of slack variables $s$ which turn the inequalities eq.~\eqref{eq:ilp-constraints} to equalities
@@
 We further improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis.
-The improvement strategy is motivated by the MBL hypothesis.
-That is, we want the system to have ergodicity in order to avoid Many-Body Localizations.
-We prepare the system such that Many-Body Localizations are minimized by partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.
+Converting to the Ising representation of the the problem Hamiltonian,
+\begin{equation}
+    \label{eq:HIsing}
+     H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i ,
+\end{equation}
+we can recognize that Eq.~(\ref{eq:HIsing}) exhibits spin-glass properties.
+More specifically, if the $h_i$ coefficients are randomly drawn from a Bernoulli distribution, one expects spin-localization behavior to influence the outcome of the anneal.
+In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
+More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~{\color{red} cite some AL papers here}.
+dd
+
+Our improvement strategy is motivated by the MBL hypothesis.
+That is, we want the system to be ergodic and avoid the MBL phase.
+As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.
 
 To understand which phenomena are relevant for describing the proposed offset study's scaling behavior, whether they are rooted in the quantum nature or related to hardware constraints, we simulate the anneal for a small MDS problem.
-This simulation requires solving the von Neumann equations of the time-dependent problem.
-To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
-\begin{align}
- \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}(\rho(t), H(t))
-\end{align}
-where $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
-In this work, we consider two types of decoherence models: full counting statistics and local damping.
-The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
-The local damping term models the decoherence of each qubit independently.
+This simulation solves the von Neumann equations accounting for different models of quantum decoherence, and explores whether algorithmic improvements on hardware are present in idealizes systems.
 
@@
 Results from quantum annealing are compared and discussed in contrast to simulations (\ref{sec:results:simulation}).
-All algorithms used and data obtained are publicly available (\ref{sec:open-source}).
 
@@
 %----------------------------------------------------------------------------------------
+Following Eq.~(\ref{eq:ilp:slack}), the ILP problems simplifies to solving a system of linear equations on integer valued variables.
 We map the integer variables $\vec z = \vec x, \vec s$ appearing in eq.~\eqref{eq:ilp:slack} to qubits under the following transformation~\cite{Chang:2018uoc}
@@
 \end{align}
-where $\psi_{ri} \in \{0, 1\}$.
-The number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$ (see also section \ref{sec:methods:bit-basis}).
-This transformation can be expressed as a rectangular matrix $T_z$ such that
+where $\psi_{ri} \in \{0, 1\}$. The number of qubits used to represent the $i$-th integer variable is allowed to vary with $R_i$.
+The integer-vector qubit transformation can be expressed as a rectangular matrix.
+For example, a vector of two integer variables $z_0$ and $z_1$ represented by one and two qubits respectively is given as
+\begin{align}
+ \begin{pmatrix}
+  z_0 \\
+  z_1
+ \end{pmatrix}
+ = &
+ \begin{pmatrix}
+  2^0 & 0   & 0   \\
+  0   & 2^0 & 2^1
+ \end{pmatrix}
+ \begin{pmatrix}
+  \psi_{00} \\
+  \psi_{01} \\
+  \psi_{11}
+ \end{pmatrix}
+ \equiv T^z \begin{pmatrix}
+  \psi_{00} \\
+  \psi_{01} \\
+  \psi_{11}
+ \end{pmatrix}
+\end{align}
+If all variables are represented by the same number of qubits--$R_i$ is a constant for all $i$--then one can express the transformation as tensor product of bit vectors
+\begin{align}
+ \mathcal{R} =  & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},    \\
+ \mathcal{Z} =  & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},    \\
+ |\mathds{1}| = & |\mathcal{Z}|,                 \\
+ T^z =          & \mathds{1}\otimes \mathcal{R}.
+\end{align}
+
+As a result, the $\vec x$ and $\vec s$ map to the binary vector $\vec \Psi$ under the transformation
 \begin{equation}
@@
 
-The integer linear (and quadratic equivalently, see section \ref{sec:methods:ilp:quadratic}) optimization problem can be mapped to a minimization of the quadratic objective function
+The integer linear optimization problem is then solved through the minimization of the quadratic objective function
 \begin{align}
@@
 
-A solution to the ILP is found by identifying the qubit vector $\vec \Psi^{(0)}$ which minimizes $ \chi^2$.
 The integer solution to the original ILP is computed by $\vec x^{(0)} = T_x \vec \Psi_x^{(0)}$ and the original solution to the problem is computed by shifting the annealer extracted energy $E \equiv  \chi^2(\vec \Psi^{(0)}) $ by $p \left \| \vec b \right\|^2$.
@@
 We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.
+Details of the mapping of ILP to MDS is given in Sec.~\ref{sec:methods:mds-qubo}.
 This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer.
@@
 Further detail is given in Sec.~\ref{sec:methods:minor_embedding}.
-We study the effects offset the two groups of qubits over a total range between 0\% and 5\% of $c$.
-The results of this study is shown in Fig.~\ref{fig:baseline}.
+We study the effects of delaying the anneal schedule of one group of qubits over the other and present the results of this study is shown in Fig.~\ref{fig:baseline}.
 
@@
 The black line (offset$=0.0$) in Fig.~\ref{fig:baseline} shows results from the baseline experiment, without modification to the DWave annealing schedule, and observe improvement over random guessing (blue).
-However, We explore one avenue towards improving the experiment results by introducing per-qubit annealing offsets into the time evolution.
 
@@
 
+We explore one avenue towards improving the experiment results by introducing per-qubit annealing offsets into the time evolution.
 The results in yellow (green) delays the annealing of qubits subject to stronger (weaker) external fields.
@@
 
-Simulation results are obtained by solving the von Neumann equation subject to two decoherence models: local damping and full-counting statistics.
+To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
+\begin{align}
+ \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}(\rho(t), H(t))
+\end{align}
+where $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
+In this work, we consider two types of decoherence models: full counting statistics and local damping.
+The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
+The local damping term models the decoherence of each qubit independently.
 Details of the master equation are given in Sec.~\ref{sec:methods:lindblad}.
-The time dependence of $A(s)$ and $B(s)$ are given by the DWave annealing schedule with offsets in Fig.~\ref{fig:anneal_schedule}.
+
 The graph $G(2)$ has the interesting feature of having a degenerate ground state depending on whether qubit 0 or 1 is chosen to be the MDS solution.
@@
 We confirm that scaling with respect to offset from the simulation matches what is observed from experiment, and provides evidence suggesting that the improvements are related to quantum mechanics.
-An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets and effects of local damping are presented in Sec.~\ref{sec:app:offset}, and further supports this observation.
+An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets and effects of local damping are presented in Sec.~\ref{sec:methods:annealing-schedule}, and further supports this observation.
 
@@
 \ghissue{Decoherance study}{31}
-
-%========================================================================================
-\section{CONCLUSION}
-\label{sec:conclusion}
-%========================================================================================
 
@@
 %========================================================================================
-
 %----------------------------------------------------------------------------------------
-\subsection{Integer Programming Mapping to QUBO}
-\label{sec:methods:ilp}
-
+\subsection{Additional Mappings to QUBO}
+\label{sec:methods:ILP-to-QUBO}
 %----------------------------------------------------------------------------------------
-\subsubsection{Bit basis}
-\label{sec:methods:bit-basis}
-%----------------------------------------------------------------------------------------
-
-The integer-vector qubit transformation, eq.~\eqref{eq}, can be expressed as a rectangular matrix.
-For example, a vector of two integer variables $z_0$ and $z_1$ represented by one and two qubits respectively is given as
-\begin{align}
- \begin{pmatrix}
-  z_0 \\
-  z_1
- \end{pmatrix}
- = &
- \begin{pmatrix}
-  2^0 & 0   & 0   \\
-  0   & 2^0 & 2^1
- \end{pmatrix}
- \begin{pmatrix}
-  \psi_{00} \\
-  \psi_{01} \\
-  \psi_{11}
- \end{pmatrix}
- \equiv T^z \begin{pmatrix}
-  \psi_{00} \\
-  \psi_{01} \\
-  \psi_{11}
- \end{pmatrix}
-\end{align}
-If all variables are represented by the same number of qubits--$R_i$ is a constant for all $i$--then one can express the transformation as tensor product of bit vectors
-\begin{align}
- \mathcal{R} =  & \begin{pmatrix} 2^0 & \dots & 2^{R-1}\end{pmatrix},    \\
- \mathcal{Z} =  & \begin{pmatrix} z_0 & \dots & z_{N-1}\end{pmatrix},    \\
- |\mathds{1}| = & |\mathcal{Z}|,                 \\
- T^z =          & \mathds{1}\otimes \mathcal{R}.
-\end{align}
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Comment on ILP QUBO penalty term}
-\label{sec:methods:ilp-qubo-comments}
-%----------------------------------------------------------------------------------------
-
-The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
-Thus some knowledge of the problem is required.
-In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
-After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
-Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Integer quadratic optimization}
-\label{sec:methods:ilp:quadratic}
-%----------------------------------------------------------------------------------------
-
-Because quantum annealing is capable of solving quadratic problems, we extend the proposed algorithm to solve integer quadratic optimization problems as well such that
-\begin{align}
- \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
-\end{align}
-without the introduction of auxiliary qubits.
-
-In this case the $Q_{xx}$ component of the Qubo, eq.~\eqref{eq:qubo:components} obtains a new term
-\begin{equation}
-    Q_{xx} \to Q_{xx} + T_x^T d T_x \, .
-\end{equation}
-
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\subsection{Offset study}
-\label{sec:methods:experiment}
+\subsubsection{Integer quadratic optimization}
+\label{sec:methods:ilp:quadratic}
 %----------------------------------------------------------------------------------------
+
+Because quantum annealing is capable of solving quadratic problems, we extend the proposed algorithm to solve integer quadratic optimization problems as well such that
+\begin{align}
+ \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
+\end{align}
+without the introduction of auxiliary qubits.
+
+In this case the $Q_{xx}$ component of the Qubo, eq.~\eqref{eq:qubo:components} obtains a new term
+\begin{equation}
+    Q_{xx} \to Q_{xx} + T_x^T d T_x \, .
+\end{equation}
+
+%----------------------------------------------------------------------------------------
+\subsection{ILP on the DWave}
+\label{sec:methods:ILP-on-DWave}
+%----------------------------------------------------------------------------------------
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Comment on ILP QUBO penalty term}
+\label{sec:methods:ilp-qubo-comments}
+%----------------------------------------------------------------------------------------
+
+The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} {\color{red}@chris what equation is this?} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
+Thus some knowledge of the problem is required.
+In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
+After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
+Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
 
@@
 The resulting Ising Hamiltonian has external field equal to $h = (2.75, 1.5, -1.0, -1.25, -1.0)$.
-Following the offset strategy described in Sec.~\ref{sec:discussion:offsets}, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
+Following the offset strategy described in Sec.~\ref{sec:results:qa}, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
 This imbalance in the two groups may perhaps explain the reason why effects of delaying the weaker fields are more pronounced, since delaying the strong fields only differs from the baseline by a single qubit.
@@
 In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
-Details of the DWave annealing schedule use to generate Fig.~\ref{fig:anneal_schedule} and further documentation are provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.
+Further documentation is provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.
 

### 2020-09-10 paper/figures/clean_plots.py
update plots to pretty legends

@@ -306,7 +306,7 @@ def plot_distribution():
     ax.set_xticks(X)
     ax.set_xticklabels(Xlabel, rotation="0")
 
-    plt.legend()
+    plt.legend(fancybox=True, framealpha=0.5)
 
     plt.savefig("../new_figures/final_state_distribution.pdf", transparent=True)
 
@@ -439,7 +439,7 @@ def plot_all():
     ax.set_xlabel("graph size", p["textargs"])
     ax.set_ylabel("probability", p["textargs"])
 
-    plt.legend()
+    plt.legend(fancybox=True, framealpha=0.5)
     print(prob)
 
     plt.savefig("../new_figures/DWave_scaling.pdf", transparent=True)
@@ -518,14 +518,14 @@ def plot_tdse():
     """simulation result
     """
     offset = list(0.01 * (np.arange(11) - 5))
-    prob = [gettdsetheory(os) for os in offset]
+    prob = [gettdsetheory(os, normalized_time=[0.0, 1.0]) for os in offset]
     ax.errorbar(x=offset, y=prob, ls="--", marker="o", color=os_color["sim"], label="theory")
     """labels
     """
     ax.set_xlabel("offset", p["textargs"])
     ax.set_ylabel("probability", p["textargs"])
 
-    plt.legend()
+    plt.legend(fancybox=True, framealpha=0.5)
     plt.savefig("../new_figures/NN2_offset_scaling.pdf", transparent=True)
 
 def plot_tdse_extended():
@@ -535,21 +535,21 @@ def plot_tdse_extended():
     """
     offset = list(0.01 * (np.arange(11) - 5))
 
-    prob = [gettdsetheory(os, normalized_time = [0.0, 1.0]) for os in offset]
-    ax.errorbar(x=offset, y=prob, ls="--", marker="o", color="k", alpha=0.5, label="default")
+    prob = [gettdsetheory(os, normalized_time = [-0.1, 1.1], gamma_local=0) for os in offset]
+    ax.errorbar(x=offset, y=prob, ls="-", marker="o", color=blue, alpha=0.5, label="extended f.c. only")
 
     prob = [gettdsetheory(os, normalized_time = [-0.1, 1.1]) for os in offset]
     ax.errorbar(x=offset, y=prob, ls="-", marker="o", color=red, alpha=0.5, label="extended")
 
-    prob = [gettdsetheory(os, normalized_time = [-0.1, 1.1], gamma_local=0) for os in offset]
[…]

### 2020-09-10 paper/figures/qlpdb_plots.py

@@ -70,7 +70,7 @@ def plot_prob(datadict, datadict2, datadict3):
     ax.set_yscale("log")
     ax.set_xlabel("Nodes in graph")
     ax.set_ylabel("Probability of getting MDS solution")
-    plt.legend()
+    plt.legend(fancybox=True, framealpha=0.5)
     plt.savefig("./scaling_plot.pdf")
     plt.draw()
     plt.show()
@@ -89,7 +89,7 @@ def plot_prob(datadict, datadict2, datadict3):
     ax.set_yscale("log")
     ax.set_xlabel("Nodes in graph")
     ax.set_ylabel("Improvement over random guessing")
-    plt.legend()
+    plt.legend(fancybox=True, framealpha=0.5)
     plt.savefig("./ratio.pdf")
     plt.draw()
     plt.show()
@@ -119,7 +119,7 @@ def plot_prob(datadict, datadict2, datadict3):
     #)
     ax.set_xlabel("Nodes in graph")
     ax.set_ylabel("Percent improvement over Constant")
-    plt.legend()
+    plt.legend(fancybox=True, framealpha=0.5)
     plt.savefig("./ratio_pct.pdf")
     plt.draw()
     plt.show()

### 2020-09-10 paper/figures/clean_plots.py
scaling with local only

@@ -494,10 +494,12 @@ def gettdse(offset=0.0):
     return prob
 
 
-def gettdsetheory(offset=0.0, normalized_time = "[0, 1]", gamma_local = None):
+def gettdsetheory(offset=0.0, normalized_time = "[0, 1]", gamma_local = None, gamma=None):
     sim = Sim()
     if gamma_local is not None:
         sim.params["wave"]["gamma_local"] = gamma_local
+    if gamma is not None:
+        sim.params["wave"]["gamma"] = gamma
     query, sol, tdse = sim.get_data(offset, normalized_time)
     H = tdse._constructIsingH(np.array(tdse.ising["Jij"]), np.array(tdse.ising["hi"])).todense().tolist()
     eval, evec = eigh(H)
@@ -543,6 +545,9 @@ def plot_tdse_extended():
 
     prob = [gettdsetheory(os, normalized_time = [0.0, 1.0]) for os in offset]
     ax.errorbar(x=offset, y=prob, ls="--", marker="o", color="k", alpha=0.5, label="default")
+
+    prob = [gettdsetheory(os, normalized_time = [-0.1, 1.1], gamma=0) for os in offset]
+    ax.errorbar(x=offset, y=prob, ls="--", marker="o", color=green, alpha=0.5, label="extended local only")
 
     """labels
     """
@@ -954,17 +959,20 @@ if __name__ == "__main__":
     For DWave only
     """
     # plot_anneal_time() # this is not current, maybe drop this
-    plot_all()
+    #plot_all()
+
     #plot_random_ratio()
     # plot_dwave_mi()
     """
     For TDSE simulation
     """
-    plot_tdse()
+    #plot_tdse()
     plot_tdse_extended()
-    plot_distribution()
-    plot_annealcurve()
-    plot_timedepprob()
+    #plot_distribution()
+    #plot_annealcurve()
+    #plot_timedepprob()
+
+
     # plot_hybridization()
     # plot_mi()
     # plot_timedepsz()

### 2020-09-11 paper/figures/clean_plots.py
update clean plots for stupid color bar

@@ -1,4 +1,6 @@
+import matplotlib as mpl
 import matplotlib.pyplot as plt
+from matplotlib.colors import ListedColormap
 import seaborn as sns
 from qlpdb.data.models import Data as data_Data
 import pickle
@@ -43,6 +45,12 @@ os_alpha[0.04] = 0.8
 os_alpha[0.05] = 1.0
 os_alpha[0.06] = 0.4
 os_alpha[0.07] = 0.2
+
+OFFSETS = 0.01 * (np.arange(11) - 5)
+OFFSET_COLORS = sns.diverging_palette(250, 30, l=65, center="dark", n=11)
+OFFSET_MAP = dict(zip(OFFSETS, OFFSET_COLORS))
+OFFSET_CMAP = ListedColormap(OFFSET_COLORS)
+sns.palplot(OFFSET_COLORS)
 
 """
 ###################################
@@ -253,24 +261,27 @@ def getallspintheory(offset=0.0):
     prob = {states[idx]: state_prob[idx] for idx in range(2 ** 5)}
     return prob
 
-
-def plot_distribution():
-    offset = 0.01 * (np.arange(11) - 5)
+def plot_distribution(offset=OFFSETS):
     count_energy = {oi: getallspinconfig(offset=oi) for oi in offset}
-    count = {oi: {spin_energy[0]: count_energy[oi][spin_energy] for spin_energy in count_energy[oi]} for oi in
-             count_energy}
-    energy = {oi: {spin_energy[0]: spin_energy[1] for spin_energy in count_energy[oi]} for oi in count_energy}
-    print(count_energy)
+    count = {
+        oi: {
+            spin_energy[0]: count_energy[oi][spin_energy]
+            for spin_energy in count_energy[oi]
+        }
+        for oi in count_energy
+    }
+    energy = {
+        oi: {spin_energy[0]: spin_energy[1] for spin_energy in count_energy[oi]}
+        for oi in count_energy
+    }
     # Xlabel = [tuple([int(q) for q in list(format(i, '05b'))]) for i in range(2 ** 5)]
     # X = np.arange(2 ** 5)
     Xlabel = [(0, 1, 0, 0, 0), (1, 0, 0, 1, 0), (1, 1, 1, 1, 1)]
     X = np.array(range(len(Xlabel)))
 
-    plt.figure(figsize=p["figsize"])
-    ax = plt.axes(p["aspect_ratio"])
+    fig, ax = plt.subplots(figsize=p["figsize"])
[…]

### 2020-09-11 paper/main.tex

@@
 
-In the simulation, we are also reserve the ability to remove the systematic errors by extending the annealing schedule as shown in Fig.~\ref{fig:anneal_schedule_ext}.
-With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians.
-The dependence on offset for $G(2)$ (Fig.~(\ref{fig:dwave1us})) remains the same under the extended anneal schedule (Fig.~\ref{fig:anneal_schedule_ext}), confirming that the behavior is not a systematic artifact.
-
 \begin{figure}
@@
 \end{figure}
+
+In the simulation, we are also reserve the ability to remove the systematic errors by extending the annealing schedule as shown by the red data points in Fig.~\ref{fig:anneal_schedule_ext}.
+With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians.
+The dependence on offset for $G(2)$ (Fig.~(\ref{fig:dwave1us})) remains the same under the extended anneal schedule (Fig.~\ref{fig:anneal_schedule_ext}), confirming that the behavior is not a systematic artifact.
+
+The quantum system can be further idealized by including only the full-counting statistics model (blue), or local decoherence (green).
+We observe in both cases that the overall scaling follows the story of the MBL hypothesis.
+Perhaps more importantly, we observe that a simulation without local decoherence, where the relaxation is dependent on precisely the instantaneous value of $|h_i|$, exhibits the same scaling as experiment.
+This result suggests that our strategy for setting annealing offsets is improving the algorithm beyond the simple explanation of qubits freezing due to single-particle amplitude damping.
+In fact, the simulation with only amplitude damping (green) does not fully capture the results of the experiment.
+We observe hints of a phase transition with respect to offset (which may be thought of as some measure of disorder) when dynamical thermalization effects are removed.
+This is a tantalizing observation, and also is strong evidence for the inclusion of the full-counting statistics model.
+
+It unfortunately does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to 1 within machine precision.
 

### 2020-09-12 paper/main.tex
ref fig for sim check
clean up plots

@@
 \affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
-	\author{Chih-Chieh~Chen (\begin{CJK*}{UTF8}{bsmi}\mbox{陳志傑}\end{CJK*})}
+	\author{Chih-Chieh~Chen }
 \affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
@@
 The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction.
-{\color{red} Are you suppose to reference Fig. 7 here?}
+The oscillation is depicted in Figure \ref{figcheck}, where the simulation matches the expected theoretical behavior.
 
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./figures/check.png}
+	\includegraphics[width=\columnwidth]{./new_figures/vacuum_probability.pdf}
 	\caption{check}
-	\label{fig:check}
+	\label{figcheck}
 \end{figure}

### 2020-09-12 paper/figures/clean_plots.py

@@ -66,7 +66,7 @@ sns.palplot(OFFSET_COLORS)
 
 """
 ###################################
-#####  Simulation Data Class  #####
+#####  simulation Data Class  #####
 ###################################
 """
 
@@ -310,7 +310,7 @@ def plot_distribution(offset=OFFSETS):
             height=height,
             width=width,
             color=OFFSET_COLORS[idx],
-            label="Experiment" if idx == 6 else None,
+            label="experiment" if idx == 6 else None,
             zorder=1,
             alpha=0.9,
             align="edge",
@@ -321,7 +321,7 @@ def plot_distribution(offset=OFFSETS):
         prob = getallspintheory(os)
         height = [prob[Xi] for Xi in Xlabel]
         if idx == len(offset) - 1:
-            label = "Simulation"
+            label = "simulation"
         else:
             label = None
         ax.bar(
@@ -338,8 +338,8 @@ def plot_distribution(offset=OFFSETS):
 
     """labels
     """
-    ax.set_xlabel("Final State Distribution", p["textargs"])
-    ax.set_ylabel("Ground State Probability", p["textargs"])
+    ax.set_xlabel("final state distribution", p["textargs"])
+    ax.set_ylabel("ground state probability", p["textargs"])
     ax.set_xticks(X)
     ax.set_xticklabels(Xlabel, rotation="0")
 
@@ -349,7 +349,7 @@ def plot_distribution(offset=OFFSETS):
         cmap=OFFSET_CMAP,
         norm=mpl.colors.Normalize(vmin=-0.05, vmax=0.05),
         orientation="horizontal",
-        label="Offset",
+        label="offset",
     )
     cax.set_xticklabels(colorbar_label)
     ax.legend(bbox_to_anchor=(0.9, 0.98, 0.045, 0.01), fancybox=True, shadow=False, frameon=True, framealpha=0.3)
@@ -470,14 +470,14 @@ def plot_all():
     for os in offset:
         color = OFFSET_MAP[os]
         if os == 0.0:
-            ax.errorbar(x=graphsize, y=prob[os], ls="-", marker="o", color=color, alpha=os_alpha[os], label="Experiment")
[…]

### 2020-09-12 paper/main.tex
author contributions

@@
 \author{Chia~Cheng~Chang (\begin{CJK*}{UTF8}{bsmi}張家丞\end{CJK*})}
-\affiliation{RIKEN Interdisciplinary Theoretical and Mathematical Sciences (iTHEMS), Wako, Saitama 351-0198, Japan}
+\affiliation{RIKEN iTHEMS, Wako, Saitama 351-0198, Japan}
 \affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
@@
 \ghissue{Acknowledgements}{22}
-We thank x, y, z...
+
+We thank Long Gang Pang for inspiring discussions.
 
@@
 
-\ghissue{Author contributions}{23}
-C.K. drank a lot of coffee.
+Initial idea was proposed by Chang.
+All authors contributed to the design of test cases.
+Calculations were performed on the D-Wave by Chang and K\"oerber.
+Numerical simulations were performed by Chen, Chang, and K\"orber.
+All authors contributed to writing and editing of the final manuscript.
 

### 2020-09-12 paper/main.tex
some acknowledgements and filled out affiliations

@@
 
-\author{Chia~Cheng~Chang (\begin{CJK*}{UTF8}{bsmi}張家丞\end{CJK*})}
+\author{Chia~Cheng~Chang}
 \affiliation{RIKEN iTHEMS, Wako, Saitama 351-0198, Japan}
@@
 \affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
+\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
 \author{Christopher K\"orber}
+\affiliation{Institut f\"ur Theoretische Physik II, Ruhr-Universit\"at Bochum, D-44780 Bochum, Germany}
 \affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
-\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
 \author{Travis~Humble}
 \affiliation{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
+\affiliation{Computational Sciences and Engineering, Oak Ridge National Laboratory, Oak Ridge, Tennessee, 37831, USA}
 \author{Jim~Ostrowski}
-\affiliation{University of Tennessee}
+\affiliation{Industrial and Systems Engineering, University of Tennessee, Knoxville, Tennessee 37996, USA}
 
@@
 We thank Long Gang Pang for inspiring discussions.
+We thank David Johnson, Vlad Papish and the rest of D-Wave Support for answering detailed questions about the D-Wave annealer.
 

### 2020-09-12 paper/main.tex
add references

@@
 We further improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis.
+\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}
 Converting to the Ising representation of the the problem Hamiltonian,
@@
 In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
-More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~{\color{red} cite some AL papers here}.
+More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~{\color{red} cite some AL papers here} \cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001}.
 dd
@@
 That is, we want the system to be ergodic and avoid the MBL phase.
-As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.
+As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.\cite{doi:10.7566/JPSJ.89.044001}
 
@@
 
-We consider two types of decoherence models: full counting statistics and local damping.
+We consider two types of decoherence models: full counting statistics \cite{PhysRevE.90.022103} and local damping.
 The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.

### 2020-09-12 paper/main.tex
added sentence about g.s asymmetry

@@
 In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
-More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~{\color{red} cite some AL papers here} \cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001}.
+More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001}.
 dd
@@
 That is, we want the system to be ergodic and avoid the MBL phase.
-As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.\cite{doi:10.7566/JPSJ.89.044001}
+As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields~\cite{doi:10.7566/JPSJ.89.044001}.
 
@@
 The simulation (black) captures main features of the experimental result: 1) significant probability to populate both ground states (rather than populating only one), 2) asymmetry in ground state population due to systematic effects of offset lifting the final state degeneracy spanning approximately the correct range, 3) population of first excited state with systematically lower probability when the strong field is delayed.
+The asymmetry in the ground state distribution is a result of annealing offsets lifting the ground state degeneracy.
+Within the broken symmetry, the non-degenerate ground state switches between the two states depending on which qubit group is delayed.
 This result can be obtained by tuning three free parameters: the simulation temperature to the order of 10 milliKelvin, and the two coefficients of the two decoherence models at the order of 1 to 10 $ns$.

### 2020-09-12 paper/main.tex
minor word fixing and caption

@@
 
-In the simulation, we are also reserve the ability to remove the systematic errors by extending the annealing schedule as shown by the red data points in Fig.~\ref{fig:anneal_schedule_ext}.
+In the simulation, we also reserve the ability to remove the systematic errors by extending the annealing schedule as shown by the red data points in Fig.~\ref{fig:anneal_schedule_ext}.
 With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians.
@@
 	\includegraphics[width=\columnwidth]{./new_figures/vacuum_probability.pdf}
-	\caption{check}
+	\caption{Time dependent vacuum probability of 5 qubits system under pure transverse field.}
 	\label{figcheck}

### 2020-09-13 paper/main.tex
fixed all captions

@@
 	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds2.pdf}\\
-	\centering\bf{a} && \centering\bf{b} && \centering\bf{c}
+	\centering\textbf{a} && \centering\textbf{b} && \centering\textbf{c}
 	\end{tabular}
@@
 Vertices in the dominating set $D$ are highlighted in blue.
-{\bf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 2$.
-{\bf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.
-{\bf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 1$.}
+{\textbf{a)}} A dominating set of $G$ with domination number $\overline{\overline{D}} = 2$.
+{\textbf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.
+{\textbf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 1$.}
 	\label{fig:dominating_sets}
@@
 In this paper, we propose an algorithm that maps ILP problems to QUBO.
-This is achieved by the introduction of slack variables $s$ which turn the inequalities eq.~\eqref{eq:ilp-constraints} to equalities
+This is achieved by the introduction of slack variables $s$ which turn the inequalities Eq.~\eqref{eq:ilp-constraints} to equalities
 \begin{align}
@@
 
-We further improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis.
-\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}
+We further improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}.
 Converting to the Ising representation of the the problem Hamiltonian,
@@
 More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001}.
-dd
 
@@
 Following Eq.~(\ref{eq:ilp:slack}), the ILP problems simplifies to solving a system of linear equations on integer valued variables.
-We map the integer variables $\vec z = \vec x, \vec s$ appearing in eq.~\eqref{eq:ilp:slack} to qubits under the following transformation~\cite{Chang:2018uoc}
+We map the integer variables $\vec z = \vec x, \vec s$ appearing in Eq.~\eqref{eq:ilp:slack} to qubits under the following transformation~\cite{Chang:2018uoc}
 \begin{align}
@@
 	\includegraphics[width=\columnwidth]{./new_figures/DWave_scaling.pdf}
-	\caption{Baseline result of DWave (black) compared to random guessing (blue).
+	\caption{Baseline result of DWave (black) compared to random guessing (dashed green).
 The jagged nature of random guessing reflects the degeneracy of the ground state.
-The legend labels the values of annealing offsets employed.
-A positive offsets (yellow) indicates that qubits with large values of $|h_i|$ are annealing with a delayed schedule, while negative offsets (green) delay the schedule of qubits with small values of $h_i$.}
+Negative offsets with a `s' tag (blue) are results from delays of large values of $|h_i|$, while negative offsets with the `w' label (red) delay the schedule of qubits with small values of $h_i$.}
 	\label{fig:baseline}
@@
 
-\begin{figure}
+\begin{figure}[b]
 	\centering
 	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
-	\caption{The probability of finding the MDS for $G(2)$ from DWave (orange) and results from simulation with both decoherence terms (blue).
-     The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times.}
+	\caption{The probability of finding the MDS for $G(2)$ from DWave (black) and simulation (dashed yellow) at annealing times of 1 $\mu s$.}
 	\label{fig:dwave1us}
@@
 	\includegraphics[width=\columnwidth]{./new_figures/final_state_distribution.pdf}
-	\caption{{\color{red}I need to add dwave final state distribution here too.}}
+	\caption{Final state distribution from DWave (solid bars) and simulation (black outline).
+The colors label the type of offset  The $(0, 1, 0, 0, 0)$ state is the first solution where vertex 1 is in the dominating set.
+The $(1, 0, 0, 1, 0)$ state is the second solution where vertex 0 is in the dominating set.
+The first excited state is the $(1, 1, 1, 1, 1)$ state where both vertices are in the dominating set.}
 	\label{fig:final_state_distribution}
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{Minimum Dominating Set Qubo}
+\subsubsection{Minimum Dominating Set QUBO}
 \label{sec:methods:mds-qubo}
@@
 
-The target QUBO in the notation of eq.~\eqref{eq:matrix_form} reads
+The target QUBO in the notation of Eq.~\eqref{eq:matrix_form} reads
  {\small
@@
 
-In this case the $Q_{xx}$ component of the Qubo, eq.~\eqref{eq:qubo:components} obtains a new term
+In this case the $Q_{xx}$ component of the QUBO, Eq.~\eqref{eq:qubo:components} obtains a new term
 \begin{equation}
@@
 
-The minimal energy solution to eq.~\eqref{eq:initial-ip-def} and eq.~\eqref{eq:qubo-min} {\color{red}@chris what equation is this?} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
+The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:qubo-min} {\color{red}@chris what equation is this?} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
 Thus some knowledge of the problem is required.
-In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large $p$-values increase the highest available energy of the system by multiples of $p$.
+In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values of For$p$ increase the highest available energy of the system by multiples of $p$.
 After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
@@
 
-To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
+To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we evaluate the master equation in Lindblad form
 \begin{align}
- \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
+ \partial_t \rho (t) = &  \frac{-i}{\hbar} \left[H(t) , \rho(t)\right] \nonumber \\
+ & + \sum_j \left(2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}\right) ,
 \end{align}
@@
  \label{eq:annealH}
- H_{anneal}(t) & =  - \sum_i  A_i(t)\sigma^x_i                                                                      & \notag \\
- +             & \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  , &
+ H_{anneal}(t)  = & - \sum_i  A_i(t)\sigma^x_i +\sum_i B_{i}(t) h_i \sigma^z_i \notag \\
+ & + \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j  ,
 \end{align}
@@
 \begin{align}
-\mathcal{L}[\rho (t)] &=& \Gamma_{fc} \sum_j   (2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}) \notag \\
-&& + e^{-\beta \Delta E_j} (2 S_j^\dagger \rho(t) S_j - \{ S_j S^\dagger_j, \rho(t) \} )
+\mathcal{L}[\rho (t)] = & \Gamma_{\textrm{fc}} \sum_j   \left(2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}\right) \notag \\
+& + e^{-\beta \Delta E_j} \left(2 S_j^\dagger \rho(t) S_j - \{ S_j S^\dagger_j, \rho(t) \} \right)
 \end{align}
@@
 \begin{align}
-\mathcal{L}[\rho (t)] &=&  \Gamma_{loc} \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \notag \\
-&& + e^{-\beta 2|h_j| }  (2L_j^\dagger \rho(t) L_j - \{ L_j L_j^\dagger, \rho(t) \}) ),
+\mathcal{L}[\rho (t)] = &  \Gamma_{\textrm{loc}} \sum_j \left(2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \right)\notag \\
+& + e^{- 2 \beta |h_j| }  \left(2L_j^\dagger \rho(t) L_j - \{ L_j L_j^\dagger, \rho(t) \} \right) ,
 \end{align}
@@
 \begin{equation}
-\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
+\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}\left(e^{-\beta H(0)}\right)} ,
 \end{equation}
@@
 \begin{align}
-P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
+P =  \mbox{Tr} \left( \rho (t) \pi_{\mbox{gnd}} \right)  ,
 \end{align}
@@
   \caption{
-  Anneal schedules for amplitudes of initial Hamiltonian (top left to bottom right) and final Hamiltonian (bottom left to top right) are displayed for a complete anneal schedule.
-  Different colors represent different offesets: delayed (light to dark), default (black).
+  Anneal schedules for amplitudes of initial Hamiltonian (dashed) and final Hamiltonian (solid).
+  Offset 0.0 (black) and -0.05 (purple) are displayed.
+  Intermediate values lie between and are suppressed for clarity.
  }
@@
 
-\begin{figure}
+\begin{figure*}
     \centering
-	\includegraphics[width=\columnwidth]{./new_figures/anneal_schedule_extended.pdf}
-	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling_extended.pdf}
-	\caption{{\color{red}I need to add dwave final state distribution here too.}}
+	\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
+	\includegraphics[width=0.5\textwidth]{./new_figures/anneal_schedule_extended.pdf}
+    &
+	\includegraphics[width=0.5\textwidth]{./new_figures/NN2_offset_scaling_extended.pdf}\\
+	\centering \textbf{a} & \centering \textbf{b}
+	\end{tabular}
+	\centering
+	\caption{Extended annealing schedule and simulation result.
+\textbf{a)} The annealing time is increased by 10\% at both the start and end, and the initial values of $A(s)$ and $B(s)$ at non-zero offset are also not extrapolated in comparison to Fig.~\ref{fig:anneal_schedule}.
+Therefore, the initial and final Hamiltonian are no longer suffer systematic error at non-zero offset.
+\textbf{b)} The default (dashed yellow) result is one presented in Fig.~\ref{fig:dwave1us}.
+Results from extended schedules are presented shown with solid lines with full-counting statistics and amplitude damping (red), only full counting-statistics (blue), and only amplitude damping (green).
+    }
 	\label{fig:anneal_schedule_ext}
-\end{figure}
+\end{figure*}
 
@@
 
-It unfortunately does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to 1 within machine precision.
+It unfortunately does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to unity.
 
@@
 The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction.
-The oscillation is depicted in Figure \ref{figcheck}, where the simulation matches the expected theoretical behavior.
+The oscillation is depicted in Fig.~\ref{figcheck}, where the simulation matches the expected theoretical behavior.
 
@@
 	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
-	\caption{(Left) The time-dependent probability of resolving the ground state and (Right) the corresponding mutual information.
-(Top) Simulation with decoherence included and (Bottom) without decoherence.}
+	\caption{Time-dependent probability for resolving the ground state for simulation results presented in Sec.~\ref{sec:results:simulation}.
+Different offsets are labeled in the same way as Fig.~\ref{fig:baseline}.}
 	\label{fig:td_prob}

### 2020-09-13 paper/figures/clean_plots.py

@@ -629,7 +629,7 @@ def getannealcurve(offset=0.05, normalized_time=[0.0, 1.0]):
     return X, yA, yB
 
 def plot_annealcurve():
-    offset = [0.0, 0.01, 0.02, 0.03, 0.04, 0.05]
+    offset = [0.0, 0.05]
     fig = plt.figure(figsize=p["figsize"])
     ax = plt.axes(p["aspect_ratio"])
     for os in offset:
@@ -637,14 +637,14 @@ def plot_annealcurve():
             colorA = OFFSET_MAP3[0.0]
             colorB = OFFSET_MAP3[0.0]
         else:
-            colorA = OFFSET_MAP3[os]
-            colorB = OFFSET_MAP3[-os]
+            colorA = purple #OFFSET_MAP3[os]
+            colorB = purple #OFFSET_MAP3[-os]
         s, yA, yB = getannealcurve(os, normalized_time=[0, 1])
         if os == 0.05:
-            ax.errorbar(x=s, y=yA, color=colorA, marker="None", ls="-", label="$A(s)$")
+            ax.errorbar(x=s, y=yA, color=colorA, marker="None", ls="--", label="$A(s)$")
             ax.errorbar(x=s, y=yB, color=colorB, marker="None", ls="-", label=("$B(s)$"))
         else:
-            ax.errorbar(x=s, y=yA, color=colorA, marker="None", ls="-")
+            ax.errorbar(x=s, y=yA, color=colorA, marker="None", ls="--")
             ax.errorbar(x=s, y=yB, color=colorB, marker="None", ls="-")
     """labels
        """
@@ -665,7 +665,7 @@ def plot_annealcurve():
     fig.savefig("../new_figures/anneal_schedule.pdf", transparent=True)
 
 def plot_annealcurve_extended():
-    offset = [0.0, 0.01, 0.02, 0.03, 0.04, 0.05]
+    offset = [0.0, 0.05]
     fig = plt.figure(figsize=p["figsize"])
     ax = plt.axes(p["aspect_ratio"])
     for os in offset:
@@ -673,14 +673,14 @@ def plot_annealcurve_extended():
             colorA = OFFSET_MAP3[0.0]
             colorB = OFFSET_MAP3[0.0]
         else:
-            colorA = OFFSET_MAP3[os]
-            colorB = OFFSET_MAP3[-os]
+            colorA = purple #OFFSET_MAP3[os]
+            colorB = purple #OFFSET_MAP3[-os]
[…]

### 2020-09-13 paper/main.tex
add some citations

@@
 
-ILP is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}.
-In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
+ILP is a commonly tackled problem applicable to situations such as {\color{red} x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}}.
+In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~{\color{red}\cite{}}.
 Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
@@
 We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
-As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a well-studied problem for quantum annealers~\cite{}.
+As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a well-studied problem for quantum annealers~{\color{red}\cite{}}.
 
@@
 
-Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{}.
+Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{1998PhRvE..58.5355K, 2000quant.ph..1106F}.
 Through the adiabatic theorem of quantum mechanics, the annealer is initially prepared in a trivial ground state while the final Hamiltonian encodes the solution to the ILP.
-Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems~\cite{2018Glover}.
+Due to the explosion in research efforts towards hardware implementations of quantum annealers and future improvements to the annealing schedule~\cite{doi:10.7566/JPSJ.89.044001}, mapping ILP to QUBO provides a path forward towards obtaining optimal solutions to the class of integer optimization problems~\cite{2018Glover}.
 
@@
 That is, we want the system to be ergodic and avoid the MBL phase.
-As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields~\cite{doi:10.7566/JPSJ.89.044001}.
+As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.
 
@@
 We would like to emphasize that while the annealing offsets are motivated by the MBL hypothesis, and the results also follow those expectations, we do not have definitive proof that MBL plays a crucial role.
-The reason is because observations of MBL inevitably require the study of finite-size scaling, and our current simulation while being extremely thorough and explicit, is exponentially slow to evaluate making evaluations of even $G(3)$ untenable.
+The reason is because observations of MBL inevitably require the study of finite-size scaling~\cite{2015PhRvB..91h1103L}, and our current simulation while being extremely thorough and explicit, is exponentially slow to evaluate making evaluations of even $G(3)$ untenable.
 However, the intersection of time-dependent quantum mechanics and emergent phenomena such at MBL is an exciting direction that is pertinent to adiabatic quantum computing.

### 2020-09-13 paper/main.tex
more citations

@@
 In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
-More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001}.
+More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001,ALET2018498,PhysRevB.82.174411,PhysRevLett.109.017202}.
 
@@
 where $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
-In this work, we consider two types of decoherence models: full counting statistics and local damping.
+In this work, we consider two types of decoherence models: full counting statistics and local damping. \cite{10.5555/1972505}
 The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.

### 2020-09-13 paper/main.tex
find place to cite floppy qubits

--- 2020-09-13 paper/main.tex
@@
 
-Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{1998PhRvE..58.5355K, 2000quant.ph..1106F}.
+Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{1998PhRvE..58.5355K, 2000quant.ph..1106F, RevModPhys.80.1061}.
 Through the adiabatic theorem of quantum mechanics, the annealer is initially prepared in a trivial ground state while the final Hamiltonian encodes the solution to the ILP.
@@
 The simulation (black) captures main features of the experimental result: 1) significant probability to populate both ground states (rather than populating only one), 2) asymmetry in ground state population due to systematic effects of offset lifting the final state degeneracy spanning approximately the correct range, 3) population of first excited state with systematically lower probability when the strong field is delayed.
-The asymmetry in the ground state distribution is a result of annealing offsets lifting the ground state degeneracy.
+The asymmetry in the ground state distribution at non-zero offset is a result of annealing offsets lifting the ground state degeneracy.
 Within the broken symmetry, the non-degenerate ground state switches between the two states depending on which qubit group is delayed.
+At zero offset, a slight asymmetry exists, and may be due to sampling bias~\cite{}.
+
 This result can be obtained by tuning three free parameters: the simulation temperature to the order of 10 milliKelvin, and the two coefficients of the two decoherence models at the order of 1 to 10 $ns$.
@@
 As a result, details of the embedding are important.
-We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the DWave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module.
+We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the DWave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module~\cite{2008arXiv0804.4884C}.
 The same embedding is used for all DWave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.

### 2020-09-13 paper/main.tex
some citations

@@
 where $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
-In this work, we consider two types of decoherence models: full counting statistics and local damping. \cite{10.5555/1972505}
-The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
+In this work, we consider two types of decoherence models: full-counting statistics~\cite{PhysRevE.90.022103} and single-qubit amplitude damping (local damping)~\cite{10.5555/1972505}.
+The full-counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
 The local damping term models the decoherence of each qubit independently.
@@
 Within the broken symmetry, the non-degenerate ground state switches between the two states depending on which qubit group is delayed.
-At zero offset, a slight asymmetry exists, and may be due to sampling bias~\cite{}.
+At zero offset, a slight asymmetry exists, and may be due to sampling bias~\cite{2016PhRvA..93e2320K, 2017PhRvL.118g0502M}.
 
@@
 
-We consider two types of decoherence models: full counting statistics \cite{PhysRevE.90.022103} and local damping.
-The full counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
-The local damping term models the decoherence of each qubit independently.
-For full counting statistics, the Lindblad operator is
+For full-counting statistics, the Lindblad operator is
 \begin{align}
@@
 \textbf{b)} The default (dashed yellow) result is one presented in Fig.~\ref{fig:dwave1us}.
-Results from extended schedules are presented shown with solid lines with full-counting statistics and amplitude damping (red), only full counting-statistics (blue), and only amplitude damping (green).
+Results from extended schedules are presented shown with solid lines with full-counting statistics and amplitude damping (red), only full-counting-statistics (blue), and only amplitude damping (green).
     }

### 2020-09-13 paper/main.tex
citation

@@
 where $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
-In this work, we consider two types of decoherence models: full-counting statistics~\cite{PhysRevE.90.022103} and single-qubit amplitude damping (local damping)~\cite{10.5555/1972505}.
+In this work, we consider two types of decoherence models: full-counting statistics~\cite{PhysRevE.90.022103,RevModPhys.81.1665} and single-qubit amplitude damping (local damping)~\cite{10.5555/1972505,preskill1998lecture}.
 The full-counting statistics term models the global decoherence to all the qubits due to the classical reservoir.

### 2020-09-13 paper/main.tex
edits

--- 2020-09-13 paper/main.tex
@@
 Within the broken symmetry, the non-degenerate ground state switches between the two states depending on which qubit group is delayed.
-At zero offset, a slight asymmetry exists, and may be due to sampling bias~\cite{2016PhRvA..93e2320K, 2017PhRvL.118g0502M}.
+At zero offset, a slight asymmetry exists in the simulation because the Hamiltonian is only degenerate at the last moment, while the DWave is also subject to sampling bias~\cite{2016PhRvA..93e2320K, 2017PhRvL.118g0502M}.
 

### 2020-09-13 paper/main.tex
more citations
minor edits

@@
 \begin{document}
-\title{Solutions to Integer Programming from Quantum Annealing}
+\title{Integer Programming on Ising Spin-Glass}
 
@@
  To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
- For this reason, we developed an algorithm that solves integer linear programming problems (ILP), a classically NP-hard problem, on a quantum annealer (QA), and investigated problem and hardware-specific limitations.
- This work presents the formalism of how to map ILP problems to the annealing architectures, how to systematically improve computations utilizing optmizied anneal schedules and models the anneal process through a simmulation.
+ For this reason, we developed an algorithm that solves integer linear programming problems, a classically NP-hard problem, on a quantum annealer, and investigated problem and hardware-specific limitations.
+ This work presents the formalism of how to map ILP problems to the annealing architectures, how to systematically improve computations utilizing optimized anneal schedules and models the anneal process through a simulation.
  It illustrates the effects of decoherence and Many-Body Localization, for the Minimum Dominating Set problem, and compares annealing results against numerical simulations of the quantum architecture.
- We find that the QA ILP algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decoherence.
+ We find that the algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decoherence.
  Simulations qualitatively reproduce algorithmic improvements of the modified annealing schedule, suggesting the improvements have origins from quantum effects.
@@
 %----------------------------------------------------------------------------------------
-\subsection{ILP QUBO}
+\subsection{QUBO Formulation of ILP}
 \label{sec:results:qa1}
@@
 %----------------------------------------------------------------------------------------
-\subsection{Dominating Set scaling \& offset study}
+\subsection{Application to the Dominating Set}
 \label{sec:results:qa}
@@
 This result can be obtained by tuning three free parameters: the simulation temperature to the order of 10 milliKelvin, and the two coefficients of the two decoherence models at the order of 1 to 10 $ns$.
+These values are consistent with the reported DWave operating temperature~\cite{dwave_temp} and coherence times for flux qubits~\cite{2003Sci...299.1869C}.
 Additional insights of the simulation are given in Sec.~\ref{sec:methods:simulation_details}.
@@
 
-\subsection{Final remarks}
+\subsection{Final Remarks}
 \label{sec:results:final}
@@
 
-We thank Long Gang Pang for inspiring discussions.
+We thank Long Gang Pang for initial discussions.
 We thank David Johnson, Vlad Papish and the rest of D-Wave Support for answering detailed questions about the D-Wave annealer.

### 2020-09-13 paper/main.tex
nigel <3

@@
 The reason is because observations of MBL inevitably require the study of finite-size scaling~\cite{2015PhRvB..91h1103L}, and our current simulation while being extremely thorough and explicit, is exponentially slow to evaluate making evaluations of even $G(3)$ untenable.
-However, the intersection of time-dependent quantum mechanics and emergent phenomena such at MBL is an exciting direction that is pertinent to adiabatic quantum computing.
+However, the intersection of time-dependent quantum mechanics and emergent phenomena~\cite{Goldenfeld:1992qy} such at MBL is an exciting direction that is pertinent to adiabatic quantum computing.
 

### 2020-09-13 paper/main.tex
typo

--- 2020-09-13 paper/main.tex
@@
 The reason is because observations of MBL inevitably require the study of finite-size scaling~\cite{2015PhRvB..91h1103L}, and our current simulation while being extremely thorough and explicit, is exponentially slow to evaluate making evaluations of even $G(3)$ untenable.
-However, the intersection of time-dependent quantum mechanics and emergent phenomena such at MBL is an exciting direction that is pertinent to adiabatic quantum computing.
+However, the intersection of time-dependent quantum mechanics and emergent phenomena~\cite{Goldenfeld:1992qy} is an exciting direction that is pertinent to adiabatic quantum computing.
 

### 2020-09-14 paper/main.tex
Added data section

@@
 \affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
+\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
 \author{Travis~Humble}
@@
 %========================================================================================
-
-\ghissue{Data availability}{21}
+We provide access to all the software utilized and data presented in this publication in the associated GitHub repository \cite{github:cchang5/quantum_linear_programming}.
+The utilized software is contained in two installable Python modules:
+\begin{itemize}
+    \item[\texttt{qlp}] for mapping MDS problems to QUBOs and perfoming simulations,
+    \item[\texttt{qlpdb}] for interfacing and documenting simulation and experiment data through EspressoDB \cite{Chang:2019khk}.
+\end{itemize}
+The data itself is stored in a SQLite file and associated repository subdirectories.
+We provide further documentation in the repository readme file.
 

### 2020-09-14 paper/main.tex
Added funding infos
Fixed reference issue for penalty resolution

@@
 \begin{align}
+ \label{eq:ilp-slack-bit-energy}
  \chi^2(\vec \Psi)
@@
 
-The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:qubo-min} {\color{red}@chris what equation is this?} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
+The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:ilp-slack-bit-energy} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
 Thus some knowledge of the problem is required.
-In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values of For$p$ increase the highest available energy of the system by multiples of $p$.
+In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values of For $p$ increase the highest available energy of the system by multiples of $p$.
 After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
@@
 We thank David Johnson, Vlad Papish and the rest of D-Wave Support for answering detailed questions about the D-Wave annealer.
+C.K. gratefully acknowledges funding through the Alexander von Humboldt Foundation through a Feodor Lynen Research Fellowship.
 
@@
 All authors contributed to the design of test cases.
-Calculations were performed on the D-Wave by Chang and K\"oerber.
+Calculations were performed on the D-Wave by Chang and K\"orber.
 Numerical simulations were performed by Chen, Chang, and K\"orber.

### 2020-09-14 paper/main.tex
Added Travis & Jim in contributions
Added discussion section

@@
 The results in yellow (green) delays the annealing of qubits subject to stronger (weaker) external fields.
-We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the anneal schedule, in agreement with the MBL hypothesis.
-The phenomena is observed across different problem sizes and hints at the possibility of a generic improvement strategy.
+We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the anneal schedule.
 
@@
 We confirm that scaling with respect to offset from the simulation matches what is observed from experiment, and provides evidence suggesting that the improvements are related to quantum mechanics.
-An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets and effects of local damping are presented in Sec.~\ref{sec:methods:annealing-schedule}, and further supports this observation.
+An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets and effects of local damping are presented in Sec.~\ref{sec:methods:annealing-schedule}.
 
@@
 
-\subsection{Final Remarks}
-\label{sec:results:final}
-We would like to emphasize that while the annealing offsets are motivated by the MBL hypothesis, and the results also follow those expectations, we do not have definitive proof that MBL plays a crucial role.
-The reason is because observations of MBL inevitably require the study of finite-size scaling~\cite{2015PhRvB..91h1103L}, and our current simulation while being extremely thorough and explicit, is exponentially slow to evaluate making evaluations of even $G(3)$ untenable.
+%========================================================================================
+\section{DISCUSSION}
+\label{sec:discussion}
+%========================================================================================
+
+We have presented a general mapping for ILP problems to QUBO representations used by Quantum Annelears.
+We have tested this mapping's scaling in case of the MDS problem for line graphs $G(v)$.
+While the mapping outperforms random guessing for finding the optimal solution to the problem, the application of this problem in QA, for current hardware, is currently only successful for relatively small graphs.
+The applicability range depends more on the finite precision of matching the QUBO coefficients to hardware constraints and less from the qubit scaling itself.
+
+As this mapping comes with a tunable parameter, such constraints can be lifted in a problem-specific manner to extend the applicability (Sec.~\ref{sec:methods:ILP-on-DWave}).
+Furthermore, the same algorithm can be extended to quadratic constraint optimization problems (Sec.~\ref{sec:methods:ilp:quadratic}).
+
+We have also proposed a new annealing optimization scheme based on the MBL hypothesis--introducing offsets for delaying the anneal schedules of individual qubits based on the external magnetic field--which generally improves the probability of finding correct ground states of the system.
+This phenomenon is observed across different problem sizes and hints at the possibility of a generic improvement strategy.
+
+To further understand the nature of MBL inspired anneal schedule offset approach's origin, we simulate the Annealer for an MDS Problem G(2) graph.
+This simulation utilizes two decoherence models, local dampening and full-counting statistics, with three free parameters.
+We find that Annealing offsets lift the problems degeneracy and non-trivially, resulting in different, offset-based final state distributions.
+The final state distribution gives us a very sensitive observable to tune the simulation temperature, and agrees well with the experimental operating temperature.
+For the simulation to reproduce the experiments final state distribution, effects of full-counting statistics are required.
+For fixed simulation parameters, scaling concerning offset from the simulation matches what is observed from the experiment, which provides evidence suggesting that the improvements are related to quantum mechanics.
+
+Analyzing the effects of both the decoherence model individually (Sec.~\ref{sec:methods:annealing-schedule}), we observe in both cases that the overall scaling follows the story of the MBL hypothesis.
+Perhaps more importantly, we observe that a simulation without local decoherence, where the relaxation is dependent on precisely the instantaneous value of the external magnetic field, exhibits the same scaling as the experiment.
+This result suggests that our strategy for setting annealing offsets is improving the algorithm beyond the simple explanation of qubits freezing due to single-particle amplitude damping.
+The simulation with only amplitude damping does not fully capture the results of the experiment.
+We observe hints of a phase transition concerning offset (which may be considered some measure of disorder) when dynamical thermalization effects are removed.
+This observation is a tantalizing and strong evidence for the inclusion of the full-counting statistics model.
+
+We want to emphasize that while the annealing offsets are motivated by the MBL hypothesis, and the results also follow those expectations, we do not have definitive proof that MBL plays a crucial role.
+The reason is because observations of MBL inevitably require the study of finite-size scaling~\cite{2015PhRvB..91h1103L}, and our current simulation, while being extremely thorough and explicit, is exponentially slow to evaluate, making evaluations of even $G(3)$ untenable.
 However, the intersection of time-dependent quantum mechanics and emergent phenomena~\cite{Goldenfeld:1992qy} is an exciting direction that is pertinent to adiabatic quantum computing.
-
-\ghissue{Conclusion}{20}
 
@@
 %----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Comment on ILP QUBO penalty term}
-\label{sec:methods:ilp-qubo-comments}
-%----------------------------------------------------------------------------------------
-
 The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:ilp-slack-bit-energy} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
@@
 Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
-
 %----------------------------------------------------------------------------------------
@@
 All authors contributed to the design of test cases.
-Calculations were performed on the D-Wave by Chang and K\"orber.
+Ostrowski guided the ILP problem selection and Humble guided D-Wave related efforts.
+Calculations on the D-Wave were performed  by Chang and K\"orber.
 Numerical simulations were performed by Chen, Chang, and K\"orber.

### 2020-09-14 paper/main.tex
Added back in accidentally removed section

@@
 
-As this mapping comes with a tunable parameter, such constraints can be lifted in a problem-specific manner to extend the applicability (Sec.~\ref{sec:methods:ILP-on-DWave}).
+As this mapping comes with a tunable parameter, such constraints can be lifted in a problem-specific manner to extend the applicability (Sec.~\ref{sec:methods:ilp-qubo-comments}).
 Furthermore, the same algorithm can be extended to quadratic constraint optimization problems (Sec.~\ref{sec:methods:ilp:quadratic}).
@@
 %----------------------------------------------------------------------------------------
+
+%----------------------------------------------------------------------------------------
+\subsubsection{Comment on ILP QUBO penalty term}
+\label{sec:methods:ilp-qubo-comments}
+%----------------------------------------------------------------------------------------
+
 The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:ilp-slack-bit-energy} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.

### 2020-09-16 paper/main.tex
ornl olcf acknowledgement

--- 2020-09-14 paper/main.tex
@@
 \usepackage{xcolor}
+\usepackage{enumitem}
 
@@
 \begin{document}
-\title{Integer Programming on Ising Spin-Glass}
+\title{Integer Programming from Quantum Annealing and Open Quantum Systems}
 
@@
 We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.
+This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer.
+In particular, the number of qubits required to solve MDS scales at worse as $n_V \log_2 n_V$ where $n_V$ is the number of vertices for a generic graph before minor embedding.
 Details of the mapping of ILP to MDS is given in Sec.~\ref{sec:methods:mds-qubo}.
-This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer.
-Additionally the MDS solution is known analytically, and contains both unique and degenerate solutions.
+
+For the graph $G(n)$ the MDS solution is known analytically, and contains both unique and degenerate solutions.
 In particular, the domination number for $G(n)$ is $\lceil n/3 \rceil$ while the number of MDS solutions for $n$ vertices is
@@
 Details of the master equation are given in Sec.~\ref{sec:methods:lindblad}.
+Implementation of the anneal schedule and annealing offsets for the simulation are discussed in Sec.~\ref{sec:methods:annealing-schedule}.
 
@@
 These values are consistent with the reported DWave operating temperature~\cite{dwave_temp} and coherence times for flux qubits~\cite{2003Sci...299.1869C}.
-Additional insights of the simulation are given in Sec.~\ref{sec:methods:simulation_details}.
+Additional insights of the simulation are given in Sec.~\ref{sec:discussion:time_evolution}.
 
@@
 We confirm that scaling with respect to offset from the simulation matches what is observed from experiment, and provides evidence suggesting that the improvements are related to quantum mechanics.
-An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets and effects of local damping are presented in Sec.~\ref{sec:methods:annealing-schedule}, and further supports this observation.
+An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets and effects of local damping are presented in Sec.~\ref{sec:discussion:idealqa}, and further supports this observation.
 
@@
 
-\ghissue{Decoherance study}{31}
+\section{Discussion}
+
+\subsection{Dynamics of Time Evolution}
+\label{sec:discussion:time_evolution}
+
+ The time-dependent overlap with the exact Ising ground state is shown in Fig.~\ref{fig:td_prob} from applying the simulator to $G(2)$.
+We observe for all cases that the system undergoes what is analogous to a magnetic phase transition around $s\sim 0.4$.
+After the phase transition, we are able to confirm that the system collapses to effectively a classical state in the sense that the density matrix becomes a diagonal matrix.
+The steady increase in probability after the phase transition is a sensitive balance between the competing effects between full-counting statistics and local damping.
+In our example, full-counting statistics is tuned to be slightly stronger, resulting in what amounts to a final thermal annealing step.
+If local damping is relatively stronger, then the probability after the phase transition will slowly decrease as the system decoheres into its local ground state.
+While we believe both effects are important in DWave, the experimental results are not precise enough for us to conclude which is the dominant effect.
+We emphasize however, that the simulation suggests that the ground state is recovered predominantly due to the quantum phase transition.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
+	\caption{Time-dependent probability for resolving the ground state for simulation results presented in Sec.~\ref{sec:results:simulation}.
+Different offsets are labeled in the same way as Fig.~\ref{fig:baseline}.}
+	\label{fig:td_prob}
+\end{figure}
+
+Finally, we comment that in order for the simulation to obtain the final state distribution shown in Fig.~\ref{fig:final_state_distribution}, effects of full-counting statistics are required.
+Absent some dynamical thermalization effect, the $G(2)$ problem is too small such that at a total annealing time of 1$\mu s$, the annealing offsets lift the ground state degeneracy by an amount such that diabatic transitions are absent, and the simulation is populated predominantly by the unique ground state.
+The final state distribution gives us a very sensitive observable to tune the simulation temperature, and agrees well with the experimental operating temperature.
+
+\subsection{Idealized Quantum Annealing}
+\label{sec:discussion:idealqa}
+
+\begin{figure*}
+    \centering
+	\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
+	\includegraphics[width=0.5\textwidth]{./new_figures/anneal_schedule_extended.pdf}
+    &
+	\includegraphics[width=0.5\textwidth]{./new_figures/NN2_offset_scaling_extended.pdf}\\
+	\centering \textbf{a} & \centering \textbf{b}
+	\end{tabular}
+	\centering
+	\caption{Extended annealing schedule and simulation result.
+\textbf{a)} The annealing time is increased by 10\% at both the start and end, and the initial values of $A(s)$ and $B(s)$ at non-zero offset are also not extrapolated in comparison to Fig.~\ref{fig:anneal_schedule}.
+Therefore, the initial and final Hamiltonian are no longer suffer systematic error at non-zero offset.
+\textbf{b)} The default (dashed yellow) result is one presented in Fig.~\ref{fig:dwave1us}.
+Results from extended schedules are presented shown with solid lines with full-counting statistics and amplitude damping (red), only full-counting-statistics (blue), and only amplitude damping (green).
+    }
+	\label{fig:anneal_schedule_ext}
+\end{figure*}
+
+In the simulation, we also reserve the ability to remove the systematic errors by extending the annealing schedule as shown by the red data points in Fig.~\ref{fig:anneal_schedule_ext}.
+With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians.
+The dependence on offset for $G(2)$ (Fig.~\ref{fig:dwave1us}) remains the same under the extended anneal schedule (Fig.~\ref{fig:anneal_schedule_ext}), confirming that the behavior is not a systematic artifact.
+
+The quantum system can be further idealized by including only the full-counting statistics model (blue), or local decoherence (green).
+We observe in both cases that the overall scaling follows the story of the MBL hypothesis.
+Perhaps more importantly, we observe that a simulation without local decoherence, where the relaxation is dependent on precisely the instantaneous value of $|h_i|$, exhibits the same scaling as experiment.
+This result suggests that our strategy for setting annealing offsets is improving the algorithm beyond the simple explanation of qubits freezing due to single-particle amplitude damping.
+In fact, the simulation with only amplitude damping (green) does not fully capture the results of the experiment.
+We observe hints of a phase transition with respect to offset (which may be thought of as some measure of disorder) when dynamical thermalization effects are removed.
+This is a tantalizing observation, and also is strong evidence for the inclusion of the full-counting statistics model.
+
+It unfortunately does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to unity.
 
@@
 However, the intersection of time-dependent quantum mechanics and emergent phenomena~\cite{Goldenfeld:1992qy} is an exciting direction that is pertinent to adiabatic quantum computing.
-
-\ghissue{Conclusion}{20}
 
@@
 
-\begin{figure*}
-    \centering
-	\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
-	\includegraphics[width=0.5\textwidth]{./new_figures/anneal_schedule_extended.pdf}
-    &
-	\includegraphics[width=0.5\textwidth]{./new_figures/NN2_offset_scaling_extended.pdf}\\
-	\centering \textbf{a} & \centering \textbf{b}
-	\end{tabular}
-	\centering
-	\caption{Extended annealing schedule and simulation result.
-\textbf{a)} The annealing time is increased by 10\% at both the start and end, and the initial values of $A(s)$ and $B(s)$ at non-zero offset are also not extrapolated in comparison to Fig.~\ref{fig:anneal_schedule}.
-Therefore, the initial and final Hamiltonian are no longer suffer systematic error at non-zero offset.
-\textbf{b)} The default (dashed yellow) result is one presented in Fig.~\ref{fig:dwave1us}.
-Results from extended schedules are presented shown with solid lines with full-counting statistics and amplitude damping (red), only full-counting-statistics (blue), and only amplitude damping (green).
-    }
-	\label{fig:anneal_schedule_ext}
-\end{figure*}
-
-In the simulation, we also reserve the ability to remove the systematic errors by extending the annealing schedule as shown by the red data points in Fig.~\ref{fig:anneal_schedule_ext}.
-With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians.
-The dependence on offset for $G(2)$ (Fig.~(\ref{fig:dwave1us})) remains the same under the extended anneal schedule (Fig.~\ref{fig:anneal_schedule_ext}), confirming that the behavior is not a systematic artifact.
-
-The quantum system can be further idealized by including only the full-counting statistics model (blue), or local decoherence (green).
-We observe in both cases that the overall scaling follows the story of the MBL hypothesis.
-Perhaps more importantly, we observe that a simulation without local decoherence, where the relaxation is dependent on precisely the instantaneous value of $|h_i|$, exhibits the same scaling as experiment.
-This result suggests that our strategy for setting annealing offsets is improving the algorithm beyond the simple explanation of qubits freezing due to single-particle amplitude damping.
-In fact, the simulation with only amplitude damping (green) does not fully capture the results of the experiment.
-We observe hints of a phase transition with respect to offset (which may be thought of as some measure of disorder) when dynamical thermalization effects are removed.
-This is a tantalizing observation, and also is strong evidence for the inclusion of the full-counting statistics model.
-
-It unfortunately does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to unity.
-
 %----------------------------------------------------------------------------------------
-\subsubsection{Other Simulation Details}
+\subsubsection{Pure Transverse Field Simulation}
 \label{sec:methods:simulation_details}
@@
 
-Next, the simulator is applied to the $G(2)$ problem and the result is summarized in Fig.~\ref{fig:td_prob} where the time-dependent overlap with the exact Ising ground state is shown.
-We observe for all cases that the system undergoes what is analogous to a magnetic phase transition around $s\sim 0.4$.
-After the phase transition, we are able to confirm that the system collapses to effectively a classical state in the sense that the density matrix becomes a diagonal matrix.
-The steady increase in probability after the phase transition is a sensitive balance between the competing effects between full-counting statistics and local damping.
-In our example, full-counting statistics is tuned to be slightly stronger, resulting in what amounts to a final thermal annealing step.
-If local damping is relatively stronger, then the probability after the phase transition will slowly decrease as the system decoheres into its local ground state.
-While we believe both effects are important in DWave, the experimental results are not precise enough for us to conclude which is the dominant effect.
-We emphasize however, that the simulation suggests that the ground state is recovered predominantly due to the quantum phase transition.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
-	\caption{Time-dependent probability for resolving the ground state for simulation results presented in Sec.~\ref{sec:results:simulation}.
-Different offsets are labeled in the same way as Fig.~\ref{fig:baseline}.}
-	\label{fig:td_prob}
-\end{figure}
-
-Finally, we comment that in order for the simulation to obtain the final state distribution shown in Fig.~\ref{fig:final_state_distribution}, effects of full-counting statistics are required.
-Absent some dynamical thermalization effect, the $G(2)$ problem is too small such that at a total annealing time of 1$\mu s$, the annealing offsets lift the ground state degeneracy by an amount such that diabatic transitions are absent, and the simulation is populated predominantly by the unique ground state.
-The final state distribution gives us a very sensitive observable to tune the simulation temperature, and agrees well with the experimental operating temperature.
-
 %========================================================================================
@@
 %========================================================================================
-We provide access to all the software utilized and data presented in this publication in the associated GitHub repository \cite{github:cchang5/quantum_linear_programming}.
+We provide access to all the software utilized and data presented in this publication in the associated GitHub repository~\cite{github:cchang5/quantum_linear_programming}.
 The utilized software is contained in two installable Python modules:
-\begin{itemize}
-    \item[\texttt{qlp}] for mapping MDS problems to QUBOs and perfoming simulations,
-    \item[\texttt{qlpdb}] for interfacing and documenting simulation and experiment data through EspressoDB \cite{Chang:2019khk}.
+\begin{itemize}[leftmargin=*]
+    \itemsep0em
+    \item[] \texttt{qlp} for mapping MDS problems to QUBOs and performing simulations,
+    \item[] \texttt{qlpdb} for interfacing and documenting simulation and experiment data through EspressoDB~\cite{Chang:2019khk}.
 \end{itemize}
 The data itself is stored in a SQLite file and associated repository subdirectories.
-We provide further documentation in the repository readme file.
+We provide further documentation in the repository \texttt{readme} file.
 
@@
 
-\ghissue{Acknowledgements}{22}
-
 We thank Long Gang Pang for initial discussions.
 We thank David Johnson, Vlad Papish and the rest of D-Wave Support for answering detailed questions about the D-Wave annealer.
+
+This material is based upon work supported by the U.S.
+Department of Energy, Office of Science, Office of Nuclear Physics, Quantum Horizons: QIS Research and Innovation for Nuclear Science under Award Number FWP-NQISCCAWL.
+Lawrence Berkeley National Laboratory (LBNL) is operated by The Regents of the University of California (UC) for the U.S. Department of Energy (DOE) under Federal Prime Agreement DE-AC02-05CH11231.
+This research used resources of the Oak Ridge Leadership Computing Facility at the Oak Ridge National Laboratory, which is supported by the Office of Science of the U.S.
+Department of Energy under Contract No.
+DE-AC05-00OR22725.
 C.K. gratefully acknowledges funding through the Alexander von Humboldt Foundation through a Feodor Lynen Research Fellowship.
@@
 Initial idea was proposed by Chang.
+Ostrowski guided the ILP problem selection.
 All authors contributed to the design of test cases.
-Calculations were performed on the D-Wave by Chang and K\"orber.
-Numerical simulations were performed by Chen, Chang, and K\"orber.
+Calculations and code development for the D-Wave were performed by Chang and K\"orber.
+Code for numerical simulations was developed by Chen and K\"orber, and cross-checked by Chang.
+Simulations were performed by Chang and Chen.
+Chang, Chen, K\"orber, and Humble interpreted the results.
 All authors contributed to writing and editing of the final manuscript.
@@
 \bibliography{qilp}
-\ghissue{References}{24}
 %========================================================================================

### 2020-09-23 paper/main.tex
im done

@@
 \author{Travis~Humble}
-\affiliation{Quantum Computing Institute, Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA}
 \affiliation{Computational Sciences and Engineering, Oak Ridge National Laboratory, Oak Ridge, Tennessee, 37831, USA}
@@
 
-ILP is a commonly tackled problem applicable to situations such as {\color{red} x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}}.
-In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~{\color{red}\cite{}}.
+ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the Minimum Dominating Set Problem (MDS).
+In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4}.
 Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
@@
 We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
-As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a well-studied problem for quantum annealers~{\color{red}\cite{}}.
+As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a well-studied problem for quantum annealers.
 
@@
 
-Due to the importance and difficulty in this work, we present a method to obtain optimal solutions to ILP by employing quantum annealing methods.
+We present a method to obtain optimal solutions to ILP by employing quantum annealing methods.
 
-Quantum annealing solves a general quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{1998PhRvE..58.5355K, 2000quant.ph..1106F, RevModPhys.80.1061}.
+Current implementations of quantum annealing solves the quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{1998PhRvE..58.5355K, 2000quant.ph..1106F, RevModPhys.80.1061}.
 Through the adiabatic theorem of quantum mechanics, the annealer is initially prepared in a trivial ground state while the final Hamiltonian encodes the solution to the ILP.
@@
 
-A quantum annealer evolves the ground state of an initial Hamiltonian into the problems Hamiltonian's ground state by adiabatically changing the hardware that implements Hamiltonian.
-Thus, the implemented Hamiltonian is explicitly time dependent
+In the simplest model for quantum annealing, the pure state of a quantum system evolves adiabatically to prepare an eigenstate of the encoded problem Hamiltonian.
+The time-dependent Hamiltonian is given as
 \begin{equation}
@@
 \end{equation}
-and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ encodes the problem to be solved.
+and $H^\textrm{init}=-\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ encodes the problem to be solved.
+In practice, and as discussed in Sec.~\ref{sec:methods:lindblad}, modeling dynamics that arise during quantum annealing requires a more robust description of the thermally populated mixed quantum states and the open dynamical processes that govern population of the sought-after eigenstate.
 
 In this paper, we propose an algorithm that maps ILP problems to QUBO.
-This is achieved by the introduction of slack variables $s$ which turn the inequalities Eq.~\eqref{eq:ilp-constraints} to equalities
+This is achieved by the introduction of slack variables $s_a$ which turns the inequalities Eq.~\eqref{eq:ilp-constraints} to equalities
 \begin{align}
@@
 
-We further improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}.
+We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}.
 Converting to the Ising representation of the the problem Hamiltonian,
@@
 \end{equation}
-we can recognize that Eq.~(\ref{eq:HIsing}) exhibits spin-glass properties.
+we recognize that Eq.~(\ref{eq:HIsing}) exhibits spin-glass properties.
 More specifically, if the $h_i$ coefficients are randomly drawn from a Bernoulli distribution, one expects spin-localization behavior to influence the outcome of the anneal.
@@
 Our improvement strategy is motivated by the MBL hypothesis.
-That is, we want the system to be ergodic and avoid the MBL phase.
 As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.
@@
 Lawrence Berkeley National Laboratory (LBNL) is operated by The Regents of the University of California (UC) for the U.S. Department of Energy (DOE) under Federal Prime Agreement DE-AC02-05CH11231.
-This research used resources of the Oak Ridge Leadership Computing Facility at the Oak Ridge National Laboratory, which is supported by the Office of Science of the U.S.
-Department of Energy under Contract No.
-DE-AC05-00OR22725.
 C.K. gratefully acknowledges funding through the Alexander von Humboldt Foundation through a Feodor Lynen Research Fellowship.
+This work used resources of the Oak Ridge Leadership Computing Facility, which is a DOE Office of Science User Facility supported under Contract DE-AC05-00OR22725.
+This manuscript has been authored by UT-Battelle, LLC under Contract No. DE-AC05-00OR22725 with the U.S. Department of Energy.
+The United States Government retains and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a non-exclusive, paid-up, irrevocable, world-wide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes.
+The Department of Energy will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan.
+(http://energy.gov/downloads/doe-public-access-plan).
 

### 2020-09-23 paper/main.tex
Abstract

@@
  For this reason, we developed an algorithm that solves integer linear programming problems, a classically NP-hard problem, on a quantum annealer, and investigated problem and hardware-specific limitations.
- This work presents the formalism of how to map ILP problems to the annealing architectures, how to systematically improve computations utilizing optimized anneal schedules and models the anneal process through a simulation.
- It illustrates the effects of decoherence and Many-Body Localization, for the Minimum Dominating Set problem, and compares annealing results against numerical simulations of the quantum architecture.
+ This work presents the formalism of how to map ILP problems to the annealing architectures, how to systematically improve computations utilizing optimized anneal schedules, and models the anneal process through a simulation.
+ It illustrates the effects of decoherence and Many-Body Localization for the Minimum Dominating Set problem, and compares annealing results against numerical simulations of the quantum architecture.
  We find that the algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decoherence.

### 2020-09-23 paper/main.tex
Intro phrasing

@@
 %========================================================================================
-
 Integer Linear Programming (ILP) is an integer optimization problem subject to inequality constraints
@@
 We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
-As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a well-studied problem for quantum annealers.
+As a result, the solution to the dominating set problem can not be obtained by solving the maximum independent set problem, a well-studied problem for quantum annealers.
 
@@
 Our improvement strategy is motivated by the MBL hypothesis.
-As a result, we employ a modified annealing schedule which relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.
+As a result, we employ a modified annealing schedule that relies on partitioning the Hamiltonian into regions of relatively weak and strong external magnetic fields.
 
 To understand which phenomena are relevant for describing the proposed offset study's scaling behavior, whether they are rooted in the quantum nature or related to hardware constraints, we simulate the anneal for a small MDS problem.
-This simulation solves the von Neumann equations accounting for different models of quantum decoherence, and explores whether algorithmic improvements on hardware are present in idealizes systems.
+This simulation solves the von Neumann equations accounting for different quantum decoherence models and explores whether algorithmic improvements on hardware are present in idealized systems.
 

### 2020-09-23 paper/main.tex
DWave -> D-Wave

@@
 In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4}.
-Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
+Standard classical heuristic algorithms follow a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
 The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem can be obtained in polynomial time, the optimal integer solution in general must be found in the $2^n$ integer solutions which surround the real number solution.
@@
 
-We present a method to obtain optimal solutions to ILP by employing quantum annealing methods.
+In this work, we present a method to obtain optimal solutions to ILP by employing quantum annealing methods.
 
-Current implementations of quantum annealing solves the quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{1998PhRvE..58.5355K, 2000quant.ph..1106F, RevModPhys.80.1061}.
+Current implementations of quantum annealing solve the quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{1998PhRvE..58.5355K, 2000quant.ph..1106F, RevModPhys.80.1061}.
 Through the adiabatic theorem of quantum mechanics, the annealer is initially prepared in a trivial ground state while the final Hamiltonian encodes the solution to the ILP.
@@
 \end{equation}
-and $H^\textrm{init}=-\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ encodes the problem to be solved.
+and $H^\textrm{init}=-\sum_i\sigma^x_i$ (on the D-Wave), while $H^\textrm{problem}$ encodes the problem to be solved.
 In practice, and as discussed in Sec.~\ref{sec:methods:lindblad}, modeling dynamics that arise during quantum annealing requires a more robust description of the thermally populated mixed quantum states and the open dynamical processes that govern population of the sought-after eigenstate.
 
-In this paper, we propose an algorithm that maps ILP problems to QUBO.
-This is achieved by the introduction of slack variables $s_a$ which turns the inequalities Eq.~\eqref{eq:ilp-constraints} to equalities
+The mapping of ILPs to QUBOs we propose is realized by introducing slack variables $s_a$ which turn the inequalities Eq.~\eqref{eq:ilp-constraints} to equalities
 \begin{align}
@@
 \end{align}
-While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+While, in general, the coefficients of the inequality constraints are not required to be integer valued, this real valued inequalities can be trivially rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
 Furthermore, this formalism can be generalized to constrained quadratic optimizations \ref{sec:methods:ilp:quadratic}.
@@
 
-We first present the QUBO mapping for ILP (\ref{sec:results:qa1}), and demonstrate the methodology on an example implementation in case of the Minimal Dominating Set problem (\ref{sec:results:qa}) on the DWave quantum annealer.
+We first present the QUBO mapping for ILP (\ref{sec:results:qa1}), and demonstrate the methodology on an example implementation in case of the Minimal Dominating Set problem (\ref{sec:results:qa}) on the D-Wave quantum annealer.
 Results from quantum annealing are compared and discussed in contrast to simulations (\ref{sec:results:simulation}).
@@
 We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.
-This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a DWave quantum annealer.
+This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a D-Wave quantum annealer.
 In particular, the number of qubits required to solve MDS scales at worse as $n_V \log_2 n_V$ where $n_V$ is the number of vertices for a generic graph before minor embedding.
@@
 The annealing time is set to 500$\mu$s after performing a study on various annealing times the $G(6)$ graph.
-The black line (offset$=0.0$) in Fig.~\ref{fig:baseline} shows results from the baseline experiment, without modification to the DWave annealing schedule, and observe improvement over random guessing (blue).
+The black line (offset$=0.0$) in Fig.~\ref{fig:baseline} shows results from the baseline experiment, without modification to the D-Wave annealing schedule, and observe improvement over random guessing (blue).
 
@@
 	\includegraphics[width=\columnwidth]{./new_figures/DWave_scaling.pdf}
-	\caption{Baseline result of DWave (black) compared to random guessing (dashed green).
+	\caption{Baseline result of D-Wave (black) compared to random guessing (dashed green).
 The jagged nature of random guessing reflects the degeneracy of the ground state.
@@
 	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
-	\caption{The probability of finding the MDS for $G(2)$ from DWave (black) and simulation (dashed yellow) at annealing times of 1 $\mu s$.}
+	\caption{The probability of finding the MDS for $G(2)$ from D-Wave (black) and simulation (dashed yellow) at annealing times of 1 $\mu s$.}
 	\label{fig:dwave1us}
@@
 Within the broken symmetry, the non-degenerate ground state switches between the two states depending on which qubit group is delayed.
-At zero offset, a slight asymmetry exists in the simulation because the Hamiltonian is only degenerate at the last moment, while the DWave is also subject to sampling bias~\cite{2016PhRvA..93e2320K, 2017PhRvL.118g0502M}.
+At zero offset, a slight asymmetry exists in the simulation because the Hamiltonian is only degenerate at the last moment, while the D-Wave is also subject to sampling bias~\cite{2016PhRvA..93e2320K, 2017PhRvL.118g0502M}.
 
 This result can be obtained by tuning three free parameters: the simulation temperature to the order of 10 milliKelvin, and the two coefficients of the two decoherence models at the order of 1 to 10 $ns$.
-These values are consistent with the reported DWave operating temperature~\cite{dwave_temp} and coherence times for flux qubits~\cite{2003Sci...299.1869C}.
+These values are consistent with the reported D-Wave operating temperature~\cite{dwave_temp} and coherence times for flux qubits~\cite{2003Sci...299.1869C}.
 Additional insights of the simulation are given in Sec.~\ref{sec:discussion:time_evolution}.
@@
 	\includegraphics[width=\columnwidth]{./new_figures/final_state_distribution.pdf}
-	\caption{Final state distribution from DWave (solid bars) and simulation (black outline).
+	\caption{Final state distribution from D-Wave (solid bars) and simulation (black outline).
 The colors label the type of offset  The $(0, 1, 0, 0, 0)$ state is the first solution where vertex 1 is in the dominating set.
@@
 If local damping is relatively stronger, then the probability after the phase transition will slowly decrease as the system decoheres into its local ground state.
-While we believe both effects are important in DWave, the experimental results are not precise enough for us to conclude which is the dominant effect.
+While we believe both effects are important in D-Wave, the experimental results are not precise enough for us to conclude which is the dominant effect.
 We emphasize however, that the simulation suggests that the ground state is recovered predominantly due to the quantum phase transition.
@@
 %----------------------------------------------------------------------------------------
-\subsection{ILP on the DWave}
-\label{sec:methods:ILP-on-DWave}
+\subsection{ILP on the D-Wave}
+\label{sec:methods:ILP-on-D-Wave}
 %----------------------------------------------------------------------------------------
@@
 As a result, details of the embedding are important.
-We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the DWave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module~\cite{2008arXiv0804.4884C}.
-The same embedding is used for all DWave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
+We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the D-Wave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module~\cite{2008arXiv0804.4884C}.
+The same embedding is used for all D-Wave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
 Additionally, solving the same graph as a function of offset on the exact same qubits removes (or at least keeps consistent) the systematic effects due to solving a problem on different physical qubits.
@@
 After embedding the QUBO for $G(2)$ requires 5 qubits (an increase from 4), where by construction, qubits 0 and 3 form the qubit chain.
-We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by DWave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the minimum dominating set.
+We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by D-Wave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the minimum dominating set.
 
@@
 In this section, we discuss the details of the annealing schedule with respect to the dimensionless normalized time $s$.
-On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
-In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
-Further documentation is provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.
+On D-Wave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
+In Fig.~\ref{fig:anneal_schedule}, the default D-Wave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
+Further documentation is provided by D-Wave in Ref.~\cite{dwave_as, dwave_as_docu}.
 
@@
 
-We verify that our implementation of annealing offsets on the simulator is consistent with DWave by solving the following three qubit Hamiltonian
+We verify that our implementation of annealing offsets on the simulator is consistent with D-Wave by solving the following three qubit Hamiltonian
 \begin{align}
@@
 
-We confirm that with different combinations of annealing offsets, the degeneracy is lifted on the DWave results as expected by solving for the modified problem Hamiltonian spectrum, as well as dialing in annealing offset in the simulation of this three qubit test case.
+We confirm that with different combinations of annealing offsets, the degeneracy is lifted on the D-Wave results as expected by solving for the modified problem Hamiltonian spectrum, as well as dialing in annealing offset in the simulation of this three qubit test case.
 

### 2020-09-23 paper/main.tex
Fix typo in master eqn

@@
 
-We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delays the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}.
+We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delay the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}.
 Converting to the Ising representation of the the problem Hamiltonian,
@@
     \label{eq:HIsing}
-     H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i ,
+     H^{\textrm{problem}} \leftrightarrow H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i ,
 \end{equation}
@@
  &=
- \vec c^T T_x \vec \Psi_x + p \left\| A T_s \vec \Psi_x + T_s \vec \Psi_s + \vec b \right\|^2
+ \vec c^T T_x \vec \Psi_x + p \left\| A T_x \vec \Psi_x + T_s \vec \Psi_s + \vec b \right\|^2
 \end{align}

### 2020-09-23 paper/main.tex
Updated plot reference

@@
 The integer solution to the original ILP is computed by $\vec x^{(0)} = T_x \vec \Psi_x^{(0)}$ and the original solution to the problem is computed by shifting the annealer extracted energy $E \equiv  \chi^2(\vec \Psi^{(0)}) $ by $p \left \| \vec b \right\|^2$.
-The slack components of this vector $\vec \Psi_s$ can be utilized to check if the contraints are indeed fulfilled.
+The slack components of this vector $\vec \Psi_s$ can be utilized to check if the constraints are indeed fulfilled.
 
@@
 The annealing time is set to 500$\mu$s after performing a study on various annealing times the $G(6)$ graph.
-The black line (offset$=0.0$) in Fig.~\ref{fig:baseline} shows results from the baseline experiment, without modification to the D-Wave annealing schedule, and observe improvement over random guessing (blue).
+The black line (offset$=0.0$) in Fig.~\ref{fig:baseline} shows results from the baseline experiment, without modification to the D-Wave annealing schedule, and observe improvement over random guessing (dashed green).
 

### 2020-09-23 paper/main.tex
Results edits

@@
 \begin{equation}
+    \label{eq:bit-vector-mapping}
     \begin{pmatrix}
@@
 %----------------------------------------------------------------------------------------
-\subsection{Application to the Dominating Set}
+\subsection{Annealer Results for the Dominating Set}
 \label{sec:results:qa}
@@
 
-We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$ as shown in Fig.~\ref{fig:linear}.
-This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph allowing for scaling plots to be generated when using a D-Wave quantum annealer.
+We demonstrate the proposed algorithm in order to obtain the MDS on a series of linear graphs $G(n)$, as shown in Fig.~\ref{fig:linear}.
+This type of graph is chosen because the small number of nearest-neighbor connections is more efficiently embedded into the chimera graph, allowing scaling plots to be generated when using a D-Wave quantum annealer.
 In particular, the number of qubits required to solve MDS scales at worse as $n_V \log_2 n_V$ where $n_V$ is the number of vertices for a generic graph before minor embedding.
@@
 For even the smallest graph $G(2)$, the MDS problem is not native to the chimera graph and must be embedded.
-Following the hypothesis of MBL, we therefore, must look at the values of $h_i$ after embedding.
-The qubits then split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| + \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding.
+Following the hypothesis of MBL, we, therefore, must look at the values of $h_i$ after embedding.
+The qubits split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| + \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding.
 Further detail is given in Sec.~\ref{sec:methods:minor_embedding}.
@@
 We explore one avenue towards improving the experiment results by introducing per-qubit annealing offsets into the time evolution.
-The results in yellow (green) delays the annealing of qubits subject to stronger (weaker) external fields.
-We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the anneal schedule, in agreement with the MBL hypothesis.
+The blue (red) results delay qubits' annealing subject to stronger (weaker) external fields.
+We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the annealing schedule, in agreement with the MBL hypothesis.
 The phenomena is observed across different problem sizes and hints at the possibility of a generic improvement strategy.
@@
 \label{sec:results:simulation}
-In order to understand the effects of annealing offsets, we simulate the annealing process for the $G(2)$ graph embedded in chimera topography.
-In order to shorten the simulation time, we repeat the same anneal process with a total annealing time of 1 $\mu s$ and count the number of correct ground state occurances.
+To understand the effects of annealing offsets, we simulate the annealing process for the $G(2)$ graph embedded in chimera topography.
+We repeat the same anneal process with a shortend total annealing time of 1 $\mu s$, reducing the computational demands of the simulation, and count the number of correct ground state occurrences.
 The resulting ground state probability as a function of offset measured over 100,000 observations is shown in Fig.~\ref{fig:dwave1us}.
@@
 Details of the master equation are given in Sec.~\ref{sec:methods:lindblad}.
-Implementation of the anneal schedule and annealing offsets for the simulation are discussed in Sec.~\ref{sec:methods:annealing-schedule}.
+Implementation of the annealing schedule and annealing offsets for the simulation are discussed in Sec.~\ref{sec:methods:annealing-schedule}.
 
-The graph $G(2)$ has the interesting feature of having a degenerate ground state depending on whether qubit 0 or 1 is chosen to be the MDS solution.
+The graph $G(2)$ has degenerate ground states depending on whether qubit 0 or 1 is chosen to be the MDS solution.
 This degeneracy is reflected in the experimental result and provides a non-trivial benchmark for our simulation.
-Fig.~\ref{fig:final_state_distribution} show the final state distribution of the three lowest lying state.
-The states $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ are the two degenerate ground states of the embedded Hamiltonian, while $(1, 1, 1, 1, 1)$ is the first excited state which yields an incorrect solution.
+Fig.~\ref{fig:final_state_distribution} show the final state distribution of the three lowest-lying state.
+The states $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ are the two degenerate ground states of the embedded Hamiltonian, while $(1, 1, 1, 1, 1)$ is the first excited state which yields an incorrect solution\footnote{According to Eq.~\eqref{eq:bit-vector-mapping}, the first two vector components represent the nodes of the graph while the following components represent the slack variables after embedding.}.
 All other states receive negligible probability at the end of annealing.
-The simulation (black) captures main features of the experimental result: 1) significant probability to populate both ground states (rather than populating only one), 2) asymmetry in ground state population due to systematic effects of offset lifting the final state degeneracy spanning approximately the correct range, 3) population of first excited state with systematically lower probability when the strong field is delayed.
-The asymmetry in the ground state distribution at non-zero offset is a result of annealing offsets lifting the ground state degeneracy.
-Within the broken symmetry, the non-degenerate ground state switches between the two states depending on which qubit group is delayed.
+The simulation (black) captures the main features of the experimental result:
+\begin{enumerate}
+    \item Significant probability of populating both ground states (rather than populating only one)
+    \item Asymmetry in ground state population due to offsets and spanning approximately the correct range
+    \item Population of first excited state with systematically lower probability when the strong field is delayed
+\end{enumerate}
+The asymmetry in the ground state distribution at non-zero offset results from annealing offsets lifting the ground state degeneracy.
+The non-degenerate ground state switches between the two states within the broken symmetry, depending on which qubit group is delayed.
 At zero offset, a slight asymmetry exists in the simulation because the Hamiltonian is only degenerate at the last moment, while the D-Wave is also subject to sampling bias~\cite{2016PhRvA..93e2320K, 2017PhRvL.118g0502M}.
@@
 The resulting probability of recovering the correct solution as a function of annealing offset is given in Fig.~\ref{fig:dwave1us}.
-We confirm that scaling with respect to offset from the simulation matches what is observed from experiment, and provides evidence suggesting that the improvements are related to quantum mechanics.
-An additional study where an extended annealing schedule is employed in the simulation which removes systematic errors introduced by annealing offsets and effects of local damping are presented in Sec.~\ref{sec:discussion:idealqa}, and further supports this observation.
+We confirm that the simulation's offset-scaling follows the experiment's scaling, which suggests that the improvements are related to quantum mechanics.
+An additional study where an extended annealing schedule is employed in the simulation, which removes systematic errors introduced by annealing offsets and effects of local damping are presented in Sec.~\ref{sec:discussion:idealqa}, and further supports this observation.
 

### 2020-09-23 paper/main.tex
First discussion draft

@@
 \section{Discussion}
-
 \subsection{Dynamics of Time Evolution}
@@
 We observe for all cases that the system undergoes what is analogous to a magnetic phase transition around $s\sim 0.4$.
-After the phase transition, we are able to confirm that the system collapses to effectively a classical state in the sense that the density matrix becomes a diagonal matrix.
+After the phase transition, we can confirm that the system collapses to effectively a classical state in the sense that the density matrix becomes a diagonal matrix.
 The steady increase in probability after the phase transition is a sensitive balance between the competing effects between full-counting statistics and local damping.
-In our example, full-counting statistics is tuned to be slightly stronger, resulting in what amounts to a final thermal annealing step.
-If local damping is relatively stronger, then the probability after the phase transition will slowly decrease as the system decoheres into its local ground state.
-While we believe both effects are important in D-Wave, the experimental results are not precise enough for us to conclude which is the dominant effect.
-We emphasize however, that the simulation suggests that the ground state is recovered predominantly due to the quantum phase transition.
+In our example, the full-counting statistics decoherance rate is tuned to be slightly stronger compared to the local dampening decoherance rate, effectively resulting in a final thermal annealing process after the phase transition.
+If local damping were relatively larger, then the probability after the phase transition will slowly decrease as the system decoheres into its local ground state.
+While we believe both effects are essential to simulate D-Wave, due to the competing effects of both decoherence models, we emphasize that a fully quantitative comparison of both decoherence models cannot be made just considering the $G(2)$ graph.
+However, we emphasize that the simulation suggests that the ground state is recovered predominantly due to the quantum phase transition happing around $s\sim 0.4$.
 
@@
 
-Finally, we comment that in order for the simulation to obtain the final state distribution shown in Fig.~\ref{fig:final_state_distribution}, effects of full-counting statistics are required.
-Absent some dynamical thermalization effect, the $G(2)$ problem is too small such that at a total annealing time of 1$\mu s$, the annealing offsets lift the ground state degeneracy by an amount such that diabatic transitions are absent, and the simulation is populated predominantly by the unique ground state.
-The final state distribution gives us a very sensitive observable to tune the simulation temperature, and agrees well with the experimental operating temperature.
+Finally, we comment that effects of full-counting statistics are required for the simulation to obtain the final state distribution shown in Fig.~\ref{fig:final_state_distribution}.
+Because of the smallness of the $G(2)$ problem (and the utilized total annealing time of 1$\mu s$), the annealing offsets lift the ground state degeneracy in a manor that diabatic transitions do not occur--setting a discrete, fixed groundstate probability for given offsets.
+Thus, if dynamical thermalization effects were absent, the simulation would populate predominantly one of the two unique ground states depending on the offsets.
+Once dynamical thermalization effects are present, the final state distribution  continously depends on offsets and becomes a very sensitive observable to tune the simulation temperature, which, if properly tuned, agrees well with the experimental operating temperature.
 
@@
 
-In the simulation, we also reserve the ability to remove the systematic errors by extending the annealing schedule as shown by the red data points in Fig.~\ref{fig:anneal_schedule_ext}.
+In the simulation, we also reserve the ability to remove the systematic errors by extending the annealing schedule, as shown by the red data points in Fig.~\ref{fig:anneal_schedule_ext}.
 With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians.
@@
 
-The quantum system can be further idealized by including only the full-counting statistics model (blue), or local decoherence (green).
+The quantum system can be further idealized by including either the full-counting statistics model (blue) or the local decoherence model (green) solely.
 We observe in both cases that the overall scaling follows the story of the MBL hypothesis.
-Perhaps more importantly, we observe that a simulation without local decoherence, where the relaxation is dependent on precisely the instantaneous value of $|h_i|$, exhibits the same scaling as experiment.
+Perhaps more importantly, we observe that a simulation without local decoherence, where the relaxation is dependent on precisely the instantaneous value of $|h_i|$, exhibits the same scaling as the experiment.
 This result suggests that our strategy for setting annealing offsets is improving the algorithm beyond the simple explanation of qubits freezing due to single-particle amplitude damping.
-In fact, the simulation with only amplitude damping (green) does not fully capture the results of the experiment.
-We observe hints of a phase transition with respect to offset (which may be thought of as some measure of disorder) when dynamical thermalization effects are removed.
-This is a tantalizing observation, and also is strong evidence for the inclusion of the full-counting statistics model.
+The simulation with only amplitude damping (green) does not fully capture the results of the experiment.
+We observe hints of a phase transition depending on the offset (which may be considered some measure of disorder) when dynamical thermalization effects are removed.
+This dependence is a tantalizing observation and strong evidence for the inclusion of the full-counting statistics model.
 
-It unfortunately does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to unity.
+Unfortunately, it does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to unity.
 
@@
 \label{sec:results:final}
-We would like to emphasize that while the annealing offsets are motivated by the MBL hypothesis, and the results also follow those expectations, we do not have definitive proof that MBL plays a crucial role.
-The reason is because observations of MBL inevitably require the study of finite-size scaling~\cite{2015PhRvB..91h1103L}, and our current simulation while being extremely thorough and explicit, is exponentially slow to evaluate making evaluations of even $G(3)$ untenable.
+We want to emphasize that while the annealing offsets are motivated by the MBL hypothesis, and the results also follow those expectations, we do not have definitive proof that MBL plays a crucial role.
+The reason is because observations of MBL inevitably require the study of finite-size scaling~\cite{2015PhRvB..91h1103L}, and our current simulation, while being extremely thorough and explicit, is exponentially slow to evaluate, making evaluations of even $G(3)$ untenable.
 However, the intersection of time-dependent quantum mechanics and emergent phenomena~\cite{Goldenfeld:1992qy} is an exciting direction that is pertinent to adiabatic quantum computing.

### 2020-09-23 paper/main.tex
Further conclusion updates

@@
 
-In the simulation, we also reserve the ability to remove the systematic errors by extending the annealing schedule, as shown by the red data points in Fig.~\ref{fig:anneal_schedule_ext}.
+In the simulation, we also reserve the ability to remove systematic errors associated with finite annealing schedules by extending them, as shown by the red data points in Fig.~\ref{fig:anneal_schedule_ext}.
 With the extended schedule, all qubits start and end with the same values of $A$ and $B$ and faithfully preserves the initial and final Hamiltonians.
@@
 
-The quantum system can be further idealized by including either the full-counting statistics model (blue) or the local decoherence model (green) solely.
+The quantum system can be further idealized by including either solely the full-counting statistics model (blue) or solely the local decoherence model (green)\footnote{For problems without diabatic transitions, like the MDS problem for a $G(2)$ graph and an anneal time of $1\mu s$, removing all decoherence models results in ground state probabilities equal to unity.}.
 We observe in both cases that the overall scaling follows the story of the MBL hypothesis.
@@
 We observe hints of a phase transition depending on the offset (which may be considered some measure of disorder) when dynamical thermalization effects are removed.
-This dependence is a tantalizing observation and strong evidence for the inclusion of the full-counting statistics model.
-
-Unfortunately, it does not make much sense to remove all decoherence models for the $G(2)$ graph for an anneal time of $1\mu s$ since all probabilities go to unity.
+This observation is a strong evidence for the inclusion of the full-counting statistics model.
 
@@
 We want to emphasize that while the annealing offsets are motivated by the MBL hypothesis, and the results also follow those expectations, we do not have definitive proof that MBL plays a crucial role.
-The reason is because observations of MBL inevitably require the study of finite-size scaling~\cite{2015PhRvB..91h1103L}, and our current simulation, while being extremely thorough and explicit, is exponentially slow to evaluate, making evaluations of even $G(3)$ untenable.
+Observations of MBL inevitably require the study of finite-size scaling~\cite{2015PhRvB..91h1103L}, and our current simulation, while being extremely thorough and explicit, is exponentially slow to evaluate, making evaluations of even $G(3)$ unfeasible.
 However, the intersection of time-dependent quantum mechanics and emergent phenomena~\cite{Goldenfeld:1992qy} is an exciting direction that is pertinent to adiabatic quantum computing.

### 2020-09-23 paper/main.tex
Updated equations to match main section and cross-checked with code

@@
 \end{equation}
-which is related to the qubit vector $\vec \Psi_s$ by $\vec s = T_s \vec \Psi_s$, to encode the inequality constraint such that
+which is related to the qubit vector $\vec \Psi_s$ by $\vec s = T_s \vec \Psi_s$.
+The inequality constraint is encoded by
 \begin{align}
@@
  &
- \vec \Psi_x + J \vec \Psi_x - T_s \Psi_s  - \vec 1 = 0\,,
+ (\mathbbm{1} + J)\vec \Psi_x - T_s \Psi_s  - \vec 1 = 0\,,
  \\
@@
 \end{align}
-where the nearest-neighbor sum is expressed by $J$ (zero diagonal and symmetric for non-directional graphs), the adjacency matrix for $G$.
+where the nearest-neighbor sum is expressed by the adjacency matrix $J$ (zero diagonal and symmetric for non-directional graphs).
 The algorithm uses
@@
 \end{equation}
-qubits to encode the vertices and to embed the slack variables.
+qubits to encode the vertices and slack variables before embedding.
 Therefore, the (logical) qubit vector $\vec \Psi$ at worst scales with $n_V \log_2 n_V$ qubits for fully connected graphs.
@@
   \begin{align}
-   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - 2 \mathrm{diag}(|J|) - \mathbbm{1} \right] \,, \\
-   Q_{sx} & = - p(\mathbbm{1}+J^T)T_s\,,                                                                     \\
-   Q_{ss} & = p\left[{T_s}^T T_s + 2\mathrm{diag}(|T_s|)\right]\,,                                  \\
-   C      & =  p \overline{\overline{V}}\,,
+   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - \mathrm{diag}\left(J^T \vec 1 + \vec 1^T J\right) - \mathbbm{1} \right] \,, \\
+   Q_{sx} & = - p(\mathbbm{1}+J)^TT_s\,,                                                                     \\
+   Q_{ss} & = p\left[{T_s}^T T_s + \mathrm{diag}\left(T_s^T \vec 1 + \vec 1^T  T_s\right)\right]\,,                                  \\
+   C      & =  p \overline{\overline{V}}\,.
   \end{align}}
-where $ |M| \equiv \sum_{\nu} M_{\nu \mu}$.
 

### 2020-09-23 paper/main.tex
Updated Linblad eq indices and final discussion

@@
 \begin{align}
+ \label{eq:sim:linblad-eq}
  \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}(\rho(t), H(t))
@@
 
-The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:ilp-slack-bit-energy} are exactly the same if the penalty term is larger than the energy gap of the first excited solution: $p > E_1 - E_0$.
+The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:ilp-slack-bit-energy} are exactly the same if the penalty term is greater or equal to the energy gap of the first excited solution: $p \geq E_1 - E_0$.
 Thus some knowledge of the problem is required.
-In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values of For $p$ increase the highest available energy of the system by multiples of $p$.
+In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values for $p$ increase the highest available energy of the system by multiples of $p$.
 After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
@@
 
-To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we evaluate the master equation in Lindblad form
-\begin{align}
- \partial_t \rho (t) = &  \frac{-i}{\hbar} \left[H(t) , \rho(t)\right] \nonumber \\
- & + \sum_j \left(2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}\right) ,
-\end{align}
-where $\rho (t)$ is the density matrix at time $t$.
-$H(t)$ is the time-dependent Hamiltonian
+To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we evaluate the master equation Eq.~\eqref{eq:sim:linblad-eq} in Lindblad form.
+The explicit time-dependence of the Hamiltonian is given by
 \begin{align}
  \label{eq:annealH}
- H_{anneal}(t)  = & - \sum_i  A_i(t)\sigma^x_i +\sum_i B_{i}(t) h_i \sigma^z_i \notag \\
+ H(t)  = & - \sum_i  A_i(t)\sigma^x_i +\sum_i B_{i}(t) h_i \sigma^z_i \notag \\
  & + \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j  ,
@@
 where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
-The site dependency takes into account of the annealing offset.
-$[,]$ denotes the Lie bracket.
-$L_j$ are the Lindblad operators for decoherence.
-$\{, \}$ denotes the anti-commutator.
+The site dependency takes into account of the annealing offsets.
+The simulation takes two decoherance models into account.
+Full-counting statistics and local decoherence.
 
@@
 \begin{align}
-\mathcal{L}[\rho (t)] = & \Gamma_{\textrm{fc}} \sum_j   \left(2 S_j \rho(t) S_j^\dagger - \{ S^\dagger_j S_j, \rho(t) \}\right) \notag \\
-& + e^{-\beta \Delta E_j} \left(2 S_j^\dagger \rho(t) S_j - \{ S_j S^\dagger_j, \rho(t) \} \right)
+\mathcal{L}_{\textrm{fc}}(\rho (t), H(t)) = & \Gamma_{\textrm{fc}} \sum_{j, i<j} \left[  \left(2 S_{ij} \rho(t) S_{ij}^\dagger - \{ S^\dagger_{ij} S_{ij}, \rho(t) \}\right) \notag \right.
+\\
+& \left. + e^{-\beta \Delta E_{ij}} \left(2 S_{ij}^\dagger \rho(t) S_{ij} - \{ S_{ij} S^\dagger_{ij}, \rho(t) \} \right)\right]
 \end{align}
-where $j$ is the index for the inter-level spacing $\Delta E_j=E_\mu-E_\nu>0$. $S_j=|E_\nu \rangle \langle E_\mu|$ denotes the many-body lowering operator.
-$\{, \}$ denotes the anti-commutator. $\Gamma = 1/T_c$ is the decoherence rate for coherence time $T_c$.
+where $\{, \}$ denotes the anti-commutator, $(ij)$ is the index for the inter-level spacing $\Delta E_{ij}=E_j-E_i>0$,  $S_{ij}=|E_i \rangle \langle E_j|$ denotes the many-body lowering operator and $\Gamma_{fc} = 1/T_{fc}$ is the full-counting decoherence rate for coherence time $T_{fc}$.
 That is, due to the interaction with the classical thermal bath, there is a probability that the system hops from each higher-energy many-body state to a lower-energy many-body state.
 The probability of the inverse process is given by a Boltzmann factor.
+
 To model the local decoherence of each qubits in the non-interacting limit, we also consider the amplitude damping for non-interacting qubits.
-The Lindblad operator is
+For the local decoherance model, the Lindblad operator is
 \begin{align}
-\mathcal{L}[\rho (t)] = &  \Gamma_{\textrm{loc}} \sum_j \left(2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \right)\notag \\
+\mathcal{L}_{\textrm{loc}}(\rho (t), H(t)) = &  \Gamma_{\textrm{loc}} \sum_j \left(2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \right)\notag \\
 & + e^{- 2 \beta |h_j| }  \left(2L_j^\dagger \rho(t) L_j - \{ L_j L_j^\dagger, \rho(t) \} \right) ,
@@
 In this section, we discuss the details of the annealing schedule with respect to the dimensionless normalized time $s$.
-On D-Wave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
+On D-Wave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits (see E.~\eqref{eq:annealH}).
 In Fig.~\ref{fig:anneal_schedule}, the default D-Wave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
@@
 
-The coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
+The coefficients $A(s)$ and $B(s)$ follow the underlying control variable $c(s)$, which is designed to grow the persistent current $I_p(s)$ linearly in time.
 The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
-As a result, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
+Because annealing schedules are finite, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
 Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
-We extrapolate their values by a linear extrapolation, and only employ negative offsets such that this effect only enters at the beginning of the annealing process rather than the end.
+We only employ negative offsets such that this unkonwn coefficient range, approximated by a linear extrapolation, only enters at the beginning of the annealing process.
 
@@
 which has a doubly-degenerate ground state of $(0, 1, 1)$ and $(1, 0, 1)$.
-An annealing offset is then applied to either qubit 0 or 1, and breaks the ground state degeneracy of the system.
+An annealing offset is then applied to either qubit 0 or 1, and thus breaks the ground state degeneracy of the system.
 Because of the systematic error introduced when assigning an offset to a qubit, the final Hamiltonian given by Eq.~(\ref{eq:annealH}) will have small deviations from the input problem Hamiltonian.

### 2020-09-23 paper/main.tex
travis comments

@@
 \affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
-\author{Travis~Humble}
+\author{Travis~S.~Humble}
 \affiliation{Computational Sciences and Engineering, Oak Ridge National Laboratory, Oak Ridge, Tennessee, 37831, USA}
@@
  This work presents the formalism of how to map ILP problems to the annealing architectures, how to systematically improve computations utilizing optimized anneal schedules, and models the anneal process through a simulation.
- It illustrates the effects of decoherence and Many-Body Localization for the Minimum Dominating Set problem, and compares annealing results against numerical simulations of the quantum architecture.
+ It illustrates the effects of decoherence and many body localization for the minimum dominating set problem, and compares annealing results against numerical simulations of the quantum architecture.
  We find that the algorithm outperforms random guessing but is limited to small problems and that annealing schedules can be adjusted to reduce the effects of decoherence.
@@
 
-ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the Minimum Dominating Set Problem (MDS).
+ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the minimum dominating set problem (MDS).
 In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4}.
@@
 
-An important ILP application is the Minimum Dominating Set problem, which is representatively considered in this work.
+An important ILP application is the MDS problem, which is representatively considered in this work.
 For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, a dominating set $D$ is a specific subset of vertices $D \subseteq V$.
@@
 The domination number of $D$ is given by the cardinality of $|D| \equiv \overline{\overline{D}}$.
-The Minimum Dominating Set (MDS) is defined by $D$ with the smallest domination number.
-Fig.~\ref{fig:dominating_sets}c shows an example of the minimum dominating set of $G(V, E)$ and is different from the minimal dominating set.
-We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
+The MDS is defined by $D$ with the smallest domination number.
+Fig.~\ref{fig:dominating_sets}c shows an example of the MDS of $G(V, E)$ and is different from the minimal dominating set.
+We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the MDS, in general, can have a smaller domination number.
 As a result, the solution to the dominating set problem can not be obtained by solving the maximum independent set problem, a well-studied problem for quantum annealers.
@@
 {\textbf{b)}} A minimal dominating set of $G$ with domination number of $\overline{\overline{D}} = 2$.
-{\textbf{c)}} The minimum dominating set of $G$ with domination number of $\overline{\overline{D}} = 1$.}
+{\textbf{c)}} The MDS of $G$ with domination number of $\overline{\overline{D}} = 1$.}
 	\label{fig:dominating_sets}
@@
 In the case of quantum annealing, when an algorithm is mapped to its Ising representation, the values of $h_i$ will frequently take on various values, mimicking spin-glass like behavior.
-More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences Many-Body Localization (MBL) effects, the many-body analog of Anderson Localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001,ALET2018498,PhysRevB.82.174411,PhysRevLett.109.017202}.
+More explicitly, the spin-glass enters a glassy state when more disorder is introduced ($|h_i|$ becomes large), and as a consequence, the wavefunction experiences many body localization (MBL) effects, the many-body analog of Anderson localization~\cite{doi:10.1146/annurev-conmatphys-031214-014726,PhysRevE.90.022103,RevModPhys.91.021001,ALET2018498,PhysRevB.82.174411,PhysRevLett.109.017202}.
 
@@
 
-For the following studies, we perform experiments on the \texttt{DW\_2000Q\_6} solver.
+Due to near-term limitations, hardware realizations of quantum annealing are unique, and possess for example, different lattice layouts (due to faulty qubits), annealing schedules, and qubit fidelity.
+For the following studies, we perform experiments specifically on the \texttt{DW\_2000Q\_6} solver.
 The annealing time is set to 500$\mu$s after performing a study on various annealing times the $G(6)$ graph.
@@
 \end{align}
-where $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
+where $\hbar$ is the reduced Plank's constant, $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
 In this work, we consider two types of decoherence models: full-counting statistics~\cite{PhysRevE.90.022103,RevModPhys.81.1665} and single-qubit amplitude damping (local damping)~\cite{10.5555/1972505,preskill1998lecture}.
@@
 
-The solution to the Minimum Dominating Set problem can be expressed as an integer optimization problem given by,
+The solution to the MDS problem can be expressed as an integer optimization problem given by,
 \begin{align}
@@
 qubits to encode the vertices and slack variables before embedding.
-Therefore, the (logical) qubit vector $\vec \Psi$ at worst scales with $n_V \log_2 n_V$ qubits for fully connected graphs.
+Therefore, the (logical) binary vector $\vec \Psi$ at worst scales with $n_V \log_2 n_V$ qubits for fully connected graphs.
 
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{Integer quadratic optimization}
+\subsubsection{Integer Quadratic Optimization}
 \label{sec:methods:ilp:quadratic}
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{Comment on ILP QUBO penalty term}
+\subsubsection{Comment on ILP QUBO Penalty Term}
 \label{sec:methods:ilp-qubo-comments}
@@
 As a result, details of the embedding are important.
-We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the D-Wave Oceans Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module~\cite{2008arXiv0804.4884C}.
+We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the D-Wave Ocean Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module~\cite{2008arXiv0804.4884C}.
 The same embedding is used for all D-Wave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
@@
 After embedding the QUBO for $G(2)$ requires 5 qubits (an increase from 4), where by construction, qubits 0 and 3 form the qubit chain.
-We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by D-Wave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the minimum dominating set.
+We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by D-Wave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the MDS.
 
@@
 %----------------------------------------------------------------------------------------
-\subsubsection{Annealing schedule and offsets}
+\subsubsection{Annealing Schedule and Offsets}
 \label{sec:methods:annealing-schedule}
@@
 	\includegraphics[width=\columnwidth]{./new_figures/vacuum_probability.pdf}
-	\caption{Time dependent vacuum probability of 5 qubits system under pure transverse field.}
+	\caption{Time-dependent vacuum probability of 5 qubits system under pure transverse field.}
 	\label{figcheck}

### 2020-11-12 paper/v1/main.tex
update title

--- 2020-09-23 paper/main.tex
@@
-%! suppress = LineBreak
-\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography,aps,10pt]{revtex4-2}
+\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography,aps,10pt]{revtex4-1}
+\pdfoutput=1
 \usepackage{CJK}
@@
 \begin{document}
-\title{Integer Programming from Quantum Annealing and Open Quantum Systems}
+\title{Integer Programming with Quantum Annealing from an Open Quantum System}
 
@@
 \affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
-\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
+\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
 \author{Christopher K\"orber}
@@
 
-ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the minimum dominating set problem (MDS).
 In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4}.
 Standard classical heuristic algorithms follow a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
-The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem can be obtained in polynomial time, the optimal integer solution in general must be found in the $2^n$ integer solutions which surround the real number solution.
+The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem must lie on the vertices of the feasibility region, while the optimal integer solution may in general be at any integer solution inside the feasibility region.
 While greedy algorithms do not guarantee optimal global solutions, they find approximate solutions in polynomial time, which can be utilized in further computations.
+ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the minimum dominating set problem (MDS).
+ILP can also be used to identify reaction pathways of biological system, and has recently been explored in the context of quantum annealing~\cite{2020arXiv200713788H}.
 
@@
 	\begin{tabular}{p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
-	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds0.pdf}
+	\includegraphics[width=0.2\textwidth]{./MDS_mds0.pdf}
 &&
-	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds1.pdf}
+	\includegraphics[width=0.2\textwidth]{./MDS_mds1.pdf}
 &&
-	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds2.pdf}\\
+	\includegraphics[width=0.2\textwidth]{./MDS_mds2.pdf}\\
 	\centering\textbf{a} && \centering\textbf{b} && \centering\textbf{c}
@@
 
-We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delay the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}.
+We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delay the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14,2020RPPh...83e4401H}.
 Converting to the Ising representation of the the problem Hamiltonian,
@@
 	$G(n):$ &
-	\raisebox{-.4\height}{\includegraphics[width=0.8\columnwidth]{./new_figures/linear_graph.pdf}}
+	\raisebox{-.4\height}{\includegraphics[width=0.8\columnwidth]{./linear_graph.pdf}}
 	\end{tabular}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/DWave_scaling.pdf}
+	\includegraphics[width=\columnwidth]{./DWave_scaling.pdf}
 	\caption{Baseline result of D-Wave (black) compared to random guessing (dashed green).
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
+	\includegraphics[width=\columnwidth]{./NN2_offset_scaling.pdf}
 	\caption{The probability of finding the MDS for $G(2)$ from D-Wave (black) and simulation (dashed yellow) at annealing times of 1 $\mu s$.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/final_state_distribution.pdf}
+	\includegraphics[width=\columnwidth]{./final_state_distribution.pdf}
 	\caption{Final state distribution from D-Wave (solid bars) and simulation (black outline).
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
+	\includegraphics[width=\columnwidth]{./time_dependent_probability.pdf}
 	\caption{Time-dependent probability for resolving the ground state for simulation results presented in Sec.~\ref{sec:results:simulation}.
@@
 	\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
-	\includegraphics[width=0.5\textwidth]{./new_figures/anneal_schedule_extended.pdf}
+	\includegraphics[width=0.5\textwidth]{./anneal_schedule_extended.pdf}
     &
-	\includegraphics[width=0.5\textwidth]{./new_figures/NN2_offset_scaling_extended.pdf}\\
+	\includegraphics[width=0.5\textwidth]{./NN2_offset_scaling_extended.pdf}\\
 	\centering \textbf{a} & \centering \textbf{b}
@@
  \centering
-  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
+  \includegraphics[width=\columnwidth]{./anneal_schedule.pdf}
   \caption{
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/vacuum_probability.pdf}
+	\includegraphics[width=\columnwidth]{./vacuum_probability.pdf}
 	\caption{Time-dependent vacuum probability of 5 qubits system under pure transverse field.}
@@
 \bibliographystyle{apsrev4-1}
-\bibliography{qilp}
+\bibliography{main.bib}
 %========================================================================================
-
 \end{document}

### 2021-02-02 paper/v2/main.tex
add v2

--- 2020-11-12 paper/v1/main.tex
@@
 The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem must lie on the vertices of the feasibility region, while the optimal integer solution may in general be at any integer solution inside the feasibility region.
-While greedy algorithms do not guarantee optimal global solutions, they find approximate solutions in polynomial time, which can be utilized in further computations.
+While greedy algorithms do not guarantee optimal global solutions, they find feasible solutions in polynomial time, which can be utilized in further computations.
 ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the minimum dominating set problem (MDS).
@@
 \end{align}
-While, in general, the coefficients of the inequality constraints are not required to be integer valued, this real valued inequalities can be trivially rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+While, in general, the coefficients of the inequality constraints are not required to be integer valued, this real valued inequalities can be rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+Current hardware however, offers approximately 10 bits of precision over the control of value of the coupling and biases, limiting the usefulness of rescaling.
+
 Furthermore, this formalism can be generalized to constrained quadratic optimizations \ref{sec:methods:ilp:quadratic}.
@@
 For example, in the case of the MDS, $p\geq 1$ suffices.}.
+The exact value of a sufficiently large penalty coefficient changes the excited-state spectrum of the time-dependent Hamiltonian, and while leaving the ground state unchanged, will impact the performance on quantum annealers due to the limited control over couplings and biases.
+Therefore, choosen the smallest valid penalty coefficient is observed to be optimal for quantum annealers today.
 The objective function $\chi^2$ can be represented as a QUBO Hamiltonian
@@
 %========================================================================================
+\section{CORRESPONDING AUTHOR}
+%========================================================================================
+Correspondence to chiachang@berkeley.edu.
+
+%========================================================================================
 \section{ADDITIONAL INFORMATION}

### 2021-02-04 paper/v2/main.tex
rewrote integer programming paragraph

@@
 \usepackage{enumitem}
-
+\usepackage{soul}
 \usepackage{hyperref}
@@
 
-In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4}.
+While ILP is NP-Hard, extremely large instances of ILP are solved are rutinely solved on a daily basis in a variety of industries such as transportation, energy, and online dating.
+The fact that instances with millions of integer variables can be solved is due to the incredible improvement in classical ILP methods.
+One estimate has that the speed of ILP algorithms, combined with hardware improvements, have lead to a speedup of around 200 billion\cite{bertsimas2014statistics}.
+Despite this fact, there are still very small problems that still require several months, or even years of computational effort to solve.
+For example, the Steiner Triple Covering problems can be notoriously difficult, an instance with only 135 binary variables, \mathtt{STS135}, required over 120 days of computations~\cite{ostrowski2011solving}.
+Another example is the football pool problem, where an instance with only 729 binary variables still remains unsolved after years of computational effort~\cite{linderoth2009improving}.
+In both these cases, the underlying problem is a covering problem.
+
+{\color{red} In general, ILP is classically NP-hard, and as a result, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4}.
 Standard classical heuristic algorithms follow a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
@@
 ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the minimum dominating set problem (MDS).
-ILP can also be used to identify reaction pathways of biological system, and has recently been explored in the context of quantum annealing~\cite{2020arXiv200713788H}.
+ILP can also be used to identify reaction pathways of biological system, and has recently been explored in the context of quantum annealing~\cite{2020arXiv200713788H}.}
 
-An important ILP application is the MDS problem, which is representatively considered in this work.
+In this paper we will consider instances of the minimum dominating set (MDS) problem.
 For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, a dominating set $D$ is a specific subset of vertices $D \subseteq V$.

### 2021-02-11 paper/main.tex

@@
 
-ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the minimum dominating set problem (MDS).
-In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4}.
+While ILP is NP-Hard, extremely large instances of ILP are rutinely solved on a daily basis in a variety of industries such as transportation, energy, online dating, network optimization, graph optimization and has recently been explored in the context of quantum annealing~\cite{2020arXiv200713788H}.
+The fact that instances with millions of integer variables can be solved is due to the incredible improvement in classical ILP methods.
+One estimate has that the speed of ILP algorithms, combined with hardware improvements, have lead to a speedup of around 200 billion\cite{bertsimas2014statistics}.
+Despite this fact, there are still very small problems that still require several months, or even years, of computational effort to solve.
+For example, the Steiner Triple Covering problems can be notoriously difficult; an instance with only 135 binary variables, \texttt{STS135}, required over 120 days of computations~\cite{ostrowski2011solving}.
+Another example is the football pool problem, where an instance with only 729 binary variables still remains unsolved after years of computational effort~\cite{linderoth2009improving}.
+In both these cases, the underlying problem is a covering problem.
+
+In general, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4} to solve ILP problems.
 Standard classical heuristic algorithms follow a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
-The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem can be obtained in polynomial time, the optimal integer solution in general must be found in the $2^n$ integer solutions which surround the real number solution.
-While greedy algorithms do not guarantee optimal global solutions, they find approximate solutions in polynomial time, which can be utilized in further computations.
+While greedy algorithms do not guarantee optimal global solutions, they find feasible solutions in polynomial time, which can be utilized in further computations.
 
-An important ILP application is the MDS problem, which is representatively considered in this work.
+In this paper we will consider instances of the minimum dominating set (MDS) problem.
 For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, a dominating set $D$ is a specific subset of vertices $D \subseteq V$.
@@
 \end{align}
-While, in general, the coefficients of the inequality constraints are not required to be integer valued, this real valued inequalities can be trivially rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+While, in general, the coefficients of the inequality constraints are not required to be integer valued, this real valued inequalities can be rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+Current hardware however, offers approximately 10 bits of precision over the control of value of the coupling and biases, limiting the usefulness of rescaling.
+
 Furthermore, this formalism can be generalized to constrained quadratic optimizations \ref{sec:methods:ilp:quadratic}.
 
-We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delay the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14}.
+We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delay the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14,2020RPPh...83e4401H}.
 Converting to the Ising representation of the the problem Hamiltonian,

### 2021-02-13 paper/main.tex

--- 2020-09-23 paper/main.tex
@@
 \bibliographystyle{apsrev4-1}
-\bibliography{qilp}
+\bibliography{main.bib}
 %========================================================================================

### 2021-03-08 paper/v2/main.tex
Added iop style files and doctored tex + bib to make it compile

@@
-\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography,aps,10pt]{revtex4-1}
+\documentclass[10pt]{iopart}
 \pdfoutput=1
@@
 \usepackage[T1]{fontenc}
+\usepackage{iopams}
+\expandafter\let\csname equation*\endcsname\relax
+\expandafter\let\csname endequation*\endcsname\relax
 \usepackage{amsmath}
@@
 
-\author{Chia~Cheng~Chang}
-\affiliation{RIKEN iTHEMS, Wako, Saitama 351-0198, Japan}
-\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
-\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
-	\author{Chih-Chieh~Chen }
-\affiliation{R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
-\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
-\author{Christopher K\"orber}
-\affiliation{Institut f\"ur Theoretische Physik II, Ruhr-Universit\"at Bochum, D-44780 Bochum, Germany}
-\affiliation{Department of Physics, University of California, Berkeley, California 94720, USA}
-\affiliation{Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
-\author{Travis~S.~Humble}
-\affiliation{Computational Sciences and Engineering, Oak Ridge National Laboratory, Oak Ridge, Tennessee, 37831, USA}
-\author{Jim~Ostrowski}
-\affiliation{Industrial and Systems Engineering, University of Tennessee, Knoxville, Tennessee 37996, USA}
+\author{Chia~Cheng~Chang $^{1, 2, 3}$, Chih-Chieh~Chen$^{4, 3}$, Christopher K\"orber $^{5, 2, 3}$, Travis~S.~Humble $^6$, Jim~Ostrowski $^7$}
+\address{$^1$ RIKEN iTHEMS, Wako, Saitama 351-0198, Japan}
+\address{$^2$ Department of Physics, University of California, Berkeley, California 94720, USA}
+\address{$^3$ Nuclear Science Division, Lawrence Berkeley National Laboratory, Berkeley, California 94720, USA}
+\address{$^4$ R\&D Group, Grid Inc., Tokyo 107-0061, Japan}
+\address{$^5$ Institut f\"ur Theoretische Physik II, Ruhr-Universit\"at Bochum, D-44780 Bochum, Germany}
+\address{$^6$ Computational Sciences and Engineering, Oak Ridge National Laboratory, Oak Ridge, Tennessee, 37831, USA}
+\address{$^7$ Industrial and Systems Engineering, University of Tennessee, Knoxville, Tennessee 37996, USA}
 
@@
 
-\preprint{RIKEN-iTHEMS-Report-20}
+%\preprint{RIKEN-iTHEMS-Report-20}
 
@@
 
-While ILP is NP-Hard, extremely large instances of ILP are solved are rutinely solved on a daily basis in a variety of industries such as transportation, energy, and online dating.
+While ILP is NP-Hard, extremely large instances of ILP are rutinely solved on a daily basis in a variety of industries such as transportation, energy, online dating, network optimization, graph optimization and has recently been explored in the context of quantum annealing~\cite{2020arXiv200713788H}.
 The fact that instances with millions of integer variables can be solved is due to the incredible improvement in classical ILP methods.
 One estimate has that the speed of ILP algorithms, combined with hardware improvements, have lead to a speedup of around 200 billion\cite{bertsimas2014statistics}.
-Despite this fact, there are still very small problems that still require several months, or even years of computational effort to solve.
-For example, the Steiner Triple Covering problems can be notoriously difficult, an instance with only 135 binary variables, \mathtt{STS135}, required over 120 days of computations~\cite{ostrowski2011solving}.
+Despite this fact, there are still very small problems that still require several months, or even years, of computational effort to solve.
+For example, the Steiner Triple Covering problems can be notoriously difficult; an instance with only 135 binary variables, \texttt{STS135}, required over 120 days of computations~\cite{ostrowski2011solving}.
 Another example is the football pool problem, where an instance with only 729 binary variables still remains unsolved after years of computational effort~\cite{linderoth2009improving}.
@@
 
-{\color{red} In general, ILP is classically NP-hard, and as a result, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4}.
+In general, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4} to solve ILP problems.
 Standard classical heuristic algorithms follow a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
-The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem must lie on the vertices of the feasibility region, while the optimal integer solution may in general be at any integer solution inside the feasibility region.
 While greedy algorithms do not guarantee optimal global solutions, they find feasible solutions in polynomial time, which can be utilized in further computations.
-ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the minimum dominating set problem (MDS).
-ILP can also be used to identify reaction pathways of biological system, and has recently been explored in the context of quantum annealing~\cite{2020arXiv200713788H}.}
 
@@
 	\begin{tabular}{p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
-	\includegraphics[width=0.2\textwidth]{./MDS_mds0.pdf}
+	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds0.pdf}
 &&
-	\includegraphics[width=0.2\textwidth]{./MDS_mds1.pdf}
+	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds1.pdf}
 &&
-	\includegraphics[width=0.2\textwidth]{./MDS_mds2.pdf}\\
+	\includegraphics[width=0.2\textwidth]{./new_figures/MDS_mds2.pdf}\\
 	\centering\textbf{a} && \centering\textbf{b} && \centering\textbf{c}
@@
 	$G(n):$ &
-	\raisebox{-.4\height}{\includegraphics[width=0.8\columnwidth]{./linear_graph.pdf}}
+	\raisebox{-.4\height}{\includegraphics[width=0.8\columnwidth]{./new_figures/linear_graph.pdf}}
 	\end{tabular}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./DWave_scaling.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/DWave_scaling.pdf}
 	\caption{Baseline result of D-Wave (black) compared to random guessing (dashed green).
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./NN2_offset_scaling.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/NN2_offset_scaling.pdf}
 	\caption{The probability of finding the MDS for $G(2)$ from D-Wave (black) and simulation (dashed yellow) at annealing times of 1 $\mu s$.}
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./final_state_distribution.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/final_state_distribution.pdf}
 	\caption{Final state distribution from D-Wave (solid bars) and simulation (black outline).
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./time_dependent_probability.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
 	\caption{Time-dependent probability for resolving the ground state for simulation results presented in Sec.~\ref{sec:results:simulation}.
@@
 	\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
-	\includegraphics[width=0.5\textwidth]{./anneal_schedule_extended.pdf}
+	\includegraphics[width=0.5\textwidth]{./new_figures/anneal_schedule_extended.pdf}
     &
-	\includegraphics[width=0.5\textwidth]{./NN2_offset_scaling_extended.pdf}\\
+	\includegraphics[width=0.5\textwidth]{./new_figures/NN2_offset_scaling_extended.pdf}\\
 	\centering \textbf{a} & \centering \textbf{b}
@@
  \centering
-  \includegraphics[width=\columnwidth]{./anneal_schedule.pdf}
+  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
   \caption{
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./vacuum_probability.pdf}
+	\includegraphics[width=\columnwidth]{./new_figures/vacuum_probability.pdf}
 	\caption{Time-dependent vacuum probability of 5 qubits system under pure transverse field.}
@@
 
-\bibliographystyle{apsrev4-1}
+%\bibliographystyle{apsrev4-1}
+\bibliographystyle{iopart-num}
 \bibliography{main.bib}

### 2021-03-08 paper/v2/main.tex
Reshuffled sections
More reshuffling. Need to fixe references

@@
 
-In this work, we present a method to obtain optimal solutions to ILP by employing quantum annealing methods.
-
 Current implementations of quantum annealing solve the quadratic binary optimization problem (QUBO) by slowly varying a time-dependent Hamiltonian~\cite{1998PhRvE..58.5355K, 2000quant.ph..1106F, RevModPhys.80.1061}.
@@
 In practice, and as discussed in Sec.~\ref{sec:methods:lindblad}, modeling dynamics that arise during quantum annealing requires a more robust description of the thermally populated mixed quantum states and the open dynamical processes that govern population of the sought-after eigenstate.
-
-The mapping of ILPs to QUBOs we propose is realized by introducing slack variables $s_a$ which turn the inequalities Eq.~\eqref{eq:ilp-constraints} to equalities
-\begin{align}
-  \label{eq:ilp:slack}
-  & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
-  & x_i, s_a \in \mathbb{Z} \geq 0.
-\end{align}
-While, in general, the coefficients of the inequality constraints are not required to be integer valued, this real valued inequalities can be rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
-Current hardware however, offers approximately 10 bits of precision over the control of value of the coupling and biases, limiting the usefulness of rescaling.
-
-Furthermore, this formalism can be generalized to constrained quadratic optimizations \ref{sec:methods:ilp:quadratic}.
 
@@
 
+\textbf{What do we do and where do you find it...}
+
+We provide access to all the software utilized and data presented in this publication in the associated GitHub repository~\cite{github:cchang5/quantum_linear_programming}.
+The utilized software is contained in two installable Python modules:
+\begin{itemize}[leftmargin=*]
+    \itemsep0em
+    \item[] \texttt{qlp} for mapping MDS problems to QUBOs and performing simulations,
+    \item[] \texttt{qlpdb} for interfacing and documenting simulation and experiment data through EspressoDB~\cite{Chang:2019khk}.
+\end{itemize}
+The data itself is stored in a SQLite file and associated repository subdirectories.
+We provide further documentation in the repository \texttt{readme} file.
+
 %========================================================================================
-\section{RESULTS}
-\label{sec:results}
+\section{METHODS}
+\label{sec:methods}
 %========================================================================================
 
-We first present the QUBO mapping for ILP (\ref{sec:results:qa1}), and demonstrate the methodology on an example implementation in case of the Minimal Dominating Set problem (\ref{sec:results:qa}) on the D-Wave quantum annealer.
-Results from quantum annealing are compared and discussed in contrast to simulations (\ref{sec:results:simulation}).
-
-%----------------------------------------------------------------------------------------
 \subsection{QUBO Formulation of ILP}
@@
 %----------------------------------------------------------------------------------------
+
+The mapping of ILPs to QUBOs we propose is realized by introducing slack variables $s_a$ which turn the inequalities Eq.~\eqref{eq:ilp-constraints} to equalities
+\begin{align}
+  \label{eq:ilp:slack}
+  & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
+  & x_i, s_a \in \mathbb{Z} \geq 0.
+\end{align}
+While, in general, the coefficients of the inequality constraints are not required to be integer valued, this real valued inequalities can be rescaled such that $s_i \in \mathbbm{Z}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
+Current hardware however, offers approximately 10 bits of precision over the control of value of the coupling and biases, limiting the usefulness of rescaling.
+
+Furthermore, this formalism can be generalized to constrained quadratic optimizations \ref{sec:methods:ilp:quadratic}.
+
 Following Eq.~(\ref{eq:ilp:slack}), the ILP problems simplifies to solving a system of linear equations on integer valued variables.
@@
 
+The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:ilp-slack-bit-energy} are exactly the same if the penalty term is greater or equal to the energy gap of the first excited solution: $p \geq E_1 - E_0$.
+Thus some knowledge of the problem is required.
+In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values for $p$ increase the highest available energy of the system by multiples of $p$.
+After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
+Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
+
+Because quantum annealing is capable of solving quadratic problems, the proposed algorithm can be extended to also solve integer quadratic optimization problems as well such that
+\begin{align}
+ \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
+\end{align}
+without the introduction of auxiliary qubits.
+
+In this case the $Q_{xx}$ component of the QUBO, Eq.~\eqref{eq:qubo:components} obtains a new term
+\begin{equation}
+    Q_{xx} \to Q_{xx} + T_x^T d T_x \, .
+\end{equation}
+
 %----------------------------------------------------------------------------------------
-\subsection{Annealer Results for the Dominating Set}
-\label{sec:results:qa}
+\subsection{Minimum Dominating Set QUBO}
+\label{sec:methods:mds-qubo}
 %----------------------------------------------------------------------------------------
+
+The solution to the MDS problem can be expressed as an integer optimization problem given by,
+\begin{align}
+ f(\vec x) = & \min\left(\sum_{v \in V} x_v\right),                    \\
+\end{align}
+subject to
+\begin{align}
+ & x_v + \sum_{j \in \mathcal{N}(v)} x_j \geq 1, \\
+ & x_v \in \{0, 1\}
+\end{align}
+where $\mathcal{N}(v)$ represents the set of all direct neighbors of vertex $v$ and the dimension of the dependent variable $x$ is the number of vertices $n_V \equiv \overline{\overline{V}}$.
+The problem minimizes the number of vertices in $D$ with a binary variable $\vec x = \vec \Psi_x$ encoded by single qubit, subject to the constraint that at least one vertex in $\mathcal{N}(\nu)$ is in $D$.
+For each vertex in $V$ we introduce slack variables
+\begin{equation}
+    \vec s \in \left\{ \mathbb{Z}^{n_V} \, \middle| \, 0 \leq s_{v} \leq |\mathcal{N}(v)| \quad \forall v\in V \right\} \, ,
+\end{equation}
+which is related to the qubit vector $\vec \Psi_s$ by $\vec s = T_s \vec \Psi_s$.
+The inequality constraint is encoded by
+\begin{align}
+ f(\vec \Psi_x)
+ =
+ & \min\left(\vec 1 \cdot \vec \Psi_x \right) \, ,
+\end{align}
+subject to
+\begin{align}
+ &
+ (\mathbbm{1} + J)\vec \Psi_x - T_s \Psi_s  - \vec 1 = 0\,,
+ \\
+ &
+ (\vec \Psi_s)_\nu \in \{ 0, 1\}
+\end{align}
+where the nearest-neighbor sum is expressed by the adjacency matrix $J$ (zero diagonal and symmetric for non-directional graphs).
+The algorithm uses
+\begin{equation}
+    N_q = \overline{\overline{V}} + \sum_{v \in V} \log_2 \mathcal{N}(v)
+\end{equation}
+qubits to encode the vertices and slack variables before embedding.
+Therefore, the (logical) binary vector $\vec \Psi$ at worst scales with $n_V \log_2 n_V$ qubits for fully connected graphs.
+
+The target QUBO in the notation of Eq.~\eqref{eq:matrix_form} reads
+ {\small
+  \begin{align}
+   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - \mathrm{diag}\left(J^T \vec 1 + \vec 1^T J\right) - \mathbbm{1} \right] \,, \\
+   Q_{sx} & = - p(\mathbbm{1}+J)^TT_s\,,                                                                     \\
+   Q_{ss} & = p\left[{T_s}^T T_s + \mathrm{diag}\left(T_s^T \vec 1 + \vec 1^T  T_s\right)\right]\,,                                  \\
+   C      & =  p \overline{\overline{V}}\,.
+  \end{align}}
+
+%==========================================
+\subsection{MDS on the D-Wave}
+\label{sec:methods:MDS-on-D-Wave}
+
 \begin{figure}[b]
@@
 The qubits split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| + \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding.
-Further detail is given in Sec.~\ref{sec:methods:minor_embedding}.
+
+Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
+As a result, details of the embedding are important.
+We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the D-Wave Ocean Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module~\cite{2008arXiv0804.4884C}.
+The same embedding is used for all D-Wave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
+Additionally, solving the same graph as a function of offset on the exact same qubits removes (or at least keeps consistent) the systematic effects due to solving a problem on different physical qubits.
+We note that comparisons between different graphs in Fig.~\ref{fig:baseline} are subject to this uncontrolled systematic.
+
+After embedding the QUBO for $G(2)$ requires 5 qubits (an increase from 4), where by construction, qubits 0 and 3 form the qubit chain.
+We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by D-Wave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the MDS.
+
+The resulting Ising Hamiltonian has external field equal to $h = (2.75, 1.5, -1.0, -1.25, -1.0)$.
+Following the offset strategy described in Sec.~\ref{sec:results:qa}, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
+This imbalance in the two groups may perhaps explain the reason why effects of delaying the weaker fields are more pronounced, since delaying the strong fields only differs from the baseline by a single qubit.
+
+%----------------------------------------------------------------------------------------
+\subsection{Simulation of a Quantum Annealer}
+\label{sec:methods:simulation}
+%----------------------------------------------------------------------------------------
+
+%----------------------------------------------------------------------------------------
+%\subsubsection{The Lindblad Equation}
+%\label{sec:methods:lindblad}
+%----------------------------------------------------------------------------------------
+
+To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
+\begin{align}
+ \label{eq:sim:linblad-eq}
+ \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}(\rho(t), H(t))
+\end{align}
+where $\hbar$ is the reduced Plank's constant, $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
+In this work, we consider two types of decoherence models: full-counting statistics~\cite{PhysRevE.90.022103,RevModPhys.81.1665} and single-qubit amplitude damping (local damping)~\cite{10.5555/1972505,preskill1998lecture}.
+The full-counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
+The local damping term models the decoherence of each qubit independently.
+Details of the master equation are given in Sec.~\ref{sec:methods:lindblad}.
+Implementation of the annealing schedule and annealing offsets for the simulation are discussed in Sec.~\ref{sec:methods:annealing-schedule}.
+
+To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we evaluate the master equation Eq.~\eqref{eq:sim:linblad-eq} in Lindblad form.
+The explicit time-dependence of the Hamiltonian is given by
+\begin{align}
+ \label{eq:annealH}
+ H(t)  = & - \sum_i  A_i(t)\sigma^x_i +\sum_i B_{i}(t) h_i \sigma^z_i \notag \\
+ & + \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j  ,
+\end{align}
+where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
+The site dependency takes into account of the annealing offsets.
+The simulation takes two decoherance models into account.
+Full-counting statistics and local decoherence.
+
+For full-counting statistics, the Lindblad operator is
+\begin{align}
+\mathcal{L}_{\textrm{fc}}(\rho (t), H(t)) = & \Gamma_{\textrm{fc}} \sum_{j, i<j} \left[  \left(2 S_{ij} \rho(t) S_{ij}^\dagger - \{ S^\dagger_{ij} S_{ij}, \rho(t) \}\right) \notag \right.
+\\
+& \left. + e^{-\beta \Delta E_{ij}} \left(2 S_{ij}^\dagger \rho(t) S_{ij} - \{ S_{ij} S^\dagger_{ij}, \rho(t) \} \right)\right]
+\end{align}
+where $\{, \}$ denotes the anti-commutator, $(ij)$ is the index for the inter-level spacing $\Delta E_{ij}=E_j-E_i>0$,  $S_{ij}=|E_i \rangle \langle E_j|$ denotes the many-body lowering operator and $\Gamma_{fc} = 1/T_{fc}$ is the full-counting decoherence rate for coherence time $T_{fc}$.
+That is, due to the interaction with the classical thermal bath, there is a probability that the system hops from each higher-energy many-body state to a lower-energy many-body state.
+The probability of the inverse process is given by a Boltzmann factor.
+
+To model the local decoherence of each qubits in the non-interacting limit, we also consider the amplitude damping for non-interacting qubits.
+For the local decoherance model, the Lindblad operator is
+\begin{align}
+\mathcal{L}_{\textrm{loc}}(\rho (t), H(t)) = &  \Gamma_{\textrm{loc}} \sum_j \left(2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \right)\notag \\
+& + e^{- 2 \beta |h_j| }  \left(2L_j^\dagger \rho(t) L_j - \{ L_j L_j^\dagger, \rho(t) \} \right) ,
+\end{align}
+where $j$ is the index for qubit.
+$L_j= \sigma^{+}_j=|1\rangle \langle 0|$ for $h_j>0$ and $L_j= \sigma^{-}_j=|0\rangle \langle 1|$ for $h_j<0$.
+That is, each qubit is damped toward its local ground state if we ignore all the interactions.
+
+The initial condition is the Gibbs canonical ensemble
+\begin{equation}
+\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}\left(e^{-\beta H(0)}\right)} ,
+\end{equation}
+where $\beta$ is the inverse temperature.
+The probability to get the ground state at measurement is
+\begin{align}
+P =  \mbox{Tr} \left( \rho (t) \pi_{\mbox{gnd}} \right)  ,
+\end{align}
+where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
+Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
+
+For the simulation results presented, we set the temperature to 22.5 milliKelvin.
+The coherence time for local decoherence is set to 15$ns$, and 1$ns$ for full-counting statistics.
+
+%----------------------------------------------------------------------------------------
+%\subsubsection{Annealing Schedule and Offsets}
+%\label{sec:methods:annealing-schedule}
+%----------------------------------------------------------------------------------------
+In this section, we discuss the details of the annealing schedule with respect to the dimensionless normalized time $s$.
+On D-Wave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits (see E.~\eqref{eq:annealH}).
+In Fig.~\ref{fig:anneal_schedule}, the default D-Wave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
+Further documentation is provided by D-Wave in Ref.~\cite{dwave_as, dwave_as_docu}.
+
+\begin{figure}[htb]
+ \centering
+  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
+  \caption{
+  Anneal schedules for amplitudes of initial Hamiltonian (dashed) and final Hamiltonian (solid).
+  Offset 0.0 (black) and -0.05 (purple) are displayed.
+  Intermediate values lie between and are suppressed for clarity.
+ }
+ \label{fig:anneal_schedule}
+\end{figure}
+
+The coefficients $A(s)$ and $B(s)$ follow the underlying control variable $c(s)$, which is designed to grow the persistent current $I_p(s)$ linearly in time.
+The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
+Because annealing schedules are finite, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
+Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
+We only employ negative offsets such that this unkonwn coefficient range, approximated by a linear extrapolation, only enters at the beginning of the annealing process.
+
+We verify that our implementation of annealing offsets on the simulator is consistent with D-Wave by solving the following three qubit Hamiltonian
+\begin{align}
+	\label{eq:offset_test_hamiltonian}
+	H^{\textrm{problem}} =
+	\begin{pmatrix}
+		-0.25 & 1 & 0 \\
+		0 & -0.25 & 0 \\
+		0 & 0 & -0.25
+	\end{pmatrix}
+\end{align}
+which has a doubly-degenerate ground state of $(0, 1, 1)$ and $(1, 0, 1)$.
+An annealing offset is then applied to either qubit 0 or 1, and thus breaks the ground state degeneracy of the system.
+Because of the systematic error introduced when assigning an offset to a qubit, the final Hamiltonian given by Eq.~(\ref{eq:annealH}) will have small deviations from the input problem Hamiltonian.
+For example, we expect a negative offset to qubit 0 to Eq.~(\ref{eq:offset_test_hamiltonian}) will yield $(1, 0, 1)$ as the unique ground state given Eq.~(\ref{eq:annealH}).
+
+We confirm that with different combinations of annealing offsets, the degeneracy is lifted on the D-Wave results as expected by solving for the modified problem Hamiltonian spectrum, as well as dialing in annealing offset in the simulation of this three qubit test case.
+
+%----------------------------------------------------------------------------------------
+%\subsubsection{Pure Transverse Field Simulation}
+%\label{sec:methods:simulation_details}
+%----------------------------------------------------------------------------------------
+To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e. $A(s)=A(0)$ and $B(s)=0$.
+The initial state is pure zero state $\rho=|00...0\rangle \langle 00...0|$.
+In this case the analytical solution can be obtained for the wave function oscillation.
+The time-dependent probability is $P_{0}=\cos^{2n}(s)=\cos^{2n}(t/T)$ where $n$ is the number of qubits and $T$ is the annealing time.
+For annealing time $T=1/A(0)$, we expect to see perfect one-period oscillation.
+The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction.
+The oscillation is depicted in Fig.~\ref{figcheck}, where the simulation matches the expected theoretical behavior.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{./new_figures/vacuum_probability.pdf}
+	\caption{Time-dependent vacuum probability of 5 qubits system under pure transverse field.}
+	\label{figcheck}
+\end{figure}
+
+%========================================================================================
+\section{RESULTS}
+\label{sec:results}
+%========================================================================================
+
 We study the effects of delaying the anneal schedule of one group of qubits over the other and present the results of this study is shown in Fig.~\ref{fig:baseline}.
@@
 
-%----------------------------------------------------------------------------------------
-\subsection{Simulation Results}
-%----------------------------------------------------------------------------------------
-\label{sec:results:simulation}
 To understand the effects of annealing offsets, we simulate the annealing process for the $G(2)$ graph embedded in chimera topography.
@@
 \end{figure}
-
-To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
-\begin{align}
- \label{eq:sim:linblad-eq}
- \partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \mathcal{L}(\rho(t), H(t))
-\end{align}
-where $\hbar$ is the reduced Plank's constant, $\rho (t)$ is the density matrix at time $t$, $H(t)$ is the time-dependent Hamiltonian and $\mathcal{L}$ is the Linblad operator implementing the decoherence models.
-In this work, we consider two types of decoherence models: full-counting statistics~\cite{PhysRevE.90.022103,RevModPhys.81.1665} and single-qubit amplitude damping (local damping)~\cite{10.5555/1972505,preskill1998lecture}.
-The full-counting statistics term models the global decoherence to all the qubits due to the classical reservoir.
-The local damping term models the decoherence of each qubit independently.
-Details of the master equation are given in Sec.~\ref{sec:methods:lindblad}.
-Implementation of the annealing schedule and annealing offsets for the simulation are discussed in Sec.~\ref{sec:methods:annealing-schedule}.
 
@@
 %========================================================================================
-\section{METHODS}
-\label{sec:methods}
-%========================================================================================
-%----------------------------------------------------------------------------------------
-\subsection{Additional Mappings to QUBO}
-\label{sec:methods:ILP-to-QUBO}
-%----------------------------------------------------------------------------------------
-%----------------------------------------------------------------------------------------
-\subsubsection{Minimum Dominating Set QUBO}
-\label{sec:methods:mds-qubo}
-%----------------------------------------------------------------------------------------
-
-The solution to the MDS problem can be expressed as an integer optimization problem given by,
-\begin{align}
- f(\vec x) = & \min\left(\sum_{v \in V} x_v\right),                    \\
-\end{align}
-subject to
-\begin{align}
- & x_v + \sum_{j \in \mathcal{N}(v)} x_j \geq 1, \\
- & x_v \in \{0, 1\}
-\end{align}
-where $\mathcal{N}(v)$ represents the set of all direct neighbors of vertex $v$ and the dimension of the dependent variable $x$ is the number of vertices $n_V \equiv \overline{\overline{V}}$.
-The problem minimizes the number of vertices in $D$ with a binary variable $\vec x = \vec \Psi_x$ encoded by single qubit, subject to the constraint that at least one vertex in $\mathcal{N}(\nu)$ is in $D$.
-For each vertex in $V$ we introduce slack variables
-\begin{equation}
-    \vec s \in \left\{ \mathbb{Z}^{n_V} \, \middle| \, 0 \leq s_{v} \leq |\mathcal{N}(v)| \quad \forall v\in V \right\} \, ,
-\end{equation}
-which is related to the qubit vector $\vec \Psi_s$ by $\vec s = T_s \vec \Psi_s$.
-The inequality constraint is encoded by
-\begin{align}
- f(\vec \Psi_x)
- =
- & \min\left(\vec 1 \cdot \vec \Psi_x \right) \, ,
-\end{align}
-subject to
-\begin{align}
- &
- (\mathbbm{1} + J)\vec \Psi_x - T_s \Psi_s  - \vec 1 = 0\,,
- \\
- &
- (\vec \Psi_s)_\nu \in \{ 0, 1\}
-\end{align}
-where the nearest-neighbor sum is expressed by the adjacency matrix $J$ (zero diagonal and symmetric for non-directional graphs).
-The algorithm uses
-\begin{equation}
-    N_q = \overline{\overline{V}} + \sum_{v \in V} \log_2 \mathcal{N}(v)
-\end{equation}
-qubits to encode the vertices and slack variables before embedding.
-Therefore, the (logical) binary vector $\vec \Psi$ at worst scales with $n_V \log_2 n_V$ qubits for fully connected graphs.
-
-The target QUBO in the notation of Eq.~\eqref{eq:matrix_form} reads
- {\small
-  \begin{align}
-   Q_{xx} & = \mathbbm{1} + p\left[J^T J + J^T + J - \mathrm{diag}\left(J^T \vec 1 + \vec 1^T J\right) - \mathbbm{1} \right] \,, \\
-   Q_{sx} & = - p(\mathbbm{1}+J)^TT_s\,,                                                                     \\
-   Q_{ss} & = p\left[{T_s}^T T_s + \mathrm{diag}\left(T_s^T \vec 1 + \vec 1^T  T_s\right)\right]\,,                                  \\
-   C      & =  p \overline{\overline{V}}\,.
-  \end{align}}
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Integer Quadratic Optimization}
-\label{sec:methods:ilp:quadratic}
-%----------------------------------------------------------------------------------------
-
-Because quantum annealing is capable of solving quadratic problems, we extend the proposed algorithm to solve integer quadratic optimization problems as well such that
-\begin{align}
- \vec x_0 = \mathrm{arg}\min\limits_{x}\left(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i\right)
-\end{align}
-without the introduction of auxiliary qubits.
-
-In this case the $Q_{xx}$ component of the QUBO, Eq.~\eqref{eq:qubo:components} obtains a new term
-\begin{equation}
-    Q_{xx} \to Q_{xx} + T_x^T d T_x \, .
-\end{equation}
-
-%----------------------------------------------------------------------------------------
-\subsection{ILP on the D-Wave}
-\label{sec:methods:ILP-on-D-Wave}
-%----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Comment on ILP QUBO Penalty Term}
-\label{sec:methods:ilp-qubo-comments}
-%----------------------------------------------------------------------------------------
-
-The minimal energy solution to Eq.~\eqref{eq:initial-ip-def} and Eq.~\eqref{eq:ilp-slack-bit-energy} are exactly the same if the penalty term is greater or equal to the energy gap of the first excited solution: $p \geq E_1 - E_0$.
-Thus some knowledge of the problem is required.
-In principle, it is possible to set the penalty term arbitrarily large, at the cost of problem resolution: large values for $p$ increase the highest available energy of the system by multiples of $p$.
-After normalization of the QUBO, this corresponds to decreasing the energy gap between the ground state and the first excited state.
-Thus, if solvers have finite precision, one must estimate reasonable values for $p$: for large $p$ more solutions fulfill the constraints, while for small $p$, more solutions minimize the objective function.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Minor Embedding}
-\label{sec:methods:minor_embedding}
-%----------------------------------------------------------------------------------------
-Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
-As a result, details of the embedding are important.
-We obtain an embedding for $G(n)$ with the \texttt{embed\_qubo} function provided by the D-Wave Ocean Python package~\cite{dwave_oceans} under the \texttt{dwave.embedding} module~\cite{2008arXiv0804.4884C}.
-The same embedding is used for all D-Wave solves of the same graph (independent of offset), and consequently the simulation solves the resulting embedded Hamiltonian for $G(2)$.
-Additionally, solving the same graph as a function of offset on the exact same qubits removes (or at least keeps consistent) the systematic effects due to solving a problem on different physical qubits.
-We note that comparisons between different graphs in Fig.~\ref{fig:baseline} are subject to this uncontrolled systematic.
-
-After embedding the QUBO for $G(2)$ requires 5 qubits (an increase from 4), where by construction, qubits 0 and 3 form the qubit chain.
-We confirm through brute force evaluation of the eigenvalue decomposition of the 5 qubit Hamiltonian, that the embedding provided by D-Wave solves the expected ILP problem for $G(2)$, with degenerate ground states at $(0, 1, 0, 0, 0)$ and $(1, 0, 0, 1, 0)$ corresponding to whether vertex 0 or 1 is chosen for the MDS solution, and $(1, 1, 1, 1, 1)$ as the first (non-degenerate) excited state where both vertex 1 and 0 are in the set yielding a valid dominating set but not the MDS.
-
-The resulting Ising Hamiltonian has external field equal to $h = (2.75, 1.5, -1.0, -1.25, -1.0)$.
-Following the offset strategy described in Sec.~\ref{sec:results:qa}, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
-This imbalance in the two groups may perhaps explain the reason why effects of delaying the weaker fields are more pronounced, since delaying the strong fields only differs from the baseline by a single qubit.
-
-%----------------------------------------------------------------------------------------
-\subsection{Simulation of a Quantum Annealer}
-\label{sec:methods:simulation}
-%----------------------------------------------------------------------------------------
-
-%----------------------------------------------------------------------------------------
-\subsubsection{The Lindblad Equation}
-\label{sec:methods:lindblad}
-%----------------------------------------------------------------------------------------
-
-To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we evaluate the master equation Eq.~\eqref{eq:sim:linblad-eq} in Lindblad form.
-The explicit time-dependence of the Hamiltonian is given by
-\begin{align}
- \label{eq:annealH}
- H(t)  = & - \sum_i  A_i(t)\sigma^x_i +\sum_i B_{i}(t) h_i \sigma^z_i \notag \\
- & + \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j  ,
-\end{align}
-where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions.
-The site dependency takes into account of the annealing offsets.
-The simulation takes two decoherance models into account.
-Full-counting statistics and local decoherence.
-
-For full-counting statistics, the Lindblad operator is
-\begin{align}
-\mathcal{L}_{\textrm{fc}}(\rho (t), H(t)) = & \Gamma_{\textrm{fc}} \sum_{j, i<j} \left[  \left(2 S_{ij} \rho(t) S_{ij}^\dagger - \{ S^\dagger_{ij} S_{ij}, \rho(t) \}\right) \notag \right.
-\\
-& \left. + e^{-\beta \Delta E_{ij}} \left(2 S_{ij}^\dagger \rho(t) S_{ij} - \{ S_{ij} S^\dagger_{ij}, \rho(t) \} \right)\right]
-\end{align}
-where $\{, \}$ denotes the anti-commutator, $(ij)$ is the index for the inter-level spacing $\Delta E_{ij}=E_j-E_i>0$,  $S_{ij}=|E_i \rangle \langle E_j|$ denotes the many-body lowering operator and $\Gamma_{fc} = 1/T_{fc}$ is the full-counting decoherence rate for coherence time $T_{fc}$.
-That is, due to the interaction with the classical thermal bath, there is a probability that the system hops from each higher-energy many-body state to a lower-energy many-body state.
-The probability of the inverse process is given by a Boltzmann factor.
-
-To model the local decoherence of each qubits in the non-interacting limit, we also consider the amplitude damping for non-interacting qubits.
-For the local decoherance model, the Lindblad operator is
-\begin{align}
-\mathcal{L}_{\textrm{loc}}(\rho (t), H(t)) = &  \Gamma_{\textrm{loc}} \sum_j \left(2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \} \right)\notag \\
-& + e^{- 2 \beta |h_j| }  \left(2L_j^\dagger \rho(t) L_j - \{ L_j L_j^\dagger, \rho(t) \} \right) ,
-\end{align}
-where $j$ is the index for qubit.
-$L_j= \sigma^{+}_j=|1\rangle \langle 0|$ for $h_j>0$ and $L_j= \sigma^{-}_j=|0\rangle \langle 1|$ for $h_j<0$.
-That is, each qubit is damped toward its local ground state if we ignore all the interactions.
-
-The initial condition is the Gibbs canonical ensemble
-\begin{equation}
-\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}\left(e^{-\beta H(0)}\right)} ,
-\end{equation}
-where $\beta$ is the inverse temperature.
-The probability to get the ground state at measurement is
-\begin{align}
-P =  \mbox{Tr} \left( \rho (t) \pi_{\mbox{gnd}} \right)  ,
-\end{align}
-where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $.
-Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
-
-For the simulation results presented, we set the temperature to 22.5 milliKelvin.
-The coherence time for local decoherence is set to 15$ns$, and 1$ns$ for full-counting statistics.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Annealing Schedule and Offsets}
-\label{sec:methods:annealing-schedule}
-%----------------------------------------------------------------------------------------
-In this section, we discuss the details of the annealing schedule with respect to the dimensionless normalized time $s$.
-On D-Wave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits (see E.~\eqref{eq:annealH}).
-In Fig.~\ref{fig:anneal_schedule}, the default D-Wave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
-Further documentation is provided by D-Wave in Ref.~\cite{dwave_as, dwave_as_docu}.
-
-\begin{figure}[htb]
- \centering
-  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
-  \caption{
-  Anneal schedules for amplitudes of initial Hamiltonian (dashed) and final Hamiltonian (solid).
-  Offset 0.0 (black) and -0.05 (purple) are displayed.
-  Intermediate values lie between and are suppressed for clarity.
- }
- \label{fig:anneal_schedule}
-\end{figure}
-
-The coefficients $A(s)$ and $B(s)$ follow the underlying control variable $c(s)$, which is designed to grow the persistent current $I_p(s)$ linearly in time.
-The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
-Because annealing schedules are finite, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
-Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
-We only employ negative offsets such that this unkonwn coefficient range, approximated by a linear extrapolation, only enters at the beginning of the annealing process.
-
-We verify that our implementation of annealing offsets on the simulator is consistent with D-Wave by solving the following three qubit Hamiltonian
-\begin{align}
-	\label{eq:offset_test_hamiltonian}
-	H^{\textrm{problem}} =
-	\begin{pmatrix}
-		-0.25 & 1 & 0 \\
-		0 & -0.25 & 0 \\
-		0 & 0 & -0.25
-	\end{pmatrix}
-\end{align}
-which has a doubly-degenerate ground state of $(0, 1, 1)$ and $(1, 0, 1)$.
-An annealing offset is then applied to either qubit 0 or 1, and thus breaks the ground state degeneracy of the system.
-Because of the systematic error introduced when assigning an offset to a qubit, the final Hamiltonian given by Eq.~(\ref{eq:annealH}) will have small deviations from the input problem Hamiltonian.
-For example, we expect a negative offset to qubit 0 to Eq.~(\ref{eq:offset_test_hamiltonian}) will yield $(1, 0, 1)$ as the unique ground state given Eq.~(\ref{eq:annealH}).
-
-We confirm that with different combinations of annealing offsets, the degeneracy is lifted on the D-Wave results as expected by solving for the modified problem Hamiltonian spectrum, as well as dialing in annealing offset in the simulation of this three qubit test case.
-
-%----------------------------------------------------------------------------------------
-\subsubsection{Pure Transverse Field Simulation}
-\label{sec:methods:simulation_details}
-%----------------------------------------------------------------------------------------
-To check the correctness of simulator and unit conversion, we tested a simple annealing schedule for pure transverse field, i.e. $A(s)=A(0)$ and $B(s)=0$.
-The initial state is pure zero state $\rho=|00...0\rangle \langle 00...0|$.
-In this case the analytical solution can be obtained for the wave function oscillation.
-The time-dependent probability is $P_{0}=\cos^{2n}(s)=\cos^{2n}(t/T)$ where $n$ is the number of qubits and $T$ is the annealing time.
-For annealing time $T=1/A(0)$, we expect to see perfect one-period oscillation.
-The energy spectrum for this system can be analytically obtained, so we also checked the Boltzmann distribution in the initial density matrix construction.
-The oscillation is depicted in Fig.~\ref{figcheck}, where the simulation matches the expected theoretical behavior.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{./new_figures/vacuum_probability.pdf}
-	\caption{Time-dependent vacuum probability of 5 qubits system under pure transverse field.}
-	\label{figcheck}
-\end{figure}
-
-%========================================================================================
-\section{DATA AVAILABILITY}
-\label{sec:open-source}
-%========================================================================================
-We provide access to all the software utilized and data presented in this publication in the associated GitHub repository~\cite{github:cchang5/quantum_linear_programming}.
-The utilized software is contained in two installable Python modules:
-\begin{itemize}[leftmargin=*]
-    \itemsep0em
-    \item[] \texttt{qlp} for mapping MDS problems to QUBOs and performing simulations,
-    \item[] \texttt{qlpdb} for interfacing and documenting simulation and experiment data through EspressoDB~\cite{Chang:2019khk}.
-\end{itemize}
-The data itself is stored in a SQLite file and associated repository subdirectories.
-We provide further documentation in the repository \texttt{readme} file.
-
-%========================================================================================
 \section{ACKNOWLEDGEMENTS}
@@
 
+% %========================================================================================
+% \section{AUTHOR CONTRIBUTIONS}
+% %========================================================================================
+%
+% Initial idea was proposed by Chang.
+% Ostrowski guided the ILP problem selection.
+% All authors contributed to the design of test cases.
+% Calculations and code development for the D-Wave were performed by Chang and K\"orber.
+% Code for numerical simulations was developed by Chen and K\"orber, and cross-checked by Chang.
+% Simulations were performed by Chang and Chen.
+% Chang, Chen, K\"orber, and Humble interpreted the results.
+% All authors contributed to writing and editing of the final manuscript.
+%
+% %========================================================================================
+% \section{CORRESPONDING AUTHOR}
+% %========================================================================================
+% Correspondence to chiachang@berkeley.edu.
+%
+% %========================================================================================
+% \section{ADDITIONAL INFORMATION}
+% %========================================================================================
+%
+% \textbf{Competing Interests:} The authors declare no competing interests.
+
+%\bibliographystyle{apsrev4-1}
+
 %========================================================================================
-\section{AUTHOR CONTRIBUTIONS}
+\section{Bibliography}
 %========================================================================================
 
-Initial idea was proposed by Chang.
-Ostrowski guided the ILP problem selection.
-All authors contributed to the design of test cases.
-Calculations and code development for the D-Wave were performed by Chang and K\"orber.
-Code for numerical simulations was developed by Chen and K\"orber, and cross-checked by Chang.
-Simulations were performed by Chang and Chen.
-Chang, Chen, K\"orber, and Humble interpreted the results.
-All authors contributed to writing and editing of the final manuscript.
+\bibliographystyle{iopart-num}
+\bibliography{main.bib}
 
 %========================================================================================
-\section{CORRESPONDING AUTHOR}
+\appendix
+\section{Appendix}
 %========================================================================================
-Correspondence to chiachang@berkeley.edu.
 
 %========================================================================================
-\section{ADDITIONAL INFORMATION}
-%========================================================================================
-
-\textbf{Competing Interests:} The authors declare no competing interests.
-
-%\bibliographystyle{apsrev4-1}
-\bibliographystyle{iopart-num}
-\bibliography{main.bib}
-%========================================================================================
 \end{document}

### 2021-03-08 paper/v2/main.tex
Minor edits

@@
 
-While ILP is NP-Hard, extremely large instances of ILP are rutinely solved on a daily basis in a variety of industries such as transportation, energy, online dating, network optimization, graph optimization and has recently been explored in the context of quantum annealing~\cite{2020arXiv200713788H}.
+While ILP is NP-Hard, extremely large instances of ILP are solved on a daily basis in a variety of industries such as transportation, energy, online dating, network optimization, graph optimization and has recently been explored in the context of quantum annealing~\cite{2020arXiv200713788H}.
 The fact that instances with millions of integer variables can be solved is due to the incredible improvement in classical ILP methods.
-One estimate has that the speed of ILP algorithms, combined with hardware improvements, have lead to a speedup of around 200 billion\cite{bertsimas2014statistics}.
-Despite this fact, there are still very small problems that still require several months, or even years, of computational effort to solve.
+One estimate has that the speed of ILP algorithms, combined with hardware improvements, have lead to a speedup of around 200 billion~\cite{bertsimas2014statistics}.
+Despite this fact, there are still very small problems that require several months, or even years, of computational effort to solve.
 For example, the Steiner Triple Covering problems can be notoriously difficult; an instance with only 135 binary variables, \texttt{STS135}, required over 120 days of computations~\cite{ostrowski2011solving}.
@@
 
-In this paper we will consider instances of the minimum dominating set (MDS) problem.
+In this paper we will consider instances of an particular ILP problem: the minimum dominating set (MDS) problem.
 For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, a dominating set $D$ is a specific subset of vertices $D \subseteq V$.

### 2021-03-08 paper/v2/main.tex
linting

@@
 \documentclass[10pt]{iopart}
-\pdfoutput=1
+%\pdfoutput=1
 \usepackage{CJK}
@@
 Standard classical heuristic algorithms follow a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
-While greedy algorithms do not guarantee optimal global solutions, they find feasible solutions in polynomial time, which can be utilized in further computations.
+While greedy algorithms do not guarantee optimal global solutions, they find feasible solutions--satisfying all constraints--in polynomial time, which can be utilized in further computations.
 
@@
 
-For general graphs, existing algorithms on classical computers find MDS solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or approximate solutions in polynomial time.
+For general graphs, existing algorithms on classical computers find MDS solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or feasible solutions in polynomial time.
 For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
@@
 and $H^\textrm{init}=-\sum_i\sigma^x_i$ (on the D-Wave), while $H^\textrm{problem}$ encodes the problem to be solved.
-In practice, and as discussed in Sec.~\ref{sec:methods:lindblad}, modeling dynamics that arise during quantum annealing requires a more robust description of the thermally populated mixed quantum states and the open dynamical processes that govern population of the sought-after eigenstate.
-
-We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delay the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14,2020RPPh...83e4401H}.
+In practice, modeling dynamics that arise during quantum annealing requires a more robust description of the thermally populated mixed quantum states and the open dynamical processes that govern population of the sought-after eigenstate.
 Converting to the Ising representation of the the problem Hamiltonian,
@@
 
+In this paper, we present the mapping of ILPs to QUBOs and solve specific realizations, MDS problems for specific graphs, on a quantum annealer.
+We improve the quantum annealer's performance by utilizing annealing offsets, which effectively delay the annealing schedule on a per-qubit basis~\cite{PhysRevA.96.042322,hsu2018quantum,10.1007/978-3-030-14082-3_14,2020RPPh...83e4401H}.
 Our improvement strategy is motivated by the MBL hypothesis.
@@
 
-\textbf{What do we do and where do you find it...}
-
-We provide access to all the software utilized and data presented in this publication in the associated GitHub repository~\cite{github:cchang5/quantum_linear_programming}.
-The utilized software is contained in two installable Python modules:
-\begin{itemize}[leftmargin=*]
-    \itemsep0em
-    \item[] \texttt{qlp} for mapping MDS problems to QUBOs and performing simulations,
-    \item[] \texttt{qlpdb} for interfacing and documenting simulation and experiment data through EspressoDB~\cite{Chang:2019khk}.
-\end{itemize}
-The data itself is stored in a SQLite file and associated repository subdirectories.
-We provide further documentation in the repository \texttt{readme} file.
+In Sec.~\ref{sec:methods}, we display how a general ILP is mapped onto QUBOs (Sec.~\ref{sec:results:qa1}), provide an explicit example in case of the MDS problem (Sec.~\ref{sec:methods:mds-qubo}), specify how the QUBO is embedded on the annealer (Sec.~\ref{sec:methods:MDS-on-D-Wave}), how the annealing schedules are realized (Sec.~\ref{sec:methods:anneal-schedule}), and how we have simulated the annealer (Sec.~\ref{sec:methods:simulation}).
+In Sec.~\ref{sec:results} we present our results and discuss them in Sec.~\ref{sec:discussion}.
+All data and software utilized in this paper can be found online (see also Sec.~\ref{sec:data}).
 
@@
 Current hardware however, offers approximately 10 bits of precision over the control of value of the coupling and biases, limiting the usefulness of rescaling.
-
-Furthermore, this formalism can be generalized to constrained quadratic optimizations \ref{sec:methods:ilp:quadratic}.
 
@@
 In particular, the number of qubits required to solve MDS scales at worse as $n_V \log_2 n_V$ where $n_V$ is the number of vertices for a generic graph before minor embedding.
-Details of the mapping of ILP to MDS is given in Sec.~\ref{sec:methods:mds-qubo}.
 
@@
 
-Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
 As a result, details of the embedding are important.
@@
 The resulting Ising Hamiltonian has external field equal to $h = (2.75, 1.5, -1.0, -1.25, -1.0)$.
-Following the offset strategy described in Sec.~\ref{sec:results:qa}, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
+Following the MBL inspired offset strategy, qubit(s) 0 (1, 2, 3, 4) are placed in the set with relatively stronger (weaker) final external fields.
 This imbalance in the two groups may perhaps explain the reason why effects of delaying the weaker fields are more pronounced, since delaying the strong fields only differs from the baseline by a single qubit.
+
+%----------------------------------------------------------------------------------------
+\subsection{Annealing schedules}
+\label{sec:methods:anneal-schedule}
+%----------------------------------------------------------------------------------------
+
+Our proposed offset strategy is motivated by the structure of the Hamiltonian being evaluated by the annealer.
+On D-Wave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits.
+In Fig.~\ref{fig:anneal_schedule}, the default D-Wave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
+Further documentation is provided by D-Wave in Ref.~\cite{dwave_as, dwave_as_docu}.
+
+\begin{figure}[htb]
+ \centering
+  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
+  \caption{
+  Anneal schedules for amplitudes of initial Hamiltonian (dashed) and final Hamiltonian (solid).
+  Offset 0.0 (black) and -0.05 (purple) are displayed.
+  Intermediate values lie between and are suppressed for clarity.
+ }
+ \label{fig:anneal_schedule}
+\end{figure}
+
+The coefficients $A(s)$ and $B(s)$ follow the underlying control variable $c(s)$, which is designed to grow the persistent current $I_p(s)$ linearly in time.
+The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
+Because annealing schedules are finite, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
+Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
+We only employ negative offsets such that this unkonwn coefficient range, approximated by a linear extrapolation, only enters at the beginning of the annealing process.
 
@@
 The local damping term models the decoherence of each qubit independently.
-Details of the master equation are given in Sec.~\ref{sec:methods:lindblad}.
-Implementation of the annealing schedule and annealing offsets for the simulation are discussed in Sec.~\ref{sec:methods:annealing-schedule}.
 
@@
 %----------------------------------------------------------------------------------------
-In this section, we discuss the details of the annealing schedule with respect to the dimensionless normalized time $s$.
-On D-Wave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits (see E.~\eqref{eq:annealH}).
-In Fig.~\ref{fig:anneal_schedule}, the default D-Wave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
-Further documentation is provided by D-Wave in Ref.~\cite{dwave_as, dwave_as_docu}.
-
-\begin{figure}[htb]
- \centering
-  \includegraphics[width=\columnwidth]{./new_figures/anneal_schedule.pdf}
-  \caption{
-  Anneal schedules for amplitudes of initial Hamiltonian (dashed) and final Hamiltonian (solid).
-  Offset 0.0 (black) and -0.05 (purple) are displayed.
-  Intermediate values lie between and are suppressed for clarity.
- }
- \label{fig:anneal_schedule}
-\end{figure}
-
-The coefficients $A(s)$ and $B(s)$ follow the underlying control variable $c(s)$, which is designed to grow the persistent current $I_p(s)$ linearly in time.
-The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
-Because annealing schedules are finite, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
-Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
-We only employ negative offsets such that this unkonwn coefficient range, approximated by a linear extrapolation, only enters at the beginning of the annealing process.
+%In this section, we discuss the details of the annealing schedule with respect to the dimensionless normalized time $s$.
 
@@
 \section{Discussion}
+\label{sec:discussion}
+
 \subsection{Dynamics of Time Evolution}
@@
 	\includegraphics[width=\columnwidth]{./new_figures/time_dependent_probability.pdf}
-	\caption{Time-dependent probability for resolving the ground state for simulation results presented in Sec.~\ref{sec:results:simulation}.
+	\caption{Time-dependent probability for resolving the ground state for simulation results presented in Sec.~\ref{sec:methods:simulation}.
 Different offsets are labeled in the same way as Fig.~\ref{fig:baseline}.}
@@
 %========================================================================================
+\section{Data availability}
+\label{sec:data}
+%========================================================================================
+
+We provide access to all the software utilized and data presented in this publication in the associated GitHub repository~\cite{github:cchang5/quantum_linear_programming}.
+The utilized software is contained in two installable Python modules:
+\begin{itemize}[leftmargin=*]
+    \itemsep0em
+    \item[] \texttt{qlp} for mapping MDS problems to QUBOs and performing simulations,
+    \item[] \texttt{qlpdb} for interfacing and documenting simulation and experiment data through EspressoDB~\cite{Chang:2019khk}.
+\end{itemize}
+The data itself is stored in a SQLite file and associated repository subdirectories.
+We provide further documentation in the repository \texttt{readme} file.
+
+%========================================================================================
 \end{document}

### 2021-03-15 paper/v2/main.tex
change title, remove heuristics paragraph (jims comment), and update abstract slightly

@@
 \begin{document}
-\title{Integer Programming with Quantum Annealing from an Open Quantum System}
+\title[QA and Open Quantum Systems for MDS]{A Study of Quantum Annealing and Open Quantum Systems for the Minimum Dominating Set}
 
@@
  To practically benefit from quantum architecture, one has to identify problems and algorithms with favorable scaling and improve on corresponding limitations depending on available hardware.
- For this reason, we developed an algorithm that solves integer linear programming problems, a classically NP-hard problem, on a quantum annealer, and investigated problem and hardware-specific limitations.
+ For this reason, we developed an algorithm that solves integer linear programming problems and its application to the minimum dominating set, a classically NP-hard problem, on a quantum annealer, and investigated problem and hardware-specific limitations.
  This work presents the formalism of how to map ILP problems to the annealing architectures, how to systematically improve computations utilizing optimized anneal schedules, and models the anneal process through a simulation.
@@
 In both these cases, the underlying problem is a covering problem.
-
-In general, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4} to solve ILP problems.
-Standard classical heuristic algorithms follow a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
-While greedy algorithms do not guarantee optimal global solutions, they find feasible solutions--satisfying all constraints--in polynomial time, which can be utilized in further computations.
 
